---
title: "KSR_2020"
author: "Sophie Breitbart"
output:
  html_document:
    number_sections: true
    df_print: paged
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
editor_options: 
  chunk_output_type: console

---
# Set up notebook
## Load packages
```{r}
library(dplyr)
library(reshape)
library(reshape2)
library(tidyr)
library(ggplot2)
library(ggExtra)
library("ggpubr")
library(devtools)
library(rpart)
library("tibble", lib.loc="~/R/win-library/3.5")
library(ISLR)
library(MASS)
library(car)
library(data.table)
library(plyr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(Hmisc)
library(lme4)
library(nlme)
library(reshape)
library(lmerTest)
library(tidyverse)
library(vegan)
library(lindia)
library(e1071)
library(ggpubr)
library(forcats)
library(car)
library(multcomp)
library(lsmeans)
library(ggbiplot)
library(ggplot2)
require(MASS)
require(scales)
require(car)
require(ggplot2)
require(ggiraph)
require(ggiraphExtra)
library(geosphere)
library(vctrs)
library(here)
```

## Add functions
```{r}
diagnostic<-function(x){
  plot(x)
  hist(x)
  qqnorm(x)
  qqline(x,lty=2, col="Red")

  skew<-function(x){
    m3<-sum((x-mean(x))^3)/length(x)
    s3<-sqrt(var(x))^3
    m3/s3}

  kurtosis<-function(x){
    m4<-sum((x-mean(x))^4)/length(x)
    s4<-var(x)^2
    m4/s4-3}

  print(paste("Kurtosis=", kurtosis(x), sep=""))
  print(paste("Skew=", skew(x), sep=""))
}

# diagnostic(x)
```

## Import KSR field data
```{r, import}
# 2019 data-----
data_clean_2019 <- read.csv(here("./CommonGardenExperiment_2019Data/clean_data/clean_data_2019KSR.csv"), na.strings=c("NO PLANT", "none"), blank.lines.skip=TRUE, header=TRUE, sep=",")

# 2020 data-----
heights_both <- read.csv(here("./CommonGardenExperiment_2020Data/clean_data/2020_heights_clean.csv")) %>%
  dplyr::select(., -1)

herbivory_both <- read.csv(here("./CommonGardenExperiment_2020Data/clean_data/2020_herbivory_clean.csv")) %>%
  dplyr::select(., -1)

survival <- read.csv(here("./CommonGardenExperiment_2020Data/clean_data/2020_survival_clean.csv")) %>%
  dplyr::select(., -1)

weevil_both <- read.csv(here("./CommonGardenExperiment_2020Data/clean_data/2020_weevil_damage_clean.csv")) %>%
  dplyr::select(., -1)

herbivores <- read.csv(here("./CommonGardenExperiment_2020Data/clean_data/2020_insect_herbivores_clean.csv")) %>%
  dplyr::select(., -1)

reproductive <- read.csv(here("./CommonGardenExperiment_2020Data/clean_data/2020_reproductive_clean.csv")) %>%
  dplyr::select(., -1)

flowering_2020 <- read.csv(here("./CommonGardenExperiment_2020Data/clean_data/2020_floweringplants_clean.csv")) %>%
  dplyr::select(., -1)

```

# Clean data
## survival
### Find which plants had grown at season start --> make new survival_both df
Isn't a foolproof method for assessing overwinter mortality, but will tell which plants had no visible growth during first data collection in June
```{r}
# Make new column signifying if pots contained zero alive plants, or at least one- 0 or 1
## First, copy first height column associaed with first ramet (if 0, that means pot was empty/had no alive ramets)

survival_overwinter <- heights_both[,c(1:10)]
survival_overwinter$Mortality_binary <- survival_overwinter$Total_Height_June

## Now change all instances of >0 to 1. If >=0, then at least one ramet present.
survival_overwinter <- survival_overwinter %>%
  mutate(., Mortality_binary = ifelse((Mortality_binary == 0 & Ramets_June < 1), "1", "0"))

### make new binary mortality column factor
survival_overwinter$Mortality_binary <- as.factor(survival_overwinter$Mortality_binary)

# check appropriate columns are factors
str(survival_overwinter)


# extract mortality column from survival_overwinter df and add to survival df
survival_both <- left_join(survival, survival_overwinter, by = c("Row", "Column", "Block", "Population", "Family", "Replicate"))
# rename cols
survival_both <- dplyr::rename(survival_both, Dead_Sept = Dead)
survival_both <- dplyr::rename(survival_both, Dead_June = Mortality_binary)
survival_both <- dplyr::rename(survival_both, Comment_Sept = Comment)
# get rid of date columns & June height and # ramets cols
survival_both <- survival_both[,-c(8, 11:13)]
# reorder cols
survival_both <- survival_both[, c(1:6, 10,9,8,7)]
```

### find plants deemed dead during both data collection assessments and years
```{r}
# these plants were DEAD for all data collections in 2020
dead_2020 <- survival_both %>% filter(., Dead_June == 1 & Dead_Sept == 1)

# shows which plants were dead or alive throughout all data collections in 2020
survival_both <- transform(survival_both, dead_2020 = ifelse(Dead_June == 1 & Dead_Sept == 1, 1,0))

# these plants were dead for all data collections in 2019
dead_2019 <- data_clean_2019 %>% filter(., (Dead_DC1 == 'yes' | Dead_DC1 == 'maybe' | Dead_DC1 == 'nothing there') & Dead_DC2 == 1 & Dead_DC3 == 1)

# these plants were dead either throughout 2019 OR 2020
dead_either_2019or2020_fullyear <- full_join(dead_2019[,c(1:6, 9:11)], dead_2020, by = c("Row", "Column", "Block", "Population", "Family", "Replicate"))

# these plants were dead throughout 2019 AND 2020
# # THESE ARE THE PLANTS THAT HAVE BEEN DEAD FROM THE START, PRESUMABLY
dead_bothyears <- inner_join(dead_2019[,c(1:6, 9:11)], dead_2020[,c(1:7,9)],  by = c("Row", "Column", "Block", "Population", "Family", "Replicate")) 

# new df to see which plants I thought were dead in 2019 but really weren't in 2020
# SO: should be in dead2019 but NOT in dead2020
zombies <- anti_join(dead_2019, dead_2020, by = c("Row", "Column"))

```

### Remove plants that were dead since early 2019 from ALL dfs
```{r}
# remove dead_bothyears plants from 2020 dataset
heights_both <- anti_join(heights_both, dead_bothyears, by = c("Row", "Column"))
herbivory_both <- anti_join(herbivory_both, dead_bothyears, by = c("Row", "Column"))
survival_2020 <- anti_join(survival_both, dead_bothyears, by = c("Row", "Column"))
weevil_both <- anti_join(weevil_both, dead_bothyears, by = c("Row", "Column"))
herbivores <- anti_join(herbivores, dead_bothyears, by = c("Row", "Column"))
reproductive <- anti_join(reproductive, dead_bothyears, by = c("Row", "Column"))
```

## heights: Calculate relative growth rate
```{r}

# some plants had heights of 0 in June, Sept, or both:
## If they were 0 in June but >0 in September: June = 1, since ln(1)=0.
# If they were >0 in June but 0 in September: Sept = 1.
# If June = 0 and Sept = 0, it will be NA.
heights_both <- heights_both %>% dplyr::mutate(.,
                              rel_growth_rate = case_when(
                                Total_Height_June > 0 & Total_Height_Sept > 0 ~ (log(Total_Height_Sept) - log(Total_Height_June))/ date_diff,
                                Total_Height_June > 0 & Total_Height_Sept == 0  ~ (1 - log(Total_Height_June)) / date_diff,
                                Total_Height_June == 0 & Total_Height_Sept > 0  ~ (log(Total_Height_Sept) - 1) / date_diff))


```
## weevil damage: standardize weevil scar length by total height
```{r}
# add June height so I can standardize weevil scar length by total height
weevil_both <- weevil_both %>%
  left_join(., heights_both[,-c(7, 9:15)], by = c("Row", "Column", "Block", "Population", "Family", "Replicate")) %>%
  mutate(Scar_length_cm = Scar_length_mm / 10) %>%
  
# standardize weevil scar length by total height
## value may be over 1 because 1) oftentimes there were multiple scars per ramet on different sides, and 2) height was measured in June and scars in July, so the plants were likely taller when scars were measured
  mutate(scar_div_Juneheight = Scar_length_cm / (Total_Height_June)) %>%
  dplyr::select(., -Scar_length_mm)

```

## herbivory: calculate average herbivory
```{r}
# Clean columns to get average herbivory
# JULY------
### Replace non-numeric entries with NA and remove dashes (which symbolize no leaf) 
herbivory_both$Herbivory.July_mean <- herbivory_both$Herbivory.July

herbivory_both$Herbivory.July_mean <- gsub('too small', NA, herbivory_both$Herbivory.July_mean)

# converts plants we weren't able to assess to NA (from 0)- represents either a lack of plant or no leaves
herbivory_both <- herbivory_both %>%
    mutate(Herbivory.July_mean = na_if(Herbivory.July_mean, "0"))

herbivory_both$Herbivory.July_mean <- gsub('-', "", herbivory_both$Herbivory.July_mean)

herbivory_both$Herbivory.July_mean <- gsub(' ', "", herbivory_both$Herbivory.July_mean)


library(stringi)
### Calculate mean herbivory for ramet 1 in new column
herbivory_both$Herbivory.July_mean <- sapply(strsplit(as.character(herbivory_both$Herbivory.July_mean), ",", fixed=T), function(x) mean(as.numeric(x)))

# SEPT------
### Replace non-numeric entries with NA and remove dashes (which symbolize no leaf) 
herbivory_both$Herbivory.Sept_mean <- herbivory_both$Herbivory.Sept

herbivory_both$Herbivory.Sept_mean <- gsub('too small', NA, herbivory_both$Herbivory.Sept_mean)

# converts plants we weren't able to assess to NA (from 0)- represents either a lack of plant or no leaves
herbivory_both <- herbivory_both %>%
    mutate(Herbivory.Sept_mean = na_if(Herbivory.Sept_mean, "0"))

herbivory_both$Herbivory.Sept_mean <- gsub('-', "", herbivory_both$Herbivory.Sept_mean)

herbivory_both$Herbivory.Sept_mean <- gsub(' ', "", herbivory_both$Herbivory.Sept_mean)


library(stringi)
### Calculate mean herbivory for ramet 1 in new column
herbivory_both$Herbivory.Sept_mean <- sapply(strsplit(as.character(herbivory_both$Herbivory.Sept_mean), ",", fixed=T), function(x) mean(as.numeric(x)))
```

## Add transect data (e.g. city_dist values)
### Add City_dist values with Haversine formula
```{r}
# import data
Distances <- read.csv(here("./CommonGardenExperiment_2019Data/raw_data/Transect_Milkweed_HaversineData_forjoining.csv"), na.strings=c("NO PLANT", "none"), blank.lines.skip=TRUE, header=TRUE, sep=",")

# Ref lat and longs are for Yonge & Dundas intersection in downtown Toronto
Distances$Ref_Lat <- "43.656327"
Distances$Ref_Long <- "-79.380904"

# Make lat/long cols numeric
Distances$Latitude <- as.numeric(as.character(Distances$Latitude))
Distances$Longitude <- as.numeric(as.character(Distances$Longitude))
Distances$Ref_Lat <- as.numeric(as.character(Distances$Ref_Lat))
Distances$Ref_Long <- as.numeric(as.character(Distances$Ref_Long))

# Find distances from Yonge/Dundas to sample sites (in meters)
Distances <- Distances %>% mutate(CTD_m = distHaversine(cbind(Longitude, Latitude), cbind(Ref_Long, Ref_Lat)))

# conver to km
Distances$City_dist <- Distances$CTD / 1000

# drop ref lat, long, and city_dist (in m) cols
Distances <- Distances[,-c(7:9)]

```

### Add transect data to all dfs via merge
```{r}
# TRIED TO AUTOMATE WITH LAPPLY AND PURRR BUT NOT WORKING YET
# # make list of dfs
# df.list <- list(heights_both,
#                 herbivory_both,
#                 survival_2020,
#                 weevil_both,
#                 herbivores,
#                 reproductive,
#                 flowering_2020)
# 
# # Add distances to city center
# df.list <- lapply(df.list, function(x)
#   x <- merge(x, y = Distances, by = "Population", all.x = TRUE))

# doing it manually
heights_both <- merge(heights_both, y = Distances, by = "Population", all.x = TRUE)
herbivory_both <- merge(herbivory_both, y = Distances, by = "Population", all.x = TRUE)
survival_2020 <- merge(survival_2020, y = Distances, by = "Population", all.x = TRUE)
weevil_both <- merge(weevil_both, y = Distances, by = "Population", all.x = TRUE)
herbivores <- merge(herbivores, y = Distances, by = "Population", all.x = TRUE)
reproductive <- merge(reproductive, y = Distances, by = "Population", all.x = TRUE)
flowering_2020 <- merge(flowering_2020, y = Distances, by = "Population", all.x = TRUE)


# recode North & South as urban (CAN'T MAKE THIS WORK SO DOING IT MANUALLY)
# df.list <- purrr::lmap(df.list, function(x) 
#   x$Urb_Rur <- x$Transect_ID %>%
#     dplyr::mutate(Urb_Rur = dplyr::recode(Urb_Rur,
#                                           'North' = "Urban",
#                                           'South' = "Urban",
#                                           'Rural' = "Rural")))
#                                           
# lapply(df.list, function(x)
# dplyr::mutate(Urb_Rur = Transect_ID) %>%
# dplyr::mutate(Urb_Rur = dplyr::recode(Urb_Rur,
#                                       'North' = "Urban",
#                                       'South' = "Urban",
#                                       'Rural' = "Rural")))


heights_both <- heights_both %>% 
  dplyr::mutate(Urb_Rur = Transect_ID) %>%
  dplyr::mutate(Urb_Rur = dplyr::recode(Urb_Rur,
                                        'North' = "Urban",
                                        'South' = "Urban",
                                        'Rural' = "Rural"))

herbivory_both <- herbivory_both %>% 
  dplyr::mutate(Urb_Rur = Transect_ID) %>%
  dplyr::mutate(Urb_Rur = dplyr::recode(Urb_Rur,
                                        'North' = "Urban",
                                        'South' = "Urban",
                                        'Rural' = "Rural"))

survival_2020 <- survival_2020 %>% 
  dplyr::mutate(Urb_Rur = Transect_ID) %>%
  dplyr::mutate(Urb_Rur = dplyr::recode(Urb_Rur,
                                        'North' = "Urban",
                                        'South' = "Urban",
                                        'Rural' = "Rural"))

weevil_both <- weevil_both %>% 
  dplyr::mutate(Urb_Rur = Transect_ID) %>%
  dplyr::mutate(Urb_Rur = dplyr::recode(Urb_Rur,
                                        'North' = "Urban",
                                        'South' = "Urban",
                                        'Rural' = "Rural"))

herbivores <- herbivores %>% 
  dplyr::mutate(Urb_Rur = Transect_ID) %>%
  dplyr::mutate(Urb_Rur = dplyr::recode(Urb_Rur,
                                        'North' = "Urban",
                                        'South' = "Urban",
                                        'Rural' = "Rural"))

reproductive <- reproductive %>% 
  dplyr::mutate(Urb_Rur = Transect_ID) %>%
  dplyr::mutate(Urb_Rur = dplyr::recode(Urb_Rur,
                                        'North' = "Urban",
                                        'South' = "Urban",
                                        'Rural' = "Rural"))

flowering_2020 <- flowering_2020 %>% 
  dplyr::mutate(Urb_Rur = Transect_ID) %>%
  dplyr::mutate(Urb_Rur = dplyr::recode(Urb_Rur,
                                        'North' = "Urban",
                                        'South' = "Urban",
                                        'Rural' = "Rural"))


```

### Add urb_score data
```{r}
# Import urb_index values for each of these rows
urb_scores <- read.csv(here("./CommonGardenExperiment_2020Data/raw_data/Urbanization_Score/Urbanization_Scores_Table.csv"),  header=T, na.strings=c("","NA"))

# get rid of unnecessary cols, rename Patch ID to Pop_ID for joins
urb_scores <- urb_scores[,c(2,8)]
names(urb_scores)[1] <- "Pop_ID"

urb_scores <- dplyr::inner_join(urb_scores, urb_scores, by = "Pop_ID") 

# doing it manually
heights_both <- merge(heights_both, y = urb_scores, by = "Pop_ID", all.x = TRUE)
herbivory_both <- merge(herbivory_both, y = urb_scores, by = "Pop_ID", all.x = TRUE)
survival_2020 <- merge(survival_2020, y = urb_scores, by = "Pop_ID", all.x = TRUE)
weevil_both <- merge(weevil_both, y = urb_scores, by = "Pop_ID", all.x = TRUE)
herbivores <- merge(herbivores, y = urb_scores, by = "Pop_ID", all.x = TRUE)
reproductive <- merge(reproductive, y = urb_scores, by = "Pop_ID", all.x = TRUE)
flowering_2020 <- merge(flowering_2020, y = urb_scores, by = "Pop_ID", all.x = TRUE)

```

# Find averages per family & population
## reproductive
### Binary: flowering success
```{r}

# Find family means
flowered2020_familymeans <- reproductive  %>%
  dplyr::select(., c(2:7, 10, 14, 16:18)) %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      sum_flowered_indivs = sum(as.integer(Flowered2020)),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())


# Find population means
flowered2020_popmeans <- flowered2020_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      sum_flowered_indivs = sum(as.integer(sum_flowered_indivs)),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score)) %>%
  as.data.frame(flowered2020_popmeans) %>%
  
# add percent flowered column
  dplyr::mutate(., percent_flowered = sum_flowered_indivs / sum_replicates)

# remove pops with only 1 rep?




# Use SummarySE to get stats per family & population

### NOT TRANSFORMED
# SSE_fams_height_2020 <- summarySE(DC7_2020_heights, measurevar="Total_Height", groupvars=c("Population", "Family"), na.rm=TRUE)
# SSE_fams_height_2020 <- merge(x = SSE_fams_height_2020, y = Distances, by = "Population", all.x = TRUE)
# 
# SSE_pops_height_2020 <- summarySE(SSE_fams_height_2020, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)
# ## removing pops with only 1 representative (4 pops)
# SSE_pops_height_2020 <- merge(x = SSE_pops_height_2020 %>% filter(N > 1), y = Distances, by = "Population", all.x = TRUE)


```



## Height
```{r}

# Find family means
heights_both2020_familymeans <- heights_both %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      sum_height_June = sum(Total_Height_June),
      sum_height_Sept = sum(Total_Height_Sept),
      mean_Ramets_June = mean(Ramets_June),
      mean_Ramets_Sept = mean(Ramets_Sept),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      mean_rel_growth_rate = mean(rel_growth_rate),
      Urb_score = first(Urb_score),
      nPlants=n())
## divide total height by num. plants/pop
heights_both2020_familymeans$mean_height_June <- heights_both2020_familymeans$sum_height_June / heights_both2020_familymeans$sum_replicates

heights_both2020_familymeans$mean_height_Sept <- heights_both2020_familymeans$sum_height_Sept / heights_both2020_familymeans$sum_replicates


# Find population means
heights_both2020_popmeans <- heights_both2020_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      sum_height_June = sum(sum_height_June),
      sum_height_Sept = sum(sum_height_Sept),
      mean_Ramets_June = mean(mean_Ramets_June),
      mean_Ramets_Sept = mean(mean_Ramets_Sept),
      mean_height_June = mean(mean_height_June),
      mean_height_Sept = mean(mean_height_Sept),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      mean_rel_growth_rate = mean(mean_rel_growth_rate))



# # Use SummarySE to get stats per family & population
# ## HEIGHTS
# intermediate1 <- summarySE(heights_both, measurevar="Total_Height_June", groupvars=c("Population", "Family"), na.rm=TRUE)
# 
# intermediate2 <- summarySE(heights_both, measurevar="Total_Height_Sept", groupvars=c("Population", "Family"), na.rm=TRUE)
# 
# heights_2020_familymeans_stats <- left_join(intermediate1, intermediate2, by = c("Population", "Family"), suffix = c(".July", ".Sept"))
# 
# 
# # Use SummarySE to get stats per family & population
# ## no. ramets
# intermediate1 <- summarySE(heights_both, measurevar="Ramets_June", groupvars=c("Population", "Family"), na.rm=TRUE)
# 
# intermediate2 <- summarySE(heights_both, measurevar="Ramets_Sept", groupvars=c("Population", "Family"), na.rm=TRUE)
# 
# ramets_2020_familymeans_stats <- left_join(intermediate1, intermediate2, by = c("Population", "Family"), suffix = c(".June", ".Sept"))
# 
# # Add transect data via merge
# ramets_2020_familymeans_stats <- merge(ramets_2020_familymeans_stats, Distances, by = "Population", all.x = TRUE)
# 
# 
# 
# # SSE_pops_height_2020 <- summarySE(intermediates, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)

```


## Weevil scar lengths
```{r}
# Find family means
weevil_both2020_familymeans <- weevil_both %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      mean_scar_div_Juneheight = mean(scar_div_Juneheight, na.rm = TRUE),
      mean_scar = mean(Scar_length_cm),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())


# Find population means
weevil_both2020_popmeans <- weevil_both2020_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      mean_scar_div_Juneheight = mean(mean_scar_div_Juneheight, na.rm = TRUE),
      mean_scar = mean(mean_scar),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score))



# Use SummarySE to get stats per family & population

### NOT TRANSFORMED
# SSE_fams_height_2020 <- summarySE(DC7_2020_heights, measurevar="Total_Height", groupvars=c("Population", "Family"), na.rm=TRUE)
# SSE_fams_height_2020 <- merge(x = SSE_fams_height_2020, y = Distances, by = "Population", all.x = TRUE)
# 
# SSE_pops_height_2020 <- summarySE(SSE_fams_height_2020, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)
# ## removing pops with only 1 representative (4 pops)
# SSE_pops_height_2020 <- merge(x = SSE_pops_height_2020 %>% filter(N > 1), y = Distances, by = "Population", all.x = TRUE)


```
## Herbivores
```{r}

# Find family means
herbivores2020_familymeans <- herbivores %>%
  group_by(Population, Family, Sample) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      mean_Monarch_Quantity_Past = mean(Monarch_Quantity_Past),
      mean_Monarch_Quantity_Observed = mean(Monarch_Quantity_Observed),
      mean_Tetraopes_tetropthalmus = mean(Tetraopes_tetropthalmus),
      mean_Liriomyza_asclepiadis = mean(Liriomyza_asclepiadis),
      mean_Aphis_nerii = mean(Aphis_nerii),
      mean_Aphis_asclepiadis = mean(Aphis_asclepiadis),
      mean_Myzocallis_asclepiadis = mean(Myzocallis_asclepiadis),
      mean_Euchaetes_egle = mean(Euchaetes_egle),
      mean_Lygaeus_kalmii = mean(Lygaeus_kalmii),
      mean_Labidomera_clivicollis = mean(Labidomera_clivicollis),
      mean_Rhyssomatus_lineaticollis = mean(Rhyssomatus_lineaticollis),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())
herbivores2020_familymeans <- as.data.frame(herbivores2020_familymeans)


# Find population means
herbivores2020_popmeans <- herbivores2020_familymeans %>%
  group_by(Population, Sample) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      mean_Monarch_Quantity_Past = mean(mean_Monarch_Quantity_Past),
      mean_Monarch_Quantity_Observed = mean(mean_Monarch_Quantity_Observed),
      mean_Tetraopes_tetropthalmus = mean(mean_Tetraopes_tetropthalmus),
      mean_Liriomyza_asclepiadis = mean(mean_Liriomyza_asclepiadis),
      mean_Aphis_nerii = mean(mean_Aphis_nerii),
      mean_Aphis_asclepiadis = mean(mean_Aphis_asclepiadis),
      mean_Myzocallis_asclepiadis = mean(mean_Myzocallis_asclepiadis),
      mean_Euchaetes_egle = mean(mean_Euchaetes_egle),
      mean_Lygaeus_kalmii = mean(mean_Lygaeus_kalmii),
      mean_Labidomera_clivicollis = mean(mean_Labidomera_clivicollis),
      mean_Rhyssomatus_lineaticollis = mean(mean_Rhyssomatus_lineaticollis),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score))
herbivores2020_popmeans <- as.data.frame(herbivores2020_popmeans)


# Use SummarySE to get stats per family & population

### NOT TRANSFORMED
# SSE_fams_height_2020 <- summarySE(DC7_2020_heights, measurevar="Total_Height", groupvars=c("Population", "Family"), na.rm=TRUE)
# SSE_fams_height_2020 <- merge(x = SSE_fams_height_2020, y = Distances, by = "Population", all.x = TRUE)
# 
# SSE_pops_height_2020 <- summarySE(SSE_fams_height_2020, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)
# ## removing pops with only 1 representative (4 pops)
# SSE_pops_height_2020 <- merge(x = SSE_pops_height_2020 %>% filter(N > 1), y = Distances, by = "Population", all.x = TRUE)


```


## Herbivory
```{r}
# Find family means
herbivory2020_familymeans <- herbivory_both %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      Herbivory.July_mean = mean(Herbivory.July_mean, na.rm = T),
      Herbivory.Sept_mean = mean(Herbivory.Sept_mean, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())
herbivory2020_familymeans <- as.data.frame(herbivory2020_familymeans)


# Find population means
herbivory2020_popmeans <- herbivory2020_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      Herbivory.July_mean = mean(Herbivory.July_mean, na.rm = T),
      Herbivory.Sept_mean = mean(Herbivory.Sept_mean, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score))
herbivory2020_popmeans <- as.data.frame(herbivory2020_popmeans)


# Use SummarySE to get stats per family & population

### NOT TRANSFORMED
# SSE_fams_height_2020 <- summarySE(DC7_2020_heights, measurevar="Total_Height", groupvars=c("Population", "Family"), na.rm=TRUE)
# SSE_fams_height_2020 <- merge(x = SSE_fams_height_2020, y = Distances, by = "Population", all.x = TRUE)
# 
# SSE_pops_height_2020 <- summarySE(SSE_fams_height_2020, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)
# ## removing pops with only 1 representative (4 pops)
# SSE_pops_height_2020 <- merge(x = SSE_pops_height_2020 %>% filter(N > 1), y = Distances, by = "Population", all.x = TRUE)


```



## Survival
```{r}
# Find family means
survival2020_familymeans <- survival_2020 %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      survival_mean = mean(dead_2020, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())
survival2020_familymeans <- as.data.frame(survival2020_familymeans)


# Find population means
survival2020_popmeans <- survival2020_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      survival_mean = mean(survival_mean, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score))
survival2020_popmeans <- as.data.frame(survival2020_popmeans)


# Use SummarySE to get stats per family & population

### NOT TRANSFORMED
# SSE_fams_height_2020 <- summarySE(DC7_2020_heights, measurevar="Total_Height", groupvars=c("Population", "Family"), na.rm=TRUE)
# SSE_fams_height_2020 <- merge(x = SSE_fams_height_2020, y = Distances, by = "Population", all.x = TRUE)
# 
# SSE_pops_height_2020 <- summarySE(SSE_fams_height_2020, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)
# ## removing pops with only 1 representative (4 pops)
# SSE_pops_height_2020 <- merge(x = SSE_pops_height_2020 %>% filter(N > 1), y = Distances, by = "Population", all.x = TRUE)


```


# Visualize spatial patterns
## Blocks in plot
```{r}
blocks <- ggplot(data =  weevil_both, aes(x = Column, y = Row)) + 
      geom_tile(aes(fill = Block), colour = "black") +
      scale_y_reverse() +
  theme_minimal()
blocks

png("blocks.png", width = 800, height = 400)
print(blocks)
dev.off()
```

## Weevil damage
```{r}
# binary: damaged or not during first weevil damage assessment
weevil_matrix_data_binary <- weevil_both[,c("Row", "Column", "Weevil_dam_binary")]

weevil_plot_binary <- ggplot(data =  weevil_matrix_data_binary, aes(x = Column, y = Row)) + 
      geom_tile(aes(fill = Weevil_dam_binary), colour = "black") +
      scale_y_reverse() +
  scale_fill_manual(values = c("yellow", "red"),
                      name = "Weevil Damage",
                      labels = c("No", "Yes"))

weevil_plot_binary


# quantitative: how long was the scar? during second weevil damage assessment
weevil_matrix_data_quant <- weevil_both[,c("Row", "Column", "Scar_length_mm")]

weevil_plot_quant <- ggplot(data =  weevil_matrix_data_quant, aes(x = Column, y = Row, fill = Scar_length_mm)) + 
      geom_tile(aes(fill = Scar_length_mm), colour = "black") +
      scale_y_reverse()
weevil_plot_quant

# quantitative: how long was the scar? during second weevil damage assessment- ONLY IF HAD SCAR
weevil_matrix_data_quant <- weevil_both[,c("Row", "Column", "Scar_length_mm")]

ggplot(data =  weevil_matrix_data_quant %>% filter(.,Scar_length_mm > 0), aes(x = Column, y = Row, fill = Scar_length_mm)) + 
      geom_tile(aes(fill = Scar_length_mm), colour = "black") +
      scale_y_reverse()


# quantitative: how long was the scar? during second weevil damage assessment- ONLY IF HAD SCAR- STANDARDIZED BY HEIGHT
weevil_matrix_data_standardized <- weevil_both[,c("Row", "Column", "scar_div_Juneheight")]

ggplot(data =  weevil_matrix_data_standardized %>% filter(.,scar_div_Juneheight > 0), aes(x = Column, y = Row, fill = scar_div_Juneheight)) +
  geom_tile(aes(fill = scar_div_Juneheight), colour = "black") +
  scale_fill_gradientn(colours = topo.colors(50)) +
  scale_y_reverse() +
  labs(fill = "Scar length per cm height")

# hist(log(weevil_both$scar_div_Juneheight)
# png("weevil_matrix_binary.png", width = 800, height = 400)
# print(weevil_plot_binary)
# dev.off()
```

## Mortality
```{r}
mortality_matrix_data <- dead_2020[,c("Row", "Column", "Dead_June")]

mortality_plot <- ggplot(data =  mortality_matrix_data, aes(x = Column, y = Row)) + 
      geom_tile(aes(fill = Dead_June), colour = "black") +
      scale_y_reverse() +
      scale_fill_discrete(name = "Mortality", labels = c("Dead", "Alive"))


png("mortality_matrix.png", width = 800, height = 400)
print(mortality_plot)
dev.off()
```

## Flowering
### Flowering plants
```{r}
flowering_matrix_data <- reproductive[,c("Row", "Column", "Flowered2020")]

flowering_plot <- ggplot(data =  flowering_matrix_data, aes(x = Column, y = Row)) + 
  geom_tile(aes(fill = Flowered2020), colour = "black") +
  scale_y_reverse() +
  scale_fill_manual(values = c("yellow", "red"),
                      name = "Flowering Plants",
                      labels = c("No", "Yes"))
flowering_plot

png("flowering_matrix.png", width = 800, height = 400)
print(flowering_plot)
dev.off()
```



# Statistics
## reproductive
### Plants that flowered
#### Flowering success
##### Sig difference between urb vs rural? (Odds ratio)
```{r}
# # How many plants flowered per subtransect? using 2019 alive plants
# tib1 <- reproductive %>%
#   filter(Alive_DC1 != '0')%>%
#   group_by(Flowered2020, Urb_Rur) %>%
#   tally()
# tib1
# 
# 
# Flowered_ttest <- matrix(c(21, 3, 556, 282), nrow = 2,
#                          dimnames = list(
#                            c("Urban", "Rural"),
#                            c("Flowered", "Didn't Flower")))
# 
# fisher.test(Flowered_ttest, alternative = "two.sided")
# # odds ratio = 3.5464
# # p = 0.02859
# # medium effect size


# How many plants flowered per subtransect? using 2020 alive plants
reproductive <- anti_join(reproductive, dead_2020, by = c("Row", "Column"))

tib2 <- reproductive %>%
  group_by(Flowered2020, Urb_Rur) %>%
  tally()
tib2


Flowered_ttest2 <- matrix(c(
  as.integer(tib2[3,3]),
  as.integer(tib2[4,3]),
  as.integer(tib2[1,3]),
  as.integer(tib2[2,3])),
  nrow = 2,
  dimnames = list(
    c("Urban", "Rural"),
    c("Flowered", "Didn't Flower")))

fisher.test(Flowered_ttest2, alternative = "two.sided")
# odds ratio = 3.5148
# p = 0.0445
# medium effect size

chisq.test(Flowered_ttest2)
# X-squared = 3.7416, df = 1, p-value = 0.05307





# How many populations had at least one plant flower per subtransect? using 2020 alive plants
reproductive <- anti_join(reproductive, dead_2020, by = c("Row", "Column"))

tib3 <- reproductive[,c(1:6, 78:86)] %>%
  group_by(Population, Flowered2020, Urb_Rur) %>%
  dplyr::summarise(Pops = n_distinct(Population),
                   Urb_Rur = first(Urb_Rur)) %>%
  group_by(Population, Urb_Rur) %>%
  dplyr::summarise(Flowered = sum(as.integer(Flowered2020)),
                   Urb_Rur = first(Urb_Rur)) %>%
  group_by(Urb_Rur, Flowered) %>%
  dplyr::summarise(Pops = n_distinct(Population))
  
tib3
# Flowered = 1: Didn't flower
# Flowered = 3: Did flower



Flowered_ttest3 <- matrix(c(
  as.integer(tib3[2,3]),
  as.integer(tib3[4,3]),
  as.integer(tib3[3,3]),
  as.integer(tib3[2,3])),
  nrow = 2,
  dimnames = list(
    c("Urban", "Rural"),
    c("Flowered", "Didn't Flower")))

fisher.test(Flowered_ttest3, alternative = "two.sided")
# odds ratio = 3.5750
# p = 0.1006 (NOT SIGNIFICANT; CAN'T REJECT NULL)
# medium effect size


chisq.test(Flowered_ttest3)
# X-squared = 2.0551, df = 1, p-value = 0.1517
```



##### Sig difference between urb:north vs urb:south? (Odds ratio)
```{r}
# How many plants flowered per subtransect? using 2020 alive plants
reproductive <- anti_join(reproductive, dead_2020, by = c("Row", "Column"))

tib4 <- reproductive %>%
  filter(., Transect_ID != 'Rural') %>%
  group_by(Flowered2020, Transect_ID) %>%
  tally()
tib4


Flowered_ttest4 <- matrix(c(
  as.integer(tib4[3,3]),
  as.integer(tib4[4,3]),
  as.integer(tib4[1,3]),
  as.integer(tib4[2,3])),
  nrow = 2,
  dimnames = list(
    c("North", "South"),
    c("Flowered", "Didn't Flower")))

fisher.test(Flowered_ttest4, alternative = "two.sided")
# odds ratio = 0.7970 (inverted = 1.2547)
# p = 0.6618 (CAN'T REJECT THE NULL)
# negligible effect size

chisq.test(Flowered_ttest4)
# X-squared = 0.081128, df = 1, p-value = 0.7758






# How many populations had at least one plant flower per subtransect? using 2020 alive plants
reproductive <- anti_join(reproductive, dead_2020, by = c("Row", "Column"))

tib5 <- reproductive[,c(1:6, 78:86)] %>%
  filter(., Transect_ID != "Rural") %>%
  group_by(Population, Flowered2020, Transect_ID) %>%
  dplyr::summarise(Pops = n_distinct(Population),
                   Transect_ID = first(Transect_ID)) %>%
  group_by(Population, Transect_ID) %>%
  dplyr::summarise(Flowered = sum(as.integer(Flowered2020)),
                   Transect_ID = first(Transect_ID)) %>%
  group_by(Transect_ID, Flowered) %>%
  dplyr::summarise(Pops = n_distinct(Population))
  
tib5
# Flowered = 1: Didn't flower
# Flowered = 3: Did flower



Flowered_ttest5 <- matrix(c(
  as.integer(tib5[2,3]),
  as.integer(tib5[4,3]),
  as.integer(tib5[3,3]),
  as.integer(tib5[2,3])),
  nrow = 2,
  dimnames = list(
    c("North", "South"),
    c("Flowered", "Didn't Flower")))

fisher.test(Flowered_ttest5, alternative = "two.sided")
# odds ratio = 0.4737 (reciprocal = 2.1110)
# p = 0.4521 (NOT SIGNIFICANT; CAN'T REJECT NULL)
# small effect size

chisq.test(Flowered_ttest5)
# X-squared = 0.41878, df = 1, p-value = 0.5175
```


##### Block effect?
```{r}
glmer(Flowered2020 ~ Block + (1|Population/Family),
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=1,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

car::Anova(glmer(Flowered2020 ~ Block + (1|Population/Family),
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=1,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# Block is significant, so yes, the number of plants that flowered DID significantly vary by block.

summary(glmer(Flowered2020 ~ Block + (1|Population/Family),
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=1,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
```

#### Flower count
##### Mean flower count/inflorescence
###### Sig difference along gradient?
####### lmer: **YES: Both city_dist and urb_score significant
######## City_dist
```{r}
### NESTED RANDOM EFFECTS-----
flowercount_2020_lmer_gradient <- lmer(mean_flower_count ~ (1|Block) + (1|Population/Family) + City_dist, REML = F,data = flowering_2020)
# is singular

# ANOVA
car::Anova(flowercount_2020_lmer_gradient)
# distance is sig

library(MuMIn)
r.squaredGLMM(flowercount_2020_lmer_gradient)


### CROSSED RANDOM EFFECTS-----
lmer(mean_flower_count ~ (1|Block) + (1|Population:Family) + City_dist, data = flowering_2020, REML = F)
# singular

car::Anova(lmer(mean_flower_count ~ (1|Block) + (1|Population:Family) + City_dist, data = flowering_2020, REML = F))
# distance is sig


# ANy variation among families or populations?
ranova(lmer(mean_flower_count ~ (1|Population/Family), data = flowering_2020, REML = T))
# no... is singular
```

######## Urb_score
```{r}
### NESTED RANDOM EFFECTS-----
flowercount_2020_lmer_gradient_urbscore <- lmer(mean_flower_count ~ (1|Block) + (1|Population/Family) + Urb_score, data = flowering_2020, REML = F)
# is singular

# ANOVA
car::Anova(flowercount_2020_lmer_gradient_urbscore)
# sig

library(MuMIn)
r.squaredGLMM(flowercount_2020_lmer_gradient_urbscore)


### CROSSED RANDOM EFFECTS-----
lmer(mean_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score, data = flowering_2020, REML = F)
# singular

car::Anova(lmer(mean_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score, data = flowering_2020, REML = F))
#  sig

```

###### Sig difference btwn urban subtransects?
####### lmer: *NO: Nothing sig for city_dist or urb_score
######## City_dist
```{r}
### NESTED RANDOM EFFECTS-----
flowercount_2020_lmer_subtr <- lmer(mean_flower_count ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
# is singular

# ANOVA
car::Anova(flowercount_2020_lmer_subtr)
# nothing sig
AIC(flowercount_2020_lmer_subtr)

car::Anova(lmer(mean_flower_count ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))
# nothing sig

r.squaredGLMM(flowercount_2020_lmer_subtr)
# is this worth doing, since I have two regression lines?

AIC(lmer(mean_flower_count ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))


### CROSSED RANDOM EFFECTS-----
lmer(mean_flower_count ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
# is singular

# ANOVA
car::Anova(lmer(mean_flower_count ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)
# nothing sig


car::Anova(lmer(mean_flower_count ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)
# nothing sig



# ANy variation among families or populations?
ranova(lmer(mean_flower_count ~ (1|Population/Family), data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = T))
# no... is singular
car::Anova(lmer(mean_flower_count ~ (1|Population/Family) + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))
# no... is singular

```
######## Urb_score
```{r}
### NESTED RANDOM EFFECTS-----
flowercount_2020_lmer_subtr_urbscore <- lmer(mean_flower_count ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
# is singular

# ANOVA
car::Anova(flowercount_2020_lmer_subtr_urbscore)
# nothing sig
AIC(flowercount_2020_lmer_subtr_urbscore)

car::Anova(lmer(mean_flower_count ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))
# nothing sig

r.squaredGLMM(flowercount_2020_lmer_subtr_urbscore)
# is this worth doing, since I have two regression lines?

AIC(lmer(mean_flower_count ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))


### CROSSED RANDOM EFFECTS-----
lmer(mean_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
# is singular

# ANOVA
car::Anova(lmer(mean_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)
# nothing sig


car::Anova(lmer(mean_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)
# nothing sig

```

##### Total flower count
###### Sig difference along gradient?
####### glmer: *Marginally sig for city_dist, insig for urb_score
######## City_dist
```{r}
### nested RANDOM EFFECTS-----
flowercountsum_2020_glmer_gradient <- glmer(total_flower_count ~ (1|Block) + (1|Population/Family) + City_dist, data = flowering_2020, family = 'poisson')
# is singular...


# ANOVA
car::Anova(flowercountsum_2020_glmer_gradient)
# distance is marginally sig

r.squaredGLMM(flowercountsum_2020_glmer_gradient)


### CROSSED RANDOM EFFECTS-----
glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + City_dist, data = flowering_2020, family = 'poisson')
# NOT singular!


# ANOVA
car::Anova(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + City_dist, data = flowering_2020, family = 'poisson')
)
# distance is marginally sig




# ANy variation among families or populations?
# ranova(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + City_dist, data = flowering_2020, family = 'poisson'))
```

######## Urb_score
```{r}
### nested RANDOM EFFECTS-----
flowercountsum_2020_glmer_gradient_urbscore <- glmer(total_flower_count ~ (1|Block) + (1|Population/Family) + Urb_score, data = flowering_2020, family = 'poisson')
# is singular...


# ANOVA
car::Anova(flowercountsum_2020_glmer_gradient_urbscore)
# not sig

r.squaredGLMM(flowercountsum_2020_glmer_gradient_urbscore)


### CROSSED RANDOM EFFECTS-----
glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score, data = flowering_2020, family = 'poisson')
# NOT singular!


# ANOVA
car::Anova(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score, data = flowering_2020, family = 'poisson')
)
# not sig

```

###### Sig difference btwn urban subtransects?
####### glmer: *NO for both city_dist & urb_score
######## City_dist
```{r}
### NESTED RANDOM EFFECTS-----
flowercountsum_2020_glmer_subtr <- glmer(total_flower_count ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
                                     data = flowering_2020 %>% filter(Transect_ID != "Rural"))
# singular

# ANOVA
car::Anova(flowercountsum_2020_glmer_subtr)
AIC(flowercountsum_2020_glmer_subtr)
# nothing sig


car::Anova(glmer(total_flower_count ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural")))
# nothing sig

car::Anova(glmer(total_flower_count ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural")))
# nothing sig



### CROSSED RANDOM EFFECTS-----
glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,data = flowering_2020 %>% filter(Transect_ID != "Rural"))
# singular

# ANOVA
car::Anova(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,data = flowering_2020 %>% filter(Transect_ID != "Rural"))
)
AIC(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,data = flowering_2020 %>% filter(Transect_ID != "Rural"))
)
# nothing sig


car::Anova(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,data = flowering_2020 %>% filter(Transect_ID != "Rural"))
)
# nothing sig
AIC(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,data = flowering_2020 %>% filter(Transect_ID != "Rural"))
)

```

######## Urb_score
```{r}
### NESTED RANDOM EFFECTS-----
flowercountsum_2020_glmer_subtr_urbscore <- glmer(total_flower_count ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
                                     data = flowering_2020 %>% filter(Transect_ID != "Rural"),
                                     family = poisson)
# singular

# ANOVA
car::Anova(flowercountsum_2020_glmer_subtr_urbscore)
AIC(flowercountsum_2020_glmer_subtr_urbscore)
# nothing sig


car::Anova(glmer(total_flower_count ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"),
                                     family = poisson))
# nothing sig

car::Anova(glmer(total_flower_count ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"),
                                     family = poisson))
# nothing sig



### CROSSED RANDOM EFFECTS-----
glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,data = flowering_2020 %>% filter(Transect_ID != "Rural"),
                                     family = poisson)
# NOT singular

# ANOVA
car::Anova(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,data = flowering_2020 %>% filter(Transect_ID != "Rural"),
                                     family = poisson)
)
AIC(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,data = flowering_2020 %>% filter(Transect_ID != "Rural"),
                                     family = poisson)
)
# nothing sig


car::Anova(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,data = flowering_2020 %>% filter(Transect_ID != "Rural"),
                                     family = poisson)
)
# nothing sig
AIC(glmer(total_flower_count ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,data = flowering_2020 %>% filter(Transect_ID != "Rural"),
                                     family = poisson)
)

```


#### Flower size
##### Mean flower size/inflorescence
###### lmer
####### gradient: *NOt sig for either city_dist or urb_score
######## City_dist
```{r}
### NESTED RANDOM EFFECTS-----
lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + City_dist, data = flowering_2020, REML = F)
# is singular

# ANOVA
car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + City_dist, data = flowering_2020, REML = F)
)
# distance not sig

library(MuMIn)
r.squaredGLMM(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + City_dist, data = flowering_2020, REML = F)
)


### CROSSED RANDOM EFFECTS-----
lmer(Overall_mean ~ (1|Block) + (1|Population:Family) + City_dist, data = flowering_2020, REML = F)
# singular

car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population:Family) + City_dist, data = flowering_2020, REML = F))
# distance not sig


# ANy variation among families or populations?
ranova(lmer(Overall_mean ~ (1|Population/Family), data = flowering_2020, REML = T))
# no
```


######## Urb_score
```{r}
### NESTED RANDOM EFFECTS-----
lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + Urb_score, data = flowering_2020,
     REML = F, lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
# singular

# ANOVA
car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + Urb_score, data = flowering_2020, REML = F)
)
# not sig

library(MuMIn)
r.squaredGLMM(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + Urb_score, data = flowering_2020, REML = F)
)


### CROSSED RANDOM EFFECTS-----
lmer(Overall_mean ~ (1|Block) + (1|Population:Family) + Urb_score, data = flowering_2020, REML = F)
# singular

car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population:Family) + Urb_score, data = flowering_2020, REML = F))
# urb_score not sig

```

####### urban subtransects: *Main effects sig for both; interaxn sig for city_dist (marg sig for urb_score)
######## City_dist
```{r}
### NESTED RANDOM EFFECTS-----
lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
# is singular

# remove block?
lmer(Overall_mean ~ (1|Population/Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
# is singular

# ANOVA
car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))
# main effects and interaxn sig

car::Anova(lmer(Overall_mean ~  (1|Population/Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))
# still singular,  everything  sig

AIC(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)

car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))
# both main effects sig

r.squaredGLMM(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)
# very high r-sq...is this worth doing, since I have two regression lines?

AIC(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))


### CROSSED RANDOM EFFECTS-----
lmer(Overall_mean ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
# NOT singular

# ANOVA
car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)
# everything sig


car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)
# main effects sig



# ANy variation among families or populations?
ranova(lmer(Overall_mean ~ (1|Population/Family), data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = T))
# no
car::Anova(lmer(Overall_mean ~ (1|Population/Family) + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))
# YES... variance DOES differ by subtransect... is singular

```
######## Urb_score
```{r}
### NESTED RANDOM EFFECTS-----
lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
# is singular

# remove block?
lmer(Overall_mean ~ (1|Population/Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
# is singular

# ANOVA
car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))
# main effects sig

car::Anova(lmer(Overall_mean ~  (1|Population/Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))
# still singular, main effects sig

AIC(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)

car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))
# both main effects sig

r.squaredGLMM(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)
# very high r-sq...is this worth doing, since I have two regression lines?

AIC(lmer(Overall_mean ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F))


### CROSSED RANDOM EFFECTS-----
lmer(Overall_mean ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
# is singular

# ANOVA
car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)
# main effects sig


car::Anova(lmer(Overall_mean ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID, data = flowering_2020 %>% filter(Transect_ID != "Rural"), REML = F)
)
# main effects sig

```

### All plants
#### Regressions (is urbanization related to flowering?)
##### glmer
###### Entire gradient: *Nothing sig for either
####### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
glmer(Flowered2020 ~ (1|Block) + (1|Population/Family) + City_dist,
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=0)

car::Anova(glmer(Flowered2020 ~ (1|Block) + (1|Population/Family) + City_dist,
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=0))
# nothing significant



### CROSSED RANDOM EFFECTS-----
glmer(Flowered2020 ~ (1|Block) + (1|Population:Family) + City_dist,
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=0)

car::Anova(glmer(Flowered2020 ~ (1|Block) + (1|Population:Family) + City_dist,
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=0))
# nothing significant


# ranova(glmer(Flowered2020 ~ (1|Population/Family), data = reproductive, REML = T, family = binomial(link = "logit")))

# ranova(lmer(Flowered2020 ~ (1|Population/Family), data = reproductive, REML = T))
```

####### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
glmer(Flowered2020 ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=0)

car::Anova(glmer(Flowered2020 ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=0))
# nothing significant



### CROSSED RANDOM EFFECTS-----
glmer(Flowered2020 ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=0)

car::Anova(glmer(Flowered2020 ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = reproductive,
  family = binomial(link = "logit"),
  nAGQ=0))
# nothing significant

```

###### Urban subtransects: *Nothing sig for either
####### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
glmer(Flowered2020  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
  data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
# is singular w/the glmerControl added; doesn't converge without it!

car::Anova(glmer(Flowered2020  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
  data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


# Just main effects
car::Anova(glmer(Flowered2020  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
  data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
glmer(Flowered2020  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
  data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
# No warnings!!

car::Anova(glmer(Flowered2020  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
  data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


# Just main effects
car::Anova(glmer(Flowered2020  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
                 data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
                 family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


AIC(glmer(Flowered2020  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
                 data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),        family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))

AIC(glmer(Flowered2020  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
                 data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),        family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# AIC <2 apart; both "best models" though just main effects lower AIC
```

####### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
glmer(Flowered2020  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
  data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
# is singular w/the glmerControl added; doesn't converge without it!

car::Anova(glmer(Flowered2020  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
  data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


# Just main effects
car::Anova(glmer(Flowered2020  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
  data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
glmer(Flowered2020  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
  data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
# No warnings!!

car::Anova(glmer(Flowered2020  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
  data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


# Just main effects
car::Anova(glmer(Flowered2020  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
                 data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),
                 family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


AIC(glmer(Flowered2020  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
                 data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),        family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))

AIC(glmer(Flowered2020  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
                 data = reproductive %>% dplyr::filter(., Transect_ID != "Rural"),        family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# AIC <2 apart; both "best models" though just main effects lower AIC
```


## Heights
### June height
#### lmer
##### Entire gradient
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Total_Height_June ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F)
# is singular...

car::Anova(lmer(Total_Height_June ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F))
# distance is marginally significant


r.squaredGLMM(lmer(Total_Height_June ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F))

### CROSSED RANDOM EFFECTS-----
lmer(Total_Height_June ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F)
# NOT singular!

car::Anova(lmer(Total_Height_June ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F))
# distance is marginally significant




# ANy variation within families or populations?
m.1 <- lmer(Total_Height_June ~ (1|Population/Family), data = heights_both, REML = T)

ranova(m.1)
# YES for within families
sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_JuneHeight_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_JuneHeight_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Total_Height_June ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F)
# is singular...

car::Anova(lmer(Total_Height_June ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F))
# nothing significant


r.squaredGLMM(lmer(Total_Height_June ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F))

### CROSSED RANDOM EFFECTS-----
lmer(Total_Height_June ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F)
# NOT singular!

car::Anova(lmer(Total_Height_June ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F))
# nothing significant

```

##### Urban subtransects
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Total_Height_June  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)


car::Anova(lmer(Total_Height_June  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Total_Height_June  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Total_Height_June  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# No warnings!!

car::Anova(lmer(Total_Height_June  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Total_Height_June  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID, 
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


AIC(lmer(Total_Height_June  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Total_Height_June  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best models" though just main effects lower AIC




# ANy variation among families or populations?
m.1 <- lmer(Total_Height_June ~ (1|Population/Family), data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
ranova(m.1)
# YES for among families

m.2 <- lmer(Total_Height_June ~ (1|Population/Family) + Transect_ID, data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
car::Anova(m.2)
# not among transects though


m.3 <- lmer(Total_Height_June ~ (1|Population/Family) + Transect_ID, data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
car::Anova(m.3)
# not sig in this or m.2


sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_JuneHeight_urban_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_JuneHeight_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
write.table(car::Anova(m.2), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_JuneHeight_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Total_Height_June  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)


car::Anova(lmer(Total_Height_June  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Total_Height_June  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Total_Height_June  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# No warnings!!

car::Anova(lmer(Total_Height_June  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Total_Height_June  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID, 
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


AIC(lmer(Total_Height_June  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Total_Height_June  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best models" though just main effects lower AIC

```


### Sept height
#### lmer
##### Entire gradient
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Total_Height_Sept ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F)
# is singular...

car::Anova(lmer(Total_Height_Sept ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F))
# distance is marginally significant


### CROSSED RANDOM EFFECTS-----
lmer(Total_Height_Sept ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F)
# NOT singular!

car::Anova(lmer(Total_Height_Sept ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F))
# distance is marginally significant

r.squaredGLMM(lmer(Total_Height_Sept ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F))

# ANy variation within families or populations?
m.1 <- lmer(Total_Height_Sept ~ (1|Population/Family), data = heights_both, REML = T)

ranova(m.1)
# YES for among families (marginally sig)
sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_SeptHeight_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_SeptHeight_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Total_Height_Sept ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F)
# is singular...

car::Anova(lmer(Total_Height_Sept ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F))
# not significant


### CROSSED RANDOM EFFECTS-----
lmer(Total_Height_Sept ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F)
# NOT singular!

car::Anova(lmer(Total_Height_Sept ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F))
# not significant

r.squaredGLMM(lmer(Total_Height_Sept ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F))

```


##### Urban subtransects
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Total_Height_Sept  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)


car::Anova(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Total_Height_Sept  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# No warnings!!

car::Anova(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


AIC(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best models" though just main effects lower AIC




# ANy variation among families or populations?
m.1 <- lmer(Total_Height_Sept ~ (1|Population/Family), data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
ranova(m.1)
# YES for among families (marg sig)

m.2 <- lmer(Total_Height_Sept ~ (1|Population/Family) + Transect_ID, data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
car::Anova(m.2)
# not among transects though


m.3 <- lmer(Total_Height_Sept ~ (1|Population/Family) + Transect_ID, data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
car::Anova(m.3)
# not sig in this or m.2


sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_SeptHeight_urban_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_SeptHeight_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
write.table(car::Anova(m.2), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_SeptHeight_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```


###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Total_Height_Sept  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)


car::Anova(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Total_Height_Sept  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# No warnings!!

car::Anova(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


AIC(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Total_Height_Sept  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best models" though just main effects lower AIC

```



## Weevil scars: standardized by June height
### lmer
#### Entire gradient
##### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(scar_div_Juneheight ~ (1|Block) + (1|Population/Family) + City_dist,
  data = weevil_both, REML = F)
# is singular...

car::Anova(lmer(scar_div_Juneheight ~ (1|Block) + (1|Population/Family) + City_dist,
  data = weevil_both, REML = F))
# nothing significant


### CROSSED RANDOM EFFECTS-----
lmer(scar_div_Juneheight ~ (1|Block) + (1|Population:Family) + City_dist,
  data = weevil_both, REML = F)
# NOT singular!

car::Anova(lmer(scar_div_Juneheight ~ (1|Block) + (1|Population:Family) + City_dist,
  data = weevil_both, REML = F))
# nothing significant
summary(lmer(scar_div_Juneheight ~ (1|Block) + (1|Population:Family) + City_dist,
  data = weevil_both, REML = F))


r.squaredGLMM(lmer(scar_div_Juneheight ~ (1|Block) + (1|Population:Family) + City_dist,
  data = weevil_both, REML = F))


# ANy variation within families or populations?
m.1 <- lmer(scar_div_Juneheight ~ (1|Population/Family), data = weevil_both, REML = T)

ranova(m.1)
# nope
sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_Weevildivheight_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_Weevildivheight_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

##### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(scar_div_Juneheight ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = weevil_both, REML = F)
# is singular...

car::Anova(lmer(scar_div_Juneheight ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = weevil_both, REML = F))
# nothing significant


### CROSSED RANDOM EFFECTS-----
lmer(scar_div_Juneheight ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = weevil_both, REML = F)
# NOT singular!

car::Anova(lmer(scar_div_Juneheight ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = weevil_both, REML = F))
# nothing significant
summary(lmer(scar_div_Juneheight ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = weevil_both, REML = F))


r.squaredGLMM(lmer(scar_div_Juneheight ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = weevil_both, REML = F))


```


#### Urban subtransects
##### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# is singular

car::Anova(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# No warnings!!

car::Anova(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


AIC(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best model"



# ANy variation among families or populations?
m.1 <- lmer(scar_div_Juneheight ~ (1|Population/Family), data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
ranova(m.1)
# no, is singular

m.2 <- lmer(scar_div_Juneheight ~ (1|Population/Family) + Transect_ID, data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
car::Anova(m.2)
# not among transects though


m.3 <- lmer(scar_div_Juneheight ~ (1|Population/Family) + Transect_ID, data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
car::Anova(m.3)
# not sig in this or m.2


sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_Weevildivheight_urban_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_Weevildivheight_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
write.table(car::Anova(m.2), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_Weevildivheight_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

##### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# is singular

car::Anova(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
# No warnings!!

car::Anova(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# nothing significant


# Just main effects
car::Anova(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# nothing significant


AIC(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))

AIC(lmer(scar_div_Juneheight  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# AIC <2 apart; both "best model"

```


## Weevil scars: NOT standardized by June height
### lmer
#### Entire gradient
##### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Scar_length_cm ~ (1|Block) + (1|Population/Family) + City_dist,
  data = weevil_both, REML = F)
# NOT singular

car::Anova(lmer(Scar_length_cm ~ (1|Block) + (1|Population/Family) + City_dist,
  data = weevil_both, REML = F))
# nothing significant


### CROSSED RANDOM EFFECTS-----
lmer(Scar_length_cm ~ (1|Block) + (1|Population:Family) + City_dist,
  data = weevil_both, REML = F)
# NOT singular

car::Anova(lmer(Scar_length_cm ~ (1|Block) + (1|Population:Family) + City_dist,
  data = weevil_both, REML = F))
# nothing significant


r.squaredGLMM(lmer(Scar_length_cm ~ (1|Block) + (1|Population:Family) + City_dist,
  data = weevil_both, REML = F))

# ANy variation within families or populations?
m.1 <- lmer(Scar_length_cm ~ (1|Population/Family), data = weevil_both, REML = T)

ranova(m.1)
# nope
sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_Weevil_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_Weevil_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

##### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Scar_length_cm ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = weevil_both, REML = F)
# NOT singular

car::Anova(lmer(Scar_length_cm ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = weevil_both, REML = F))
# nothing significant


### CROSSED RANDOM EFFECTS-----
lmer(Scar_length_cm ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = weevil_both, REML = F)
# NOT singular

car::Anova(lmer(Scar_length_cm ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = weevil_both, REML = F))
# nothing significant


r.squaredGLMM(lmer(Scar_length_cm ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = weevil_both, REML = F))

```


#### Urban subtransects
##### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Scar_length_cm  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# NOT singular

car::Anova(lmer(Scar_length_cm  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Scar_length_cm  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Scar_length_cm  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# No warnings

car::Anova(lmer(Scar_length_cm  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Scar_length_cm  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


AIC(lmer(Scar_length_cm  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Scar_length_cm  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best model"




# ANy variation among families or populations?
m.1 <- lmer(Scar_length_cm ~ (1|Population/Family), data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
ranova(m.1)
# no

m.2 <- lmer(Scar_length_cm ~ (1|Population/Family) + Transect_ID, data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
car::Anova(m.2)
# not among transects either


m.3 <- lmer(Scar_length_cm ~ (1|Population/Family) + Transect_ID, data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
car::Anova(m.3)
# not sig in this or m.2


sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_Weevil_urban_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_Weevil_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
write.table(car::Anova(m.2), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_Weevil_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

##### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Scar_length_cm  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# NOT singular

car::Anova(lmer(Scar_length_cm  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Scar_length_cm  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Scar_length_cm  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# No warnings

car::Anova(lmer(Scar_length_cm  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Scar_length_cm  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


AIC(lmer(Scar_length_cm  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Scar_length_cm  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = weevil_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best model"
```


## Herbivores: RDA
### Examine herbivore distributions
```{r}
library(purrr)
library(tidyr)
library(ggplot2)

herbivores2020_popmeans %>%
dplyr::select(., c(3:13)) %>%
  gather() %>% 
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") +
    geom_histogram(bins = 20)
# few vars normally distributed


# Aphis asclepiadis
a.ascl_lm <- lm(mean_Aphis_asclepiadis ~ City_dist, herbivores2020_popmeans)
gg_reshist(lm(a.ascl_lm), bins = 20)
diagnostic(residuals(a.ascl_lm))
# definitely transform... very right-skewed

# cube root
par(mfrow=c(2,2))
diagnostic(residuals(lm(mean_Aphis_asclepiadis^(1/3) ~ City_dist, herbivores2020_popmeans)))
gg_reshist(lm(mean_Aphis_asclepiadis^(1/3) ~ City_dist, herbivores2020_popmeans), bins = 20)


# log
par(mfrow=c(2,2))
diagnostic(residuals(lm(log(mean_Aphis_asclepiadis + 1) ~ City_dist, herbivores2020_popmeans)))
gg_reshist(lm(log(mean_Aphis_asclepiadis + 1) ~ City_dist, herbivores2020_popmeans), bins = 20)

manova(cbind(Sepal.Length, Petal.Length) ~ Species, data = iris)
```

### RDA
```{r}

herbpopMeansJuly_PCA <- prcomp(as.matrix(herbivores2020_popmeansJuly[,c(4:15)]))
summary(herbpopMeansJuly_PCA) # 17.3% variation explained by PC1

herbpopMeansAug_PCA <- prcomp(as.matrix(herbivores2020_popmeansAug[,c(4:15)]))
summary(herbpopMeansAug_PCA) # 18.4% variation explained by PC1

# trait_loadings <- herbpopMeansAug_PCA$rotation[,'PC1']






hist(herbivores$Lygaeus_kalmii)

glmer(City_dist ~  (1|Block) + (1|Sample) + (1|Population/Family) + Lygaeus_kalmii,
  data = herbivores, family = 'poisson')


# JULY
herbivores2020_popmeansJuly <- herbivores2020_popmeans %>%
  dplyr::filter(., Sample == 'July')

rda_herb_July <- rda(herbivores2020_popmeansJuly %>%
                        dplyr::select(, c(4:14)) ~ herbivores2020_popmeansJuly$City_dist,
                na.action = "na.omit",
                scale = T)

summary(rda_herb_July)
anova(rda_herb_July)
screeplot(rda_herb_July)

RsquareAdj(rda_herb_July)


plot(rda_herb_July, type='n', scaling=1)
orditorp(rda_herb_July, display='sp', cex=0.5, scaling=1, col='blue')
text(rda_herb_July, display='cn', col='red')






# AUGUST
herbivores2020_popmeansAug <- herbivores2020_popmeans %>%
  dplyr::filter(., Sample == 'August')

rda_herb_August <- rda(herbivores2020_popmeansAug %>%
                        dplyr::select(, c(4:14)) ~ herbivores2020_popmeansAug$City_dist,
                na.action = "na.omit",
                scale = TRUE)

summary(rda_herb_August)
rda_herb_August

RsquareAdj(rda_herb_August)


plot(rda_herb_August, type='n', scaling=1)
orditorp(rda_herb_August, display='sp', cex=0.5, scaling=1, col='blue')
text(rda_herb_August, display='cn', col='red')
```

## Herbivory
### July
#### lmer
##### Entire gradient
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Herbivory.July_mean ~ (1|Block) + (1|Population/Family) + City_dist,
  data = herbivory_both, REML = F)
# is singular...

car::Anova(lmer(Herbivory.July_mean ~ (1|Block) + (1|Population/Family) + City_dist,
  data = herbivory_both, REML = F))
# distance is significant


### CROSSED RANDOM EFFECTS-----
lmer(Herbivory.July_mean ~ (1|Block) + (1|Population:Family) + City_dist,
  data = herbivory_both, REML = F)
# NOT singular!

car::Anova(lmer(Herbivory.July_mean ~ (1|Block) + (1|Population:Family) + City_dist,
  data = herbivory_both, REML = F))
# distance is significant

summary(lmer(Herbivory.July_mean ~ (1|Block) + (1|Population:Family) + City_dist,
  data = herbivory_both, REML = F))


r.squaredGLMM(lmer(Herbivory.July_mean ~ (1|Block) + (1|Population:Family) + City_dist,
  data = herbivory_both, REML = F))



# ANy variation within families or populations?
m.1 <- lmer(Herbivory.July_mean ~ (1|Population/Family), data = herbivory_both, REML = T)

ranova(m.1)
# nope
sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_HerbivoryJuly_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_HerbivoryJuly_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Herbivory.July_mean ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = herbivory_both, REML = F)
# is singular...

car::Anova(lmer(Herbivory.July_mean ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = herbivory_both, REML = F))
# not significant


### CROSSED RANDOM EFFECTS-----
lmer(Herbivory.July_mean ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = herbivory_both, REML = F)
#  singular

car::Anova(lmer(Herbivory.July_mean ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = herbivory_both, REML = F))
# not significant

summary(lmer(Herbivory.July_mean ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = herbivory_both, REML = F))


r.squaredGLMM(lmer(Herbivory.July_mean ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = herbivory_both, REML = F))

```


##### Urban subtransects
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

car::Anova(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# distance is significant


# Just main effects
car::Anova(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular... distance is significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

lmer(Herbivory.July_mean  ~ (1|Population:Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

lmer(Herbivory.July_mean  ~ (1|Population:Family) + Block + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

# try making a unique family identifier and removing pop
trial1 <- herbivory_both %>%
  dplyr::filter(., Transect_ID != "Rural") %>%
  unite("Family_Unique", c(Population,Family), remove = FALSE)

lmer(Herbivory.July_mean  ~ (1|Family_Unique) + Transect_ID,
     data = trial1, REML = F)
# still singular, even with block and distance removed...



car::Anova(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# distance is significant


# Just main effects
car::Anova(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular... distance is significant


AIC(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best models" though full model has lower AIC




# ANy variation among families or populations?
m.1 <- lmer(Herbivory.July_mean ~ (1|Population/Family), data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
ranova(m.1)
# no

m.2 <- lmer(Herbivory.July_mean ~ (1|Population/Family) + Transect_ID, data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
car::Anova(m.2)
# not among transects either


m.3 <- lmer(Herbivory.July_mean ~ (1|Population/Family) + Transect_ID, data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
car::Anova(m.3)
# not sig in this or m.2


sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_HerbivoryJuly_urban_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_HerbivoryJuly_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
write.table(car::Anova(m.2), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_HerbivoryJuly_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

car::Anova(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular... nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

lmer(Herbivory.July_mean  ~ (1|Population:Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

lmer(Herbivory.July_mean  ~ (1|Population:Family) + Block + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

# try making a unique family identifier and removing pop
trial1 <- herbivory_both %>%
  dplyr::filter(., Transect_ID != "Rural") %>%
  unite("Family_Unique", c(Population,Family), remove = FALSE)

lmer(Herbivory.July_mean  ~ (1|Family_Unique) + Transect_ID,
     data = trial1, REML = F)
# still singular, even with block and distance removed...



car::Anova(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular... nothing significant


AIC(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Herbivory.July_mean  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best models" though full model has lower AIC

```


### Sept
#### lmer
##### Entire gradient
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Herbivory.Sept_mean ~ (1|Block) + (1|Population/Family) + City_dist,
  data = herbivory_both, REML = F)
# is singular...

car::Anova(lmer(Herbivory.Sept_mean ~ (1|Block) + (1|Population/Family) + City_dist,
  data = herbivory_both, REML = F))
# nothing is significant

r.squaredGLMM(lmer(Herbivory.Sept_mean ~ (1|Block) + (1|Population/Family) + City_dist,
  data = herbivory_both, REML = F))
  

### CROSSED RANDOM EFFECTS-----
lmer(Herbivory.Sept_mean ~ (1|Block) + (1|Population:Family) + City_dist,
  data = herbivory_both, REML = F)
# NOT singular!

car::Anova(lmer(Herbivory.Sept_mean ~ (1|Block) + (1|Population:Family) + City_dist,
  data = herbivory_both, REML = F))
# distance not significant



# ANy variation within families or populations?
m.1 <- lmer(Herbivory.Sept_mean ~ (1|Population/Family), data = herbivory_both, REML = T)

ranova(m.1)
# nope
sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_HerbivorySept_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_HerbivorySept_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Herbivory.Sept_mean ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = herbivory_both, REML = F)
# is singular...

car::Anova(lmer(Herbivory.Sept_mean ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = herbivory_both, REML = F))
# nothing is significant

r.squaredGLMM(lmer(Herbivory.Sept_mean ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = herbivory_both, REML = F))
  

### CROSSED RANDOM EFFECTS-----
lmer(Herbivory.Sept_mean ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = herbivory_both, REML = F)
#  singular

car::Anova(lmer(Herbivory.Sept_mean ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = herbivory_both, REML = F))
#  not significant


```


##### Urban subtransects
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

car::Anova(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# distance is significant


# Just main effects
car::Anova(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular... distance is significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

car::Anova(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# distance is significant


# Just main effects
car::Anova(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular... distance is significant


AIC(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best models" though main effects model has lower AIC


# ANy variation among families or populations?
m.1 <- lmer(Herbivory.Sept_mean ~ (1|Population/Family), data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
ranova(m.1)
# no

m.2 <- lmer(Herbivory.Sept_mean ~ (1|Population/Family) + Transect_ID, data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
car::Anova(m.2)
# not among transects either


m.3 <- lmer(Herbivory.Sept_mean ~ (1|Population/Family) + Transect_ID, data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
car::Anova(m.3)
# not sig in this or m.2


sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_HerbivorySept_urban_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_HerbivorySept_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
write.table(car::Anova(m.2), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_HerbivorySept_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)

```

###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

car::Anova(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular... nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular...

car::Anova(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular... nothing significant


AIC(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Herbivory.Sept_mean  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = herbivory_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best models" though main effects model has lower AIC

```


## Growth Rate
### lmer
#### Entire gradient
##### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(rel_growth_rate ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F)
# is singular...

lmer(rel_growth_rate ~ (1|Population/Family) + City_dist,
  data = heights_both, REML = F)
# still singular


car::Anova(lmer(rel_growth_rate ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F))
# not significant


r.squaredGLMM(lmer(rel_growth_rate ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F))


### CROSSED RANDOM EFFECTS-----
lmer(rel_growth_rate ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F)
#  singular

lmer(rel_growth_rate ~ (1|Population:Family) + City_dist,
  data = heights_both, REML = F)
#  singular

car::Anova(lmer(rel_growth_rate ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F))
# not sig



# ANy variation within families or populations?
m.1 <- lmer(rel_growth_rate ~ (1|Population/Family), data = heights_both, REML = T)

ranova(m.1)
# nope
sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_growthrate_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_growthrate_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

##### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(rel_growth_rate ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F)
# is singular...

lmer(rel_growth_rate ~ (1|Population/Family) + Urb_score,
  data = heights_both, REML = F)
# still singular


car::Anova(lmer(rel_growth_rate ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F))
# not significant


r.squaredGLMM(lmer(rel_growth_rate ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F))


### CROSSED RANDOM EFFECTS-----
lmer(rel_growth_rate ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F)
#  singular

lmer(rel_growth_rate ~ (1|Population:Family) + Urb_score,
  data = heights_both, REML = F)
#  singular

car::Anova(lmer(rel_growth_rate ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F))
# not sig

```


#### Urban subtransects
##### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(rel_growth_rate  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular

lmer(rel_growth_rate  ~ (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular

car::Anova(lmer(rel_growth_rate  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing sig


# Just main effects
car::Anova(lmer(rel_growth_rate  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular, nothing sig



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(rel_growth_rate  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular

lmer(rel_growth_rate  ~ (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# NOT singular!


car::Anova(lmer(rel_growth_rate  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant

car::Anova(lmer(rel_growth_rate  ~ (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(rel_growth_rate  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID, 
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular... nothing sig

car::Anova(lmer(rel_growth_rate  ~ (1|Population:Family) + City_dist + Transect_ID, 
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# NOT SINGULAR!  nothing sig


AIC(lmer(rel_growth_rate  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(rel_growth_rate  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC >2 apart; just main effects lower AIC = best model





# ANy variation among families or populations?
m.1 <- lmer(rel_growth_rate ~ (1|Population/Family), data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
ranova(m.1)
# no

m.2 <- lmer(rel_growth_rate ~ (1|Population/Family) + Transect_ID, data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
car::Anova(m.2)
# not among transects either


m.3 <- lmer(rel_growth_rate ~ (1|Population/Family) + Transect_ID, data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
car::Anova(m.3)
# not sig in this or m.2


sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_growthrate_urban_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_growthrate_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
write.table(car::Anova(m.2), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_growthrate_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

##### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(rel_growth_rate  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular

lmer(rel_growth_rate  ~ (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular

car::Anova(lmer(rel_growth_rate  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing sig


# Just main effects
car::Anova(lmer(rel_growth_rate  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular, nothing sig



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(rel_growth_rate  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular

lmer(rel_growth_rate  ~ (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# NOT singular!


car::Anova(lmer(rel_growth_rate  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant

car::Anova(lmer(rel_growth_rate  ~ (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(rel_growth_rate  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID, 
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# singular... nothing sig

car::Anova(lmer(rel_growth_rate  ~ (1|Population:Family) + Urb_score + Transect_ID, 
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# NOT SINGULAR!  nothing sig


AIC(lmer(rel_growth_rate  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(rel_growth_rate  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC >2 apart; just main effects lower AIC = best model

```


## Number of Ramets
### June ramets
#### lmer
##### Entire gradient: ANOVA
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Ramets_June ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
# no warning!

car::Anova(lmer(Ramets_June ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# nothing significant


r.squaredGLMM(lmer(Ramets_June ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))

### CROSSED RANDOM EFFECTS-----
lmer(Ramets_June ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
# NOT singular!

car::Anova(lmer(Ramets_June ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# nothing significant


# Any variation within families or populations?
m.1 <- lmer(Ramets_June ~ (1|Population/Family), data = heights_both, REML = T)

ranova(m.1)
# YES- marg sig among families
sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_JuneRamets_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_JuneRamets_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Ramets_June ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
# no warning!

car::Anova(lmer(Ramets_June ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# nothing significant


r.squaredGLMM(lmer(Ramets_June ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))

### CROSSED RANDOM EFFECTS-----
lmer(Ramets_June ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
# NOT singular!

car::Anova(lmer(Ramets_June ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# nothing significant

```


##### Urban subtransects: ANOVA
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Ramets_June  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)


car::Anova(lmer(Ramets_June  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Ramets_June  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Ramets_June  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
# No warnings!!

car::Anova(lmer(Ramets_June  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# nothing significant


# Just main effects
car::Anova(lmer(Ramets_June  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID, 
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# nothing significant


AIC(lmer(Ramets_June  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))

AIC(lmer(Ramets_June  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# AIC <2 apart; both "best models" though just main effects lower AIC




# ANy variation among families or populations?
m.1 <- lmer(Ramets_June ~ (1|Population/Family), data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
ranova(m.1)
# no

m.2 <- lmer(Ramets_June ~ (1|Population/Family) + Transect_ID, data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
car::Anova(m.2)
# not among transects 


m.3 <- lmer(Ramets_June ~ (1|Population/Family) + Transect_ID, data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
car::Anova(m.3)
# not sig in this or m.2


sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_JuneRamets_urban_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_JuneRamets_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
write.table(car::Anova(m.2), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_JuneRamets_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Ramets_June  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular

car::Anova(lmer(Ramets_June  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# urb_score significant, transect marg sig


# Just main effects
car::Anova(lmer(Ramets_June  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
#  urb_score significant, transect marg sig



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Ramets_June  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
# No warnings!!

car::Anova(lmer(Ramets_June  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
#  urb_score significant, transect marg sig


# Just main effects
car::Anova(lmer(Ramets_June  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID, 
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# urb_score significant, transect marg sig


AIC(lmer(Ramets_June  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))

AIC(lmer(Ramets_June  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))))
# AIC <2 apart; both "best models" though just main effects lower AIC
```


### Sept ramets
#### lmer
##### Entire gradient: ANOVA
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Ramets_Sept ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F)
# is singular...

car::Anova(lmer(Ramets_Sept ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F))
# distance is significant


r.squaredGLMM(lmer(Ramets_Sept ~ (1|Block) + (1|Population/Family) + City_dist,
  data = heights_both, REML = F))


### CROSSED RANDOM EFFECTS-----
lmer(Ramets_Sept ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
#  singular

car::Anova(lmer(Ramets_Sept ~ (1|Block) + (1|Population:Family) + City_dist,
  data = heights_both, REML = F), control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
# distance is significant


# ANy variation within families or populations?
m.1 <- lmer(Ramets_Sept ~ (1|Population/Family), data = heights_both, REML = T)

ranova(m.1)
# no
sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_SeptRamets_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_SeptRamets_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```

###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
lmer(Ramets_Sept ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F)
# is singular...

car::Anova(lmer(Ramets_Sept ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F))
# not significant


r.squaredGLMM(lmer(Ramets_Sept ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = heights_both, REML = F))


### CROSSED RANDOM EFFECTS-----
lmer(Ramets_Sept ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
#  singular

car::Anova(lmer(Ramets_Sept ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = heights_both, REML = F), control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
# not significant


```


##### Urban subtransects: ANOVA
###### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Ramets_Sept  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular

car::Anova(lmer(Ramets_Sept  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# distance significant


# Just main effects
car::Anova(lmer(Ramets_Sept  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# distance significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Ramets_Sept  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# No warnings!!

car::Anova(lmer(Ramets_Sept  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# distance significant


# Just main effects
car::Anova(lmer(Ramets_Sept  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# distance significant


AIC(lmer(Ramets_Sept  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Ramets_Sept  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best models" though just main effects lower AIC




# ANy variation among families or populations?
m.1 <- lmer(Ramets_Sept ~ (1|Population/Family), data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
ranova(m.1)
# no

m.2 <- lmer(Ramets_Sept ~ (1|Population/Family) + Transect_ID, data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F, control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))
car::Anova(m.2)
# not among transects 


m.3 <- lmer(Ramets_Sept ~ (1|Population/Family) + Transect_ID, data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = T)
car::Anova(m.3)
# not sig in this or m.2


sum.1 <- summary(m.1)

variances1 <- print(VarCorr(m.1),comp="Variance")
variances1 <- as.data.frame(variances1)
variances1 <- variances1 %>%
  dplyr::mutate(., PVE = vcov / sum(vcov)) %>%
  dplyr::select(., c(grp, vcov, PVE)) %>%
  dplyr::rename(., Group = grp,
                Variance = vcov)


write.table(ranova(m.1), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_SeptRamets_urban_lmer_PVE.csv", col.names=TRUE, sep=",")
write.table(variances1, "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_SeptRamets_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
write.table(car::Anova(m.2), "~/R_Projects/Chapter2_KSR/Figures_Tables/ranova_PVE/2020_SeptRamets_urban_lmer_PVE.csv", col.names=TRUE, sep=",", append=TRUE)
```


###### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
lmer(Ramets_Sept  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular

car::Anova(lmer(Ramets_Sept  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Ramets_Sept  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
lmer(Ramets_Sept  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F)
# singular

car::Anova(lmer(Ramets_Sept  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


# Just main effects
car::Anova(lmer(Ramets_Sept  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# nothing significant


AIC(lmer(Ramets_Sept  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))

AIC(lmer(Ramets_Sept  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
     data = heights_both %>% dplyr::filter(., Transect_ID != "Rural"), REML = F))
# AIC <2 apart; both "best models" though just main effects lower AIC

```

## Survival
### glmer
#### Entire gradient: ANOVA
##### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
glmer(dead_2020 ~ (1|Block) + (1|Population/Family) + City_dist,
  data = survival_2020,
  family = binomial(link = "logit")(link = "logit"),
  nAGQ=0,
  control=glmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
# CONVERGES when I set nAGQ to 0

car::Anova(glmer(dead_2020 ~ (1|Block) + (1|Population/Family) + City_dist,
  data = survival_2020,
  family = binomial(link = "logit")(link = "logit"),
  nAGQ=0,
  control=glmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5))))
# nothing significant



### CROSSED RANDOM EFFECTS-----
glmer(dead_2020 ~ (1|Block) + (1|Population:Family) + City_dist,
  data = survival_2020,
  family = binomial(link = "logit"),
  nAGQ=0,
  control=glmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
# no problems


car::Anova(glmer(dead_2020 ~ (1|Block) + (1|Population:Family) + City_dist,
  data = survival_2020,
  family = binomial(link = "logit"),
  nAGQ=0,
  control=glmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5))))
# nothing significant




# ranova(glmer(Flowered2020 ~ (1|Population/Family), data = reproductive, REML = T, family = binomial(link = "logit")))

# ranova(lmer(Flowered2020 ~ (1|Population/Family), data = reproductive, REML = T))
```

##### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################


### NESTED RANDOM EFFECTS-----
glmer(dead_2020 ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = survival_2020,
  family = binomial(link = "logit"),
  nAGQ=0,
  control=glmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
# CONVERGES when I set nAGQ to 0

car::Anova(glmer(dead_2020 ~ (1|Block) + (1|Population/Family) + Urb_score,
  data = survival_2020,
  family = binomial(link = "logit"),
  nAGQ=0,
  control=glmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5))))
# nothing significant



### CROSSED RANDOM EFFECTS-----
glmer(dead_2020 ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = survival_2020,
  family = binomial(link = "logit"),
  nAGQ=0,
  control=glmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
# no problems


car::Anova(glmer(dead_2020 ~ (1|Block) + (1|Population:Family) + Urb_score,
  data = survival_2020,
  family = binomial(link = "logit"),
  nAGQ=0,
  control=glmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5))))
# nothing significant


```


#### Urban subtransects: ANOVA
##### City_dist
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
glmer(dead_2020  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
  data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
# no problems!

car::Anova(glmer(dead_2020  ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
  data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


# Just main effects
car::Anova(glmer(dead_2020  ~ (1|Block) + (1|Population/Family) + City_dist + Transect_ID,
  data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
glmer(dead_2020  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
  data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
# No warnings

car::Anova(glmer(dead_2020  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
  data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


# Just main effects
car::Anova(glmer(dead_2020  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
                 data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
                 family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


AIC(glmer(dead_2020  ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
                 data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),        family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))

AIC(glmer(dead_2020  ~ (1|Block) + (1|Population:Family) + City_dist + Transect_ID,
                 data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),        family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# AIC <2 apart; both "best models" though just main effects lower AIC
```


##### Urb_score
```{r}
# NO DIFFERENCE BETWEEN MODELS W/ CROSSED VS NESTED RANDOM EFFECTS #
###################################################################

### NESTED RANDOM EFFECTS-----
# Full model
glmer(dead_2020  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
  data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
# no problems!

car::Anova(glmer(dead_2020  ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
  data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


# Just main effects
car::Anova(glmer(dead_2020  ~ (1|Block) + (1|Population/Family) + Urb_score + Transect_ID,
  data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant



### CROSSED RANDOM EFFECTS-----
# Full model
glmer(dead_2020  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
  data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
# No warnings

car::Anova(glmer(dead_2020  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
  data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
  family = binomial(link = "logit"),
  nAGQ=0,
  glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


# Just main effects
car::Anova(glmer(dead_2020  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
                 data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),
                 family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# nothing significant


AIC(glmer(dead_2020  ~ (1|Block) + (1|Population:Family) + Urb_score * Transect_ID,
                 data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),        family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))

AIC(glmer(dead_2020  ~ (1|Block) + (1|Population:Family) + Urb_score + Transect_ID,
                 data = survival_2020 %>% dplyr::filter(., Transect_ID != "Rural"),        family = binomial(link = "logit"),
                 nAGQ=0,
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000))))
# AIC <2 apart; both "best models" though just main effects lower AIC
```



# Figures
## make themes
```{r}
# Gradient
theme_gradient_1_init <-  theme_bw() +
  theme(text = element_text(size=12))

theme_gradient_1 <-  list(theme_gradient_1_init,
        geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2),
        scale_shape(solid = F),
        geom_smooth(size=0.75, method = lm, alpha=.15, se = T, color = 'black'),
        scale_shape_manual(values = c(1, 2, 5),
                           breaks = c("North", "South", "Rural"),
                           labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                           name = "Sample Site Subtransect"),
        scale_color_manual(values = c("black", "#333333", "#666666"),
                           breaks = c("North", "South", "Rural"),
                           labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                           name = "Sample Site Subtransect"))


# Urban subtransects
theme_urbansubs_1 <- list(theme_gradient_1_init,
                geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) ,
                scale_shape(solid = F),
                geom_smooth(aes(linetype = Transect_ID,
                                color = Transect_ID, fill = Transect_ID),
                            size=0.75, method = lm, alpha=.15, se = T) ,
                scale_shape_manual(values = c(1, 2),
                                   breaks = c("North", "South"),
                                   labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                                   name = "Sample Site Subtransect") ,
                scale_color_manual(values = c("red", "blue"),
                                   breaks = c("North", "South"),
                                   labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                                   name = "Sample Site Subtransect") ,
                scale_linetype_manual(values = c("solid", "dashed"),
                                   breaks = c("North", "South"),
                                   labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                                   name = "Sample Site Subtransect") ,
                scale_fill_manual(values = c("red", "blue"),
                                   breaks = c("North", "South"),
                                   labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                                   name = "Sample Site Subtransect"))
```

## reproductive
### Plants that flowered: Regressions
#### Percent flowering plants/pop
##### Entire gradient
```{r}
# City_dist
ggplot(flowered2020_popmeans, aes(x = City_dist, y = percent_flowered)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Percent Flowering Plants/Population") +
  theme_gradient_1

# Urb_score
ggplot(flowered2020_popmeans, aes(x = Urb_score, y = percent_flowered)) + 
  labs(x = "Urbanization Score", 
    y = "Percent Flowering Plants/Population") +
  theme_gradient_1 +
  scale_x_reverse()
```

##### Urban subtransects
```{r}
# City_dist
ggplot(flowered2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = percent_flowered)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Percent Flowering Plants/Population") +
  theme_urbansubs_1

# Urb_score
ggplot(flowered2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = percent_flowered)) + 
  labs(x = "Urbanization Score", 
    y = "Percent Flowering Plants/Population") +
  theme_urbansubs_1 +
  scale_x_reverse()

```


#### Mean flower count
##### Entire gradient
```{r}
ggplot(flowering_2020, aes(x = City_dist, y = mean_flower_count)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean flower count/inflorescence") +
  theme_gradient_1


ggplot(flowering_2020, aes(x = Urb_score, y = mean_flower_count)) + 
  labs(x = "Urbanization Score", 
    y = "Mean flower count/inflorescence") +
  theme_gradient_1 +
  scale_x_reverse()
```


##### Urban subtransects
```{r}
ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_flower_count)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean flower count/inflorescence") +
  theme_urbansubs_1

ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_flower_count)) + 
  labs(x = "Urbanization Score", 
    y = "Mean flower count/inflorescence") +
  theme_urbansubs_1 +
  scale_x_reverse()
```

#### Total flower count
##### Entire gradient
```{r}

ggplot(flowering_2020, aes(x = City_dist, y = total_flower_count)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Total flower count") +
  theme_gradient_1

ggplot(flowering_2020, aes(x = Urb_score, y = total_flower_count)) + 
  labs(x = "Urbanization Score", 
    y = "Total flower count") +
  theme_gradient_1 +
  scale_x_reverse()
```


##### Urban subtransects
```{r}
ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = total_flower_count)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Total flower count") +
  theme_urbansubs_1

ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = total_flower_count)) + 
  labs(x = "Urbanization Score", 
    y = "Total flower count") +
  theme_urbansubs_1+
  scale_x_reverse()

```


#### Mean flower size
##### Entire gradient
```{r}
ggplot(flowering_2020, aes(x = City_dist, y = Overall_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean flower size") +
  theme_gradient_1

ggplot(flowering_2020, aes(x = Urb_score, y = Overall_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean flower size") +
  theme_gradient_1 +
  scale_x_reverse()



# COMBINING INTO ONE FIGURE (do a PCA instead)
ggplot() + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean flower size") +
  geom_point(aes(x = City_dist, y = Overall_mean), size=2, color = 'orange', data = flowering_2020) +
  geom_point(aes(x = City_dist, y = Flower_mean), size=2, color = 'blue', data = flowering_2020) +
  geom_point(aes(x = City_dist, y = Corolla_mean), size=2, color = 'green', data = flowering_2020) +
  geom_point(aes(x = City_dist, y = Hood_mean), size=2, color = 'purple', data = flowering_2020) +
  # xlim(0, 71) +
  # ylim(0, 120) +
  geom_smooth(aes(x = City_dist, y = Overall_mean), size=0.75, method = lm, alpha=.15, se = T, data = flowering_2020) +
  geom_smooth(aes(x = City_dist, y = Flower_mean), size=0.75, method = lm, alpha=.15, se = T, data = flowering_2020) +
  geom_smooth(aes(x = City_dist, y = Corolla_mean), size=0.75, method = lm, alpha=.15, se = T, data = flowering_2020) +
  geom_smooth(aes(x = City_dist, y = Hood_mean), size=0.75, method = lm, alpha=.15, se = T, data = flowering_2020) +
  theme_bw() 
  # theme(text = element_text(size=12)) +
  # scale_shape_manual(values = c(21, 24),
  #                    breaks = c("June", "September"),
  #                      labels = c("June", "September"),
  #                      name = "Legend") +
  # scale_color_manual(values = c("blue", "orange"),
  #                    breaks = c("June", "September"),
  #                      labels = c("June", "September"),
  #                      name = "Legend") +
  # scale_fill_manual(values = c("blue", "orange"),
  #                    breaks = c("June", "September"),
  #                      labels = c("June", "September"),
  #                      name = "Legend")
```


##### Urban subtransects
```{r}
ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = Overall_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean flower size") +
  theme_urbansubs_1


ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = Overall_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean flower size") +
  theme_urbansubs_1 +
  scale_x_reverse()
```



### Plants that flowered: Boxplots
#### Mean flower count
##### Urban subtransects
```{r}
library(viridis)

flowering_2020 %>%
  filter(Transect_ID != "Rural") %>%
  ggplot( aes(x=Transect_ID, y=mean_flower_count, fill=Transect_ID)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=2, alpha=0.5) +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    xlab("")
```

#### Plants that flowered: Older figures (may not want to use)
```{r}

# Basic scatterplot 
ggplot(DC2_2020, aes(x=City_dist, y=Flowered2020)) +
  geom_jitter(aes(colour = Transect_ID, shape = Flowered2020))

# Basic bar graph
ggplot(DC2_flowering_2020, aes(x=Urb_Rur)) + 
  geom_bar(color = 'black', fill = 'grey' ) +
  ylim(0,24) +
  labs(x = "Sample Site Environment",
       y = "2020 Flowering Plants") +
  theme(legend.position = 'None',
        text = element_text(size=14),
        axis.text = element_text(size = 13)) 
# +  geom_text(aes(label=unique(Urb_Rur)), position=position_dodge(width=0.9))

## splitting subtransect
ggplot(DC2_flowering_2020, aes(x=Urb_Rur, fill=Transect_ID )) + 
  geom_bar( ) +
  ylim(0,24) +
  labs(x = "Sample Site Environment",
       y = "2020 Flowering Plants") +
  scale_fill_discrete(name  ="Sample Site Subtransect",
                      breaks = c("North", "South", "Rural"),
                      labels=c("Urban: Non-Corridor", "Urban: Corridor", "Rural"))


```

## Height
### Regressions
#### Each point is a population mean
##### Entire gradient
```{r}
# JUNE HEIGHT
## Multiple R-squared:  0.05561
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_height_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 60) 

ggplot(heights_both2020_popmeans, aes(x = Urb_score, y = mean_height_June)) + 
  labs(x = 'Urbanization Score', 
    y = "June: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 60) +
  scale_x_reverse()


# SEPT HEIGHT
# Multiple R-squared:  0.05979
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "September: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 120) 

ggplot(heights_both2020_popmeans, aes(x = Urb_score, y = mean_height_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "September: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 120) +
  scale_x_reverse()


# COMBINING INTO ONE FIGURE
ggplot() + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean height (cm)") +
  geom_point(aes(x = City_dist, y = mean_height_June, fill = 'June', shape = 'June'), size=2, data = heights_both2020_popmeans) +
  geom_point(aes(x = City_dist, y = mean_height_Sept, fill = 'September', shape = 'September' ), size=2, data = heights_both2020_popmeans) +
 # scale_shape(aes(x = City_dist, y = mean_height_June), solid = T, data = heights_both2020_popmeans)+
 # scale_shape(aes(x = City_dist, y = mean_height_Sept), solid = F, data = heights_both2020_popmeans)+
  xlim(0, 71) +
  ylim(0, 120) +
  geom_smooth(aes(x = City_dist, y = mean_height_June, fill = 'June', color = 'June'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  geom_smooth(aes(x = City_dist, y = mean_height_Sept, fill = 'September', color = 'September'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(21, 24),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_color_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_fill_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") 



ggplot() + 
  labs(x = "Urbanization Score", 
    y = "Mean height (cm)") +
  geom_point(aes(x = Urb_score, y = mean_height_June, fill = 'June', shape = 'June'), size=2, data = heights_both2020_popmeans) +
  geom_point(aes(x = Urb_score, y = mean_height_Sept, fill = 'September', shape = 'September' ), size=2, data = heights_both2020_popmeans) +
 # scale_shape(aes(x = City_dist, y = mean_height_June), solid = T, data = heights_both2020_popmeans)+
 # scale_shape(aes(x = City_dist, y = mean_height_Sept), solid = F, data = heights_both2020_popmeans)+
  # xlim(0, 71) +
  ylim(0, 120) +
  geom_smooth(aes(x = Urb_score, y = mean_height_June, fill = 'June', color = 'June'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  geom_smooth(aes(x = Urb_score, y = mean_height_Sept, fill = 'September', color = 'September'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(21, 24),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_color_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_fill_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_x_reverse()
```

##### Urban subtransects
```{r}
# JUNE HEIGHT
ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean height (cm)") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 60) 

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_height_June)) + 
  labs(x = "Urbanization Score", 
    y = "June: Mean height (cm)") +
  theme_urbansubs_1 +
  ylim(0, 60) +
  scale_x_reverse()



# sept HEIGHT
ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean height (cm)") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 120)

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_height_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "Sept: Mean height (cm)") +
  theme_urbansubs_1 +
  ylim(0, 120) +
  scale_x_reverse()

```

#### Each point is a family mean
##### Entire gradient
```{r}
# JUNE HEIGHT
## Multiple R-squared:  0.05561
ggplot(heights_both2020_familymeans, aes(x = City_dist, y = mean_height_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  xlim(0, 71) +
  ylim(0, 60) +
  geom_smooth(size=0.75, method = lm, alpha=.15, se = T, color = 'black') +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2, 5),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("black", "#333333", "#666666"),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") 



# SEPT HEIGHT
# Multiple R-squared:  0.05979
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "September: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  xlim(0, 71) +
  ylim(0, 120) +
  geom_smooth(size=0.75, method = lm, alpha=.15, se = T, color = 'black') +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2, 5),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("black", "#333333", "#666666"),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect")




# COMBINING INTO ONE FIGURE
ggplot() + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean height (cm)") +
  geom_point(aes(x = City_dist, y = mean_height_June, fill = 'June', shape = 'June'), size=2, data = heights_both2020_popmeans) +
  geom_point(aes(x = City_dist, y = mean_height_Sept, fill = 'September', shape = 'September' ), size=2, data = heights_both2020_popmeans) +
 # scale_shape(aes(x = City_dist, y = mean_height_June), solid = T, data = heights_both2020_popmeans)+
 # scale_shape(aes(x = City_dist, y = mean_height_Sept), solid = F, data = heights_both2020_popmeans)+
  xlim(0, 71) +
  ylim(0, 120) +
  geom_smooth(aes(x = City_dist, y = mean_height_June, fill = 'June', color = 'June'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  geom_smooth(aes(x = City_dist, y = mean_height_Sept, fill = 'September', color = 'September'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(21, 24),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_color_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_fill_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") 
```

##### Urban subtransects
```{r}
# JUNE HEIGHT

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  geom_smooth(aes(linetype = Transect_ID, color = Transect_ID, fill = Transect_ID),size=0.75, method = lm, alpha=.15, se = T) +
  xlim(0, 35) +
  ylim(0, 60) +
  theme_bw() +
  theme(text = element_text(size=12),
        legend.position = 'none') +
  scale_shape_manual(values = c(1, 2),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_linetype_manual(values = c("solid", "dashed"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_fill_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect")



# sept HEIGHT

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  geom_smooth(aes(linetype = Transect_ID, color = Transect_ID, fill = Transect_ID),size=0.75, method = lm, alpha=.15, se = T) +
  xlim(0, 35) +
  ylim(0, 120) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_linetype_manual(values = c("solid", "dashed"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_fill_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect")
```



## Weevil damage
### Standardized by June height
#### Regressions
##### Entire gradient
```{r}
# Multiple R-squared: 0.0008
ggplot(weevil_both2020_popmeans, aes(x = City_dist, y = mean_scar_div_Juneheight)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Weevil scar length/cm") +
  theme_gradient_1


ggplot(weevil_both2020_popmeans, aes(x = Urb_score, y = mean_scar_div_Juneheight)) + 
  labs(x = 'Urbanization Score', 
    y = "Weevil scar length/cm") +
  theme_gradient_1 +
  scale_x_reverse()

```

##### Urban subtransects
```{r}

# R-squared = 0.04079
ggplot(weevil_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_scar_div_Juneheight)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Weevil scar length/cm") +
  theme_urbansubs_1 +
  ylim(0, 0.2) 


ggplot(weevil_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_scar_div_Juneheight)) + 
  labs(x = "Urbanization Score", 
    y = "Weevil scar length/cm") +
  theme_urbansubs_1 +
  ylim(0, 0.2) +
  scale_x_reverse()
```

### NOT Standardized by June height
#### Regressions
##### Entire gradient
```{r}
# Multiple R-squared: 0.003591
ggplot(weevil_both2020_popmeans, aes(x = City_dist, y = mean_scar)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Total weevil scar length") +
  theme_gradient_1

ggplot(weevil_both2020_popmeans, aes(x = Urb_score, y = mean_scar)) + 
  labs(x = "Urbanization Score", 
    y = "Total weevil scar length") +
  theme_gradient_1 +
  scale_x_reverse()
```

##### Urban subtransects
```{r}
ggplot(weevil_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_scar)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Total weevil scar length") +
  theme_urbansubs_1

ggplot(weevil_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_scar)) + 
  labs(x = "Urbanization Score", 
    y = "Total weevil scar length") +
  theme_urbansubs_1+
  scale_x_reverse()
```

## Herbivory
### Regressions
#### Entire gradient
```{r}
# JULY HERBIVORY
## NO TRANSFORMATIONS OR OUTLIERS REMOVED-----
## Multiple R-squared: 0.08834
ggplot(herbivory2020_popmeans, aes(x = City_dist, y = Herbivory.July_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 15) 

ggplot(herbivory2020_popmeans, aes(x = Urb_score, y = Herbivory.July_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean Herbivory") +
  theme_gradient_1 +
  ylim(0, 15) +
  scale_x_reverse()



# SEPT HEIGHT-----
# Multiple R-squared:  0.01975
ggplot(herbivory2020_popmeans, aes(x = City_dist, y = Herbivory.Sept_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(herbivory2020_popmeans, aes(x = Urb_score, y = Herbivory.Sept_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean Herbivory") +
  theme_gradient_1 +
  xlim(0, 71) +
  scale_x_reverse()


# COMBINING INTO ONE FIGURE-----
ggplot() + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  geom_point(aes(x = City_dist, y = Herbivory.July_mean, fill = 'July', shape = 'July'), size=2, data = herbivory2020_popmeans) +
  geom_point(aes(x = City_dist, y = Herbivory.Sept_mean, fill = 'September', shape = 'September' ), size=2, data = herbivory2020_popmeans) +
 # scale_shape(aes(x = City_dist, y = mean_height_June), solid = T, data = heights_both2020_popmeans)+
 # scale_shape(aes(x = City_dist, y = mean_height_Sept), solid = F, data = heights_both2020_popmeans)+
  xlim(0, 71) +
  # ylim(0, 120) +
  geom_smooth(aes(x = City_dist, y = Herbivory.July_mean, fill = 'July', color = 'July'), size=0.75, method = lm, alpha=.15, se = T, data = herbivory2020_popmeans) +
  geom_smooth(aes(x = City_dist, y = Herbivory.Sept_mean, fill = 'September', color = 'September'), size=0.75, method = lm, alpha=.15, se = T, data = herbivory2020_popmeans) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(21, 24),
                     breaks = c("July", "September"),
                       labels = c("July", "September"),
                       name = "Legend") +
  scale_color_manual(values = c("blue", "orange"),
                     breaks = c("July", "September"),
                       labels = c("July", "September"),
                       name = "Legend") +
  scale_fill_manual(values = c("blue", "orange"),
                     breaks = c("July", "September"),
                       labels = c("July", "September"),
                       name = "Legend") 
```

#### Urban subtransects
```{r}
# JULY HERBIVORY
ggplot(herbivory2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = Herbivory.July_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 15) 

ggplot(herbivory2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = Herbivory.July_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean Herbivory") +
  theme_urbansubs_1 +
  ylim(0, 15) +
  scale_x_reverse()


# sept herbivory
ggplot(herbivory2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = Herbivory.Sept_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 40)    

ggplot(herbivory2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = Herbivory.Sept_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean Herbivory") +
  theme_urbansubs_1 +
  ylim(0, 40) +
  scale_x_reverse()

```


## No. of Ramets
### Regressions
#### Each point is a population mean
##### Entire gradient
```{r}
# JUNE RAMETS
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_Ramets_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean No. Ramets") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 5)

ggplot(heights_both2020_popmeans, aes(x = Urb_score, y = mean_Ramets_June)) + 
  labs(x = "Urbanization Score", 
    y = "June: Mean No. Ramets") +
  theme_gradient_1 +
  ylim(0, 5) +
  scale_x_reverse()


# SEPT ramets
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_Ramets_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "September: Mean No. Ramets") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 4) 

ggplot(heights_both2020_popmeans, aes(x = Urb_score, y = mean_Ramets_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "September: Mean No. Ramets") +
  theme_gradient_1 +
  ylim(0, 4) +
  scale_x_reverse()


# COMBINING INTO ONE FIGURE
ggplot() + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean No. Ramets") +
  geom_point(aes(x = City_dist, y = mean_Ramets_June, fill = 'June', shape = 'June'), size=2, data = heights_both2020_popmeans) +
  geom_point(aes(x = City_dist, y = mean_Ramets_Sept, fill = 'September', shape = 'September' ), size=2, data = heights_both2020_popmeans) +
 # scale_shape(aes(x = City_dist, y = mean_height_June), solid = T, data = heights_both2020_popmeans)+
 # scale_shape(aes(x = City_dist, y = mean_height_Sept), solid = F, data = heights_both2020_popmeans)+
  xlim(0, 71) +
  ylim(0, 5) +
  geom_smooth(aes(x = City_dist, y = mean_Ramets_June, fill = 'June', color = 'June'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  geom_smooth(aes(x = City_dist, y = mean_Ramets_Sept, fill = 'September', color = 'September'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(21, 24),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_color_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_fill_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") 
```

##### Urban subtransects
```{r}
# JUNE ramets
p1 <- ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_Ramets_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean No. Ramets") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 4.2) 

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_Ramets_June)) + 
  labs(x = "Urbanization Score", 
    y = "June: Mean No. Ramets") +
  theme_urbansubs_1 +
  ylim(0, 4.2) +
  scale_x_reverse()


# sept ramets
p2 <- ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_Ramets_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean No. Ramets") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 4)

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_Ramets_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "Sept: Mean No. Ramets") +
  theme_urbansubs_1 +
  ylim(0, 4)+
  scale_x_reverse()



library(patchwork)
p1 + p2
```

#### Each point is a family mean
##### Entire gradient
```{r}
# JUNE HEIGHT
ggplot(ramets_2020_familymeans_stats, aes(x = City_dist, y = Ramets_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean No. Ramets") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=1.5) +
  scale_shape(solid = F)+
  geom_errorbar(aes(ymin=Ramets_June-se.June, ymax=Ramets_June+se.June), width = 0.25) +
  xlim(0, 71) +
  ylim(0, 8) +
  geom_smooth(size=0.75, method = lm, alpha=.15, se = T, color = 'black') +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2, 5),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("black", "#333333", "#666666"),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") 


# SEPT HEIGHT
ggplot(ramets_2020_familymeans_stats, aes(x = City_dist, y = Ramets_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean No. Ramets") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=1.5) +
  scale_shape(solid = F)+
  geom_errorbar(aes(ymin=Ramets_June-se.Sept, ymax=Ramets_June+se.Sept), width = 0.25) +
  xlim(0, 71) +
  ylim(0, 8) +
  geom_smooth(size=0.75, method = lm, alpha=.15, se = T, color = 'black') +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2, 5),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("black", "#333333", "#666666"),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") 

```

##### Urban subtransects
```{r}
# JUNE HEIGHT

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  geom_smooth(aes(linetype = Transect_ID, color = Transect_ID, fill = Transect_ID),size=0.75, method = lm, alpha=.15, se = T) +
  xlim(0, 35) +
  ylim(0, 60) +
  theme_bw() +
  theme(text = element_text(size=12),
        legend.position = 'none') +
  scale_shape_manual(values = c(1, 2),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_linetype_manual(values = c("solid", "dashed"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_fill_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect")



# sept HEIGHT

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  geom_smooth(aes(linetype = Transect_ID, color = Transect_ID, fill = Transect_ID),size=0.75, method = lm, alpha=.15, se = T) +
  xlim(0, 35) +
  ylim(0, 120) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_linetype_manual(values = c("solid", "dashed"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_fill_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect")
```



## Growth rate
### Regressions
#### Entire gradient
```{r}
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_rel_growth_rate)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Relative Growth Rate") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(-0.01, 0.015) 

ggplot(heights_both2020_popmeans, aes(x = Urb_score, y = mean_rel_growth_rate)) + 
  labs(x = "Urbanization Score", 
    y = "Relative Growth Rate") +
  theme_gradient_1 +
  ylim(-0.01, 0.015)+
  scale_x_reverse()


```

#### Urban subtransects
```{r}
ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_rel_growth_rate)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Relative Growth Rate") +
  theme_urbansubs_1 +
  xlim(0, 35) 

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_rel_growth_rate)) + 
  labs(x = "Urbanization Score", 
    y = "Relative Growth Rate") +
  theme_urbansubs_1 +
  scale_x_reverse()
```

## Survival
### Regressions
#### Entire gradient
```{r}
ggplot(survival2020_popmeans, aes(x = City_dist, y = survival_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mortality") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(survival2020_popmeans, aes(x = Urb_score, y = survival_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mortality") +
  theme_gradient_1 +
  scale_x_reverse()

```

#### Urban subtransects
```{r}
ggplot(survival2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = survival_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mortality") +
  theme_urbansubs_1 +
  xlim(0, 35) 

ggplot(survival2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = survival_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mortality") +
  theme_urbansubs_1 +
  scale_x_reverse()
```
