---
title: "KSR_2020"
author: "Sophie Breitbart"
output:
  html_document:
    number_sections: true
    df_print: paged
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
editor_options: 
  chunk_output_type: console


WHEN TOTALLY DONE, type this:
renv::activate()
renv::snapshot()

---
# Set up notebook
## Load packages
```{r}
library(dplyr)
library(reshape)
library(reshape2)
library(DHARMa)
library(flextable)
library(glmmTMB)
library(redres)
library(tidyr)
library(broom.mixed)
library(tidyverse)
library(readxl)
library(broom)
library(knitr)
library(ggplot2)
library(ggExtra)
library("ggpubr")
library(devtools)
library(rpart)
library("tibble", lib.loc="~/R/win-library/3.5")
library(ISLR)
library(MASS)
library(car)
library(data.table)
library(plyr)
library(dplyr)
library(MuMIn)
library(ggplot2)
library(gridExtra)
library(Hmisc)
library(lme4)
library(nlme)
library(reshape)
library(lmerTest)
library(tidyverse)
library(vegan)
library(lindia)
library(e1071)
library(ggpubr)
library(forcats)
library(car)
library(multcomp)
library(lsmeans)
library(ggbiplot)
library(ggplot2)
require(MASS)
require(scales)
require(car)
require(ggplot2)
require(ggiraph)
require(ggiraphExtra)
library(geosphere)
library(vctrs)
library(here)
library(stringi)
```

## Import data
```{r}
# 2019 data-----
data_clean_2019 <- read.csv(here::here("./CommonGardenExperiment_2019Data/clean_data/clean_data_2019KSR.csv"), na.strings=c("NO PLANT", "none"), blank.lines.skip=TRUE, header=TRUE, sep=",") %>%
  dplyr::select(., -c(1:2))

# 2020 data-----
heights_both_2020 <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_heights_clean.csv")) %>%
  dplyr::select(., -c(1:2))

herbivory_both_2020 <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_herbivory_clean.csv")) %>%
  dplyr::select(., -c(1:2))

survival_2020 <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_survival_clean.csv")) %>%
  dplyr::select(., -c(1:2))

weevil_both <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_weevil_damage_clean.csv")) %>%
  dplyr::select(., -c(1:2))

reproductive <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_reproductive_clean.csv")) %>%
  dplyr::select(., -c(1:2))

flowering_2020 <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_floweringplants_clean.csv")) %>%
  dplyr::select(., -c(1:2))
```

## Make combined 2019/2020 dfs
```{r}
# heights (includes heights and num. ramets)-----
## first make copy of data_clean_2019 with colnames that match heights_both_2020's
heights_2019 <- data_clean_2019 %>%
  dplyr::select(., c(1:6, 11:13, 18:19, 25:41)) %>%
  dplyr::filter(., Dead_2019 == 0) %>%
  dplyr::rename(., Dead = Dead_2019,
                Ramets_midJune = Num_Ramets_DC2, # doing this & following rows to compare btwn years
                Ramets_Sept = Num_Ramets_DC3, 
                Total_Height_midJune = Total_Height_DC2,
                Total_Height_Sept = Total_height_DC3) 
heights_2019$Year = 2019
heights_2019$rel_growth_rate <- as.character(heights_2019$rel_growth_rate)
heights_2019$rel_growth_rate <- as.numeric(heights_2019$rel_growth_rate)


# copy of 2020 data w/colnames that match 2019's
heights_2020 <- heights_both_2020 %>%
  dplyr::select(., -c(16)) %>%
  dplyr::rename(., Ramets_midJune = Ramets_June, # doing this & following rows to compare btwn years
                Total_Height_midJune = Total_Height_June) 
heights_2020$Year = 2020

# combine yearly dfs
heights_19_20 <- rbind.fill(heights_2019, heights_2020)
heights_19_20$Year <- as.factor(heights_19_20$Year)
heights_19_20$Family <- as.factor(heights_19_20$Family)
heights_19_20$Population <- as.factor(heights_19_20$Population)
heights_19_20$rel_growth_rate <- as.numeric(heights_19_20$rel_growth_rate)

# rm(heights_2019, heights_2020)

heights_19_20$Population <- as.factor(heights_19_20$Population)
heights_19_20$Family <- as.factor(heights_19_20$Family)




# herbivory-----
## first make copy of data_clean_2019 with colnames that match heights_both_2020's
herb_2019 <- data_clean_2019 %>%
  dplyr::select(., c(1:6, 18:19, 21, 32, 35:41)) %>%
  dplyr::filter(., Dead_2019 == 0) %>%
  dplyr::rename(., Dead = Dead_2019,
                Herbivory_mean_Sept = Herbivory_mean_DC3 # doing this to compare btwn years
                ) 
herb_2019$Year = 2019
herb_2019$Herbivory_mean_Sept <- as.character(herb_2019$Herbivory_mean_Sept)
herb_2019$Herbivory_mean_Sept <- as.numeric(herb_2019$Herbivory_mean_Sept)

# copy of 2020 data w/colnames that match 2019's
herb_2020 <- herbivory_both_2020 %>%
  dplyr::select(., -c(18)) %>%
  dplyr::rename(., Herbivory_mean_Sept = Herbivory.Sept_mean # doing thisto compare btwn years
                ) 
herb_2020$Year = 2020

# combine yearly dfs
herbivory_19_20 <- rbind.fill(herb_2019, herb_2020)

# rm(herb_2019, herb_2020)

herbivory_19_20$Population <- as.factor(herbivory_19_20$Population)
herbivory_19_20$Family <- as.factor(herbivory_19_20$Family)





# survival-----

## first make copy of data_clean_2019 with colnames that match heights_both_2020's
surv_2019 <- data_clean_2019 %>%
  dplyr::select(., c(1:6, 14:16, 25, 32, 35:41)) %>%
  dplyr::rename(., Dead = Dead_2019                ) 
surv_2019$Year = 2019

# copy of 2020 data w/colnames that match 2019's
surv_2020 <- survival_2020 %>%
  dplyr::select(., -c(12)) %>%
  dplyr::rename(., Dead = dead_2020 # doing thisto compare btwn years
                ) 
surv_2020$Year = 2020

# combine yearly dfs
survival_19_20 <- rbind.fill(surv_2019, surv_2020)

# rm(surv_2019, surv_2020)

survival_19_20$Population <- as.factor(survival_19_20$Population)
survival_19_20$Family <- as.factor(survival_19_20$Family)
survival_19_20$Block <- as.factor(survival_19_20$Block)
survival_19_20$Year <- as.factor(survival_19_20$Year)


```

# Find family & population means
## reproductive
### Binary: flowering success
```{r}

# Find family means
flowered2020_familymeans <- reproductive  %>%
  dplyr::select(., c(2:7, 10, 14, 16:18)) %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      sum_flowered_indivs = sum(as.integer(Flowered2020)),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())


# Find population means
flowered2020_popmeans <- flowered2020_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      sum_flowered_indivs = sum(as.integer(sum_flowered_indivs)),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score)) %>%
  as.data.frame(flowered2020_popmeans) %>%
  
# add percent flowered column
  dplyr::mutate(., percent_flowered = sum_flowered_indivs / sum_replicates)

# remove pops with only 1 rep?




# Use SummarySE to get stats per family & population

### NOT TRANSFORMED
# SSE_fams_height_2020 <- summarySE(DC7_2020_heights, measurevar="Total_Height", groupvars=c("Population", "Family"), na.rm=TRUE)
# SSE_fams_height_2020 <- merge(x = SSE_fams_height_2020, y = Distances, by = "Population", all.x = TRUE)
# 
# SSE_pops_height_2020 <- summarySE(SSE_fams_height_2020, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)
# ## removing pops with only 1 representative (4 pops)
# SSE_pops_height_2020 <- merge(x = SSE_pops_height_2020 %>% filter(N > 1), y = Distances, by = "Population", all.x = TRUE)


```



## Height
### 2019
```{r}

# Find family means
heights_both2019_familymeans <- heights_2019 %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      sum_height_earlyJune = sum(Total_Height_DC1),
      sum_height_midJune = sum(Total_Height_midJune),
      sum_height_Sept = sum(Total_Height_Sept),
      mean_Ramets_earlyJune = mean(Num_Ramets_DC1),
      mean_Ramets_midJune = mean(Ramets_midJune),
      mean_Ramets_Sept = mean(Ramets_Sept),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      mean_rel_growth_rate = mean(rel_growth_rate, na.rm = TRUE),
      Urb_score = first(Urb_score),
      nPlants=n())
## divide total height by num. plants/pop
heights_both2019_familymeans$mean_height_midJune <- heights_both2019_familymeans$sum_height_midJune / heights_both2019_familymeans$sum_replicates

heights_both2019_familymeans$mean_height_earlyJune <- heights_both2019_familymeans$sum_height_earlyJune / heights_both2019_familymeans$sum_replicates

heights_both2019_familymeans$mean_height_Sept <- heights_both2019_familymeans$sum_height_Sept / heights_both2019_familymeans$sum_replicates


# Find population means
heights_both2019_popmeans <- heights_both2019_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      sum_height_earlyJune = sum(sum_height_earlyJune),
      sum_height_midJune = sum(sum_height_midJune),
      sum_height_Sept = sum(sum_height_Sept),
      mean_Ramets_earlyJune = mean(mean_Ramets_earlyJune),
      mean_Ramets_midJune = mean(mean_Ramets_midJune),
      mean_Ramets_Sept = mean(mean_Ramets_Sept),
      mean_height_earlyJune = mean(mean_height_earlyJune),
      mean_height_midJune = mean(mean_height_midJune),
      mean_height_Sept = mean(mean_height_Sept),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      mean_rel_growth_rate = mean(mean_rel_growth_rate))


```



### 2020
```{r}

# Find family means
heights_both2020_familymeans <- heights_both_2020 %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      sum_height_June = sum(Total_Height_June),
      sum_height_Sept = sum(Total_Height_Sept),
      mean_Ramets_June = mean(Ramets_June),
      mean_Ramets_Sept = mean(Ramets_Sept),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      mean_rel_growth_rate = mean(rel_growth_rate),
      Urb_score = first(Urb_score),
      nPlants=n())
## divide total height by num. plants/pop
heights_both2020_familymeans$mean_height_June <- heights_both2020_familymeans$sum_height_June / heights_both2020_familymeans$sum_replicates

heights_both2020_familymeans$mean_height_Sept <- heights_both2020_familymeans$sum_height_Sept / heights_both2020_familymeans$sum_replicates


# Find population means
heights_both2020_popmeans <- heights_both2020_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      sum_height_June = sum(sum_height_June),
      sum_height_Sept = sum(sum_height_Sept),
      mean_Ramets_June = mean(mean_Ramets_June),
      mean_Ramets_Sept = mean(mean_Ramets_Sept),
      mean_height_June = mean(mean_height_June),
      mean_height_Sept = mean(mean_height_Sept),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      mean_rel_growth_rate = mean(mean_rel_growth_rate))



# # Use SummarySE to get stats per family & population
# ## HEIGHTS
# intermediate1 <- summarySE(heights_both_2020, measurevar="Total_Height_June", groupvars=c("Population", "Family"), na.rm=TRUE)
# 
# intermediate2 <- summarySE(heights_both_2020, measurevar="Total_Height_Sept", groupvars=c("Population", "Family"), na.rm=TRUE)
# 
# heights_2020_familymeans_stats <- left_join(intermediate1, intermediate2, by = c("Population", "Family"), suffix = c(".July", ".Sept"))
# 
# 
# # Use SummarySE to get stats per family & population
# ## no. ramets
# intermediate1 <- summarySE(heights_both_2020, measurevar="Ramets_June", groupvars=c("Population", "Family"), na.rm=TRUE)
# 
# intermediate2 <- summarySE(heights_both_2020, measurevar="Ramets_Sept", groupvars=c("Population", "Family"), na.rm=TRUE)
# 
# ramets_2020_familymeans_stats <- left_join(intermediate1, intermediate2, by = c("Population", "Family"), suffix = c(".June", ".Sept"))
# 
# # Add transect data via merge
# ramets_2020_familymeans_stats <- merge(ramets_2020_familymeans_stats, Distances, by = "Population", all.x = TRUE)
# 
# 
# 
# # SSE_pops_height_2020 <- summarySE(intermediates, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)

```


## Weevil scar lengths
```{r}
# Find family means
weevil_both2020_familymeans <- weevil_both %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      mean_scar_div_Juneheight = mean(scar_div_Juneheight, na.rm = TRUE),
      mean_scar = mean(Scar_length_cm),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())


# Find population means
weevil_both2020_popmeans <- weevil_both2020_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      mean_scar_div_Juneheight = mean(mean_scar_div_Juneheight, na.rm = TRUE),
      mean_scar = mean(mean_scar),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score))



# Use SummarySE to get stats per family & population

### NOT TRANSFORMED
# SSE_fams_height_2020 <- summarySE(DC7_2020_heights, measurevar="Total_Height", groupvars=c("Population", "Family"), na.rm=TRUE)
# SSE_fams_height_2020 <- merge(x = SSE_fams_height_2020, y = Distances, by = "Population", all.x = TRUE)
# 
# SSE_pops_height_2020 <- summarySE(SSE_fams_height_2020, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)
# ## removing pops with only 1 representative (4 pops)
# SSE_pops_height_2020 <- merge(x = SSE_pops_height_2020 %>% filter(N > 1), y = Distances, by = "Population", all.x = TRUE)


```
## Herbivory
### 2019
```{r}
# Find family means
herbivory2019_familymeans <- herb_2019 %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      Herbivory.Sept_mean = mean(Herbivory_mean_Sept, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())
herbivory2019_familymeans <- as.data.frame(herbivory2019_familymeans)


# Find population means
herbivory2019_popmeans <- herbivory2019_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      Herbivory.Sept_mean = mean(Herbivory.Sept_mean, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score))
herbivory2019_popmeans <- as.data.frame(herbivory2019_popmeans)

```

### 2020
```{r}
# Find family means
herbivory2020_familymeans <- herbivory_both_2020 %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      Herbivory.July_mean = mean(Herbivory.July_mean, na.rm = T),
      Herbivory.Sept_mean = mean(Herbivory.Sept_mean, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())
herbivory2020_familymeans <- as.data.frame(herbivory2020_familymeans)


# Find population means
herbivory2020_popmeans <- herbivory2020_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      Herbivory.July_mean = mean(Herbivory.July_mean, na.rm = T),
      Herbivory.Sept_mean = mean(Herbivory.Sept_mean, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score))
herbivory2020_popmeans <- as.data.frame(herbivory2020_popmeans)


# Use SummarySE to get stats per family & population

### NOT TRANSFORMED
# SSE_fams_height_2020 <- summarySE(DC7_2020_heights, measurevar="Total_Height", groupvars=c("Population", "Family"), na.rm=TRUE)
# SSE_fams_height_2020 <- merge(x = SSE_fams_height_2020, y = Distances, by = "Population", all.x = TRUE)
# 
# SSE_pops_height_2020 <- summarySE(SSE_fams_height_2020, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)
# ## removing pops with only 1 representative (4 pops)
# SSE_pops_height_2020 <- merge(x = SSE_pops_height_2020 %>% filter(N > 1), y = Distances, by = "Population", all.x = TRUE)


```


## Survival
### 2019
```{r}
# Find family means
survival2019_familymeans <- surv_2019 %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      survival_mean = mean(Dead, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())
survival2019_familymeans <- as.data.frame(survival2019_familymeans)


# Find population means
survival2019_popmeans <- survival2019_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      survival_mean = mean(survival_mean, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score))
survival2019_popmeans <- as.data.frame(survival2019_popmeans)

```


### 2020
```{r}
# Find family means
survival2020_familymeans <- survival_2020 %>%
  group_by(Population, Family) %>%
    dplyr::summarise(
      sum_replicates = n_distinct(Replicate),
      survival_mean = mean(dead_2020, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score),
      nPlants=n())
survival2020_familymeans <- as.data.frame(survival2020_familymeans)


# Find population means
survival2020_popmeans <- survival2020_familymeans %>%
  group_by(Population) %>%
    dplyr::summarise(
      sum_replicates = sum(sum_replicates),
      survival_mean = mean(survival_mean, na.rm = T),
      City_dist = first(City_dist),
      Transect_ID = first(Transect_ID),
      Urb_score = first(Urb_score))
survival2020_popmeans <- as.data.frame(survival2020_popmeans)


# Use SummarySE to get stats per family & population

### NOT TRANSFORMED
# SSE_fams_height_2020 <- summarySE(DC7_2020_heights, measurevar="Total_Height", groupvars=c("Population", "Family"), na.rm=TRUE)
# SSE_fams_height_2020 <- merge(x = SSE_fams_height_2020, y = Distances, by = "Population", all.x = TRUE)
# 
# SSE_pops_height_2020 <- summarySE(SSE_fams_height_2020, measurevar="Total_Height", groupvars=c("Population"), na.rm=TRUE)
# ## removing pops with only 1 representative (4 pops)
# SSE_pops_height_2020 <- merge(x = SSE_pops_height_2020 %>% filter(N > 1), y = Distances, by = "Population", all.x = TRUE)


```

# Figures: 2019
## Height
### Regressions
#### Each point is a population mean
##### Entire gradient
```{r}
# JUNE HEIGHT- 1
ggplot(heights_both2019_popmeans, aes(x = City_dist, y = mean_height_earlyJune)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Early June: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(heights_both2019_popmeans, aes(x = Urb_score, y = mean_height_earlyJune)) + 
  labs(x = 'Urbanization Score', 
    y = "Early June: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  scale_x_reverse()

# JUNE HEIGHT- 2
ggplot(heights_both2019_popmeans, aes(x = City_dist, y = mean_height_midJune)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mid-June: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(heights_both2019_popmeans, aes(x = Urb_score, y = mean_height_midJune)) + 
  labs(x = 'Urbanization Score', 
    y = "Mid-June: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  scale_x_reverse()


# SEPT HEIGHT
ggplot(heights_both2019_popmeans, aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "September: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(heights_both2019_popmeans, aes(x = Urb_score, y = mean_height_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "September: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  scale_x_reverse()

```

##### Urban subtransects
```{r}
# JUNE HEIGHT- 1
ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_earlyJune)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Early June: Mean height (cm)") +
  theme_urbansubs_1 +
  xlim(0, 35) 

ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_height_earlyJune)) + 
  labs(x = "Urbanization Score", 
    y = "Early June: Mean height (cm)") +
  theme_urbansubs_1 +
  scale_x_reverse()

# JUNE HEIGHT- 2
ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_midJune)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mid-June: Mean height (cm)") +
  theme_urbansubs_1 +
  xlim(0, 35) 

ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_height_midJune)) + 
  labs(x = "Urbanization Score", 
    y = "Mid-June: Mean height (cm)") +
  theme_urbansubs_1 +
  scale_x_reverse()

# sept HEIGHT
ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean height (cm)") +
  theme_urbansubs_1 +
  xlim(0, 35) 

ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_height_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "Sept: Mean height (cm)") +
  theme_urbansubs_1 +
  scale_x_reverse()

```

## No. of Ramets
### Regressions
#### Each point is a population mean
##### Entire gradient
```{r}
# JUNE RAMETS-1 
ggplot(heights_both2019_popmeans, aes(x = City_dist, y = mean_Ramets_earlyJune)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Early June: Mean No. Ramets") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(heights_both2019_popmeans, aes(x = Urb_score, y = mean_Ramets_earlyJune)) + 
  labs(x = "Urbanization Score", 
    y = "Early June: Mean No. Ramets") +
  theme_gradient_1 +
  scale_x_reverse()


# JUNE RAMETS-2
ggplot(heights_both2019_popmeans, aes(x = City_dist, y = mean_Ramets_midJune)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mid-June: Mean No. Ramets") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(heights_both2019_popmeans, aes(x = Urb_score, y = mean_Ramets_midJune)) + 
  labs(x = "Urbanization Score", 
    y = "Mid-June: Mean No. Ramets") +
  theme_gradient_1 +
  scale_x_reverse()


# SEPT ramets
ggplot(heights_both2019_popmeans, aes(x = City_dist, y = mean_Ramets_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "September: Mean No. Ramets") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(heights_both2019_popmeans, aes(x = Urb_score, y = mean_Ramets_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "September: Mean No. Ramets") +
  theme_gradient_1 +
  scale_x_reverse()


```

##### Urban subtransects
```{r}
# JUNE ramets- 1
ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_Ramets_earlyJune)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Early June: Mean No. Ramets") +
  theme_urbansubs_1 +
  xlim(0, 35)  

ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_Ramets_earlyJune)) + 
  labs(x = "Urbanization Score", 
    y = "Early June: Mean No. Ramets") +
  theme_urbansubs_1 +
  scale_x_reverse()


# JUNE ramets- 2
ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_Ramets_midJune)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mid-June: Mean No. Ramets") +
  theme_urbansubs_1 +
  xlim(0, 35)  

ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_Ramets_midJune)) + 
  labs(x = "Urbanization Score", 
    y = "Mid-June: Mean No. Ramets") +
  theme_urbansubs_1 +
  scale_x_reverse()


# sept ramets
ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_Ramets_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean No. Ramets") +
  theme_urbansubs_1 +
  xlim(0, 35) 

ggplot(heights_both2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_Ramets_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "Sept: Mean No. Ramets") +
  theme_urbansubs_1 +
  scale_x_reverse()


```

## Herbivory
### Regressions
#### Entire gradient
```{r}
ggplot(herbivory2019_popmeans, aes(x = City_dist, y = Herbivory.Sept_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(herbivory2019_popmeans, aes(x = Urb_score, y = Herbivory.Sept_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean Herbivory") +
  theme_gradient_1 +
  xlim(0, 71) +
  scale_x_reverse()

```

#### Urban subtransects
```{r}
# sept herbivory
ggplot(herbivory2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = Herbivory.Sept_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  theme_urbansubs_1 +
  xlim(0, 35)    

ggplot(herbivory2019_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = Herbivory.Sept_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean Herbivory") +
  theme_urbansubs_1 +
  scale_x_reverse()

```

## Survival
Not putting anything here yet... I think I'd have to make a logistic regression plot?
# Figures: 2020
## make themes
```{r}
# Gradient
theme_gradient_1_init <-  theme_bw() +
  theme(text = element_text(size=12))

theme_gradient_1 <-  list(theme_gradient_1_init,
        geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2),
        scale_shape(solid = F),
        geom_smooth(size=0.75, method = lm, alpha=.15, se = T, color = 'black'),
        scale_shape_manual(values = c(1, 2, 5),
                           breaks = c("North", "South", "Rural"),
                           labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                           name = "Sample Site Subtransect"),
        scale_color_manual(values = c("black", "#333333", "#666666"),
                           breaks = c("North", "South", "Rural"),
                           labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                           name = "Sample Site Subtransect"))


# Urban subtransects
theme_urbansubs_1 <- list(theme_gradient_1_init,
                geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) ,
                scale_shape(solid = F),
                geom_smooth(aes(linetype = Transect_ID,
                                color = Transect_ID, fill = Transect_ID),
                            size=0.75, method = lm, alpha=.15, se = T) ,
                scale_shape_manual(values = c(1, 2),
                                   breaks = c("North", "South"),
                                   labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                                   name = "Sample Site Subtransect") ,
                scale_color_manual(values = c("red", "blue"),
                                   breaks = c("North", "South"),
                                   labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                                   name = "Sample Site Subtransect") ,
                scale_linetype_manual(values = c("solid", "dashed"),
                                   breaks = c("North", "South"),
                                   labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                                   name = "Sample Site Subtransect") ,
                scale_fill_manual(values = c("red", "blue"),
                                   breaks = c("North", "South"),
                                   labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                                   name = "Sample Site Subtransect"))
```

## Visualize spatial patterns
### Blocks in plot
```{r}
blocks <- ggplot(data =  weevil_both, aes(x = Column, y = Row)) + 
      geom_tile(aes(fill = Block), colour = "black") +
      scale_y_reverse() +
  theme_minimal()
blocks

png(here::here("./Figures_Tables/Spatial_patterns/blocks.png"), width = 800, height = 400)
print(blocks)
dev.off()
```

### Weevil damage
```{r}
# binary: damaged or not during first weevil damage assessment
weevil_matrix_data_binary <- weevil_both[,c("Row", "Column", "Weevil_dam_binary")]

weevil_plot_binary <- ggplot(data = weevil_matrix_data_binary, aes(x = Column, y = Row)) + 
      geom_tile(aes(fill = as.factor(Weevil_dam_binary)), colour = "black") +
      scale_y_reverse() +
  scale_fill_manual(values = c("yellow", "red"),
                      name = "Weevil Damage",
                      labels = c("No", "Yes"))
weevil_plot_binary

png(here::here("./Figures_Tables/Spatial_patterns/weevil_matrix_binary.png"), width = 800, height = 400)
print(weevil_plot_binary)
dev.off()


# quantitative: how long was the scar? during second weevil damage assessment
weevil_matrix_data_quant <- weevil_both[,c("Row", "Column", "Scar_length_mm")]

weevil_plot_quant <- ggplot(data =  weevil_matrix_data_quant, aes(x = Column, y = Row, fill = Scar_length_mm)) + 
      geom_tile(aes(fill = Scar_length_mm), colour = "black") +
      scale_y_reverse()
weevil_plot_quant

# quantitative: how long was the scar? during second weevil damage assessment- ONLY IF HAD SCAR
weevil_matrix_data_quant <- weevil_both[,c("Row", "Column", "Scar_length_mm")]

ggplot(data =  weevil_matrix_data_quant %>% filter(.,Scar_length_mm > 0), aes(x = Column, y = Row, fill = Scar_length_mm)) + 
      geom_tile(aes(fill = Scar_length_mm), colour = "black") +
      scale_y_reverse()


# quantitative: how long was the scar? during second weevil damage assessment- ONLY IF HAD SCAR- STANDARDIZED BY HEIGHT
weevil_matrix_data_standardized <- weevil_both[,c("Row", "Column", "scar_div_Juneheight")]

ggplot(data =  weevil_matrix_data_standardized %>% filter(.,scar_div_Juneheight > 0), aes(x = Column, y = Row, fill = scar_div_Juneheight)) +
  geom_tile(aes(fill = scar_div_Juneheight), colour = "black") +
  scale_fill_gradient(colours = topo.colors(50)) +
  scale_y_reverse() +
  labs(fill = "Scar length per cm height")

# hist(log(weevil_both$scar_div_Juneheight)
# png("weevil_matrix_binary.png", width = 800, height = 400)
# print(weevil_plot_binary)
# dev.off()
```

### Mortality
```{r}
mortality_matrix_data <- dead_2020[,c("Row", "Column", "Dead_June")]

mortality_plot <- ggplot(data =  mortality_matrix_data, aes(x = Column, y = Row)) + 
      geom_tile(aes(fill = as.factor(Dead_June)), colour = "black") +
      scale_y_reverse() +
  scale_fill_manual(values = c("yellow", "red"),
                      name = "Mortality",
                          labels = c("Dead", "Alive")) 


png(here::here("./Figures_Tables/Spatial_patterns/mortality_matrix_binary.png"), width = 800, height = 400)
print(mortality_plot)
dev.off()
```

### Flowering
#### Flowering plants
```{r}
flowering_matrix_data <- reproductive[,c("Row", "Column", "Flowered2020")]

flowering_plot <- ggplot(data =  flowering_matrix_data, aes(x = Column, y = Row)) + 
  geom_tile(aes(fill = as.factor(Flowered2020)), colour = "black") +
  scale_y_reverse() +
  scale_fill_manual(values = c("yellow", "red"),
                      name = "Flowering Plants",
                      labels = c("No", "Yes"))
flowering_plot

png(here::here("./Figures_Tables/Spatial_patterns/flowering_matrix.png"), width = 800, height = 400)
print(flowering_plot)
dev.off()
```


## Look at distribution of pops along gradient
```{r}
ggplot(heights_both2020_popmeans, aes(x=City_dist)) +
  geom_histogram(binwidth=6, color="black", fill="white")

ggplot(heights_both2020_popmeans, aes(x=Urb_score)) +
  geom_histogram(binwidth=0.8, color="black", fill="white")

```

## reproductive
### Plants that flowered: Regressions
#### Percent flowering plants/pop
##### Entire gradient
```{r}
# City_dist
ggplot(flowered2020_popmeans, aes(x = City_dist, y = percent_flowered)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Percent Flowering Plants/Population") +
  theme_gradient_1

# Urb_score
ggplot(flowered2020_popmeans, aes(x = Urb_score, y = percent_flowered)) + 
  labs(x = "Urbanization Score", 
    y = "Percent Flowering Plants/Population") +
  theme_gradient_1 +
  scale_x_reverse()
```

##### Urban subtransects
```{r}
# City_dist
ggplot(flowered2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = percent_flowered)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Percent Flowering Plants/Population") +
  theme_urbansubs_1

# Urb_score
ggplot(flowered2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = percent_flowered)) + 
  labs(x = "Urbanization Score", 
    y = "Percent Flowering Plants/Population") +
  theme_urbansubs_1 +
  scale_x_reverse()

```


#### Mean flower count
##### Entire gradient
```{r}
ggplot(flowering_2020, aes(x = City_dist, y = mean_flower_count)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean flower count/inflorescence") +
  theme_gradient_1


ggplot(flowering_2020, aes(x = Urb_score, y = mean_flower_count)) + 
  labs(x = "Urbanization Score", 
    y = "Mean flower count/inflorescence") +
  theme_gradient_1 +
  scale_x_reverse()
```


##### Urban subtransects
```{r}
ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_flower_count)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean flower count/inflorescence") +
  theme_urbansubs_1

ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_flower_count)) + 
  labs(x = "Urbanization Score", 
    y = "Mean flower count/inflorescence") +
  theme_urbansubs_1 +
  scale_x_reverse()
```

#### Total flower count
##### Entire gradient
```{r}

ggplot(flowering_2020, aes(x = City_dist, y = total_flower_count)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Total flower count") +
  theme_gradient_1

ggplot(flowering_2020, aes(x = Urb_score, y = total_flower_count)) + 
  labs(x = "Urbanization Score", 
    y = "Total flower count") +
  theme_gradient_1 +
  scale_x_reverse()
```


##### Urban subtransects
```{r}
ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = total_flower_count)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Total flower count") +
  theme_urbansubs_1

ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = total_flower_count)) + 
  labs(x = "Urbanization Score", 
    y = "Total flower count") +
  theme_urbansubs_1+
  scale_x_reverse()

```


#### Mean flower size
##### Entire gradient
```{r}
ggplot(flowering_2020, aes(x = City_dist, y = Overall_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean flower size") +
  theme_gradient_1

ggplot(flowering_2020, aes(x = Urb_score, y = Overall_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean flower size") +
  theme_gradient_1 +
  scale_x_reverse()



# COMBINING INTO ONE FIGURE (do a PCA instead)
ggplot() + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean flower size") +
  geom_point(aes(x = City_dist, y = Overall_mean), size=2, color = 'orange', data = flowering_2020) +
  geom_point(aes(x = City_dist, y = Flower_mean), size=2, color = 'blue', data = flowering_2020) +
  geom_point(aes(x = City_dist, y = Corolla_mean), size=2, color = 'green', data = flowering_2020) +
  geom_point(aes(x = City_dist, y = Hood_mean), size=2, color = 'purple', data = flowering_2020) +
  # xlim(0, 71) +
  # ylim(0, 120) +
  geom_smooth(aes(x = City_dist, y = Overall_mean), size=0.75, method = lm, alpha=.15, se = T, data = flowering_2020) +
  geom_smooth(aes(x = City_dist, y = Flower_mean), size=0.75, method = lm, alpha=.15, se = T, data = flowering_2020) +
  geom_smooth(aes(x = City_dist, y = Corolla_mean), size=0.75, method = lm, alpha=.15, se = T, data = flowering_2020) +
  geom_smooth(aes(x = City_dist, y = Hood_mean), size=0.75, method = lm, alpha=.15, se = T, data = flowering_2020) +
  theme_bw() 
  # theme(text = element_text(size=12)) +
  # scale_shape_manual(values = c(21, 24),
  #                    breaks = c("June", "September"),
  #                      labels = c("June", "September"),
  #                      name = "Legend") +
  # scale_color_manual(values = c("blue", "orange"),
  #                    breaks = c("June", "September"),
  #                      labels = c("June", "September"),
  #                      name = "Legend") +
  # scale_fill_manual(values = c("blue", "orange"),
  #                    breaks = c("June", "September"),
  #                      labels = c("June", "September"),
  #                      name = "Legend")
```


##### Urban subtransects
```{r}
ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = Overall_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean flower size") +
  theme_urbansubs_1


ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = Overall_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean flower size") +
  theme_urbansubs_1 +
  scale_x_reverse()
```



#### Pod count
##### Entire gradient
```{r}
ggplot(flowering_2020, aes(x = City_dist, y = Pods)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Pods") +
  theme_gradient_1

ggplot(flowering_2020, aes(x = Urb_score, y = Pods)) + 
  labs(x = "Urbanization Score", 
    y = "Pods") +
  theme_gradient_1 +
  scale_x_reverse()

```


##### Urban subtransects
```{r}
ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = Pods)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Pods") +
  theme_urbansubs_1


ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = Pods)) + 
  labs(x = "Urbanization Score", 
    y = "Pods") +
  theme_urbansubs_1 +
  scale_x_reverse()
```

#### Peduncles/Inflorescences
##### Entire gradient
```{r}
ggplot(flowering_2020, aes(x = City_dist, y = Peduncles)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Peduncles") +
  theme_gradient_1

ggplot(flowering_2020, aes(x = Urb_score, y = Peduncles)) + 
  labs(x = "Urbanization Score", 
    y = "Peduncles") +
  theme_gradient_1 +
  scale_x_reverse()

```


##### Urban subtransects
```{r}
ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = Peduncles)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Peduncles") +
  theme_urbansubs_1


ggplot(flowering_2020 %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = Peduncles)) + 
  labs(x = "Urbanization Score", 
    y = "Peduncles") +
  theme_urbansubs_1 +
  scale_x_reverse()
```


### Plants that flowered: Boxplots
#### Mean flower count
##### Urban subtransects
```{r}
library(viridis)

flowering_2020 %>%
  filter(Transect_ID != "Rural") %>%
  ggplot( aes(x=Transect_ID, y=mean_flower_count, fill=Transect_ID)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=2, alpha=0.5) +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    xlab("")
```

## Height
### Regressions
#### Each point is a population mean
##### Entire gradient
```{r}
# JUNE HEIGHT
## Multiple R-squared:  0.05561
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_height_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 60) 

ggplot(heights_both2020_popmeans, aes(x = Urb_score, y = mean_height_June)) + 
  labs(x = 'Urbanization Score', 
    y = "June: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 60) +
  scale_x_reverse()


# SEPT HEIGHT
# Multiple R-squared:  0.05979
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "September: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 120) 

ggplot(heights_both2020_popmeans, aes(x = Urb_score, y = mean_height_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "September: Mean height (cm)") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 120) +
  scale_x_reverse()


# COMBINING INTO ONE FIGURE
ggplot() + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean height (cm)") +
  geom_point(aes(x = City_dist, y = mean_height_June, fill = 'June', shape = 'June'), size=2, data = heights_both2020_popmeans) +
  geom_point(aes(x = City_dist, y = mean_height_Sept, fill = 'September', shape = 'September' ), size=2, data = heights_both2020_popmeans) +
 # scale_shape(aes(x = City_dist, y = mean_height_June), solid = T, data = heights_both2020_popmeans)+
 # scale_shape(aes(x = City_dist, y = mean_height_Sept), solid = F, data = heights_both2020_popmeans)+
  xlim(0, 71) +
  ylim(0, 120) +
  geom_smooth(aes(x = City_dist, y = mean_height_June, fill = 'June', color = 'June'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  geom_smooth(aes(x = City_dist, y = mean_height_Sept, fill = 'September', color = 'September'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(21, 24),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_color_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_fill_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") 



ggplot() + 
  labs(x = "Urbanization Score", 
    y = "Mean height (cm)") +
  geom_point(aes(x = Urb_score, y = mean_height_June, fill = 'June', shape = 'June'), size=2, data = heights_both2020_popmeans) +
  geom_point(aes(x = Urb_score, y = mean_height_Sept, fill = 'September', shape = 'September' ), size=2, data = heights_both2020_popmeans) +
 # scale_shape(aes(x = City_dist, y = mean_height_June), solid = T, data = heights_both2020_popmeans)+
 # scale_shape(aes(x = City_dist, y = mean_height_Sept), solid = F, data = heights_both2020_popmeans)+
  # xlim(0, 71) +
  ylim(0, 120) +
  geom_smooth(aes(x = Urb_score, y = mean_height_June, fill = 'June', color = 'June'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  geom_smooth(aes(x = Urb_score, y = mean_height_Sept, fill = 'September', color = 'September'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(21, 24),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_color_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_fill_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_x_reverse()
```

##### Urban subtransects
```{r}
# JUNE HEIGHT
ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean height (cm)") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 60) 

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_height_June)) + 
  labs(x = "Urbanization Score", 
    y = "June: Mean height (cm)") +
  theme_urbansubs_1 +
  ylim(0, 60) +
  scale_x_reverse()



# sept HEIGHT
ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean height (cm)") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 120)

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_height_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "Sept: Mean height (cm)") +
  theme_urbansubs_1 +
  ylim(0, 120) +
  scale_x_reverse()

```

#### Each point is a family mean
##### Entire gradient
```{r}
# JUNE HEIGHT
## Multiple R-squared:  0.05561
ggplot(heights_both2020_familymeans, aes(x = City_dist, y = mean_height_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  xlim(0, 71) +
  ylim(0, 60) +
  geom_smooth(size=0.75, method = lm, alpha=.15, se = T, color = 'black') +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2, 5),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("black", "#333333", "#666666"),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") 



# SEPT HEIGHT
# Multiple R-squared:  0.05979
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "September: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  xlim(0, 71) +
  ylim(0, 120) +
  geom_smooth(size=0.75, method = lm, alpha=.15, se = T, color = 'black') +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2, 5),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("black", "#333333", "#666666"),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect")




# COMBINING INTO ONE FIGURE
ggplot() + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean height (cm)") +
  geom_point(aes(x = City_dist, y = mean_height_June, fill = 'June', shape = 'June'), size=2, data = heights_both2020_popmeans) +
  geom_point(aes(x = City_dist, y = mean_height_Sept, fill = 'September', shape = 'September' ), size=2, data = heights_both2020_popmeans) +
 # scale_shape(aes(x = City_dist, y = mean_height_June), solid = T, data = heights_both2020_popmeans)+
 # scale_shape(aes(x = City_dist, y = mean_height_Sept), solid = F, data = heights_both2020_popmeans)+
  xlim(0, 71) +
  ylim(0, 120) +
  geom_smooth(aes(x = City_dist, y = mean_height_June, fill = 'June', color = 'June'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  geom_smooth(aes(x = City_dist, y = mean_height_Sept, fill = 'September', color = 'September'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(21, 24),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_color_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_fill_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") 
```

##### Urban subtransects
```{r}
# JUNE HEIGHT

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  geom_smooth(aes(linetype = Transect_ID, color = Transect_ID, fill = Transect_ID),size=0.75, method = lm, alpha=.15, se = T) +
  xlim(0, 35) +
  ylim(0, 60) +
  theme_bw() +
  theme(text = element_text(size=12),
        legend.position = 'none') +
  scale_shape_manual(values = c(1, 2),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_linetype_manual(values = c("solid", "dashed"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_fill_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect")



# sept HEIGHT

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  geom_smooth(aes(linetype = Transect_ID, color = Transect_ID, fill = Transect_ID),size=0.75, method = lm, alpha=.15, se = T) +
  xlim(0, 35) +
  ylim(0, 120) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_linetype_manual(values = c("solid", "dashed"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_fill_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect")
```



## Weevil damage
### Standardized by June height
#### Regressions
##### Entire gradient
```{r}
# Multiple R-squared: 0.0008
ggplot(weevil_both2020_popmeans, aes(x = City_dist, y = mean_scar_div_Juneheight)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Weevil scar length/cm") +
  theme_gradient_1


ggplot(weevil_both2020_popmeans, aes(x = Urb_score, y = mean_scar_div_Juneheight)) + 
  labs(x = 'Urbanization Score', 
    y = "Weevil scar length/cm") +
  theme_gradient_1 +
  scale_x_reverse()

```

##### Urban subtransects
```{r}

# R-squared = 0.04079
ggplot(weevil_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_scar_div_Juneheight)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Weevil scar length/cm") +
  theme_urbansubs_1 +
  ylim(0, 0.2) 


ggplot(weevil_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_scar_div_Juneheight)) + 
  labs(x = "Urbanization Score", 
    y = "Weevil scar length/cm") +
  theme_urbansubs_1 +
  ylim(0, 0.2) +
  scale_x_reverse()
```

### NOT Standardized by June height
#### Regressions
##### Entire gradient
```{r}
# Multiple R-squared: 0.003591
ggplot(weevil_both2020_popmeans, aes(x = City_dist, y = mean_scar)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Total weevil scar length") +
  theme_gradient_1

ggplot(weevil_both2020_popmeans, aes(x = Urb_score, y = mean_scar)) + 
  labs(x = "Urbanization Score", 
    y = "Total weevil scar length") +
  theme_gradient_1 +
  scale_x_reverse()
```

##### Urban subtransects
```{r}
ggplot(weevil_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_scar)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Total weevil scar length") +
  theme_urbansubs_1

ggplot(weevil_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_scar)) + 
  labs(x = "Urbanization Score", 
    y = "Total weevil scar length") +
  theme_urbansubs_1+
  scale_x_reverse()
```

## Herbivory
### Regressions
#### Entire gradient
```{r}
# JULY HERBIVORY
## NO TRANSFORMATIONS OR OUTLIERS REMOVED-----
## Multiple R-squared: 0.08834
ggplot(herbivory2020_popmeans, aes(x = City_dist, y = Herbivory.July_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 15) 

ggplot(herbivory2020_popmeans, aes(x = Urb_score, y = Herbivory.July_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean Herbivory") +
  theme_gradient_1 +
  ylim(0, 15) +
  scale_x_reverse()



# SEPT HEIGHT-----
# Multiple R-squared:  0.01975
ggplot(herbivory2020_popmeans, aes(x = City_dist, y = Herbivory.Sept_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(herbivory2020_popmeans, aes(x = Urb_score, y = Herbivory.Sept_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean Herbivory") +
  theme_gradient_1 +
  xlim(0, 71) +
  scale_x_reverse()


# COMBINING INTO ONE FIGURE-----
ggplot() + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  geom_point(aes(x = City_dist, y = Herbivory.July_mean, fill = 'July', shape = 'July'), size=2, data = herbivory2020_popmeans) +
  geom_point(aes(x = City_dist, y = Herbivory.Sept_mean, fill = 'September', shape = 'September' ), size=2, data = herbivory2020_popmeans) +
 # scale_shape(aes(x = City_dist, y = mean_height_June), solid = T, data = heights_both2020_popmeans)+
 # scale_shape(aes(x = City_dist, y = mean_height_Sept), solid = F, data = heights_both2020_popmeans)+
  xlim(0, 71) +
  # ylim(0, 120) +
  geom_smooth(aes(x = City_dist, y = Herbivory.July_mean, fill = 'July', color = 'July'), size=0.75, method = lm, alpha=.15, se = T, data = herbivory2020_popmeans) +
  geom_smooth(aes(x = City_dist, y = Herbivory.Sept_mean, fill = 'September', color = 'September'), size=0.75, method = lm, alpha=.15, se = T, data = herbivory2020_popmeans) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(21, 24),
                     breaks = c("July", "September"),
                       labels = c("July", "September"),
                       name = "Legend") +
  scale_color_manual(values = c("blue", "orange"),
                     breaks = c("July", "September"),
                       labels = c("July", "September"),
                       name = "Legend") +
  scale_fill_manual(values = c("blue", "orange"),
                     breaks = c("July", "September"),
                       labels = c("July", "September"),
                       name = "Legend") 
```

#### Urban subtransects
```{r}
# JULY HERBIVORY
ggplot(herbivory2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = Herbivory.July_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 15) 

ggplot(herbivory2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = Herbivory.July_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean Herbivory") +
  theme_urbansubs_1 +
  ylim(0, 15) +
  scale_x_reverse()


# sept herbivory
ggplot(herbivory2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = Herbivory.Sept_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean Herbivory") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 40)    

ggplot(herbivory2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = Herbivory.Sept_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mean Herbivory") +
  theme_urbansubs_1 +
  ylim(0, 40) +
  scale_x_reverse()

```


## No. of Ramets
### Regressions
#### Each point is a population mean
##### Entire gradient
```{r}
# JUNE RAMETS
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_Ramets_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean No. Ramets") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 5)

ggplot(heights_both2020_popmeans, aes(x = Urb_score, y = mean_Ramets_June)) + 
  labs(x = "Urbanization Score", 
    y = "June: Mean No. Ramets") +
  theme_gradient_1 +
  ylim(0, 5) +
  scale_x_reverse()


# SEPT ramets
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_Ramets_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "September: Mean No. Ramets") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(0, 4) 

ggplot(heights_both2020_popmeans, aes(x = Urb_score, y = mean_Ramets_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "September: Mean No. Ramets") +
  theme_gradient_1 +
  ylim(0, 4) +
  scale_x_reverse()


# COMBINING INTO ONE FIGURE
ggplot() + 
  labs(x = "Distance to urban center (km)", 
    y = "Mean No. Ramets") +
  geom_point(aes(x = City_dist, y = mean_Ramets_June, fill = 'June', shape = 'June'), size=2, data = heights_both2020_popmeans) +
  geom_point(aes(x = City_dist, y = mean_Ramets_Sept, fill = 'September', shape = 'September' ), size=2, data = heights_both2020_popmeans) +
 # scale_shape(aes(x = City_dist, y = mean_height_June), solid = T, data = heights_both2020_popmeans)+
 # scale_shape(aes(x = City_dist, y = mean_height_Sept), solid = F, data = heights_both2020_popmeans)+
  xlim(0, 71) +
  ylim(0, 5) +
  geom_smooth(aes(x = City_dist, y = mean_Ramets_June, fill = 'June', color = 'June'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  geom_smooth(aes(x = City_dist, y = mean_Ramets_Sept, fill = 'September', color = 'September'), size=0.75, method = lm, alpha=.15, se = T, data = heights_both2020_popmeans) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(21, 24),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_color_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") +
  scale_fill_manual(values = c("blue", "orange"),
                     breaks = c("June", "September"),
                       labels = c("June", "September"),
                       name = "Legend") 
```

##### Urban subtransects
```{r}
# JUNE ramets
p1 <- ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_Ramets_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean No. Ramets") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 4.2) 

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_Ramets_June)) + 
  labs(x = "Urbanization Score", 
    y = "June: Mean No. Ramets") +
  theme_urbansubs_1 +
  ylim(0, 4.2) +
  scale_x_reverse()


# sept ramets
p2 <- ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_Ramets_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean No. Ramets") +
  theme_urbansubs_1 +
  xlim(0, 35) +
  ylim(0, 4)

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_Ramets_Sept)) + 
  labs(x = "Urbanization Score", 
    y = "Sept: Mean No. Ramets") +
  theme_urbansubs_1 +
  ylim(0, 4)+
  scale_x_reverse()



library(patchwork)
p1 + p2
```

#### Each point is a family mean
##### Entire gradient
```{r}
# JUNE HEIGHT
ggplot(ramets_2020_familymeans_stats, aes(x = City_dist, y = Ramets_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean No. Ramets") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=1.5) +
  scale_shape(solid = F)+
  geom_errorbar(aes(ymin=Ramets_June-se.June, ymax=Ramets_June+se.June), width = 0.25) +
  xlim(0, 71) +
  ylim(0, 8) +
  geom_smooth(size=0.75, method = lm, alpha=.15, se = T, color = 'black') +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2, 5),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("black", "#333333", "#666666"),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") 


# SEPT HEIGHT
ggplot(ramets_2020_familymeans_stats, aes(x = City_dist, y = Ramets_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean No. Ramets") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=1.5) +
  scale_shape(solid = F)+
  geom_errorbar(aes(ymin=Ramets_June-se.Sept, ymax=Ramets_June+se.Sept), width = 0.25) +
  xlim(0, 71) +
  ylim(0, 8) +
  geom_smooth(size=0.75, method = lm, alpha=.15, se = T, color = 'black') +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2, 5),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("black", "#333333", "#666666"),
                     breaks = c("North", "South", "Rural"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor", "Rural"),
                       name = "Sample Site Subtransect") 

```

##### Urban subtransects
```{r}
# JUNE HEIGHT

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_June)) + 
  labs(x = "Distance to urban center (km)", 
    y = "June: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  geom_smooth(aes(linetype = Transect_ID, color = Transect_ID, fill = Transect_ID),size=0.75, method = lm, alpha=.15, se = T) +
  xlim(0, 35) +
  ylim(0, 60) +
  theme_bw() +
  theme(text = element_text(size=12),
        legend.position = 'none') +
  scale_shape_manual(values = c(1, 2),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_linetype_manual(values = c("solid", "dashed"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_fill_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect")



# sept HEIGHT

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_height_Sept)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Sept: Mean height (cm)") +
  geom_point(aes(color = Transect_ID, shape = Transect_ID), size=2) +
  scale_shape(solid = F)+
  geom_smooth(aes(linetype = Transect_ID, color = Transect_ID, fill = Transect_ID),size=0.75, method = lm, alpha=.15, se = T) +
  xlim(0, 35) +
  ylim(0, 120) +
  theme_bw() +
  theme(text = element_text(size=12)) +
  scale_shape_manual(values = c(1, 2),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_color_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_linetype_manual(values = c("solid", "dashed"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect") +
  scale_fill_manual(values = c("red", "blue"),
                     breaks = c("North", "South"),
                       labels = c("Urban: Non-Corridor", "Urban: Corridor"),
                       name = "Sample Site Subtransect")
```



## Growth rate
### Regressions
#### Entire gradient
```{r}
ggplot(heights_both2020_popmeans, aes(x = City_dist, y = mean_rel_growth_rate)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Relative Growth Rate") +
  theme_gradient_1 +
  xlim(0, 71) +
  ylim(-0.01, 0.015) 

ggplot(heights_both2020_popmeans, aes(x = Urb_score, y = mean_rel_growth_rate)) + 
  labs(x = "Urbanization Score", 
    y = "Relative Growth Rate") +
  theme_gradient_1 +
  ylim(-0.01, 0.015)+
  scale_x_reverse()


```

#### Urban subtransects
```{r}
ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = mean_rel_growth_rate)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Relative Growth Rate") +
  theme_urbansubs_1 +
  xlim(0, 35) 

ggplot(heights_both2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = mean_rel_growth_rate)) + 
  labs(x = "Urbanization Score", 
    y = "Relative Growth Rate") +
  theme_urbansubs_1 +
  scale_x_reverse()
```

## Survival
### Regressions
#### Entire gradient
```{r}
ggplot(survival2020_popmeans, aes(x = City_dist, y = survival_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mortality") +
  theme_gradient_1 +
  xlim(0, 71) 

ggplot(survival2020_popmeans, aes(x = Urb_score, y = survival_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mortality") +
  theme_gradient_1 +
  scale_x_reverse()

```

#### Urban subtransects
```{r}
ggplot(survival2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = City_dist, y = survival_mean)) + 
  labs(x = "Distance to urban center (km)", 
    y = "Mortality") +
  theme_urbansubs_1 +
  xlim(0, 35) 

ggplot(survival2020_popmeans %>% filter(Transect_ID != "Rural"), aes(x = Urb_score, y = survival_mean)) + 
  labs(x = "Urbanization Score", 
    y = "Mortality") +
  theme_urbansubs_1 +
  scale_x_reverse()
```
