# Load libraries & functions
```{r}
source("libraries.R")
source("functions.R")
```

# Import data (multi-year models)
## Reproductive traits
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_Reproduc.Rmd", quiet=TRUE))

```

## Defense traits (including cardenolides)
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_Defense.Rmd", quiet=TRUE))

```

## Growth traits
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_Growth.Rmd", quiet=TRUE))
```

# Fit 1-year models
## Q1
### City_dist
#### Make lists of models
##### Defense
```{r}
def.m1 <- latex_mods_best_c[[1]]

def.m2 <- make_1yrmod(herb_e_bin_mods_best_c[[1]], "2021", herbivory)

def.m3 <- update(herb_e_quant_mods_best_c[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

def.m4 <- make_1yrmod(herb_l_bin_mods_best_c[[1]], "2021", herbivory)

def.m5 <- update(herb_l_quant_mods_best_c[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

def.m6 <- make_1yrmod(weev_bin_mods_best_c[[1]], "2021", weevil)

def.m7 <- update(weev_quant_mods_best_c[[1]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Year == "2021" &
                                   Scar_length_cm > 0))
```

##### Reproduction
```{r}
repr.m1 <- make_1yrmod(flsucc_mods_best_c[[1]], "2022", reproduc)

repr.m2 <- make_1yrmod(flowers_mods_best_c[[1]], "2022", flowering)

repr.m3 <- make_1yrmod(flsize_mods_best_c[[1]], "2022", flowering)

repr.m4 <- make_1yrmod(fltime_mods_best_c[[1]], "2022", flowering)

repr.m5 <- make_1yrmod(flstart_mods_best_c[[1]], "2022", flowering)

repr.m6 <- make_1yrmod(pods_mods_best_c[[1]], "2022", flowering)

repr.m7 <- make_1yrmod(first_pods_mods_best_c[[1]], "2022", flowering)

repr.m8 <- make_1yrmod(peduncles_mods_best_c[[1]], "2022", flowering)
```

##### Herbivores
```{r}
herb.m1 <- make_1yrmod(monarch_mods_best_c[[1]], "2021", herbivores)

herb.m2 <- make_1yrmod(asclepiadis_mods_best_c[[1]], "2021", herbivores)

herb.m3 <- make_1yrmod(clivicollis_mods_best_c[[1]], "2021", herbivores)
```

##### Growth
```{r}
grow.m1 <- ldmc_mods_best_c[[1]]

grow.m2 <- sla_mods_best_c[[1]]

grow.m3 <- make_1yrmod(heights_early_mods_best_c[[1]], "2021", heights)

grow.m4 <- make_1yrmod(heights_late_mods_best_c[[1]], "2021", heights)

grow.m5 <- make_1yrmod(rgr_mods_best_c[[1]], "2021", heights)

grow.m6 <- make_1yrmod(ramets_early_mods_best_c[[1]], "2021", heights)

grow.m7 <- make_1yrmod(ramets_late_mods_best_c[[1]], "2021", heights)

grow.m8 <- make_1yrmod(mortality_mods_best_c[[1]], "2022", survival)
```

##### All
```{r}
all_1yr_mods <- list(
  
  # defense
  def.m1,
  def.m2,
  def.m3,
  def.m4,
  def.m5,
  def.m6,
  def.m7,
  
  # reproduction
  repr.m1,
  repr.m2,
  repr.m3,
  repr.m4,
  repr.m5,
  repr.m6,
  repr.m7,
  repr.m8,
  
  # Herbivores
  herb.m1,
  herb.m2,
  herb.m3,
  
  # growth
  grow.m1,
  grow.m2,
  grow.m3,
  grow.m4,
  grow.m5,
  grow.m6,
  grow.m7,
  grow.m8
  )
```

### Urb_score
#### Make lists of models
##### Defense
```{r}
def.m1_u <- latex_mods_best_u[[1]]

def.m2_u <- make_1yrmod(herb_e_bin_mods_best_u[[1]], "2021", herbivory)

def.m3_u <- update(herb_e_quant_mods_best_u[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

def.m4_u <- make_1yrmod(herb_l_bin_mods_best_u[[1]], "2021", herbivory)

def.m5_u <- update(herb_l_quant_mods_best_u[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

def.m6_u <- make_1yrmod(weev_bin_mods_best_u[[1]], "2021", weevil)

def.m7_u <- update(weev_quant_mods_best_u[[1]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Year == "2021" &
                                   Scar_length_cm > 0))
```

##### Reproduction
```{r}
repr.m1_u <- make_1yrmod(flsucc_mods_best_u[[1]], "2022", reproduc)

repr.m2_u <- make_1yrmod(flowers_mods_best_u[[1]], "2022", flowering)

repr.m3_u <- make_1yrmod(flsize_mods_best_u[[1]], "2022", flowering)

repr.m4_u <- make_1yrmod(fltime_mods_best_u[[1]], "2022", flowering)

repr.m5_u <- make_1yrmod(flstart_mods_best_u[[1]], "2022", flowering)

repr.m6_u <- make_1yrmod(pods_mods_best_u[[1]], "2022", flowering)

repr.m7_u <- make_1yrmod(first_pods_mods_best_u[[1]], "2022", flowering)

repr.m8_u <- make_1yrmod(peduncles_mods_best_u[[1]], "2022", flowering)
```

##### Herbivores
```{r}
herb.m1_u <- make_1yrmod(monarch_mods_best_u[[1]], "2021", herbivores)

herb.m2_u <- make_1yrmod(asclepiadis_mods_best_u[[1]], "2021", herbivores)

herb.m3_u <- make_1yrmod(clivicollis_mods_best_u[[1]], "2021", herbivores)
```

##### Growth
```{r}
grow.m1_u <- ldmc_mods_best_u[[1]]

grow.m2_u <- sla_mods_best_u[[1]]

grow.m3_u <- make_1yrmod(heights_early_mods_best_u[[1]], "2021", heights)

grow.m4_u <- make_1yrmod(heights_late_mods_best_u[[1]], "2021", heights)

grow.m5_u <- make_1yrmod(rgr_mods_best_u[[1]], "2021", heights)

grow.m6_u <- make_1yrmod(ramets_early_mods_best_u[[1]], "2021", heights)

grow.m7_u <- make_1yrmod(ramets_late_mods_best_u[[1]], "2021", heights)

grow.m8_u <- make_1yrmod(mortality_mods_best_u[[1]], "2022", survival)
```

##### All
```{r}
all_1yr_mods.u <- list(
  
  # defense
  def.m1_u,
  def.m2_u,
  def.m3_u,
  def.m4_u,
  def.m5_u,
  def.m6_u,
  def.m7_u,
  
  # reproduction
  repr.m1_u,
  repr.m2_u,
  repr.m3_u,
  repr.m4_u,
  repr.m5_u,
  repr.m6_u,
  repr.m7_u,
  repr.m8_u,
  
  # Herbivores
  herb.m1_u,
  herb.m2_u,
  herb.m3_u,
  
  # growth
  grow.m1_u,
  grow.m2_u,
  grow.m3_u,
  grow.m4_u,
  grow.m5_u,
  grow.m6_u,
  grow.m7_u,
  grow.m8_u
  )
```


## Q2
### City_dist
#### Make lists of models
##### Defense
```{r}
def.tr.m1 <- latex_mods_best_c[[2]]

def.tr.m2 <- make_1yrmod_transects(herb_e_bin_mods_best_c[[2]], "2021", herbivory)

def.tr.m3 <- update(herb_e_quant_mods_best_c[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

def.tr.m4 <- make_1yrmod_transects(herb_l_bin_mods_best_c[[2]], "2021", herbivory)

def.tr.m5 <- update(herb_l_quant_mods_best_c[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

def.tr.m6 <- make_1yrmod_transects(weev_bin_mods_best_c[[2]], "2021", weevil)

def.tr.m7 <- update(weev_quant_mods_best_c[[2]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Scar_length_cm > 0))
```

##### Reproduction
```{r}
repr.tr.m1 <- make_1yrmod_transects(flsucc_mods_best_c[[2]], "2022", reproduc)

repr.tr.m2 <- make_1yrmod_transects(flowers_mods_best_c[[2]], "2022", flowering)

repr.tr.m3 <- make_1yrmod_transects(flsize_mods_best_c[[2]], "2022", flowering)

repr.tr.m4 <- make_1yrmod_transects(fltime_mods_best_c[[2]], "2022", flowering)

repr.tr.m5 <- make_1yrmod_transects(flstart_mods_best_c[[2]], "2022", flowering)

repr.tr.m6 <- make_1yrmod_transects(pods_mods_best_c[[2]], "2022", flowering)

repr.tr.m7 <- make_1yrmod_transects(first_pods_mods_best_c[[2]], "2022", flowering)

repr.tr.m8 <- make_1yrmod_transects(peduncles_mods_best_c[[2]], "2022", flowering)
```

##### Herbivores
```{r}
herb.tr.m1 <- make_1yrmod_transects(monarch_mods_best_c[[2]], "2021", herbivores)

herb.tr.m2 <- make_1yrmod_transects(asclepiadis_mods_best_c[[2]], "2021", herbivores)

herb.tr.m3 <- make_1yrmod_transects(clivicollis_mods_best_c[[2]], "2021", herbivores)
```

##### Growth
```{r}
grow.tr.m1 <- ldmc_mods_best_c[[2]]

grow.tr.m2 <- sla_mods_best_c[[2]]

grow.tr.m3 <- make_1yrmod_transects(heights_early_mods_best_c[[2]], "2021", heights)

grow.tr.m4 <- make_1yrmod_transects(heights_late_mods_best_c[[2]], "2021", heights)

grow.tr.m5 <- make_1yrmod_transects(rgr_mods_best_c[[2]], "2021", heights)

grow.tr.m6 <- make_1yrmod_transects(ramets_early_mods_best_c[[2]], "2021", heights)

grow.tr.m7 <- make_1yrmod_transects(ramets_late_mods_best_c[[2]], "2021", heights)

grow.tr.m8 <- make_1yrmod_transects(mortality_mods_best_c[[2]], "2022", survival)
```

##### All
```{r}
all_1yr_mods_tr <- list(
  
  # defense
  def.tr.m1,
  def.tr.m2,
  def.tr.m3,
  def.tr.m4,
  def.tr.m5,
  def.tr.m6,
  def.tr.m7,
  
  # reproduction
  repr.tr.m1,
  repr.tr.m2,
  repr.tr.m3,
  repr.tr.m4,
  repr.tr.m5,
  repr.tr.m6,
  repr.tr.m7,
  repr.tr.m8,
  
  # Herbivores
  herb.tr.m1,
  herb.tr.m2,
  herb.tr.m3,
  
  # growth
  grow.tr.m1,
  grow.tr.m2,
  grow.tr.m3,
  grow.tr.m4,
  grow.tr.m5,
  grow.tr.m6,
  grow.tr.m7,
  grow.tr.m8
  )
```


### Urb_score
#### Make lists of models
##### Defense
```{r}
def.tr.m1_u <-latex_mods_best_u[[2]]

def.tr.m2_u <- make_1yrmod_transects(herb_e_bin_mods_best_u[[2]], "2021", herbivory)

def.tr.m3_u <- update(herb_e_quant_mods_best_u[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

def.tr.m4_u <- make_1yrmod_transects(herb_l_bin_mods_best_u[[2]], "2021", herbivory)

def.tr.m5_u <- update(herb_l_quant_mods_best_u[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

def.tr.m6_u <- make_1yrmod_transects(weev_bin_mods_best_u[[2]], "2021", weevil)

def.tr.m7_u <- update(weev_quant_mods_best_u[[2]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Scar_length_cm > 0))
```

##### Reproduction
```{r}
repr.tr.m1_u <- make_1yrmod_transects(flsucc_mods_best_u[[2]], "2022", reproduc)

repr.tr.m2_u <- make_1yrmod_transects(flowers_mods_best_u[[2]], "2022", flowering)

repr.tr.m3_u <- make_1yrmod_transects(flsize_mods_best_u[[2]], "2022", flowering)

repr.tr.m4_u <- make_1yrmod_transects(fltime_mods_best_u[[2]], "2022", flowering)

repr.tr.m5_u <- make_1yrmod_transects(flstart_mods_best_u[[2]], "2022", flowering)

repr.tr.m6_u <- make_1yrmod_transects(pods_mods_best_u[[2]], "2022", flowering)

repr.tr.m7_u <- make_1yrmod_transects(first_pods_mods_best_u[[2]], "2022", flowering)

repr.tr.m8_u <- make_1yrmod_transects(peduncles_mods_best_u[[2]], "2022", flowering)
```

##### Herbivores
```{r}
herb.tr.m1_u <- make_1yrmod_transects(monarch_mods_best_u[[2]], "2021", herbivores)

herb.tr.m2_u <- make_1yrmod_transects(asclepiadis_mods_best_u[[2]], "2021", herbivores)

herb.tr.m3_u <- make_1yrmod_transects(clivicollis_mods_best_u[[2]], "2021", herbivores)
```

##### Growth
```{r}
grow.tr.m1_u <- ldmc_mods_best_u[[2]]

grow.tr.m2_u <- sla_mods_best_u[[2]]

grow.tr.m3_u <- make_1yrmod_transects(heights_early_mods_best_u[[2]], "2021", heights)

grow.tr.m4_u <- make_1yrmod_transects(heights_late_mods_best_u[[2]], "2021", heights)

grow.tr.m5_u <- make_1yrmod_transects(rgr_mods_best_u[[2]], "2021", heights)

grow.tr.m6_u <- make_1yrmod_transects(ramets_early_mods_best_u[[2]], "2021", heights)

grow.tr.m7_u <- make_1yrmod_transects(ramets_late_mods_best_u[[2]], "2021", heights)

grow.tr.m8_u <- make_1yrmod_transects(mortality_mods_best_u[[2]], "2022", survival)
```

##### All
```{r}
all_1yr_mods.u_tr <- list(
  
  # defense
  def.tr.m1_u,
  def.tr.m2_u,
  def.tr.m3_u,
  def.tr.m4_u,
  def.tr.m5_u,
  def.tr.m6_u,
  def.tr.m7_u,
  
  # reproduction
  repr.tr.m1_u,
  repr.tr.m2_u,
  repr.tr.m3_u,
  repr.tr.m4_u,
  repr.tr.m5_u,
  repr.tr.m6_u,
  repr.tr.m7_u,
  repr.tr.m8_u,
  
  # Herbivores
  herb.tr.m1_u,
  herb.tr.m2_u,
  herb.tr.m3_u,
  
  # growth
  grow.tr.m1_u,
  grow.tr.m2_u,
  grow.tr.m3_u,
  grow.tr.m4_u,
  grow.tr.m5_u,
  grow.tr.m6_u,
  grow.tr.m7_u,
  grow.tr.m8_u
  )
```

