# Load libraries & functions
```{r}
source("libraries.R")
source("functions.R")
```

# Import data (multi-year models)
## Reproductive traits
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_Reproduc.Rmd", quiet=TRUE))

```

## Defense traits (including cardenolides)
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_Defense.Rmd", quiet=TRUE))

```

## 2021 Herbivores
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_herbivores.Rmd", quiet=TRUE))

```

## Growth traits
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_Growth.Rmd", quiet=TRUE))
```

# Fit 1-year models
## Q1
### City_dist
#### Make lists of models
##### Defense
```{r}
def.m1 <- latex_mods_best_c[[1]]

def.m2 <- make_1yrmod(herb_e_bin_mods_best_c[[1]], "2021", herbivory)

def.m3 <- update(herb_e_quant_mods_best_c[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

def.m4 <- make_1yrmod(herb_l_bin_mods_best_c[[1]], "2021", herbivory)

def.m5 <- update(herb_l_quant_mods_best_c[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

def.m6 <- make_1yrmod(weev_bin_mods_best_c[[1]], "2021", weevil)

def.m7 <- update(weev_quant_mods_best_c[[1]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Year == "2021" &
                                   Scar_length_cm > 0))
```

##### Reproduction
```{r}
repr.m1 <- make_1yrmod(flsucc_mods_best_c[[1]], "2022", reproduc)

repr.m2 <- make_1yrmod(flowers_mods_best_c[[1]], "2022", flowering)

repr.m3 <- make_1yrmod(flsize_mods_best_c[[1]], "2022", flowering)

repr.m4 <- make_1yrmod(fltime_mods_best_c[[1]], "2022", flowering)

repr.m5 <- make_1yrmod(flstart_mods_best_c[[1]], "2022", flowering)

repr.m6 <- make_1yrmod(pods_mods_best_c[[1]], "2022", flowering)

# won't converge if I take the multi-yr mod and alter it- has to be above x - 170, so I chose to increase it by a month to 200 days
repr.m7 <- glmmTMB(Julian_first_follicle-200 ~
                               Block +
                               (1|Population/Family) +
                               City_dist, 
                             data = flowering %>%
          dplyr::filter(Year == 2022),
                             family = poisson) 

repr.m8 <- make_1yrmod(peduncles_mods_best_c[[1]], "2022", flowering)

# adding the pollinaria removed variable last here because I didn't add it earlier and don't want to reorganize everything
repr.m9 <- make_1yrmod(poll_mods_best_c[[1]], "2022", flowering)
```

##### Herbivores
```{r}
herb.m1 <- make_1yrmod(monarch_mods_best_c[[1]], "2021", herbivores)

herb.m2 <- make_1yrmod(asclepiadis_mods_best_c[[1]], "2021", herbivores)

herb.m3 <- make_1yrmod(clivicollis_mods_best_c[[1]], "2021", herbivores)
```

##### Growth
```{r}
grow.m1 <- ldmc_mods_best_c[[1]]

grow.m2 <- sla_mods_best_c[[1]]

grow.m3 <- make_1yrmod(heights_early_mods_best_c[[1]], "2021", heights)

grow.m4 <- make_1yrmod(heights_late_mods_best_c[[1]], "2021", heights)

grow.m5 <- make_1yrmod(rgr_mods_best_c[[1]], "2021", heights)

grow.m6 <- make_1yrmod(ramets_early_mods_best_c[[1]], "2021", heights)

grow.m7 <- make_1yrmod(ramets_late_mods_best_c[[1]], "2021", heights)

grow.m8 <- make_1yrmod(mortality_mods_best_c[[1]], "2022", survival)
```

##### All
```{r}
all_1yr_mods <- list(
  
  # defense
  def.m1,
  def.m2,
  def.m3,
  def.m4,
  def.m5,
  def.m6,
  def.m7,
  
  # reproduction
  repr.m1,
  repr.m2,
  repr.m3,
  repr.m4,
  repr.m5,
  repr.m6,
  repr.m7,
  repr.m8,
  repr.m9,
  
  # Herbivores
  herb.m1,
  herb.m2,
  herb.m3,
  
  # growth
  grow.m1,
  grow.m2,
  grow.m3,
  grow.m4,
  grow.m5,
  grow.m6,
  grow.m7,
  grow.m8
  )
```

### Urb_score
#### Make lists of models
##### Defense
```{r}
def.m1_u <- latex_mods_best_u[[1]]

def.m2_u <- make_1yrmod(herb_e_bin_mods_best_u[[1]], "2021", herbivory)

def.m3_u <- update(herb_e_quant_mods_best_u[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

def.m4_u <- make_1yrmod(herb_l_bin_mods_best_u[[1]], "2021", herbivory)

def.m5_u <- update(herb_l_quant_mods_best_u[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

def.m6_u <- make_1yrmod(weev_bin_mods_best_u[[1]], "2021", weevil)

def.m7_u <- update(weev_quant_mods_best_u[[1]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Year == "2021" &
                                   Scar_length_cm > 0))
```

##### Reproduction
```{r}
repr.m1_u <- make_1yrmod(flsucc_mods_best_u[[1]], "2022", reproduc)

repr.m2_u <- make_1yrmod(flowers_mods_best_u[[1]], "2022", flowering)

repr.m3_u <- make_1yrmod(flsize_mods_best_u[[1]], "2022", flowering)

repr.m4_u <- make_1yrmod(fltime_mods_best_u[[1]], "2022", flowering)

repr.m5_u <- make_1yrmod(flstart_mods_best_u[[1]], "2022", flowering)

repr.m6_u <- make_1yrmod(pods_mods_best_u[[1]], "2022", flowering)

# won't converge if I take the multi-yr mod and alter it- has to be above x - 170, so I chose to increase it by a month to 200 days
repr.m7_u <- glmmTMB(Julian_first_follicle-200 ~
                               Block +
                               (1|Population/Family) +
                               Urb_score, 
                             data = flowering %>%
          dplyr::filter(Year == 2022),
                             family = poisson) 

repr.m8_u <- make_1yrmod(peduncles_mods_best_u[[1]], "2022", flowering)

repr.m9_u <- make_1yrmod(poll_mods_best_u[[1]], "2022", flowering)
```

##### Herbivores
```{r}
herb.m1_u <- make_1yrmod(monarch_mods_best_u[[1]], "2021", herbivores)

herb.m2_u <- make_1yrmod(asclepiadis_mods_best_u[[1]], "2021", herbivores)

herb.m3_u <- make_1yrmod(clivicollis_mods_best_u[[1]], "2021", herbivores)
```

##### Growth
```{r}
grow.m1_u <- ldmc_mods_best_u[[1]]

grow.m2_u <- sla_mods_best_u[[1]]

grow.m3_u <- make_1yrmod(heights_early_mods_best_u[[1]], "2021", heights)

grow.m4_u <- make_1yrmod(heights_late_mods_best_u[[1]], "2021", heights)

grow.m5_u <- make_1yrmod(rgr_mods_best_u[[1]], "2021", heights)

grow.m6_u <- make_1yrmod(ramets_early_mods_best_u[[1]], "2021", heights)

grow.m7_u <- make_1yrmod(ramets_late_mods_best_u[[1]], "2021", heights)

grow.m8_u <- make_1yrmod(mortality_mods_best_u[[1]], "2022", survival)
```

##### All
```{r}
all_1yr_mods.u <- list(
  
  # defense
  def.m1_u,
  def.m2_u,
  def.m3_u,
  def.m4_u,
  def.m5_u,
  def.m6_u,
  def.m7_u,
  
  # reproduction
  repr.m1_u,
  repr.m2_u,
  repr.m3_u,
  repr.m4_u,
  repr.m5_u,
  repr.m6_u,
  repr.m7_u,
  repr.m8_u,
  repr.m9_u,
  
  # Herbivores
  herb.m1_u,
  herb.m2_u,
  herb.m3_u,
  
  # growth
  grow.m1_u,
  grow.m2_u,
  grow.m3_u,
  grow.m4_u,
  grow.m5_u,
  grow.m6_u,
  grow.m7_u,
  grow.m8_u
  )
```


## Q2
### City_dist
#### Make lists of models
Compare AIC of full and reduced models, then choose model w/lowest AIC
##### Defense
```{r}
# Latex-----
def.tr.m1 <- latex_mods_best_c[[2]]
AIC(
  # full model
  update(def.tr.m1, .~. + City_dist:Transect_ID),
  # reduced model
  latex_mods_best_c[[2]]
  ) # Qualitatively identical (<2 AIC apart) but reduced is lower


# Herbivory before flowering, binary-----
full1 <- make_1yrmod_transects(herb_e_bin_mods_best_c[[2]], "2021", herbivory)

AIC(
    full1,
    update(full1,
         .~. - City_dist*Transect_ID + City_dist + Transect_ID,
         data = herbivory %>%
           dplyr::filter(Year == 2021 & Transect_ID != "Rural"))) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower
def.tr.m2 <- update(full1,
         .~. - City_dist*Transect_ID + City_dist + Transect_ID,
         data = herbivory %>%
           dplyr::filter(Year == 2021 & Transect_ID != "Rural"))


# Herbivory before flowering, quant-----
full1 <- update(herb_e_quant_mods_best_c[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

AIC(
    full1,
    update(full1,
         .~. - City_dist*Transect_ID + City_dist + Transect_ID)) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower
def.tr.m3 <- update(full1,
         .~. - City_dist*Transect_ID + City_dist + Transect_ID)


# Herbivory after flowering, binary-----
def.tr.m4 <- make_1yrmod_transects(herb_l_bin_mods_best_c[[2]], "2021", herbivory)


full1 <- update(def.tr.m4,
                .~. + City_dist*Transect_ID,
                data = herbivory %>%
                  dplyr::filter(Transect_ID != "Rural" & Year == "2021"))

AIC(
    full1,
    make_1yrmod_transects(herb_l_bin_mods_best_c[[2]], "2021", herbivory)) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower
def.tr.m4 <- make_1yrmod_transects(herb_l_bin_mods_best_c[[2]], "2021", herbivory)
  


# Herbivory after flowering, quant-----
def.tr.m5 <- update(herb_l_quant_mods_best_c[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_late_binary == 1))


full1 <- update(def.tr.m5,
                .~. + City_dist*Transect_ID,
                data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

AIC(
    full1,
    def.tr.m5) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower



# Weevil damage, binary-----
def.tr.m6 <- make_1yrmod_transects(weev_bin_mods_best_c[[2]], "2021", weevil)

full1 <- update(def.tr.m6,
                .~. + City_dist*Transect_ID,
                data = weevil %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021"))

AIC(
    full1,
    def.tr.m6) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Weevil damage, quantitative-----
def.tr.m7 <- update(weev_quant_mods_best_c[[2]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Scar_length_cm > 0))

full1 <- update(def.tr.m7,
                .~. + City_dist*Transect_ID)

AIC(
    full1,
    def.tr.m7) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower
```

##### Reproduction
```{r}
# Flowering success-----
repr.tr.m1 <- make_1yrmod_transects(flsucc_mods_best_c[[2]], "2022", reproduc)

full1 <- update(repr.tr.m1,
                .~. + City_dist*Transect_ID,
                data = reproduc %>%
                  dplyr::filter(Year == "2022" & Transect_ID !=  
    "Rural"))

AIC(
    full1,
    repr.tr.m1) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Flowers-----
repr.tr.m2 <- make_1yrmod_transects(flowers_mods_best_c[[2]], "2022", flowering)

full1 <- update(repr.tr.m2,
                .~. + City_dist*Transect_ID,
                data = flowering %>%
                  dplyr::filter(Year == "2022" & Transect_ID !=  
    "Rural"))

AIC(
    full1,
    repr.tr.m2) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Flower size-----
repr.tr.m3 <- make_1yrmod_transects(flsize_mods_best_c[[2]], "2022", flowering)

full1 <- update(repr.tr.m3,
                .~. + City_dist*Transect_ID,
                data = flowering %>%
                  dplyr::filter(Year == "2022" & Transect_ID !=  
    "Rural"))

AIC(
    full1,
    repr.tr.m3) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Flowering time-----
repr.tr.m4 <- make_1yrmod_transects(fltime_mods_best_c[[2]], "2022", flowering)

full1 <- update(repr.tr.m4,
                .~. + City_dist*Transect_ID,
                data = flowering %>%
                  dplyr::filter(Year == "2022" & Transect_ID !=  
    "Rural"))

AIC(
    full1,
    repr.tr.m4) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Flowering start-----
repr.tr.m5 <- make_1yrmod_transects(flstart_mods_best_c[[2]], "2022", flowering)

full1 <- update(repr.tr.m5,
                .~. + City_dist*Transect_ID,
                data = flowering %>%
                  dplyr::filter(Year == "2022" & Transect_ID !=  
    "Rural"))

AIC(
    full1,
    repr.tr.m5) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Follicles-----
repr.tr.m6 <- make_1yrmod_transects(pods_mods_best_c[[2]], "2022", flowering)

red1 <- update(repr.tr.m6,
                .~. - City_dist*Transect_ID + City_dist + Transect_ID,
                data = flowering %>%
                  dplyr::filter(Year == "2022" & Transect_ID !=  
    "Rural"))

AIC(
    repr.tr.m6,
    red1) %>%
  as.list() # Reduced model doesn't converge so will use full

# First follicle-----
# won't converge if I take the multi-yr mod and alter it- has to be above x - 170, so I chose to increase it by a month to 200 days
repr.tr.m7 <- glmmTMB(Julian_first_follicle-200 ~
                               Block +
                               (1|Population/Family) +
                               City_dist+Transect_ID, 
                             data = flowering %>%
          dplyr::filter(Year == 2022 &
                          Transect_ID != "Rural"),
                             family = poisson)

AIC(
    update(repr.tr.m7,
           .~. + City_dist:Transect_ID),
    repr.tr.m7) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Inflorescences-----
repr.tr.m8 <- make_1yrmod_transects(peduncles_mods_best_c[[2]], "2022", flowering)

AIC(
    update(repr.tr.m8,
           .~. + City_dist:Transect_ID,
           data = flowering %>%
             dplyr::filter(Transect_ID != "Rural" & Year == "2022") ),
    repr.tr.m8) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Pollinaria removed-----
repr.tr.m9 <- make_1yrmod_transects(poll_mods_best_c[[2]], "2022", flowering)

AIC(
    update(repr.tr.m9,
           .~. + City_dist:Transect_ID,
           data = flowering %>%
             dplyr::filter(Transect_ID != "Rural" & Year == "2022") ),
    repr.tr.m9) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower
```

##### Herbivores
```{r}
# Danaus plexippus-----
herb.tr.m1 <- make_1yrmod_transects(monarch_mods_best_c[[2]], "2021", herbivores)

AIC(
    update(herb.tr.m1,
           .~. + City_dist:Transect_ID,
           data = herbivores %>%
             dplyr::filter(Transect_ID != "Rural" & Year == "2021") ),
    herb.tr.m1) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Aphis asclepiadis-----
herb.tr.m2 <- make_1yrmod_transects(asclepiadis_mods_best_c[[2]], "2021", herbivores)

AIC(
    update(herb.tr.m2,
           .~. + City_dist:Transect_ID,
           data = herbivores %>%
             dplyr::filter(Transect_ID != "Rural" & Year == "2021") ),
    herb.tr.m2) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Labidomera clivicollis-----
herb.tr.m3 <- make_1yrmod_transects(clivicollis_mods_best_c[[2]], "2021", herbivores)

AIC(
    herb.tr.m3,
    update(herb.tr.m3,
           .~. - City_dist*Transect_ID + City_dist + Transect_ID,
           data = herbivores %>%
             dplyr::filter(Transect_ID != "Rural" & Year == "2021"))) %>%
  as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower
```

##### Growth
```{r}
# LDMC-----
grow.tr.m1 <- ldmc_mods_best_c[[2]]

AIC(
  # full model
  update(grow.tr.m1, .~. + City_dist:Transect_ID),
  # reduced model
  grow.tr.m1
  ) # Qualitatively identical (<2 AIC apart) but reduced is lower


# SLA-----
grow.tr.m2 <- sla_mods_best_c[[2]]

AIC(
  update(grow.tr.m2, .~. + City_dist:Transect_ID),
  grow.tr.m2
  ) # Qualitatively identical (<2 AIC apart) but reduced is lower


# Height before flowering-----
grow.tr.m3 <- make_1yrmod_transects(heights_early_mods_best_c[[2]], "2021", heights)

AIC(
  update(grow.tr.m3, .~. + City_dist:Transect_ID,
         data = heights %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  grow.tr.m3
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower


# Height after flowering-----
grow.tr.m4 <- make_1yrmod_transects(heights_late_mods_best_c[[2]], "2021", heights)

AIC(
  update(grow.tr.m4, .~. + City_dist:Transect_ID,
         data = heights %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  grow.tr.m4
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower

grow.tr.m4 <- update(
  make_1yrmod_transects(heights_late_mods_best_c[[2]], "2021", heights),
  .~. + City_dist:Transect_ID,
  data = heights %>%
    dplyr::filter(Transect_ID != "Rural" & Year == "2021"))

# Rel growth rate-----
grow.tr.m5 <- make_1yrmod_transects(rgr_mods_best_c[[2]], "2021", heights)

AIC(
  update(grow.tr.m5, .~. + City_dist:Transect_ID,
         data = heights %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  grow.tr.m5
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Ramets before flowering-----
grow.tr.m6 <- make_1yrmod_transects(ramets_early_mods_best_c[[2]], "2021", heights)

AIC(
  update(grow.tr.m6, .~. + City_dist:Transect_ID,
         data = heights %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  grow.tr.m6
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower

grow.tr.m6 <- update(grow.tr.m6, .~. + City_dist:Transect_ID,
         data = heights %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021"))

# Ramets after flowering-----
grow.tr.m7 <- make_1yrmod_transects(ramets_late_mods_best_c[[2]], "2021", heights)

AIC(
  update(grow.tr.m7, .~. + City_dist:Transect_ID,
         data = heights %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  grow.tr.m7
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower

grow.tr.m7 <- update(grow.tr.m7, .~. + City_dist:Transect_ID,
         data = heights %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021"))

# Mortality-----
grow.tr.m8 <- make_1yrmod_transects(mortality_mods_best_c[[2]], "2022", survival)

AIC(
  grow.tr.m8,
  update(grow.tr.m8, .~. - City_dist*Transect_ID + City_dist + Transect_ID,
         data = survival %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022"))
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

grow.tr.m8 <- update(grow.tr.m8, .~. - City_dist*Transect_ID + City_dist + Transect_ID,
         data = survival %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022"))
```

##### All
```{r}
all_1yr_mods_tr <- list(
  
  # defense
  def.tr.m1,
  def.tr.m2,
  def.tr.m3,
  def.tr.m4,
  def.tr.m5,
  def.tr.m6,
  def.tr.m7,
  
  # reproduction
  repr.tr.m1,
  repr.tr.m2,
  repr.tr.m3,
  repr.tr.m4,
  repr.tr.m5,
  repr.tr.m6,
  repr.tr.m7,
  repr.tr.m8,
  repr.tr.m9,
  
  # Herbivores
  herb.tr.m1,
  herb.tr.m2,
  herb.tr.m3,
  
  # growth
  grow.tr.m1,
  grow.tr.m2,
  grow.tr.m3,
  grow.tr.m4,
  grow.tr.m5,
  grow.tr.m6,
  grow.tr.m7,
  grow.tr.m8
  )
```


### Urb_score
#### Make lists of models
##### Defense
```{r}
# Latex-----
def.tr.m1_u <- latex_mods_best_u[[2]]

AIC(
  # full model
  latex_mods_best_u[[2]],
  # reduced model
  update(def.tr.m1_u, .~. - Urb_score*Transect_ID + Urb_score + Transect_ID)
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower

# Herbivory before flowering, binary-----
def.tr.m2_u <- make_1yrmod_transects(herb_e_bin_mods_best_u[[2]], "2021", herbivory)

AIC(
  update(def.tr.m2_u, .~. + Urb_score:Transect_ID,
         data = herbivory %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  def.tr.m2_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Herbivory before flowering, quant-----
def.tr.m3_u <- update(herb_e_quant_mods_best_u[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

AIC(
  def.tr.m3_u,
  update(def.tr.m3_u, .~. - Urb_score:Transect_ID,
         data = herbivory %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021" &
                                   Herbivory_mean_early_binary == 1))
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

def.tr.m3_u <- update(def.tr.m3_u, .~. - Urb_score:Transect_ID,
         data = herbivory %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

# Herbivory after flowering, binary-----
def.tr.m4_u <- make_1yrmod_transects(herb_l_bin_mods_best_u[[2]], "2021", herbivory)

AIC(
  update(def.tr.m4_u, .~. + Urb_score:Transect_ID,
         data = herbivory %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  def.tr.m4_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Herbivory after flowering, quant-----
def.tr.m5_u <- update(herb_l_quant_mods_best_u[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

AIC(
  update(def.tr.m5_u, .~. + Urb_score:Transect_ID,
         data = herbivory %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021" &
                                   Herbivory_mean_late_binary == 1)),
  def.tr.m5_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower

def.tr.m5_u <- update(def.tr.m5_u, .~. + Urb_score:Transect_ID,
         data = herbivory %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021" &
                                   Herbivory_mean_late_binary == 1))


# Weevil damage, binary-----
def.tr.m6_u <- make_1yrmod_transects(weev_bin_mods_best_u[[2]], "2021", weevil)

AIC(
  update(def.tr.m6_u, .~. + Urb_score:Transect_ID,
         data = weevil %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  def.tr.m6_u
  ) %>% as.list() # Full model is best

def.tr.m6_u <- update(def.tr.m6_u, .~. + Urb_score:Transect_ID,
         data = weevil %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021"))

# Weevil damage, quant-----
def.tr.m7_u <- update(weev_quant_mods_best_u[[2]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Scar_length_cm > 0))


AIC(
  update(def.tr.m7_u, .~. + Urb_score:Transect_ID,
         data = weevil %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021"&
                                   Scar_length_cm > 0)),
  def.tr.m7_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower
```

##### Reproduction
```{r}
# Flowering success-----
repr.tr.m1_u <- make_1yrmod_transects(flsucc_mods_best_u[[2]], "2022", reproduc)

AIC(
  update(repr.tr.m1_u, .~. + Urb_score:Transect_ID,
         data = reproduc %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022")),
  repr.tr.m1_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower

repr.tr.m1_u <- update(repr.tr.m1_u, .~. + Urb_score:Transect_ID,
         data = reproduc %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022"))

# Flowers-----
repr.tr.m2_u <- make_1yrmod_transects(flowers_mods_best_u[[2]], "2022", flowering)

AIC(
  repr.tr.m2_u,
  update(repr.tr.m2_u, .~. - Urb_score:Transect_ID,
         data = flowering %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022"))
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

repr.tr.m2_u <- update(repr.tr.m2_u, .~. - Urb_score:Transect_ID,
         data = flowering %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022"))

# Flower size-----
repr.tr.m3_u <- make_1yrmod_transects(flsize_mods_best_u[[2]], "2022", flowering)

AIC(
  update(repr.tr.m3_u, .~. + Urb_score:Transect_ID,
         data = flowering %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022")),
  repr.tr.m3_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Flowering time-----
repr.tr.m4_u <- make_1yrmod_transects(fltime_mods_best_u[[2]], "2022", flowering)

AIC(
  update(repr.tr.m4_u, .~. + Urb_score:Transect_ID,
         data = flowering %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022")),
  repr.tr.m4_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower

repr.tr.m4_u <- update(repr.tr.m4_u, .~. + Urb_score:Transect_ID,
         data = flowering %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022"))

# Flowering start-----
repr.tr.m5_u <- make_1yrmod_transects(flstart_mods_best_u[[2]], "2022", flowering)

AIC(
  repr.tr.m5_u,
  update(repr.tr.m5_u, .~. - Urb_score:Transect_ID,
         data = flowering %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022"))
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

repr.tr.m5_u <- update(repr.tr.m5_u, .~. - Urb_score:Transect_ID,
         data = flowering %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022"))

# Follicles-----
repr.tr.m6_u <- make_1yrmod_transects(pods_mods_best_u[[2]], "2022", flowering)

AIC(
  repr.tr.m6_u,
  update(repr.tr.m6_u, .~. - Urb_score:Transect_ID,
         data = flowering %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022"))
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower


# First follicle-----
# other models of this variable won't converge if I take the multi-yr mod and alter it- has to be above x - 170, so I chose to increase it by a month to 200 days
repr.tr.m7_u <- glmmTMB(Julian_first_follicle-200 ~
                               Block +
                               (1|Population/Family) +
                               Urb_score+Transect_ID, 
                             data = flowering %>%
          dplyr::filter(Year == 2022 &
                          Transect_ID != "Rural"),
                             family = poisson)

AIC(
  update(repr.tr.m7_u, .~. + Urb_score:Transect_ID),
  repr.tr.m7_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower

repr.tr.m7_u <- update(repr.tr.m7_u, .~. + Urb_score:Transect_ID)

# Inflorescences-----
repr.tr.m8_u <- make_1yrmod_transects(peduncles_mods_best_u[[2]], "2022", flowering)

AIC(
  repr.tr.m8_u,
  update(repr.tr.m8_u, .~. - Urb_score:Transect_ID,
         data = flowering %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022"))
  ) %>% as.list() # Full model is best


# Pollinaria removed-----
repr.tr.m9_u <- make_1yrmod_transects(poll_mods_best_u[[2]], "2022", flowering)

AIC(
  update(repr.tr.m9_u, .~. + Urb_score:Transect_ID,
         data = flowering %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2022")),
  repr.tr.m9_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower
```

##### Herbivores
```{r}
# Danaus plexippus-----
herb.tr.m1_u <- make_1yrmod_transects(monarch_mods_best_u[[2]], "2021", herbivores)

AIC(
  update(herb.tr.m1_u, .~. + Urb_score:Transect_ID,
         data = herbivores %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  herb.tr.m1_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Aphis asclepiadis-----
herb.tr.m2_u <- make_1yrmod_transects(asclepiadis_mods_best_u[[2]], "2021", herbivores)

AIC(
  update(herb.tr.m2_u, .~. + Urb_score:Transect_ID,
         data = herbivores %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  herb.tr.m2_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Labidomera clivicollis-----
herb.tr.m3_u <- make_1yrmod_transects(clivicollis_mods_best_u[[2]], "2021", herbivores)

AIC(
  update(herb.tr.m3_u, .~. + Urb_score:Transect_ID,
         data = herbivores %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  herb.tr.m3_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower

herb.tr.m3_u <- update(herb.tr.m3_u, .~. + Urb_score:Transect_ID,
         data = herbivores %>%
           dplyr::filter(Transect_ID != "Rural" & Year == "2021"))
```

##### Growth
```{r}
# LDMC-----
grow.tr.m1_u <- ldmc_mods_best_u[[2]]

AIC(
  update(grow.tr.m1_u, .~. + Urb_score:Transect_ID),
  grow.tr.m1_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# SLA-----
grow.tr.m2_u <- sla_mods_best_u[[2]]

AIC(
  update(grow.tr.m2_u, .~. + Urb_score:Transect_ID),
  grow.tr.m2_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Height before flowering-----
grow.tr.m3_u <- make_1yrmod_transects(heights_early_mods_best_u[[2]], "2021", heights)

AIC(
  update(grow.tr.m3_u, .~. + Urb_score:Transect_ID,
         data = heights %>% dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  grow.tr.m3_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Height after flowering-----
grow.tr.m4_u <- make_1yrmod_transects(heights_late_mods_best_u[[2]], "2021", heights)

AIC(
  update(grow.tr.m4_u, .~. + Urb_score:Transect_ID,
         data = heights %>% dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  grow.tr.m4_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Rel growth rate-----
grow.tr.m5_u <- make_1yrmod_transects(rgr_mods_best_u[[2]], "2021", heights)

AIC(
  update(grow.tr.m5_u, .~. + Urb_score:Transect_ID,
         data = heights %>% dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  grow.tr.m5_u
  ) %>% as.list() # Full model doesn't converge so will use reduced

# Ramets before flowering-----
grow.tr.m6_u <- make_1yrmod_transects(ramets_early_mods_best_u[[2]], "2021", heights)

AIC(
  update(grow.tr.m6_u, .~. + Urb_score:Transect_ID,
         data = heights %>% dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  grow.tr.m6_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Ramets after flowering-----
grow.tr.m7_u <- make_1yrmod_transects(ramets_late_mods_best_u[[2]], "2021", heights)

AIC(
  update(grow.tr.m7_u, .~. + Urb_score:Transect_ID,
         data = heights %>% dplyr::filter(Transect_ID != "Rural" & Year == "2021")),
  grow.tr.m7_u
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but reduced is lower

# Mortality-----
grow.tr.m8_u <- make_1yrmod_transects(mortality_mods_best_u[[2]], "2022", survival)

AIC(
  grow.tr.m8_u,
  update(grow.tr.m8_u, .~. - Urb_score:Transect_ID,
         data = survival %>% dplyr::filter(Transect_ID != "Rural" & Year == "2022"))
  ) %>% as.list() # Qualitatively identical (<2 AIC apart) but full is lower

grow.tr.m8_u <- update(grow.tr.m8_u, .~. - Urb_score:Transect_ID,
         data = survival %>% dplyr::filter(Transect_ID != "Rural" & Year == "2022"))
```

##### All
```{r}
all_1yr_mods.u_tr <- list(
  
  # defense
  def.tr.m1_u,
  def.tr.m2_u,
  def.tr.m3_u,
  def.tr.m4_u,
  def.tr.m5_u,
  def.tr.m6_u,
  def.tr.m7_u,
  
  # reproduction
  repr.tr.m1_u,
  repr.tr.m2_u,
  repr.tr.m3_u,
  repr.tr.m4_u,
  repr.tr.m5_u,
  repr.tr.m6_u,
  repr.tr.m7_u,
  repr.tr.m8_u,
  repr.tr.m9_u,
  
  # Herbivores
  herb.tr.m1_u,
  herb.tr.m2_u,
  herb.tr.m3_u,
  
  # growth
  grow.tr.m1_u,
  grow.tr.m2_u,
  grow.tr.m3_u,
  grow.tr.m4_u,
  grow.tr.m5_u,
  grow.tr.m6_u,
  grow.tr.m7_u,
  grow.tr.m8_u
  )
```