---
title: "KSR 2020 Herbivore Analysis"
author: "Sophie Breitbart"
output:
  html_document:
    number_sections: true
    df_print: paged
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
editor_options: 
  chunk_output_type: console
---

*Background information:*

* Herbivore surveys were done twice: Once in July, once in August.
* The species observed are in the column names. The only species with two columns was the Monarch butterfly:
    + one column for Monarchs that had been on the plant in the past ("mean_Monarch_Quantity_Past") and which refers to empty chrysalis, empty eggs, and chrysalis with a dead butterfly inside, and
    + one column for alive Monarchs present on the plant itself ("mean_Monarch_Quantity_Observed") and which refers to all other Monarch forms (caterpillars, eggs, chrysalises with insects still inside)
* Monarchs notwithstanding, dead herbivores were not counted in the surveys. After Hellinger transformation, though, the mean_Monarch_Quantity_Past column had been converted to all 0's.
* Environmental variables are as follows:
    + To quantify urbanization, both distance from the city center and urbanization score were used, separately.
    + Transect was also used as a variable when analyzing the urban sites ONLY (i.e. excluding rural sites).


**Questions:**

* To what extent is urbanization associated with genetic divergence in phenotypic traits among subpopulations?
* Is proximity to urban corridors related to the levels of genetic divergence among urban subpopulations?


WHEN TOTALLY DONE, type this:
renv::activate()
renv::snapshot()

# Set up notebook
## Load libraries & functions
```{r}
source("libraries.R")
source("functions.R")
```

## Import data
```{r}
herbivores <- read.csv(here::here("./Joined_annual_data/herbivores.csv")) %>%
  dplyr::select(., -1) %>%
  dplyr::mutate_at(vars(c("Population",
                          "Family",
                          "Replicate",
                          "Block",
                          "Transect_ID",
                          "Sample",
                          "Patch_ID",
                          "Urb_Rur",
                          "Year",
                          "Surveyor",
                          "Date")),
                   as.character) %>%
    dplyr::mutate_at(vars(c("Population",
                            "Family",
                            "Replicate",
                            "Block",
                            "Transect_ID",
                            "Sample",
                            "Patch_ID",
                            "Urb_Rur",
                            "Year",
                            "Surveyor",
                          "Date")),
                     as.factor)

str(herbivores)  


herbivores %<>%
  dplyr::mutate(Fam_uniq = paste0(Population, "_", Family))
```

## Import final models
```{r}
source(knitr::purl("Defense_trait_analyses/Model_diagnostics_herbivores.Rmd", quiet=TRUE))

all_models <- list(
monarch_mods          , 
asclepiadis_mods           , 
clivicollis_mods)

names(all_models) <- c(
"monarch_mods"          ,
"asclepiadis_mods"           ,
"clivicollis_mods"         )
```

### Create separate lists of best vs. alt models for city_dist vs urb_score
#### Monarchs
```{r}
## Best
### City_dist
monarch_mods_best_c <- monarch_mods[c(1,4)]

### Urb_score
monarch_mods_best_u <- monarch_mods[c(2,6)]

## Alt
### City_dist
monarch_mods_alt_c <- monarch_mods[3]

### Urb_score
monarch_mods_alt_u <- monarch_mods[5]
```

#### L. asclepiadis
```{r}
## Best
### City_dist
asclepiadis_mods_best_c <- asclepiadis_mods[c(1,4)]

### Urb_score
asclepiadis_mods_best_u <- asclepiadis_mods[c(2,6)]

## Alt
### City_dist
asclepiadis_mods_alt_c <- asclepiadis_mods[3]

### Urb_score
asclepiadis_mods_alt_u <- asclepiadis_mods[5]
```


#### L. clivicollis
```{r}
## Best
### City_dist
clivicollis_mods_best_c <- clivicollis_mods[c(1,4)]

### Urb_score
clivicollis_mods_best_u <- clivicollis_mods[c(2,6)]

## Alt
### City_dist
clivicollis_mods_alt_c <- clivicollis_mods[3]

### Urb_score
clivicollis_mods_alt_u <- clivicollis_mods[5]

```

# Ranova
## Gradient / City_dist
### Generalized LMM use bootstrapping with pbmodcomp()
#### Monarchs
```{r}
# NOT PERFECT b/c can't nest family within pop
# Ben Bolker says it should work too: https://stackoverflow.com/questions/69842066/testing-for-the-significance-of-a-random-effect-in-a-mixed-model
# https://github.com/glmmTMB/glmmTMB/issues/456


# Monarchs-----
## test city_dist
# full <- glmer(Monarch_Quantity_Observed ~
#                                 (1|Block) +
#                                 (1|Population/Family) +
#                                 (1|Year) +
#                                 (1|Sample) +
#                                 City_dist,
#               data = herbivores,
#               family = poisson,
#              na.action = na.exclude # THIS LINE IS IMPORTANT
#   # ,control=glmerControl(optimizer="bobyqa",
#   #                           optCtrl=list(maxfun=2e5))
#   )
# 
# reduced <- update(full, .~. - City_dist)
# 
# monarch_ranova <- PBmodcomp(full, reduced,
#           nsim = 1000,
#           cl = makeCluster(rep("localhost", 6)))
# tidy(monarch_ranova) # not converging


# take out block and year
full <- glmer(Monarch_Quantity_Observed ~
                                # (1|Block) +
                                (1|Population/Family) +
                                # (1|Year) +
                                (1|Sample) +
                                City_dist,
              data = herbivores,
              family = poisson,
             na.action = na.exclude # THIS LINE IS IMPORTANT
  # ,control=glmerControl(optimizer="bobyqa",
  #                           optCtrl=list(maxfun=2e5))
  )

reduced <- update(full, .~. - City_dist)

monarch_ranova.pop <- PBmodcomp(full, reduced,
          nsim = 100,
          cl = makeCluster(6))
tidy(monarch_ranova.pop) #  p ~ 0.5





# take out fam
full <- glmer(Monarch_Quantity_Observed ~
                # (1|Block) + (1|Year) + 
                (1|Population) + (1|Sample) +
                                City_dist,
              data = herbivores,
              family = poisson,
             na.action = na.exclude # THIS LINE IS IMPORTANT
  )

reduced <- update(full, .~. - City_dist)

monarch_ranova.fam <- PBmodcomp(full, reduced,
          nsim = 1000,
          cl = makeCluster(rep("localhost", 6)))
tidy(monarch_ranova.fam) # Fam: p ~ 



# merge Pop and Fam ranovas
monarch_ranova1 <- CreateRanovaOutput_bootstrap(monarch_ranova.fam, monarch_ranova.pop, "Monarch butterfly") %T>%
  flextable::save_as_html(path = here::here("./Defense_trait_analyses/Tables/Ranova/Monarch.html"))
```

# ANOVA
## Monarchs
### Best Models
#### City_dist
```{r}
make_all_anovas_tidy(monarch_mods_best_c) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Best_models/monarch_citydist.png"))

lapply(monarch_mods_best_c, MuMIn::r.squaredGLMM)

```

#### Urb_score
```{r}
make_all_anovas_tidy(monarch_mods_best_u) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Best_models/monarch_urbscore.png"))
```

### Alternative Models
#### City_dist
```{r}
make_all_anovas_tidy_altmods(monarch_mods_alt_c) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Alt_models/monarch_citydist_alt.png"))
```

#### Urb_score
```{r}
make_all_anovas_tidy_altmods(monarch_mods_alt_u) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Alt_models/monarch_urbscore_alt.png"))
```
## L. asclepiadis
### Best Models
#### City_dist
```{r}
make_all_anovas_tidy(asclepiadis_mods_best_c) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Best_models/asclepiadis_citydist.png"))
```

#### Urb_score
```{r}
make_all_anovas_tidy(asclepiadis_mods_best_u) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Best_models/asclepiadis_urbscore.png"))
```

### Alt Models
#### City_dist
```{r}
make_all_anovas_tidy_altmods(asclepiadis_mods_alt_c) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Alt_models/asclepiadis_citydist_alt.png"))
```

#### Urb_score
```{r}
make_all_anovas_tidy_altmods(asclepiadis_mods_alt_u) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Alt_models/asclepiadis_urbscore_alt.png"))
```
## L. clivicollis
### Best Models
#### City_dist
```{r}
make_all_anovas_tidy(clivicollis_mods_best_c) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Best_models/clivicollis_citydist.png"))
```

#### Urb_score
```{r}
make_all_anovas_tidy(clivicollis_mods_best_u) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Best_models/clivicollis_urbscore.png"))
```

### Alt Models
#### City_dist
```{r}
make_all_anovas_tidy_altmods(clivicollis_mods_alt_c) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Alt_models/clivicollis_citydist_alt.png"))
```

#### Urb_score
```{r}
make_all_anovas_tidy_altmods(clivicollis_mods_alt_u) %>%
  save_as_image(., path = here::here("./Defense_trait_analyses/Figures/ANOVA/Herbivores/Alt_models/clivicollis_urbscore_alt.png"))
```

# R-sq values
```{r}
all_rsq <- lapply(all_models, lapply, r.squaredGLMM) %>%
  unlist(recursive = FALSE)

# adj. R2 values very small. Conditional larger though
```
# Heritability and Qst