---
title: "Defense Trait Analysis"
author: "Sophie Breitbart"
output:
  html_document:
    number_sections: true
    df_print: paged
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
editor_options: 
  chunk_output_type: console
NOTES:
  -Still to do--
    -try to do an RDA (or PCA?) with all the traits
    -make a ReadMe file for each level
    -calculate heritability coefficients

# WHEN TOTALLY DONE, type this:
# renv::activate()
# renv::snapshot()
---

+-----------------------------+-----------+-----------+-----------+
| Trait                       | 2019 Data | 2020 Data | 2021 Data |
+=============================+:=========:+:=========:+:=========:+
| Herbivory                   | X         | X         | X         |
+-----------------------------+-----------+-----------+-----------+
| Weevil damage: Quantitative |           | X         | X         |
+-----------------------------+-----------+-----------+-----------+
| Weevil damage: Binary       |           | X         |           |
+-----------------------------+-----------+-----------+-----------+
| Specific Leaf Area          |           | X         |           |
+-----------------------------+-----------+-----------+-----------+
| Dry Leaf Matter Content     |           | X         |           |
+-----------------------------+-----------+-----------+-----------+
| Cardenolide Concentration   |           | X         |           |
+-----------------------------+-----------+-----------+-----------+
| Latex Volume                |           | X         |           |
+-----------------------------+-----------+-----------+-----------+

# Set up notebook

## Load libraries and add functions

```{r}
source("libraries.R")
source("functions.R")
```

## Import data

```{r}
herbivory <- read.csv(here::here("./Joined_annual_data/herbivory.csv"), na.strings=c("NO PLANT", "none"), blank.lines.skip=TRUE, header=TRUE, sep=",") %>%
  dplyr::select(., -1)

weevil <- read.csv(here::here("./Joined_annual_data/weevil.csv"), na.strings=c("NO PLANT", "none"), blank.lines.skip=TRUE, header=TRUE, sep=",")%>%
  dplyr::select(., -1)


sla_ldmc <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_sla_ldmc_clean.csv")) %>%
  dplyr::select(., -c(1:2))

cards <-  read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/Cardenolides_forR.csv"))
```

## MAKE DIAGNOSTIC RMD NEXT, THEN FIGURE OUT HOW TO STRUCTURE REST OF THIS
### Herbivory
#### Entire gradient: *NOT sig for city_dist or urb_score
##### City_dist
```{r}
car::Anova(herbivory_gr_dist_m5)
# doesn't converge with all terms... 

r.squaredGLMM(herbivory_gr_dist_m5)
```

##### Urb_score
```{r}
car::Anova(ramets_gr_usc_m1)
# dist not significant

r.squaredGLMM(ramets_gr_usc_m1)

```

#### Urban subtransects: nothing sig
##### City_dist
```{r}
car::Anova(ramets_urb_dist_m1)
# nothing sig

r.squaredGLMM(ramets_urb_dist_m1)


# just main effects
car::Anova(ramets_urb_dist_m2_ME)
# nothing sig

r.squaredGLMM(ramets_urb_dist_m2_ME)

AIC((ramets_urb_dist_m1),
    (ramets_urb_dist_m2_ME)) # better but <2 AIC from full model
```

##### Urb_score
```{r}
car::Anova(ramets_urb_usc_m1)
# nothing sig

r.squaredGLMM(ramets_urb_usc_m1)


# just main effects
car::Anova(ramets_urb_usc_m2_ME)
# nothing sig

r.squaredGLMM(ramets_urb_usc_m2_ME)

AIC((ramets_urb_usc_m1),
    (ramets_urb_usc_m2_ME)) # better but <2 AIC from full model
```


