---
title: "Defense Trait Analysis"
author: "Sophie Breitbart"
output:
  html_document:
    number_sections: true
    df_print: paged
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
editor_options: 
  chunk_output_type: console
NOTES:
  -Still to do--
    -try to do an RDA (or PCA?) with all the traits
    -make a ReadMe file for each level
    -calculate heritability coefficients

# WHEN TOTALLY DONE, type this:
# renv::activate()
# renv::snapshot()
---

# Set up notebook
## Load libraries & functions
```{r}
source("libraries.R")
source("functions.R")
```

## Import data
```{r}
herbivores <- read.csv(here::here("./Joined_annual_data/herbivores.csv")) %>%
  dplyr::select(., -1) %>%
  dplyr::mutate_at(vars(c("Population",
                          "Family",
                          "Replicate",
                          "Block",
                          "Transect_ID",
                          "Sample",
                          "Patch_ID",
                          "Urb_Rur",
                          "Year",
                          "Surveyor",
                          "Date")),
                   as.character) %>%
    dplyr::mutate_at(vars(c("Population",
                            "Family",
                            "Replicate",
                            "Block",
                            "Transect_ID",
                            "Sample",
                            "Patch_ID",
                            "Urb_Rur",
                            "Year",
                            "Surveyor",
                          "Date")),
                     as.factor)

str(herbivores)  


herbivores %<>%
  dplyr::mutate(Fam_uniq = paste0(Population, "_", Family))
```

## Import final models
```{r}
source(knitr::purl("Defense_trait_analyses/Model_diagnostics_herbivores.Rmd", quiet=TRUE))

all_models <- list(
monarch_mods          , 
asclepiadis_mods           , 
clivicollis_mods)

names(all_models) <- c(
"monarch_mods"          ,
"asclepiadis_mods"           ,
"clivicollis_mods"         )
```

### Create separate lists of best vs. alt models for city_dist vs urb_score
#### Monarchs
```{r}
## Best
### City_dist
monarch_mods_best_c <- monarch_mods[c(1,4)]

### Urb_score
monarch_mods_best_u <- monarch_mods[c(2,6)]

## Alt
### City_dist
monarch_mods_alt_c <- monarch_mods[3]

### Urb_score
monarch_mods_alt_u <- monarch_mods[5]
```

#### L. asclepiadis
```{r}
## Best
### City_dist
asclepiadis_mods_best_c <- asclepiadis_mods[c(1,4)]

### Urb_score
asclepiadis_mods_best_u <- asclepiadis_mods[c(2,6)]

## Alt
### City_dist
asclepiadis_mods_alt_c <- asclepiadis_mods[3]

### Urb_score
asclepiadis_mods_alt_u <- asclepiadis_mods[5]
```


#### L. clivicollis
```{r}
## Best
### City_dist
clivicollis_mods_best_c <- clivicollis_mods[c(1,4)]

### Urb_score
clivicollis_mods_best_u <- clivicollis_mods[c(2,6)]

## Alt
### City_dist
clivicollis_mods_alt_c <- clivicollis_mods[3]

### Urb_score
clivicollis_mods_alt_u <- clivicollis_mods[5]

```

# Create ggpredict objects
## Monarchs
### Gradient
```{r}
# city_dist
monarch_mods_best_c[1]
monarch_gradient_01_pred <- ggeffects::ggpredict(monarch_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
monarch_mods_best_u[1]
monarch_gradient_02_pred <- ggeffects::ggpredict(monarch_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
```

### Urban Subtransects
```{r}
# city_dist
monarch_mods_best_c[2]
monarch_urbsubs_01_pred <- ggeffects::ggpredict(monarch_mods_best_c[[2]],
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
monarch_mods_best_u[2]
monarch_urbsubs_02_pred <- ggeffects::ggpredict(monarch_mods_best_u[[2]],
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```

## L. asclepiadis
### Gradient
```{r}
# city_dist
asclepiadis_mods_best_c[1] # SQRT TRANSFORMED
asclepiadis_gradient_01_pred <- ggeffects::ggpredict(asclepiadis_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 
### NOTE: Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.

# urb_score
asclepiadis_mods_best_u[1] # SQRT-TRANSFORMED
asclepiadis_gradient_02_pred <- ggeffects::ggpredict(asclepiadis_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
### NOTE: Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.

```

### Urban Subtransects
```{r}
# city_dist
asclepiadis_mods_best_c[2]# SQRT-TRANSFORMED
asclepiadis_urbsubs_01_pred <- ggeffects::ggpredict(asclepiadis_mods_best_c[[2]],
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()
### NOTE: Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.


# urb_score
asclepiadis_mods_best_u[2]# SQRT-TRANSFORMED
asclepiadis_urbsubs_02_pred <- ggeffects::ggpredict(asclepiadis_mods_best_u[[2]],
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
### NOTE: Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.
```

## L. clivicollis
### Gradient
```{r}
# city_dist
clivicollis_mods_best_c[1] #SQRT TRANSFORMED
clivicollis_gradient_01_pred <- ggeffects::ggpredict(clivicollis_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.

# urb_score
clivicollis_mods_best_u[1] #SQRT TRANSFORMED
clivicollis_gradient_02_pred <- ggeffects::ggpredict(clivicollis_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()

# Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.

```

### Urban Subtransects
```{r}
# city_dist
clivicollis_mods_best_c[2] # binary
clivicollis_urbsubs_01_pred <- ggeffects::ggpredict(clivicollis_mods_best_c[[2]],
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()
### NOTE: Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.


# urb_score
clivicollis_mods_best_u[2] # BINARY
clivicollis_urbsubs_02_pred <- ggeffects::ggpredict(clivicollis_mods_best_u[[2]],
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
### NOTE: Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.
```

# Create plots
## first, create variable associated with replicated aesthetics of figs
```{r}
# Gradient figs
rep_geoms <- c(geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F),
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3))

# Transect figs
rep_geoms2 <- c(geom_smooth(
  aes(
    x = x,
    y = predicted,
    color = group),
  size = 1,
  se = F),
  geom_ribbon(aes(
    x = x,
    ymin = predicted - std.error,
    ymax = predicted + std.error,
    fill = group),
    alpha = 0.3),
  scale_colour_brewer(labels = c("Corridor",
                                 "Non-Corridor"),
                      palette = "Set2"),
  scale_fill_brewer(labels = c("Corridor",
                               "Non-Corridor"),
                    palette = "Set2"))
```

## Gradient
### City_dist
```{r}
# LDMC-----
ggpred_Q1.citydist_ldmc <- 
ggplot(ldmc_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = "Leaf Dry Matter Content") +
  ylim(0.15, 0.18) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(ldmc_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_ldmc



# SLA-----
ggpred_Q1.citydist_sla <- ggplot(sla_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Specific Leaf Area "(cm^2/g))) +
  ylim(18, 26) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(sla_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_sla



# LATEX-----
ggpred_Q1.citydist_latex <- ggplot(latex_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = "Latex Exudation (mg)") +
  ylim(6, 10) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(latex_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_latex

# herbivory- early-----
ggpred_Q1.citydist_herb_e <- ggplot(herb_e_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Herbivory (Before Flowering) " ^{1/3})) +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(herb_e_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_herb_e


# herbivory- late-----
ggpred_Q1.citydist_herb_l <- ggplot(herb_l_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Herbivory (After Flowering) " ^{1/3})) +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(herb_l_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_herb_l


# weevil damage- binary-----
ggpred_Q1.citydist_weev_bin <- ggplot(weev_b_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = "Weevil Damage Outcome") +
    scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(0, 1.2),
    breaks = c(0, .25, .5, .75, 1)) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(weev_bin_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_weev_bin



# weevil damage- quantitative-----
ggpred_Q1.citydist_weev_quant <- ggplot(weev_q_gradient_01_pred) +
  rep_geoms +
  ylim(1.5, NA) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Weevil Scar Length (cm) " ^{1/3})) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(weev_quant_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_weev_quant
```

### Urbanization Score
```{r}
# LDMC-----
ggpred_Q1.urbscore_ldmc <- 
ggplot(ldmc_gradient_02_pred) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = "Leaf Dry Matter Content") +
  xlim(4, -4) +
  ylim(0.15, 0.18) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(ldmc_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_ldmc



# SLA-----
ggpred_Q1.urbscore_sla <- ggplot(sla_gradient_02_pred) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = expression("sqrt(Specific Leaf Area) "(cm^2/g))) +
  ylim(19.5, 21.5) +
    xlim(4, -4) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(sla_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_sla



# LATEX-----
ggpred_Q1.urbscore_latex <- ggplot(latex_gradient_02_pred) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = "Latex Exudation (mg)") +
    xlim(4, -4) +
  # ylim(6, 10) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(latex_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_latex

# herbivory- early-----
ggpred_Q1.urbscore_herb_e <- ggplot(herb_e_gradient_02_pred) +
  rep_geoms +
    xlim(4, -4) +
  labs(x = "Urbanization Score",
       y = expression("Herbivory (Before Flowering) " ^{1/3})) +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Urb. Score: p = ", tidy_anova(herb_e_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_herb_e


# herbivory- late-----
ggpred_Q1.urbscore_herb_l <- ggplot(herb_l_gradient_02_pred) +
  rep_geoms +
    xlim(4, -4) +
  labs(x = "Urbanization Score",
       y = expression("Herbivory (After Flowering) " ^{1/3})) +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Urb. Score: p = ", tidy_anova(herb_l_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_herb_l


# weevil damage- binary-----
ggpred_Q1.urbscore_weev_bin <- ggplot(weev_b_gradient_02_pred) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = "Weevil Damage Outcome") +
    xlim(4, -4) +
    scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(0, 1.15),
    breaks = c(0, .25, .50, .75, 1)) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(weev_bin_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_weev_bin



# weevil damage- quantitative-----
ggpred_Q1.urbscore_weev_quant <- ggplot(weev_q_gradient_02_pred) +
  rep_geoms +
  ylim(1.5, NA) +
    xlim(4, -4) +
  labs(x = "Urbanization Score",
       y = expression("Weevil Scar Length (cm) " ^{1/3})) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(weev_quant_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_weev_quant
```

## Urban Subtransects
### City_dist
```{r}
# LDMC-----
ggpred_Q2.citydist_ldmc <-
ggplot(ldmc_urbsubs_01_pred) +
  labs(x = "Distance to Urban Center (km)",
       y = "Leaf Dry Matter Content",
       color = "Transect",
       fill = "Transect") +
  ylim(NA, 0.19) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(ldmc_mods_best_c[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(ldmc_mods_best_c[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.citydist_ldmc

# SLA-----
ggpred_Q2.citydist_sla <- 
ggplot(sla_urbsubs_01_pred) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Specific Leaf Area "(cm^2/g)),
       color = "Transect",
       fill = "Transect") +
  ylim(NA, 22) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(sla_mods_best_c[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(sla_mods_best_c[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.citydist_sla


# latex-----
ggpred_Q2.citydist_latex <- 
ggplot(latex_urbsubs_01_pred) +
  rep_geoms2 +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Latex Exudation (g) "^{1/2}),
       color = "Transect",
       fill = "Transect") +
  ylim(6.25, 8.5) +
    xlim(0, NA) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(latex_mods_best_c[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(latex_mods_best_c[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.citydist_latex

# herbivory: Before flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
herb_e_urbsubs_01_pred$group <- factor(herb_e_urbsubs_01_pred$group,
                                   levels(herb_e_urbsubs_01_pred$group)[c(2,1)])
levels(herb_e_urbsubs_01_pred$group)

ggpred_Q2.citydist_herb_e <- 
ggplot(herb_e_urbsubs_01_pred) +
  rep_geoms2 +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Herbivory (Before Flowering) "^{1/3}),
       color = "Transect",
       fill = "Transect") +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
  xlim(0, NA) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(herb_e_mods_best_c[[2]])$p[2])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(herb_e_mods_best_c[[2]])$p[3])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.79,
                    label = paste0(" D x T: p = ", tidy_anova(herb_e_mods_best_c[[2]])$p[4])),
                size = 4.5)

ggpred_Q2.citydist_herb_e

# herbivory: After flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
herb_l_urbsubs_01_pred$group <- factor(herb_l_urbsubs_01_pred$group,
                                   levels(herb_l_urbsubs_01_pred$group)[c(2,1)])
levels(herb_l_urbsubs_01_pred$group)


ggpred_Q2.citydist_herb_l <- 
ggplot(herb_l_urbsubs_01_pred) +
  rep_geoms2 +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Herbivory (After Flowering) "^{1/3}),
       color = "Transect",
       fill = "Transect") +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
  xlim(0, NA) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 1,
                    label = paste0(" Distance: p = ", tidy_anova(herb_l_mods_best_c[[2]])$p[2])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.93,
                    label = paste0(" Transect: p = ", tidy_anova(herb_l_mods_best_c[[2]])$p[3])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.86,
                    label = paste0(" D x T: p = ", tidy_anova(herb_l_mods_best_c[[2]])$p[4])),
                size = 4.5)

ggpred_Q2.citydist_herb_l


# Weevil damage: Binary-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
weev_bin_urbsubs_01_pred$group <- factor(weev_bin_urbsubs_01_pred$group,
                                   levels(weev_bin_urbsubs_01_pred$group)[c(2,1)])
levels(weev_bin_urbsubs_01_pred$group)


ggpred_Q2.citydist_weev_bin <- 
ggplot(weev_bin_urbsubs_01_pred) +
  rep_geoms2 +
  labs(x = "Distance to Urban Center (km)",
       y = "Weevil Damage Outcome",
       color = "Transect",
       fill = "Transect") +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(0, 1.2),
    breaks = c(0, .25, .5, .75, 1)
    ) +
  xlim(0, NA) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.1,
                    label = paste0(" Distance: p = ", tidy_anova(weev_bin_mods_best_c[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.04,
                    label = paste0(" Transect: p = ", tidy_anova(weev_bin_mods_best_c[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.citydist_weev_bin


# Weevil damage: Quantitative-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
weev_quant_urbsubs_01_pred$group <- factor(weev_quant_urbsubs_01_pred$group,
                                   levels(weev_quant_urbsubs_01_pred$group)[c(2,1)])
levels(weev_quant_urbsubs_01_pred$group)


ggpred_Q2.citydist_weev_quant <- 
ggplot(weev_quant_urbsubs_01_pred) +
  rep_geoms2 +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Weevil Scar Length (cm)" ^{1/3}),
       color = "Transect",
       fill = "Transect") +
  ylim(1.4, 2) +
  xlim(0, NA) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.17,
                    label = paste0(" Distance: p = ", tidy_anova(weev_quant_mods_best_c[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Transect: p = ", tidy_anova(weev_quant_mods_best_c[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.citydist_weev_quant

```

### Urbanization Score
```{r}
# LDMC-----
ggpred_Q2.urbsubs_ldmc <-
ggplot(ldmc_urbsubs_02_pred) +
  labs(x = "Urbanization Score",
       y = "Leaf Dry Matter Content",
       color = "Transect",
       fill = "Transect") +
  ylim(NA, 0.19) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(ldmc_mods_best_u[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(ldmc_mods_best_u[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.urbsubs_ldmc


# SLA-----
ggpred_Q2.urbsubs_sla <- 
ggplot(sla_urbsubs_02_pred) +
  labs(x = "Urbanization Score",
       y = expression("Specific Leaf Area "(cm^2/g)),
       color = "Transect",
       fill = "Transect") +
  ylim(18, 22.5) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(sla_mods_best_u[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(sla_mods_best_u[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.urbsubs_sla


# latex-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
latex_urbsubs_02_pred$group <- factor(latex_urbsubs_02_pred$group,
                                   levels(latex_urbsubs_02_pred$group)[c(2,1)])
levels(latex_urbsubs_02_pred$group)

ggpred_Q2.urbsubs_latex <- 
ggplot(latex_urbsubs_02_pred) +
  rep_geoms2 +
  labs(x = "Urbanization Score",
       y = expression("Latex Exudation (g) "^{1/2}),
       color = "Transect",
       fill = "Transect") +
  # ylim(6.25, 8.5) +
  xlim(4, -2) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 1,
                                   npcy = 0.96,
                    label = paste0(" Urb. Score: p = ", tidy_anova(latex_mods_best_u[[2]])$p[2])),
                size = 4.5,
                hjust = "right") +
  ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.87,
                    label = paste0(" Transect: p = ", tidy_anova(latex_mods_best_u[[2]])$p[3])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.78,
                    label = paste0(" U x T: p = ", tidy_anova(latex_mods_best_u[[2]])$p[4])),
                size = 4.5)

ggpred_Q2.urbsubs_latex



# herbivory: Before flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
herb_e_urbsubs_02_pred$group <- factor(herb_e_urbsubs_02_pred$group,
                                   levels(herb_e_urbsubs_02_pred$group)[c(2,1)])
levels(herb_e_urbsubs_02_pred$group)


ggpred_Q2.urbsubs_herb_e <- 
ggplot(herb_e_urbsubs_02_pred) +
  rep_geoms2 +
  labs(x = "Urbanization Score",
       y = expression("Herbivory (Before Flowering) "^{1/3}),
       color = "Transect",
       fill = "Transect") +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
  xlim(4, -2) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(herb_e_mods_best_u[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(herb_e_mods_best_u[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.urbsubs_herb_e

# herbivory: After flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
herb_l_urbsubs_02_pred$group <- factor(herb_l_urbsubs_02_pred$group,
                                   levels(herb_l_urbsubs_02_pred$group)[c(2,1)])
levels(herb_l_urbsubs_02_pred$group)

ggpred_Q2.urbsubs_herb_l <- 
ggplot(herb_l_urbsubs_02_pred) +
  rep_geoms2 +
  labs(x = "Urbanization Score",
       y = expression("Herbivory (After Flowering) "^{1/3}),
       color = "Transect",
       fill = "Transect") +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
  xlim(4, -2) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(herb_l_mods_best_u[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(herb_l_mods_best_u[[2]])$p[2])),
                size = 4.5) 

ggpred_Q2.urbsubs_herb_l


# Weevil damage: Binary-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
weev_bin_urbsubs_02_pred$group <- factor(weev_bin_urbsubs_02_pred$group,
                                   levels(weev_bin_urbsubs_02_pred$group)[c(2,1)])
levels(weev_bin_urbsubs_02_pred$group)


ggpred_Q2.urbsubs_weev_bin <- 
ggplot(weev_bin_urbsubs_02_pred) +
  rep_geoms2 +
  labs(x = "Urbanization Score",
       y = "Weevil Damage Outcome",
       color = "Transect",
       fill = "Transect") +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(0, 1.2),
    breaks = c(0, .25, .5, .75, 1)
    ) +
  xlim(4, -2) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.12,
                    label = paste0(" Urb. Score: p = ", tidy_anova(weev_bin_mods_best_u[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.05,
                    label = paste0(" Transect: p = ", tidy_anova(weev_bin_mods_best_u[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.urbsubs_weev_bin


# Weevil damage: Quantitative-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
weev_quant_urbsubs_02_pred$group <- factor(weev_quant_urbsubs_02_pred$group,
                                   levels(weev_quant_urbsubs_02_pred$group)[c(2,1)])
levels(weev_quant_urbsubs_02_pred$group)


ggpred_Q2.urbsubs_weev_quant <- 
ggplot(weev_quant_urbsubs_02_pred) +
  rep_geoms2 +
  labs(x = "Urbanization Score",
       y = expression("Weevil Scar Length (cm)" ^{1/3}),
       color = "Transect",
       fill = "Transect") +
  ylim(1.4, 2) +
  xlim(4, -2) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.17,
                    label = paste0(" Urb. Score: p = ", tidy_anova(weev_quant_mods_best_u[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Transect: p = ", tidy_anova(weev_quant_mods_best_u[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.urbsubs_weev_quant

```

## Combine plots into one figure
### Gradient / City_dist
```{r}
gradient_citydist_plots <- ggarrange(
  ggpred_Q1.citydist_ldmc,
  ggpred_Q1.citydist_sla,
  ggpred_Q1.citydist_latex,
  ggpred_Q1.citydist_herb_e,
  ggpred_Q1.citydist_herb_l,
  ggpred_Q1.citydist_weev_bin,
  ggpred_Q1.citydist_weev_quant +
            font("x.text"),
          ncol = 4,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D", "E", "F", "G"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Defense_trait_analyses/Figures/Q1_grad_citydist_Defense.pdf"),
             width = 14, height = 7.5)
```


### Gradient / Urbanization Score
```{r}
gradient_urbscore_plots <- ggarrange(
  ggpred_Q1.urbscore_ldmc,
  ggpred_Q1.urbscore_sla,
  ggpred_Q1.urbscore_latex,
  ggpred_Q1.urbscore_herb_e,
  ggpred_Q1.urbscore_herb_l,
  ggpred_Q1.urbscore_weev_bin,
  ggpred_Q1.urbscore_weev_quant +
            font("x.text"),
          ncol = 4,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D", "E", "F", "G"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Defense_trait_analyses/Figures/Q1_grad_urbscore_Defense.pdf"),
             width = 14, height = 7.5)
```

### Urb Subtransects / City_dist
```{r}
urbsubs_citydist_plots <- ggarrange(
  ggpred_Q2.citydist_ldmc,
  ggpred_Q2.citydist_sla,
  ggpred_Q2.citydist_latex,
  ggpred_Q2.citydist_herb_e,
  ggpred_Q2.citydist_herb_l,
  ggpred_Q2.citydist_weev_bin,
  ggpred_Q2.citydist_weev_quant +
            font("x.text"),
          ncol = 4,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D", "E", "F", "G"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Defense_trait_analyses/Figures/Q2_urbsubs_citydist_Defense.pdf"),
             width = 14.5, height = 8)
```


### Urb Subtransects / Urbanization Score
```{r}
urbsubs_urbscore_plots <- ggarrange(
  ggpred_Q2.urbsubs_ldmc,
  ggpred_Q2.urbsubs_sla,
  ggpred_Q2.urbsubs_latex,
  ggpred_Q2.urbsubs_herb_e,
  ggpred_Q2.urbsubs_herb_l,
  ggpred_Q2.urbsubs_weev_bin,
  ggpred_Q2.urbsubs_weev_quant +
            font("x.text"),
          ncol = 4,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D", "E", "F", "G"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Defense_trait_analyses/Figures/Q2_urbsubs_urbscore_Defense.pdf"),
             width = 14.5, height = 8)
```


# Find estimated marginal means at terminii
## Urban Subtransects
### City_dist
#### Monarchs
```{r}
# PERCENT CHANGE, suburban to urban terminus:
Calc_percent_change_urbsubs(monarch_urbsubs_01_pred) # -34%
```
