---
title: "Defense Trait Analysis"
author: "Sophie Breitbart"
output:
  html_document:
    number_sections: true
    df_print: paged
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
editor_options: 
  chunk_output_type: console
NOTES:
  -Still to do--
    -try to do an RDA (or PCA?) with all the traits
    -make a ReadMe file for each level
    -calculate heritability coefficients

# WHEN TOTALLY DONE, type this:
# renv::activate()
# renv::snapshot()
---

# Set up notebook
## Load libraries and add functions

```{r}
source("libraries.R")
source("functions.R")
```

## Import data

```{r}
# SLA & LDMC-----
sla_ldmc <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_sla_ldmc_clean.csv")) %>%
  dplyr::select(., -c(1:2)) %>%
  dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block")), as.character) %>%
    dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block")), as.factor)

str(sla_ldmc)
sla_ldmc %<>%
  dplyr::mutate(Fam_uniq = paste0(Population, "_", Family))


# LATEX-----
latex <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_latex_clean.csv")) %>%
  dplyr::select(-1) %>%
  dplyr::mutate_at(vars(c(1:7, 9:12, 15, 18, 21)), as.character) %>%
    dplyr::mutate_at(vars(c(1:7, 9:12, 15, 18, 21)), as.factor) %T>%
  str()

latex %<>%
  dplyr::mutate(Fam_uniq = as.factor(paste0(Population, "_", Family)))

str(latex)


# HERBIVORY-----
herbivory <- read.csv(here::here("./Joined_annual_data/herbivory.csv")) %>%
  dplyr::select(-1) %>%
  dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block", "Year", "Transect_ID", "Urb_Rur")), as.character) %>%
    dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block", "Year", "Transect_ID", "Urb_Rur")), as.factor) %T>%
  str()

herbivory %<>%
  dplyr::mutate(Fam_uniq = as.factor(paste0(Population, "_", Family)))

herbivory$Herbivory_mean_early_recode <- herbivory$Herbivory_mean_early
herbivory$Herbivory_mean_early_recode[herbivory$Herbivory_mean_early_recode == 1] <- 0.999999
herbivory$Herbivory_mean_early_recode[herbivory$Herbivory_mean_early_recode == 0] <- 0.000001

herbivory$Herbivory_mean_late_recode <- herbivory$Herbivory_mean_late
herbivory$Herbivory_mean_late_recode[herbivory$Herbivory_mean_late_recode == 1] <- 0.999999
herbivory$Herbivory_mean_late_recode[herbivory$Herbivory_mean_late_recode == 0] <- 0.000001


# WEEVIL DAMAGE-----
weevil <- read.csv(here::here("./Joined_annual_data/weevil.csv")) %>%
  dplyr::select(-1) %>%
  dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block", "Year", "Transect_ID", "Urb_Rur")), as.character) %>%
    dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block", "Year", "Transect_ID", "Urb_Rur")), as.factor) %T>%
  str()

weevil %<>%
  dplyr::mutate(Fam_uniq = as.factor(paste0(Population, "_", Family)))
```

## Import final models
### Create full list
```{r}
source(knitr::purl("Defense_trait_analyses/Model_diagnostics_Defense.Rmd", quiet=TRUE))

all_models <- list(
ldmc_mods          , # LDMC
sla_mods           , # SLA
latex_mods         , # Latex
herb_early_mods    , # Herbivory: before flowering
herb_late_mods     , # Herbivory: after flowering
weev_mods_binomial , # Weevil scar: binomial (part of hurdle models)
weev_mods_quant)     # Weevil scar: quantitative (part of hurdle models)

names(all_models) <- c(
"ldmc_mods"          ,
"sla_mods"           ,
"latex_mods"         ,
"herb_early_mods"    ,
"herb_late_mods"     ,
"weev_mods_binomial" ,
"weev_mods_quant")
```

### Create separate lists of best vs. alt models for city_dist vs urb_score
#### LDMC
```{r}
## Best
### City_dist
ldmc_mods_best_c <- ldmc_mods[c(1,4)]

### Urb_score
ldmc_mods_best_u <- ldmc_mods[c(2,6)]

## Alt
### City_dist
ldmc_mods_alt_c <- ldmc_mods[3]

### Urb_score
ldmc_mods_alt_u <- ldmc_mods[5]
```

#### SLA
```{r}
## Best
### City_dist
sla_mods_best_c <- sla_mods[c(1,4)]

### Urb_score
sla_mods_best_u <- sla_mods[c(2,6)]

## Alt
### City_dist
sla_mods_alt_c <- sla_mods[3]

### Urb_score
sla_mods_alt_u <- sla_mods[5]
```


#### Latex
```{r}
## Best
### City_dist
latex_mods_best_c <- latex_mods[c(1,4)]

### Urb_score
latex_mods_best_u <- latex_mods[c(2,5)]

## Alt
### City_dist
latex_mods_alt_c <- latex_mods[3]

### Urb_score- NONE

```


#### Herbivory- Early
```{r}
## Best
### City_dist
herb_e_mods_best_c <- herb_early_mods[c(1,3)]

### Urb_score
herb_e_mods_best_u <- herb_early_mods[c(2,6)]

## Alt
### City_dist
herb_e_mods_alt_c <- herb_early_mods[4]

### Urb_score
herb_e_mods_alt_u <- herb_early_mods[5]

```

#### Herbivory- Late
```{r}
## Best
### City_dist
herb_l_mods_best_c <- herb_late_mods[c(1,3)]

### Urb_score
herb_l_mods_best_u <- herb_late_mods[c(2,5)]

## Alt
### City_dist
herb_l_mods_alt_c <- herb_late_mods[4]

### Urb_score- NONE
```


#### Weevil- Binomial
```{r}
## Best
### City_dist
weev_bin_mods_best_c <- weev_mods_binomial[c(1,4)]

### Urb_score
weev_bin_mods_best_u <- weev_mods_binomial[c(2,6)]

## Alt
### City_dist
weev_bin_mods_alt_c <- weev_mods_binomial[3]

### Urb_score
weev_bin_mods_alt_u <- weev_mods_binomial[5]
```

#### Weevil- Quantitative
```{r}
## Best
### City_dist
weev_quant_mods_best_c <- weev_mods_quant[c(1,4)]

### Urb_score
weev_quant_mods_best_u <- weev_mods_quant[c(2,6)]

## Alt
### City_dist
weev_quant_mods_alt_c <- weev_mods_quant[3]

### Urb_score
weev_quant_mods_alt_u <- weev_mods_quant[5]
```


# Create ggpredict objects
## LDMC
### Gradient
```{r}
# city_dist
ldmc_mods_best_c[1]
ldmc_gradient_01_pred <- ggeffects::ggpredict(ldmc_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
ldmc_mods_best_u[1]
ldmc_gradient_02_pred <- ggeffects::ggpredict(ldmc_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
```

### Urban Subtransects
```{r}
# city_dist
ldmc_mods_best_c[2]
ldmc_urbsubs_01_pred <- ggeffects::ggpredict(ldmc_mods_best_c[[2]],
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
ldmc_mods_best_u[2]
ldmc_urbsubs_02_pred <- ggeffects::ggpredict(ldmc_mods_best_u[[2]],
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```

## SLA
### Gradient
```{r}
# city_dist
sla_mods_best_c[1]
sla_gradient_01_pred <- ggeffects::ggpredict(sla_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
sla_mods_best_u[1] # SQRT-TRANSFORMED
sla_gradient_02_pred <- ggeffects::ggpredict(sla_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
### NOTE: Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.

```

### Urban Subtransects
```{r}
# city_dist
sla_mods_best_c[2]# SQRT-TRANSFORMED
sla_urbsubs_01_pred <- ggeffects::ggpredict(sla_mods_best_c[[2]],
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()
### NOTE: Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.


# urb_score
sla_mods_best_u[2]# SQRT-TRANSFORMED
sla_urbsubs_02_pred <- ggeffects::ggpredict(sla_mods_best_u[[2]],
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
### NOTE: Model has sqrt-transformed response. Back-transforming predictions to original response scale. Standard errors are still on the sqrt-scale.
```

## Latex
### Gradient
```{r}
# city_dist
latex_mods_best_c[1]
latex_gradient_01_pred <- ggeffects::ggpredict(latex_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
latex_mods_best_u[1]
latex_gradient_02_pred <- ggeffects::ggpredict(latex_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()

```

### Urban Subtransects
```{r}

```

## Herbivory- Early
### Gradient
```{r}
# city_dist
herb_e_mods_best_c[1] # CUBE ROOT-TRANSFORMED
herb_e_gradient_01_pred <- ggeffects::ggpredict(herb_e_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
herb_e_mods_best_u[1]# CUBE ROOT-TRANSFORMED
herb_e_gradient_02_pred <- ggeffects::ggpredict(herb_e_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()

```

### Urban Subtransects
```{r}
# CUBE ROOT-TRANSFORMED
# # CUBE ROOT-TRANSFORMED
```

## Herbivory- Late
### Gradient
```{r}
# city_dist
herb_l_mods_best_c[1] # CUBE ROOT-TRANSFORMED
herb_l_gradient_01_pred <- ggeffects::ggpredict(herb_l_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
herb_l_mods_best_u[1] # CUBE ROOT-TRANSFORMED
herb_l_gradient_02_pred <- ggeffects::ggpredict(herb_l_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()

```

### Urban Subtransects
```{r}
# CUBE ROOT-TRANSFORMED
# # CUBE ROOT-TRANSFORMED
```

## Weevil damage- binary
### Gradient
```{r}
# city_dist
weev_bin_mods_best_c[1]
weev_b_gradient_01_pred <- ggeffects::ggpredict(weev_bin_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
weev_bin_mods_best_u[1]
weev_b_gradient_02_pred <- ggeffects::ggpredict(weev_bin_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()

```

### Urban Subtransects
```{r}

```

## Weevil damage- quantitative
### Gradient
```{r}
# city_dist
weev_quant_mods_best_c[1] # CUBE ROOT-TRANSFORMED
weev_q_gradient_01_pred <- ggeffects::ggpredict(weev_quant_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
weev_quant_mods_best_u[1] # CUBE ROOT-TRANSFORMED
weev_q_gradient_02_pred <- ggeffects::ggpredict(weev_quant_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()

```

### Urban Subtransects
```{r}
 # CUBE ROOT-TRANSFORMED
 #  # CUBE ROOT-TRANSFORMED
```

# Create plots
## Gradient
### City_dist
```{r}
# LDMC-----
ggpred_Q1.citydist_ldmc <- 
ggplot(ldmc_gradient_01_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Distance to Urban Center (km)",
       y = "Leaf Dry Matter Content") +
  # labs( color="Year", shape="Year", fill = "Year") +
  ylim(0.15, 0.18) +
    # min(ldmc_gradient_01_pred$predicted) * 0.95,
    # max(ldmc_gradient_01_pred$predicted) * 1.05) +
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(ldmc_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_ldmc



# SLA-----
ggpred_Q1.citydist_sla <- ggplot(sla_gradient_01_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Specific Leaf Area "(cm^2/g))) +
  # labs( color="Year", shape="Year", fill = "Year") +
  ylim(18, 26) +
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(sla_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_sla





# LATEX-----
ggpred_Q1.citydist_latex <- ggplot(latex_gradient_01_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Distance to Urban Center (km)",
       y = "Latex Exudation (mg)") +
  # labs( color="Year", shape="Year", fill = "Year") +
  ylim(6, 10) +
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(latex_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_latex

# herbivory- early-----
ggpred_Q1.citydist_herb_e <- ggplot(herb_e_gradient_01_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Herbivory (Before Flowering) " ^{1/3})) +
  # labs( color="Year", shape="Year", fill = "Year") +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(herb_e_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_herb_e


# herbivory- late-----
ggpred_Q1.citydist_herb_l <- ggplot(herb_l_gradient_01_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Herbivory (After Flowering) " ^{1/3})) +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(herb_l_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_herb_l


# weevil damage- binary-----
ggpred_Q1.citydist_weev_bin <- ggplot(weev_b_gradient_01_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Distance to Urban Center (km)",
       y = "Weevil Damage Outcome") +
    scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(0, 1.2)) +
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(weev_bin_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_weev_bin



# weevil damage- quantitative-----
ggpred_Q1.citydist_weev_quant <- ggplot(weev_q_gradient_01_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  ylim(1.5, NA) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Weevil Scar Length (cm) " ^{1/3})) +
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(weev_quant_mods_best_c[[1]])$p)),
                size = 4.5)

ggpred_Q1.citydist_weev_quant
```

### Urbanization Score
```{r}
# LDMC-----
ggpred_Q1.urbscore_ldmc <- 
ggplot(ldmc_gradient_02_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Urbanization Score",
       y = "Leaf Dry Matter Content") +
  xlim(4, -4) +
  # labs( color="Year", shape="Year", fill = "Year") +
  ylim(0.15, 0.18) +
    # min(ldmc_gradient_02_pred$predicted) * 0.95,
    # max(ldmc_gradient_02_pred$predicted) * 1.05) +
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(ldmc_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_ldmc



# SLA-----
ggpred_Q1.urbscore_sla <- ggplot(sla_gradient_02_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Urbanization Score",
       y = expression("sqrt(Specific Leaf Area) "(cm^2/g))) +
  # labs( color="Year", shape="Year", fill = "Year") +
  ylim(19.5, 21.5) +
    xlim(4, -4) +
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(sla_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_sla





# LATEX-----
ggpred_Q1.urbscore_latex <- ggplot(latex_gradient_02_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Urbanization Score",
       y = "Latex Exudation (mg)") +
    xlim(4, -4) +
  # labs( color="Year", shape="Year", fill = "Year") +
  # ylim(6, 10) +
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(latex_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_latex

# herbivory- early-----
ggpred_Q1.urbscore_herb_e <- ggplot(herb_e_gradient_02_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
    xlim(4, -4) +
  labs(x = "Urbanization Score",
       y = expression("Herbivory (Before Flowering) " ^{1/3})) +
  # labs( color="Year", shape="Year", fill = "Year") +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Urb. Score: p = ", tidy_anova(herb_e_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_herb_e


# herbivory- late-----
ggpred_Q1.urbscore_herb_l <- ggplot(herb_l_gradient_02_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    xlim(4, -4) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Urbanization Score",
       y = expression("Herbivory (After Flowering) " ^{1/3})) +
  scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(NA, 1))+
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Urb. Score: p = ", tidy_anova(herb_l_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_herb_l


# weevil damage- binary-----
ggpred_Q1.urbscore_weev_bin <- ggplot(weev_b_gradient_02_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  labs(x = "Urbanization Score",
       y = "Weevil Damage Outcome") +
    xlim(4, -4) +
    scale_y_continuous(labels = scales::percent_format(
    scale = 100,
    accuracy = 1),
    limits = c(0, 1.15),
    breaks = c(0, .25, .50, .75, 1)) +
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(weev_bin_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_weev_bin



# weevil damage- quantitative-----
ggpred_Q1.urbscore_weev_quant <- ggplot(weev_q_gradient_02_pred) +
    geom_smooth(aes(x = x,
                    y = predicted),
                color = "#66a182",
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error),
                fill = "#66a182",
                alpha = 0.3) +
  ylim(1.5, NA) +
    xlim(4, -4) +
  labs(x = "Urbanization Score",
       y = expression("Weevil Scar Length (cm) " ^{1/3})) +
    scale_colour_brewer(palette = "Set2") +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(weev_quant_mods_best_u[[1]])$p)),
                size = 4.5)

ggpred_Q1.urbscore_weev_quant
```

## Combine plots into one figure
### Gradient / City_dist
```{r}
gradient_citydist_plots <- ggarrange(
  ggpred_Q1.citydist_ldmc,
  ggpred_Q1.citydist_sla,
  ggpred_Q1.citydist_latex,
  ggpred_Q1.citydist_herb_e,
  ggpred_Q1.citydist_herb_l,
  ggpred_Q1.citydist_weev_bin,
  ggpred_Q1.citydist_weev_quant +
            font("x.text"),
          ncol = 4,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D", "E", "F", "G"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Defense_trait_analyses/Figures/Q1_grad_citydist_Defense.pdf"),
             width = 14, height = 7.5)
```


### Gradient / Urbanization Score
```{r}
gradient_urbscore_plots <- ggarrange(
  ggpred_Q1.urbscore_ldmc,
  ggpred_Q1.urbscore_sla,
  ggpred_Q1.urbscore_latex,
  ggpred_Q1.urbscore_herb_e,
  ggpred_Q1.urbscore_herb_l,
  ggpred_Q1.urbscore_weev_bin,
  ggpred_Q1.urbscore_weev_quant +
            font("x.text"),
          ncol = 4,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D", "E", "F", "G"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Defense_trait_analyses/Figures/Q1_grad_urbscore_Defense.pdf"),
             width = 14, height = 7.5)
```

## Urban Subtransects
### City_dist
```{r}
# LDMC-----
ggpred_Q2.citydist_ldmc <- 
ggplot(ldmc_urbsubs_01_pred) +
    geom_smooth(aes(x = x,
                    y = predicted,
                    color = group),
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error,
                    fill = group),
                alpha = 0.3) +
  labs(x = "Distance to Urban Center (km)",
       y = "Leaf Dry Matter Content") +
  labs( color="Transect", fill = "Transect") +
  ylim(NA, 0.19) +
  xlim(0, NA) +
    # min(ldmc_gradient_01_pred$predicted) * 0.95,
    # max(ldmc_gradient_01_pred$predicted) * 1.05) +
    scale_colour_brewer(palette = "Set2") +
    scale_fill_brewer(palette = "Set2") +
  theme_1() +
  scale_fill_discrete(labels = c("Corridor", "Non-Corridor")) +
  scale_color_discrete(labels = c("Corridor", "Non-Corridor")) +

  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.17,
                    label = paste0(" Distance: p = ", tidy_anova(ldmc_mods_best_c[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Transect: p = ", tidy_anova(ldmc_mods_best_c[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.citydist_ldmc

# SLA-----
ggpred_Q2.citydist_SLA <- 
ggplot(sla_urbsubs_01_pred) +
    geom_smooth(aes(x = x,
                    y = predicted,
                    color = group),
                size = 1,
                se = F) +
    geom_ribbon(aes(x = x,
                    ymin = predicted - std.error,
                    ymax = predicted + std.error,
                    fill = group),
                alpha = 0.3) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Specific Leaf Area "(cm^2/g))) +
  labs( color="Transect", fill = "Transect") +
  ylim(NA, 22) +
    xlim(0, NA) +
    # min(SLA_gradient_01_pred$predicted) * 0.95,
    # max(SLA_gradient_01_pred$predicted) * 1.05) +
    scale_colour_brewer(palette = "Set2") +
    scale_fill_brewer(palette = "Set2") +
  theme_1() +
  scale_fill_discrete(labels = c("Corridor", "Non-Corridor")) +
  scale_color_discrete(labels = c("Corridor", "Non-Corridor")) +

  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.17,
                    label = paste0(" Distance: p = ", tidy_anova(sla_mods_best_c[[2]])$p[1])),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Transect: p = ", tidy_anova(sla_mods_best_c[[2]])$p[2])),
                size = 4.5)

ggpred_Q2.citydist_SLA
```

### Urbanization Score
```{r}

```
