---
title: "Diagnostics"
author: "Sophie Breitbart"
date: "2/23/2022"
output: html_document
---
## Import data
```{r}
sla_ldmc <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_sla_ldmc_clean.csv")) %>%
  dplyr::select(., -c(1:2)) %>%
  dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block")), as.character) %>%
    dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block")), as.factor)

str(sla_ldmc)


latex <- read.csv(here::here("./CommonGardenExperiment_2020Data/clean_data/2020_latex_clean.csv")) %>%
  dplyr::select(-1) %>%
  dplyr::mutate_at(vars(c(1:7, 9:12, 15, 18, 21)), as.character) %>%
    dplyr::mutate_at(vars(c(1:7, 9:12, 15, 18, 21)), as.factor) %T>%
  str()
```

# LDMC
## Gradient
### City_dist
```{r}
ldmc_gr_city_m1 <- glmmTMB(LDMC ~ (1|Block) + (1|Population/Family) + City_dist,
                        data = sla_ldmc,
                        REML = F)

performance::check_model(ldmc_gr_city_m1) # looks like an outlier. Remove and try again

# performance::check_model(update(ldmc_gr_city_m1, . ~ . , data = sla_ldmc %>% dplyr::filter(LDMC < 1)))
# # convergence problem. Take out block

performance::check_model(update(ldmc_gr_city_m1, . ~ (1|Population/Family) + City_dist , data = sla_ldmc %>%
                                  dplyr::filter(LDMC < 1))) # better! put back outlier to see if it changes

# performance::check_model(update(ldmc_gr_city_m1, . ~ (1|Population/Family) + City_dist , data = sla_ldmc)) # still an outlier. Keep out. Still a bit right-skewed though, so try sqrt
# 
# performance::check_model(update(ldmc_gr_city_m1, sqrt(LDMC) ~ (1|Population/Family) + City_dist , data = sla_ldmc %>% dplyr::filter(LDMC < 1))) # convergence issue again. Stick with untransformed model


ldmc_gr_city_m1 <- glmmTMB(LDMC ~ (1|Population/Family) + City_dist,
                           data = sla_ldmc %>%
                             dplyr::filter(LDMC < 1.5))

car::Anova(ldmc_gr_city_m1)
# returning NaNs. Try making family unique and then crossing?

sla_ldmc %<>%
  dplyr::mutate(Fam_uniq = paste0(Population, "_", Family))

# this works: p = 0.19
car::Anova(update(ldmc_gr_city_m1,
                  . ~ (1|Population:Fam_uniq) + City_dist ,
                  data = sla_ldmc %>%
                    dplyr::filter(LDMC < 1)))

# gives same result (p = 0.19)
car::Anova(update(ldmc_gr_city_m1,
                             . ~ (1|Population:Family) + City_dist ,
                             data = sla_ldmc %>%
                               dplyr::filter(LDMC < 1)))

# this doesn't work though
car::Anova(update(ldmc_gr_city_m1,
                             . ~ (1|Population/Fam_uniq) + City_dist ,
                             data = sla_ldmc %>%
                               dplyr::filter(LDMC < 1)))

# this DOES work and gives same result as previous models
car::Anova(update(ldmc_gr_city_m1,
                             . ~ (1|Fam_uniq) + City_dist ,
                             data = sla_ldmc %>%
                               dplyr::filter(LDMC < 1)))


# going to use this as final model
ldmc_gr_city_m1 <- glmmTMB(LDMC ~ (1|Population:Fam_uniq) + City_dist,
                             data = sla_ldmc %>%
                               dplyr::filter(LDMC < 1))
car::Anova(ldmc_gr_city_m1)
performance::check_model(ldmc_gr_city_m1)
```

### Urb_score
```{r}
ldmc_gr_usc_m1 <- glmmTMB(LDMC ~ (1|Block) + (1|Population/Family) + Urb_score,
                        data = sla_ldmc,
                        REML = F)

performance::check_model(ldmc_gr_usc_m1) # remove same outlier

performance::check_model(update(ldmc_gr_usc_m1, . ~ . ,
                                data = sla_ldmc %>%
                                  dplyr::filter(LDMC < 1)))
# works fine

car::Anova(update(ldmc_gr_usc_m1, . ~ . ,
                                data = sla_ldmc %>%
                                  dplyr::filter(LDMC < 1)))

# I took out block: result barely changed. Subbed in Fam_uniq, result didn't change.


ldmc_gr_usc_m1 <- glmmTMB(LDMC ~ (1|Block) + (1|Population/Family) + Urb_score,
                        data = sla_ldmc %>%
                                  dplyr::filter(LDMC < 1),
                        REML = F)
```

## Urban Subtransects
### City_dist
```{r}
ldmc_urbsubs_city_m1 <- glmmTMB(LDMC ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
                        data = sla_ldmc %>%
                          dplyr::filter(Transect_ID != "Rural"),
                        REML = F)
# not converging. Try changing family

performance::check_model(update(ldmc_urbsubs_city_m1, . ~ (1|Block) + (1|Population:Family) + City_dist * Transect_ID,
                                data = sla_ldmc %>%
                                  dplyr::filter(Transect_ID != "Rural") %>%
                                  dplyr::filter(LDMC < 1.5)))
# says CIty_dist and Transect ID are collinear. Otherwise looks fine. Same diagnostics as (1|Fam_uniq) and (1|Population:Fam_uniq)

car::Anova(update(ldmc_urbsubs_city_m1, . ~ (1|Block) + (1|Population:Fam_uniq) + City_dist * Transect_ID,
                                data = sla_ldmc %>%
                                  dplyr::filter(Transect_ID != "Rural") %>%
                                  dplyr::filter(LDMC < 1.5)),
           type = "III") # interaxn not sig so will use type II SS

car::Anova(update(ldmc_urbsubs_city_m1, . ~ (1|Block) + (1|Population:Fam_uniq) + City_dist * Transect_ID,
                                data = sla_ldmc %>%
                                  dplyr::filter(Transect_ID != "Rural") %>%
                                  dplyr::filter(LDMC < 1.5)),
           type = "II") # interaxn not sig


# MAIN EFFECTS MODEL
ldmc_urbsubs_city_m2 <- glmmTMB(LDMC ~ (1|Block) + (1|Population:Fam_uniq) + City_dist + Transect_ID,
                        data = sla_ldmc %>%
                                  dplyr::filter(Transect_ID != "Rural" & LDMC < 1.5),
                        REML = F)

car::Anova(ldmc_urbsubs_city_m2)

# COMPARE AIC
AIC(ldmc_urbsubs_city_m1, ldmc_urbsubs_city_m2) # m2 lower but not by more than 2 AIC
```

### Urb_score
```{r}
ldmc_urbsubs_usc_m1 <- glmmTMB(LDMC ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
                        data = sla_ldmc %>%
                          dplyr::filter(Transect_ID != "Rural"),
                        REML = F)

performance::check_model(ldmc_urbsubs_usc_m1) # not converging. Remove outlier and try again


performance::check_model(update(ldmc_urbsubs_usc_m1, . ~ .,
                                data = sla_ldmc %>%
                                  dplyr::filter(Transect_ID != "Rural" & LDMC < 1.5))) # still not converging. try using Fam_uniq

# this works. As does using (1|Fam_uniq)
performance::check_model(update(ldmc_urbsubs_usc_m1, . ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score * Transect_ID,
                                data = sla_ldmc %>%
                                  dplyr::filter(Transect_ID != "Rural" & LDMC < 1.5)))

# gives same result as (1|Fam_uniq)
car::Anova(update(ldmc_urbsubs_usc_m1, . ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score * Transect_ID,
                                data = sla_ldmc %>%
                                  dplyr::filter(Transect_ID != "Rural" & LDMC < 1.5)),
           type = "III") # interaxn not sig so try type II SS


car::Anova(update(ldmc_urbsubs_usc_m1, . ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score * Transect_ID,
                                data = sla_ldmc %>%
                                  dplyr::filter(Transect_ID != "Rural" & LDMC < 1.5)),
           type = "II")


ldmc_urbsubs_usc_m1 <- glmmTMB(LDMC ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score * Transect_ID,
                                data = sla_ldmc %>%
                                  dplyr::filter(Transect_ID != "Rural" & LDMC < 1.5))


# MAIN EFFECTS MODEL
ldmc_urbsubs_usc_m2 <- glmmTMB(LDMC ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score + Transect_ID,
                                data = sla_ldmc %>%
                                  dplyr::filter(Transect_ID != "Rural" & LDMC < 1.5))

car::Anova(ldmc_urbsubs_usc_m2)

AIC(ldmc_urbsubs_usc_m1, ldmc_urbsubs_usc_m2) # ME model best model but not <2 AIC away
```

# SLA
## Gradient
### City_dist
```{r}
sla_gr_city_m1 <- glmmTMB(SLA ~ (1|Block) + (1|Population/Family) + City_dist,
                        data = sla_ldmc,
                        REML = F)

performance::check_model(sla_gr_city_m1) 

# use fam_uniq, see if anything changes
performance::check_model(update(sla_gr_city_m1, . ~ (1|Block) + (1|Population:Fam_uniq) + City_dist)) 



# Try IDing outlier residuals, removing from df, and rerunning model
LargeResiduals <- resid(sla_gr_city_m1) > 50
# 101, 170, 220, 304, 410, 444, 787

lg_resids <- sla_ldmc %>%
  dplyr::slice(101, 170, 220, 304, 410, 444, 787)

sla_without_lgresids <- anti_join(sla_ldmc, lg_resids)


sla_gr_city_m1_no_lg_resids <- glmmTMB(SLA ~ (1|Block) + (1|Population/Family) + City_dist,
                        data = sla_without_lgresids,
                        REML = F)

performance::check_model(sla_gr_city_m1_no_lg_resids) 


car::Anova(sla_gr_city_m1) # same result as third model
car::Anova(sla_gr_city_m1_no_lg_resids) # still qualitatively same result as other two models (p >> 0.1)
car::Anova(update(sla_gr_city_m1, . ~ (1|Block) + (1|Population:Fam_uniq) + City_dist)) # same result as first model


sla_gr_city_m1 <- glmmTMB(SLA ~ (1|Block) + (1|Population:Fam_uniq) + City_dist,
                        data = sla_ldmc,
                        REML = F)

```

### Urb_score
```{r}
sla_gr_usc_m1 <- glmmTMB(SLA ~ (1|Block) + (1|Population/Family) + Urb_score,
                        data = sla_ldmc,
                        REML = F)
performance::check_model(sla_gr_usc_m1) # try sqrt transformation

performance::check_model(update(sla_gr_usc_m1, sqrt(SLA) ~ .)) # looks better

# try with fam_uniq- looks same as above
performance::check_model(update(sla_gr_usc_m1, sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score))

car::Anova(sla_gr_usc_m1) # lowest p-val but still >>0.1 so qualitatively same as other models
car::Anova(update(sla_gr_usc_m1, sqrt(SLA) ~ .)) # same as third model
car::Anova(update(sla_gr_usc_m1, sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score)) # same as second model

sla_gr_usc_m1 <- glmmTMB(sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score,
                        data = sla_ldmc,
                        REML = F)
```

## Urban Subtransects
### City_dist
```{r}
sla_urbsubs_city_m1 <- glmmTMB(SLA ~ (1|Block) + (1|Population/Family) + City_dist * Transect_ID,
                        data = sla_ldmc %>%
                          dplyr::filter(Transect_ID != "Rural"),
                        REML = F)

performance::check_model(sla_urbsubs_city_m1) # seems ok but try sqrt

performance::check_model(update(sla_urbsubs_city_m1, sqrt(SLA) ~ .)) # looks a bit better

# No interaxns sig for either so use type II SS
car::Anova(sla_urbsubs_city_m1, type = "III")
car::Anova(update(sla_urbsubs_city_m1, sqrt(SLA) ~ .), type = "III")
car::Anova(update(sla_urbsubs_city_m1, sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + City_dist * Transect_ID), type = "III")

# Qualitatively identical again
car::Anova(sla_urbsubs_city_m1, type = "II")
car::Anova(update(sla_urbsubs_city_m1, sqrt(SLA) ~ .), type = "II")
car::Anova(update(sla_urbsubs_city_m1, sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + City_dist * Transect_ID), type = "II")


sla_urbsubs_city_m1 <- glmmTMB(sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + City_dist * Transect_ID,
                        data = sla_ldmc %>%
                          dplyr::filter(Transect_ID != "Rural"),
                        REML = F)

# MAIN EFFECTS
sla_urbsubs_city_m2 <- glmmTMB(sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + City_dist + Transect_ID,
                        data = sla_ldmc %>%
                          dplyr::filter(Transect_ID != "Rural"),
                        REML = F)

AIC(sla_urbsubs_city_m1, sla_urbsubs_city_m2) # qualitatively identical but m2 best model
```

### Urb_score
```{r}
sla_urbsubs_usc_m1 <- glmmTMB(SLA ~ (1|Block) + (1|Population/Family) + Urb_score * Transect_ID,
                        data = sla_ldmc %>%
                          dplyr::filter(Transect_ID != "Rural"),
                        REML = F)

performance::check_model(sla_urbsubs_usc_m1) # seems ok but try sqrt

performance::check_model(update(sla_urbsubs_usc_m1, sqrt(SLA) ~ .)) # looks a bit better

# these are identical
car::Anova(update(sla_urbsubs_usc_m1, sqrt(SLA) ~ .), type = "III") # interaxn not sig
car::Anova(update(sla_urbsubs_usc_m1, sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score * Transect_ID), type = "III") # interaxn not sig



# Qualitatively identical again
car::Anova(update(sla_urbsubs_usc_m1, sqrt(SLA) ~ .), type = "II")
car::Anova(update(sla_urbsubs_usc_m1, sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score * Transect_ID), type = "II")


sla_urbsubs_usc_m1 <- glmmTMB(sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score * Transect_ID,
                        data = sla_ldmc %>%
                          dplyr::filter(Transect_ID != "Rural"),
                        REML = F)

# MAIN EFFECTS
sla_urbsubs_usc_m2 <- glmmTMB(sqrt(SLA) ~ (1|Block) + (1|Population:Fam_uniq) + Urb_score + Transect_ID,
                        data = sla_ldmc %>%
                          dplyr::filter(Transect_ID != "Rural"),
                        REML = F)

AIC(sla_urbsubs_usc_m1, sla_urbsubs_usc_m2) # qualitatively identical but m2 best model
```

# Latex
## Gradient
### City_dist
```{r}
ltx_gr_city_m1 <- glmmTMB(Latex_weight_mg ~ (1|Block) + (1|Population/Family) + City_dist,
                        data = latex,
                        REML = F)

performance::check_model(ltx_gr_city_m1) 

# use fam_uniq, see if anything changes
performance::check_model(update(sla_gr_city_m1, . ~ (1|Block) + (1|Population:Fam_uniq) + City_dist)) 

```

### Urb_score
```{r}

```

## Urban Subtransects
### City_dist
```{r}

```

### Urb_score
```{r}

```


# Herbivory: September (post-flowering)
## Gradient
### City_dist
```{r}
herbivory_gr_dist_m1 <- glmer(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + (1|Population/Family) + City_dist,
                              data = herbivory_19_20,
                              family = "binomial"(link = "logit"),
                              control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))

res <- simulateResiduals(herbivory_gr_dist_m1)
plot(res)
testDispersion(herbivory_gr_dist_m1)
# qqplot looks very off... try  ????
hist(herbivory_19_20$Herbivory_mean_Sept, breaks = 30)
summary(herbivory_gr_dist_m1)


herbivory_gr_dist_m2 <- glmer(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + (1|Family) + City_dist,
                              data = herbivory_19_20,
                              family = "binomial"(link = "logit"),
                              control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))
res <- simulateResiduals(herbivory_gr_dist_m2)
plot(res)

# try removing pop and making families unique
herbivory_19_20[,"FamPop"] <- paste0(herbivory_19_20$Family, "-", herbivory_19_20$Population)

herbivory_gr_dist_m3 <- glmer(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + City_dist,
                              data = herbivory_19_20,
                              family = "binomial"(link = "logit"),
                              control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))

summary(herbivory_gr_dist_m3)
# trying to find where all the variance is being eaten up/accounted for and still not finding it... try beta distribution


herbivory_gr_dist_m4 <- glmmTMB(Herbivory_mean_Sept  ~ (1|Block) + (1|Year) + (1|Population/Family) + City_dist,
                                data = herbivory_19_20,
                                family = beta_family(link="logit"))
# Error in eval(family$initialize) : y values must be 0 < y < 1
# recode: 0s as 0.00001 & 1 as 0.999999

herbivory_19_20_recode <- herbivory_19_20
herbivory_19_20_recode$Herbivory_mean_Sept[herbivory_19_20_recode$Herbivory_mean_Sept == 1] <- 0.999999
herbivory_19_20_recode$Herbivory_mean_Sept[herbivory_19_20_recode$Herbivory_mean_Sept == 0] <- 0.000001



herbivory_gr_dist_m5 <- glmmTMB(Herbivory_mean_Sept  ~ (1|Block) + (1|Year) + (1|Population/Family) + City_dist,
                                data = herbivory_19_20_recode,
                                family = beta_family(link="logit"))
res <- simulateResiduals(herbivory_gr_dist_m5)
plot(res)
# IT WORKS

hist(herbivory_19_20$Herbivory_mean_Sept, breaks = 30)
summary(herbivory_gr_dist_m5)


herbivory_gr_dist_m6 <- glmmTMB(Herbivory_mean_Sept  ~ (1|Block) + Year + (1|Population/Family) + City_dist,
                                data = herbivory_19_20_recode,
                                family = beta_family(link="logit"))
res <- simulateResiduals(herbivory_gr_dist_m6)
plot(res)

herbivory_gr_dist_m7 <- glmmTMB(Herbivory_mean_Sept  ~ (1|Block) + Year + (1|FamPop) + City_dist,
                                data = herbivory_19_20_recode,
                                family = beta_family(link="logit"))
res <- simulateResiduals(herbivory_gr_dist_m7)
plot(res)

herbivory_gr_dist_m8 <- glmmTMB(Herbivory_mean_Sept  ~  Year + (1|FamPop) + City_dist,
                                data = herbivory_19_20_recode,
                                family = beta_family(link="logit"))
res <- simulateResiduals(herbivory_gr_dist_m8)
plot(res)

car::Anova(herbivory_gr_dist_m7) # doesn't run
car::Anova(herbivory_gr_dist_m8)
```

### Urb_score
```{r}
herbivory_gr_usc_m1 <- glmer(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + (1|Population/Family) + Urb_score,
                             data = herbivory_19_20,
                             family = binomial,
                             control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))

res <- simulateResiduals(herbivory_gr_usc_m1)
plot(res)
# try beta

herbivory_gr_usc_m2 <- glmmTMB(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + (1|Population/Family) + Urb_score,
                               data = herbivory_19_20_recode,
                               family = beta_family(link="logit"))

res <- simulateResiduals(herbivory_gr_usc_m2)
plot(res)
```

## Urban Sites
### City_dist
```{r}
herbivory_urb_dist_m1 <- glmer(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + (1|Population/Family) + City_dist * Transect_ID,
                               data = herbivory_19_20 %>% dplyr::filter(., Transect_ID != "Rural"),
                               family = binomial,
                               control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))

res <- simulateResiduals(herbivory_urb_dist_m1)
plot(res)
# try beta

herbivory_urb_dist_m2 <- glmmTMB(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + (1|Population/Family) + City_dist * Transect_ID,
                                 data = herbivory_19_20_recode %>% dplyr::filter(., Transect_ID != "Rural"),
                                 family = beta_family(link="logit"))

res <- simulateResiduals(herbivory_urb_dist_m2)
plot(res)


# main effects:
herbivory_urb_dist_m2_ME <- herbivory_urb_dist_m2 <- glmmTMB(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + (1|Population/Family) + City_dist + Transect_ID,
                                                             data = herbivory_19_20_recode %>% dplyr::filter(., Transect_ID != "Rural"),
                                                             family = beta_family(link="logit"))
```

### Urb_score
```{r}
herbivory_urb_usc_m1 <- glmer(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + (1|Population/Family) + Urb_score * Transect_ID,
                              data = herbivory_19_20 %>% dplyr::filter(., Transect_ID != "Rural"),
                              family = binomial,
                              control=glmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5)))

res <- simulateResiduals(herbivory_urb_usc_m1)
plot(res)
# try beta

herbivory_urb_usc_m2 <- glmmTMB(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + (1|Population/Family) + Urb_score * Transect_ID,
                                data = herbivory_19_20_recode %>% dplyr::filter(., Transect_ID != "Rural"),
                                family = beta_family(link="logit"))

res <- simulateResiduals(herbivory_urb_usc_m2)
plot(res)


# # main effects:
herbivory_urb_usc_m2_ME <- glmmTMB(Herbivory_mean_Sept ~ (1|Block) + (1|Year) + (1|Population/Family) + Urb_score + Transect_ID,
                                   data = herbivory_19_20_recode %>% dplyr::filter(., Transect_ID != "Rural"),
                                   family = beta_family(link="logit"))

```


# Models for use in analysis
## LDMC
```{r}
## City_dist / gradient
ldmc_gr_city_m1 

## Urbanization score / gradient
ldmc_gr_usc_m1 

## City_dist / urban subtransects
ldmc_urbsubs_city_m1 # Qualitatively identical model (<2 AIC away)
ldmc_urbsubs_city_m2 # Best model

## Urbanization score  / urban subtransects
ldmc_urbsubs_usc_m1 # Qualitatively identical model (<2 AIC away)
ldmc_urbsubs_usc_m2 # Best model
```

## SLA
```{r}
## City_dist / gradient
sla_gr_city_m1 

## Urbanization score / gradient
sla_gr_usc_m1

## City_dist / urban subtransects
sla_urbsubs_city_m1 # Qualitatively identical model (<2 AIC away)
sla_urbsubs_city_m2 # Best model

## Urbanization score  / urban subtransects
sla_urbsubs_usc_m1 # Qualitatively identical model (<2 AIC away)
sla_urbsubs_usc_m2 # Best model

```

## Latex
```{r}

```

