# Set up notebook
## Load libraries & functions
```{r}
source("libraries.R")
source("functions.R")
```

## Import data
```{r}
herbivores <- read.csv(here::here("./data/Joined_annual_data/herbivores.csv")) %>%
  dplyr::select(., -1) %>%
  dplyr::mutate_at(vars(c("Population",
                          "Family",
                          "Replicate",
                          "Block",
                          "Transect_ID",
                          "Sample",
                          "Patch_ID",
                          "Urb_Rur",
                          "Year",
                          "Surveyor",
                          "Date")),
                   as.character) %>%
    dplyr::mutate_at(vars(c("Population",
                            "Family",
                            "Replicate",
                            "Block",
                            "Transect_ID",
                            "Sample",
                            "Patch_ID",
                            "Urb_Rur",
                            "Year",
                            "Surveyor",
                          "Date")),
                     as.factor)

str(herbivores)  


herbivores %<>%
  dplyr::mutate(Fam_uniq = paste0(Population, "_", Family))
```

## Import final models
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_herbivores.Rmd", quiet=TRUE))

all_models <- list(
monarch_mods          , 
asclepiadis_mods           , 
clivicollis_mods)

names(all_models) <- c(
"monarch_mods"          ,
"asclepiadis_mods"           ,
"clivicollis_mods"         )
```

# Create ggpredict objects
## Monarchs
### Gradient
```{r}
# city_dist
monarch_mods_best_c[1]
monarch_gradient_01_pred <- ggeffects::ggpredict(monarch_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
monarch_mods_best_u[1]
monarch_gradient_02_pred <- ggeffects::ggpredict(monarch_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
```

### Urban Subtransects
```{r}
# city_dist
monarch_mods_best_c[2]
monarch_urbsubs_01_pred <- ggeffects::ggpredict(monarch_mods_best_c[[2]],
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
monarch_mods_best_u[2]
monarch_urbsubs_02_pred <- ggeffects::ggpredict(monarch_mods_best_u[[2]],
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```

## L. asclepiadis
### Gradient
```{r}
# city_dist
asclepiadis_mods_best_c[1]
asclepiadis_gradient_01_pred <- ggeffects::ggpredict(asclepiadis_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 


# urb_score
asclepiadis_mods_best_u[1]
asclepiadis_gradient_02_pred <- ggeffects::ggpredict(asclepiadis_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()


```

### Urban Subtransects
```{r}
# city_dist
asclepiadis_mods_best_c[2]
asclepiadis_urbsubs_01_pred <- ggeffects::ggpredict(asclepiadis_mods_best_c[[2]],
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()


# urb_score
asclepiadis_mods_best_u[2]
asclepiadis_urbsubs_02_pred <- ggeffects::ggpredict(asclepiadis_mods_best_u[[2]],
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")

```

## L. clivicollis
### Gradient
```{r}
# city_dist
clivicollis_mods_best_c[1] 
clivicollis_gradient_01_pred <- ggeffects::ggpredict(clivicollis_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 


# urb_score
clivicollis_mods_best_u[1]
clivicollis_gradient_02_pred <- ggeffects::ggpredict(clivicollis_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()

```

### Urban Subtransects
```{r}
# city_dist
clivicollis_mods_best_c[2] # binary
clivicollis_urbsubs_01_pred <- ggeffects::ggpredict(clivicollis_mods_best_c[[2]],
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()


# urb_score
clivicollis_mods_best_u[2] # BINARY
clivicollis_urbsubs_02_pred <- ggeffects::ggpredict(clivicollis_mods_best_u[[2]],
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```

# Create plots
## Import herbivore images
```{r}
monarch_img <- readPNG("scripts/Create_regression_figs/herbivore_images/D_plexippus_phylopic.png") %>%
  rasterGrob(., interpolate=TRUE)

asclepiadis_img <- readPNG("scripts/Create_regression_figs/herbivore_images/L_asclepiadis_phylopic.png") %>%
  rasterGrob(., interpolate=TRUE)

clivicollis_img <- readPNG("scripts/Create_regression_figs/herbivore_images/L_clivicollis_phylopic.png") %>%
  rasterGrob(., interpolate=TRUE)
```

## Gradient
### City_dist
```{r}
# Monarch-----
ggpred_Q1.citydist_monarch <- 
ggplot(monarch_gradient_01_pred) +
  annotation_custom(monarch_img,
                    xmin=60, xmax=70,
                    ymin=0.73, ymax=0.8) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = expression(paste(italic(" Danaus plexippus"), " Abundance"))) +
  ylim(NA, 0.8) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05,
                                   npcy = 0.95,
                    label = paste0(" Distance: p = ", tidy_anova(monarch_mods_best_c[[1]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
                size = 4.5)

ggpred_Q1.citydist_monarch



# L. asclepiadis-----
ggpred_Q1.citydist_asclepiadis <- 
ggplot(asclepiadis_gradient_01_pred) +
  annotation_custom(asclepiadis_img,
                    xmin=60, xmax=70,
                    ymin=10.3, ymax=11) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = expression(paste(italic(" Liriomyza asclepiadis"), "Abundance "))) +
  ylim(6,11) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05,
                                   npcy = 0.95,
                    label = paste0(" Distance: p = ", tidy_anova(asclepiadis_mods_best_c[[1]])%>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
                size = 4.5)

ggpred_Q1.citydist_asclepiadis



# L. clivicollis-----
ggpred_Q1.citydist_clivicollis <- 
ggplot(clivicollis_gradient_01_pred) +
  annotation_custom(clivicollis_img,
                    xmin=60, xmax=70,
                    ymin=0.085, ymax=0.1) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = expression(paste(italic(" Liriomyza clivicollis"), "Abundance "))) +
   ylim(0, 0.1) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(clivicollis_mods_best_c[[1]])%>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
                size = 4.5)

ggpred_Q1.citydist_clivicollis

```

### Urbanization Score
```{r}
# Monarch-----
ggpred_Q1.usc_monarch <- 
ggplot(monarch_gradient_02_pred) +
  annotation_custom(monarch_img,
                    xmin=3, xmax=4,
                    ymin=0.68, ymax=0.75) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = expression(paste(italic(" Danaus plexippus"), " Abundance"))) +
  ylim(NA, 0.75) +
  xlim(4, -4) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05,
                                   npcy = 0.95,
                    label = paste0(" Urb. Score: p = ", tidy_anova(monarch_mods_best_u[[1]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
                size = 4.5)

ggpred_Q1.usc_monarch



# L. asclepiadis-----
ggpred_Q1.usc_asclepiadis <- 
ggplot(asclepiadis_gradient_02_pred) +
  annotation_custom(asclepiadis_img,
                    xmin=3, xmax=4,
                    ymin=9.6, ymax=10.2) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = expression(paste(italic(" Liriomyza asclepiadis"), "Abundance "))) +
  ylim(6,10.2) +
    xlim(4, -4) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.07,
                    label = paste0(" Urb. Score: p = ", tidy_anova(asclepiadis_mods_best_u[[1]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
                size = 4.5)

ggpred_Q1.usc_asclepiadis



# L. clivicollis-----
ggpred_Q1.usc_clivicollis <- 
ggplot(clivicollis_gradient_02_pred) +
  annotation_custom(clivicollis_img,
                    xmin=3, xmax=4,
                    ymin=0.085, ymax=0.1) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = expression(paste(italic(" Liriomyza clivicollis"), "Abundance "))) +
  ylim(0, 0.1) +
    xlim(4, -4) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(clivicollis_mods_best_u[[1]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
                size = 4.5)

ggpred_Q1.usc_clivicollis

```

## Urban Subtransects
### City_dist
```{r}
# Monarchs-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
monarch_urbsubs_01_pred$group <- factor(monarch_urbsubs_01_pred$group,
                                   levels(monarch_urbsubs_01_pred$group)[c(2,1)])
levels(monarch_urbsubs_01_pred$group)


ggpred_Q2.citydist_monarch <-
ggplot(monarch_urbsubs_01_pred) +
    annotation_custom(monarch_img,
                    xmin=28, xmax=32,
                    ymin=0.9, ymax=1) +
  labs(x = "Distance to Urban Center (km)",
       y = expression(paste(italic(" Danaus plexippus"), " Abundance")),
       color = "Transect",
       fill = "Transect") +
  ylim(NA, 1) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(monarch_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(monarch_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
                size = 4.5) 

ggpred_Q2.citydist_monarch



# L. asclepiadis-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
asclepiadis_urbsubs_01_pred$group <- factor(asclepiadis_urbsubs_01_pred$group,
                                   levels(asclepiadis_urbsubs_01_pred$group)[c(2,1)])
levels(asclepiadis_urbsubs_01_pred$group)


ggpred_Q2.citydist_asclepiadis <- 
ggplot(asclepiadis_urbsubs_01_pred) +
    annotation_custom(asclepiadis_img,
                    xmin=28, xmax=32,
                    ymin=11, ymax=12) +
  labs(x = "Distance to Urban Center (km)",
              y = expression(atop(paste(italic("Liriomyza asclepiadis")), "Abundance ")),
       color = "Transect",
       fill = "Transect") +
  ylim(5,12) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(asclepiadis_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(asclepiadis_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
                size = 4.5) 

ggpred_Q2.citydist_asclepiadis


# L. clivicollis-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
clivicollis_urbsubs_01_pred$group <- factor(clivicollis_urbsubs_01_pred$group,
levels(clivicollis_urbsubs_01_pred$group)[c(2,1)])

levels(clivicollis_urbsubs_01_pred$group)


ggpred_Q2.citydist_clivicollis <- 
ggplot(clivicollis_urbsubs_01_pred) +
      annotation_custom(clivicollis_img,
                    xmin=28, xmax=32,
                    ymin=0.22, ymax=0.25) +
  labs(x = "Distance to Urban Center (km)",
       y = expression(atop(paste(italic("Labidomera clivicollis "), "Presence"))),
       color = "Transect",
       fill = "Transect") +
  ylim(NA,0.25) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(clivicollis_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(clivicollis_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
                size = 4.5) 

ggpred_Q2.citydist_clivicollis

```

### Urbanization Score
```{r}
# Monarchs-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
monarch_urbsubs_02_pred$group <- factor(monarch_urbsubs_02_pred$group,
                                   levels(monarch_urbsubs_02_pred$group)[c(2,1)])
levels(monarch_urbsubs_02_pred$group)


ggpred_Q2.usc_monarch <-
ggplot(monarch_urbsubs_02_pred) +
    annotation_custom(monarch_img,
                    xmin=1, xmax=2,
                    ymin=0.9, ymax=1) +
  labs(x = "Urbanization Score",
       y = expression(paste(italic(" Danaus plexippus"), " Abundance")),
       color = "Transect",
       fill = "Transect") +
  ylim(NA, 1) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(monarch_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
                size = 4.5)  +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(monarch_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
                size = 4.5) 

ggpred_Q2.usc_monarch



# L. asclepiadis-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
asclepiadis_urbsubs_02_pred$group <- factor(asclepiadis_urbsubs_02_pred$group,
                                   levels(asclepiadis_urbsubs_02_pred$group)[c(2,1)])
levels(asclepiadis_urbsubs_02_pred$group)


ggpred_Q2.usc_asclepiadis <- 
ggplot(asclepiadis_urbsubs_02_pred) +
    annotation_custom(asclepiadis_img,
                    xmin=1, xmax=2,
                    ymin=11, ymax=12) +
  labs(x = "Urbanization Score",
              y = expression(atop(paste(italic("Liriomyza asclepiadis")), "Abundance ")),
       color = "Transect",
       fill = "Transect") +
  ylim(5,12) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(asclepiadis_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
                size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(asclepiadis_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
                size = 4.5) 

ggpred_Q2.usc_asclepiadis


# L. clivicollis-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
clivicollis_urbsubs_02_pred$group <- factor(clivicollis_urbsubs_02_pred$group,
                                   levels(clivicollis_urbsubs_02_pred$group)[c(2,1)])
levels(clivicollis_urbsubs_02_pred$group)


ggpred_Q2.usc_clivicollis <- 
ggplot(clivicollis_urbsubs_02_pred) +
      annotation_custom(clivicollis_img,
                    xmin=1, xmax=2,
                    ymin=0.17, ymax=0.2) +
  rep_geoms2 +
  labs(x = "Urbanization Score",
       y = expression(atop(paste(italic("Labidomera clivicollis "), "Presence"))),
       color = "Transect",
       fill = "Transect") +
  ylim(0,0.2) +
  xlim(4, -2) +
  theme_1() +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(clivicollis_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
                size = 4.5)  +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(clivicollis_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
                size = 4.5) 

ggpred_Q2.usc_clivicollis

```

## Combine plots into one figure
### Gradient / City_dist
```{r}
gradient_citydist_plots <- ggarrange(
  ggpred_Q1.citydist_monarch,
  ggpred_Q1.citydist_asclepiadis,
  ggpred_Q1.citydist_clivicollis +
            font("x.text"),
          ncol = 3,
          nrow = 1,
          align = "hv",
          labels = list("A", "B", "C"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Figures_Tables/Regressions/multi_yr_mods/Defense/Q1_grad_citydist_herbivores.pdf"),
             width = 14, height = 4)
```


### Gradient / Urbanization Score
```{r}
gradient_urbscore_plots <- ggarrange(
  ggpred_Q1.usc_monarch,
  ggpred_Q1.usc_asclepiadis,
  ggpred_Q1.usc_clivicollis + 
            font("x.text"),
          ncol = 3,
          nrow = 1,
          align = "hv",
          labels = list("A", "B", "C"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Figures_Tables/Regressions/multi_yr_mods/Defense/Q1_grad_urbscore_herbivores.pdf"),
             width = 14, height = 4)
```

### Urb Subtransects / City_dist
```{r}
urbsubs_citydist_plots <- ggarrange(
  ggpred_Q2.citydist_monarch,
  ggpred_Q2.citydist_asclepiadis,
  ggpred_Q2.citydist_clivicollis+
            font("x.text"),
          ncol = 3,
          nrow = 1,
          align = "hv",
          labels = list("A", "B", "C"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Figures_Tables/Regressions/multi_yr_mods/Defense/Q2_urbsubs_citydist_herbivores.pdf"),
             width = 14, height = 4)
```


### Urb Subtransects / Urbanization Score
```{r}
urbsubs_urbscore_plots <- ggarrange(
  ggpred_Q2.usc_monarch,
  ggpred_Q2.usc_asclepiadis,
  ggpred_Q2.usc_clivicollis +
            font("x.text"),
          ncol = 3,
          nrow = 1,
          align = "hv",
          labels = list("A", "B", "C"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Figures_Tables/Regressions/multi_yr_mods/Defense/Q2_urbsubs_urbscore_herbivores.pdf"),
             width = 14, height = 4)
```


# Find estimated marginal means at terminii
## Urban Subtransects
### City_dist
#### Monarchs
```{r}
# PERCENT CHANGE, suburban to urban terminus:
Calc_percent_change_urbsubs(monarch_urbsubs_01_pred) # -34%
```
