# Set up notebook
## Load libraries and add functions
```{r}
source("libraries.R")
source("functions.R")
```

## Import data
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_Growth.Rmd", quiet=TRUE))
```

# Create ggpredict objects
## LDMC
### Gradient
```{r}
# city_dist
ldmc_mods_best_c[1] # sqrt transformed
ldmc_gradient_01_pred <- ggeffects::ggpredict(ldmc_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
ldmc_mods_best_u[1]# sqrt transformed
ldmc_gradient_02_pred <- ggeffects::ggpredict(ldmc_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
```

### Urban Subtransects
```{r}
# city_dist
ldmc_mods_best_c[2] # log transformed
ldmc_urbsubs_01_pred <- ggeffects::ggpredict(ldmc_mods_best_c[[2]],
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
ldmc_mods_best_u[2]# log transformed
ldmc_urbsubs_02_pred <- ggeffects::ggpredict(ldmc_mods_best_u[[2]],
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```

## SLA
### Gradient
```{r}

# city_dist
sla_mods_best_c[1] # log(SLA + 1) transformed
sla_gradient_01_pred <- ggeffects::ggpredict(sla_mods_best_c[[1]],
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
sla_mods_best_u[1] # log(SLA + 1) transformed
sla_gradient_02_pred <- ggeffects::ggpredict(sla_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()

```

### Urban Subtransects
```{r}
# city_dist
sla_mods_best_c[2] # log(SLA + 1) transformed
sla_urbsubs_01_pred <- ggeffects::ggpredict(sla_mods_best_c[[2]],
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
sla_mods_best_u[2] # log(SLA + 1) transformed
sla_urbsubs_02_pred <- ggeffects::ggpredict(sla_mods_best_u[[2]],
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```

## Height- before flowering
### Gradient
```{r}

heights$heights_e_cuberoot <- (heights$Total_Height_early)^(1/3)

heights_e_mod1 <- update(
  heights_early_mods_best_c[[1]],
  heights_e_cuberoot ~ .
)

heights_e_mod2 <- update(
  heights_early_mods_best_u[[1]],
  heights_e_cuberoot ~ .
)


# city_dist
heights_early_mods_best_c[1] # cube root transfomred
heights_early_gradient_01_pred <- ggeffects::ggpredict(heights_e_mod1,
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
heights_early_mods_best_u[1] # cube root transfomred
heights_early_gradient_02_pred <- ggeffects::ggpredict(heights_e_mod2,
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
```

### Urban Subtransects
```{r}

heights_e_mod3 <- update(
  heights_early_mods_best_c[[2]],
  heights_e_cuberoot ~ .
)

heights_e_mod4 <- update(
  heights_early_mods_best_u[[2]],
  heights_e_cuberoot ~ .
)

# city_dist
heights_early_mods_best_c[2] # cube root transfomred
heights_early_urbsubs_01_pred <- ggeffects::ggpredict(heights_e_mod3,
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
heights_early_mods_best_u[2] # cube root transfomred
heights_early_urbsubs_02_pred <- ggeffects::ggpredict(heights_e_mod4,
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```


## Height- after flowering
### Gradient
```{r}
heights$heights_l_cuberoot <- (heights$Total_Height_late)^(1/3)

heights_l_mod1 <- update(
  heights_late_mods_best_c[[1]],
  heights_l_cuberoot ~ .
)

heights_l_mod2 <- update(
  heights_late_mods_best_u[[1]],
  heights_l_cuberoot ~ .
)


# city_dist
heights_late_mods_best_c[1] # cube root transfomred
heights_late_gradient_01_pred <- ggeffects::ggpredict(heights_l_mod1,
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
heights_late_mods_best_u[1] # cube root transfomred
heights_late_gradient_02_pred <- ggeffects::ggpredict(heights_l_mod2,
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
```

### Urban Subtransects
```{r}

heights_l_mod3 <- update(
  heights_late_mods_best_c[[2]],
  heights_l_cuberoot ~ .
)

heights_l_mod4 <- update(
  heights_late_mods_best_u[[2]],
  heights_l_cuberoot ~ .
)
# city_dist
heights_late_mods_best_c[2] # cube root transfomred
heights_late_urbsubs_01_pred <- ggeffects::ggpredict(heights_l_mod3,
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
heights_late_mods_best_u[2] # cube root transfomred
heights_late_urbsubs_02_pred <- ggeffects::ggpredict(heights_l_mod4,
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```

## Relative growth rate
### Gradient
```{r}
heights$rgr_cuberoot <- (heights$rel_growth_rate)^(1/3)

rgr_mod1 <- update(
  rgr_mods_best_c[[1]],
  rgr_cuberoot ~ .
)

rgr_mod2 <- update(
  rgr_mods_best_u[[1]],
  rgr_cuberoot ~ .
)

# city_dist
rgr_mods_best_c[1] # CUBE ROOT transformed
rgr_gradient_01_pred <- ggeffects::ggpredict(rgr_mod1,
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
rgr_mods_best_u[1] # CUBE ROOT transformed
rgr_gradient_02_pred <- ggeffects::ggpredict(rgr_mod2,
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()

```

### Urban Subtransects
```{r}
rgr_mod3 <- update(
  rgr_mods_best_c[[2]],
  rgr_cuberoot ~ .
)

rgr_mod4 <- update(
  rgr_mods_best_u[[2]],
  rgr_cuberoot ~ .
)

# city_dist
rgr_mods_best_c[2] # CUBE ROOT transformed
rgr_urbsubs_01_pred <- ggeffects::ggpredict(rgr_mod3,
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
rgr_mods_best_u[2] # CUBE ROOT transformed
rgr_urbsubs_02_pred <- ggeffects::ggpredict(rgr_mod4,
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```


## Ramets- before flowering
### Gradient
```{r}

# city_dist
ramets_early_mods_best_c[1] 
ramets_early_gradient_01_pred <- ggeffects::ggpredict(ramets_early_mods_best_c[[1]] ,
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
ramets_early_mods_best_u[1] 
ramets_early_gradient_02_pred <- ggeffects::ggpredict(ramets_early_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
```

### Urban Subtransects
```{r}

# city_dist
ramets_early_mods_best_c[2] 
ramets_early_urbsubs_01_pred <- ggeffects::ggpredict(ramets_early_mods_best_c[[2]] ,
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
ramets_early_mods_best_u[2] 
ramets_early_urbsubs_02_pred <- ggeffects::ggpredict(ramets_early_mods_best_u[[2]] ,
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```


## Ramets- after flowering
### Gradient
```{r}

# city_dist
ramets_late_mods_best_c[1] 
ramets_late_gradient_01_pred <- ggeffects::ggpredict(ramets_late_mods_best_c[[1]] ,
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
ramets_late_mods_best_u[1] 
ramets_late_gradient_02_pred <- ggeffects::ggpredict(ramets_late_mods_best_u[[1]],
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
```

### Urban Subtransects
```{r}

# city_dist
ramets_late_mods_best_c[2] 
ramets_late_urbsubs_01_pred <- ggeffects::ggpredict(ramets_late_mods_best_c[[2]] ,
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
ramets_late_mods_best_u[2] 
ramets_late_urbsubs_02_pred <- ggeffects::ggpredict(ramets_late_mods_best_u[[2]] ,
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")
```


## Mortality
### Gradient
```{r}
# city_dist
mortality_gradient_01_pred <- ggeffects::ggpredict(surv_gr_city_m1_all,
                                   terms = c("City_dist"),
                                   type = "fe") %>%
  as.data.frame() 

# urb_score
mortality_gradient_02_pred <- ggeffects::ggpredict(surv_gr_usc_m1_all,
                                   terms = c("Urb_score"),
                                   type = "fe") %>%
  as.data.frame()
```

### Urban subtransects
```{r}
# city_dist
mortality_urbsubs_01_pred <- ggeffects::ggpredict(surv_urbsubs_city_m1_all,
                                   terms = c("City_dist", "Transect_ID"),
                                   type = "fe") %>%
  as.data.frame()

# urb_score
mortality_urbsubs_02_pred <- ggeffects::ggpredict(surv_urbsubs_usc_m1_all,
                                   terms = c("Urb_score", "Transect_ID"),
                                   type = "fe")

```

# Create regression plots
## Gradient
### City_dist
```{r}
# LDMC-----
ggpred_Q1.citydist_ldmc <- 
ggplot(ldmc_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = "Leaf dry matter content (LDMC)") +
  ylim(NA, 0.19) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(ldmc_mods_best_c[[1]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.citydist_ldmc


# SLA-----
ggpred_Q1.citydist_sla <- ggplot(sla_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Specific leaf area (SLA) "(cm^2/g))) +
  ylim(NA, 20) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(sla_mods_best_c[[1]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.citydist_sla


# Height, before flowering-----
ggpred_Q1.citydist_height_e <- ggplot(heights_early_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Height (before flowering) (cm)" ^{1/3})) +
   ylim(0.4, 1.2) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.15, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(heights_early_mods_best_c[[1]])%>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.citydist_height_e


# Height, after flowering-----
ggpred_Q1.citydist_height_l <- ggplot(heights_late_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Height (after flowering) (cm)" ^{1/3})) +
  ylim(1.5, 2.75) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.15, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(heights_late_mods_best_c[[1]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.citydist_height_l



# RGR-----
ggpred_Q1.citydist_rgr <- ggplot(rgr_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Relative growth rate " ^{1/3})) +
  ylim(0.19, 0.22) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(rgr_mods_best_c[[1]])%>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.citydist_rgr


# Ramets, before flowering-----
ggpred_Q1.citydist_ramets_e <- ggplot(ramets_early_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = "Ramets (before flowering)") +
  ylim(1,2) +
  theme_1() +
   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.1, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(ramets_early_mods_best_c[[1]])%>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.citydist_ramets_e



# Ramets, after flowering-----
ggpred_Q1.citydist_ramets_l <- ggplot(ramets_late_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = "Ramets (after flowering)") +
   ylim(1.4,2.2) +
  theme_1() +
   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.15, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(ramets_late_mods_best_c[[1]])%>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.citydist_ramets_l


# Mortality-----

ggpred_Q1.citydist_mortality <- 
ggplot(mortality_gradient_01_pred) +
  rep_geoms +
  labs(x = "Distance to Urban Center (km)",
       y = "Probability of death at\n end of growing season") +
 ylim(0, 0.1) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Distance: p = ", tidy_anova(mortality_mods_best_c[[1]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.citydist_mortality

```

### Urb_score
```{r}
# LDMC-----
ggpred_Q1.urbscore_ldmc <- 
ggplot(ldmc_gradient_02_pred) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = "Leaf dry matter content (LDMC)") +
 ylim(0.16, 0.19) +
    xlim(4, -4) +
  theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(ldmc_mods_best_u[[1]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.urbscore_ldmc


# SLA-----
ggpred_Q1.urbscore_sla <- ggplot(sla_gradient_02_pred) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = expression("Specific leaf area (SLA) "(cm^2/g))) +
  ylim(16,20) +
    xlim(4, -4) +
theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.15, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(sla_mods_best_u[[1]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.urbscore_sla



# Height, before flowering-----
ggpred_Q1.urbscore_height_e <- ggplot(heights_early_gradient_02_pred) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = expression("Height (before flowering) (cm)" ^{1/3})) +
 #  ylim(18, 26) +
    xlim(4, -4) +
theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.95,
                    label = paste0(" Urb. Score: p = ", tidy_anova(heights_early_mods_best_u[[1]])%>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.urbscore_height_e


# Height, after flowering-----
ggpred_Q1.urbscore_height_l <- ggplot(heights_late_gradient_02_pred) +
  rep_geoms +
    xlim(4, -4) +
labs(x = "Urbanization Score",
       y = expression("Height (after flowering) (cm)" ^{1/3})) +
  ylim(1.7,2.5) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.15, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(heights_late_mods_best_u[[1]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.urbscore_height_l



# RGR-----
ggpred_Q1.urbscore_rgr <- ggplot(rgr_gradient_02_pred) +
  rep_geoms +
    xlim(4, -4) +
labs(x = "Urbanization Score",
       y = expression("Relative growth rate " ^{1/3})) +
  ylim(0.19, 0.22) +
  theme_1() +
#   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(rgr_mods_best_u[[1]])%>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.urbscore_rgr


# Ramets, before flowering-----
ggpred_Q1.urbscore_ramets_e <- ggplot(ramets_early_gradient_02_pred) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = "Ramets (before flowering)") +
    xlim(4, -4) +
  ylim(1.3, 1.8) +
  theme_1() +
   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.1, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(ramets_early_mods_best_u[[1]])%>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.urbscore_ramets_e



# Ramets, after flowering-----
ggpred_Q1.urbscore_ramets_l <- ggplot(ramets_late_gradient_02_pred) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = "Ramets (after flowering)") +
   ylim(1.5, 2) +
    xlim(4, -4) +
theme_1() +
   # adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.15, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(ramets_late_mods_best_u[[1]])%>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.urbscore_ramets_l


# Mortality-----

ggpred_Q1.urbscore_mortality <- 
ggplot(mortality_gradient_02_pred) +
  rep_geoms +
  labs(x = "Urbanization Score",
       y = "Probability of death at\n end of growing season") +
  ylim(0, 0.1) +
    xlim(4, -4) +
theme_1() +
  
# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.08,
                    label = paste0(" Urb. Score: p = ", tidy_anova(mortality_mods_best_u[[1]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q1.urbscore_mortality
```

## Urban Subtransects
### City_dist
```{r}
# LDMC-----

levels(ldmc_urbsubs_01_pred$group)
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
ldmc_urbsubs_01_pred$group <- factor(ldmc_urbsubs_01_pred$group, levels(ldmc_urbsubs_01_pred$group)[c(2,1)])

levels(ldmc_urbsubs_01_pred$group)

ggpred_Q2.citydist_ldmc <-
ggplot(ldmc_urbsubs_01_pred) +
  labs(x = "Distance to Urban Center (km)",
       y = "Leaf dry matter content (LDMC)",
       color = "Transect",
       fill = "Transect") +
 # ylim(NA, 0.19) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(ldmc_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(ldmc_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.citydist_ldmc



# SLA-----

levels(sla_urbsubs_01_pred$group)
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
sla_urbsubs_01_pred$group <- factor(sla_urbsubs_01_pred$group, levels(sla_urbsubs_01_pred$group)[c(2,1)])

levels(sla_urbsubs_01_pred$group)

ggpred_Q2.citydist_sla <- 
ggplot(sla_urbsubs_01_pred) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Specific leaf area (SLA) "(cm^2/g)),
       color = "Transect",
       fill = "Transect") +
  ylim(NA, 22) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(sla_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(sla_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.citydist_sla


# Height, before flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
heights_early_urbsubs_01_pred$group <- factor(heights_early_urbsubs_01_pred$group,                    levels(heights_early_urbsubs_01_pred$group)[c(2,1)])

levels(heights_early_urbsubs_01_pred$group)

ggpred_Q2.citydist_height_e <- 
ggplot(heights_early_urbsubs_01_pred) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Height (before flowering) (cm)" ^{1/3}), 
       color = "Transect",
       fill = "Transect") +
  ylim(0, 1.2) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(heights_early_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(heights_early_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.citydist_height_e

# Height, after flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
heights_late_urbsubs_01_pred$group <- factor(heights_late_urbsubs_01_pred$group,                    levels(heights_late_urbsubs_01_pred$group)[c(2,1)])

levels(heights_late_urbsubs_01_pred$group)

ggpred_Q2.citydist_height_l <- 
ggplot(heights_late_urbsubs_01_pred) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Height (after flowering) (cm)" ^{1/3}), 
       color = "Transect",
       fill = "Transect") +
  ylim(1, 3) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(heights_late_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(heights_late_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.citydist_height_l


# Relative growth rate-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
rgr_urbsubs_01_pred$group <- factor(rgr_urbsubs_01_pred$group,                    levels(rgr_urbsubs_01_pred$group)[c(2,1)])

levels(rgr_urbsubs_01_pred$group)

ggpred_Q2.citydist_rgr <- 
ggplot(rgr_urbsubs_01_pred) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Relative growth rate "^{1/3}),
       color = "Transect",
       fill = "Transect") +
  ylim(0.18, 0.24) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(rgr_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(rgr_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.citydist_rgr



# Ramets, before flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
ramets_early_urbsubs_01_pred$group <- factor(ramets_early_urbsubs_01_pred$group,                    levels(ramets_early_urbsubs_01_pred$group)[c(2,1)])

levels(ramets_early_urbsubs_01_pred$group)

ggpred_Q2.citydist_ramets_e <- 
ggplot(ramets_early_urbsubs_01_pred) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Ramets (before flowering) (cm)" ^{1/3}), 
       color = "Transect",
       fill = "Transect") +
#  ylim(NA, 22) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(ramets_early_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(ramets_early_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.citydist_ramets_e

# Ramets, after flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
ramets_late_urbsubs_01_pred$group <- factor(ramets_late_urbsubs_01_pred$group,                    levels(ramets_late_urbsubs_01_pred$group)[c(2,1)])

levels(ramets_late_urbsubs_01_pred$group)

ggpred_Q2.citydist_ramets_l <- 
ggplot(ramets_late_urbsubs_01_pred) +
  labs(x = "Distance to Urban Center (km)",
       y = expression("Ramets (after flowering) (cm)" ^{1/3}), 
       color = "Transect",
       fill = "Transect") +
  ylim(1.25, 2.25) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(ramets_late_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(ramets_late_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.citydist_ramets_l


# Mortality

# Mortality-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
mortality_urbsubs_01_pred$group <- factor(mortality_urbsubs_01_pred$group,                    levels(mortality_urbsubs_01_pred$group)[c(2,1)])

levels(mortality_urbsubs_01_pred$group)

ggpred_Q2.citydist_mortality <- 
ggplot(mortality_urbsubs_01_pred) +
  labs(x = "Distance to Urban Center (km)",
       y = "Probability of death at\n end of growing season",
       color = "Transect",
       fill = "Transect") +
  ylim(0, 0.25) +
  xlim(0, NA) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Distance: p = ", tidy_anova(mortality_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Distance to City Center") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(mortality_mods_best_c[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.citydist_mortality

```

### Urb score
```{r}
# LDMC-----

## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
ldmc_urbsubs_02_pred$group <- factor(ldmc_urbsubs_02_pred$group, levels(ldmc_urbsubs_02_pred$group)[c(2,1)])
levels(ldmc_urbsubs_02_pred$group)


ggpred_Q2.urbsubs_ldmc <-
ggplot(ldmc_urbsubs_02_pred) +
  labs(x = "Urbanization Score",
       y = "Leaf dry matter content (LDMC)",
       color = "Transect",
       fill = "Transect") +
  ylim(0.15, 0.2) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(ldmc_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(ldmc_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.urbsubs_ldmc



# SLA-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
sla_urbsubs_02_pred$group <- factor(sla_urbsubs_02_pred$group, levels(sla_urbsubs_02_pred$group)[c(2,1)])
levels(sla_urbsubs_02_pred$group)

ggpred_Q2.urbsubs_sla <- 
ggplot(sla_urbsubs_02_pred) +
  labs(x = "Urbanization Score",
       y = expression("Specific leaf area (SLA) "(cm^2/g)),
       color = "Transect",
       fill = "Transect") +
  ylim(14,24) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(sla_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(sla_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.urbsubs_sla


# Height, before flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
heights_early_urbsubs_02_pred$group <- factor(heights_early_urbsubs_02_pred$group,                    levels(heights_early_urbsubs_02_pred$group)[c(2,1)])

levels(heights_early_urbsubs_02_pred$group)

ggpred_Q2.urbsubs_height_e <- 
ggplot(heights_early_urbsubs_02_pred) +
  labs(x = "Urbanization Score",
       y = expression("Height (before flowering) (cm)" ^{1/3}), 
       color = "Transect",
       fill = "Transect") +
  ylim(0.25, 1.25) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(heights_early_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(heights_early_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.urbsubs_height_e

# Height, after flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
heights_late_urbsubs_02_pred$group <- factor(heights_late_urbsubs_02_pred$group,                    levels(heights_late_urbsubs_02_pred$group)[c(2,1)])

levels(heights_late_urbsubs_02_pred$group)

ggpred_Q2.urbsubs_height_l <- 
ggplot(heights_late_urbsubs_02_pred) +
  labs(x = "Urbanization Score",
       y = expression("Height (after flowering) (cm)" ^{1/3}), 
       color = "Transect",
       fill = "Transect") +
  ylim(1.5, 3) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(heights_late_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(heights_late_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.urbsubs_height_l


# Relative growth rate-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
rgr_urbsubs_02_pred$group <- factor(rgr_urbsubs_02_pred$group,                    levels(rgr_urbsubs_02_pred$group)[c(2,1)])

levels(rgr_urbsubs_02_pred$group)

ggpred_Q2.urbsubs_rgr <- 
ggplot(rgr_urbsubs_02_pred) +
  labs(x = "Urbanization Score",
       y = expression("Relative growth rate "^{1/3}),
       color = "Transect",
       fill = "Transect") +
  ylim(0.19, 0.23) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(rgr_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 1, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(rgr_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.urbsubs_rgr



# Ramets, before flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
ramets_early_urbsubs_02_pred$group <- factor(ramets_early_urbsubs_02_pred$group,                    levels(ramets_early_urbsubs_02_pred$group)[c(2,1)])

levels(ramets_early_urbsubs_02_pred$group)

ggpred_Q2.urbsubs_ramets_e <- 
ggplot(ramets_early_urbsubs_02_pred) +
  labs(x = "Urbanization Score",
       y = expression("Ramets (before flowering) (cm)" ^{1/3}), 
       color = "Transect",
       fill = "Transect") +
  ylim(1, 2.2) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.14,
                    label = paste0(" Urb. Score: p = ", tidy_anova(ramets_early_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.06,
                    label = paste0(" Transect: p = ", tidy_anova(ramets_early_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.urbsubs_ramets_e

# Ramets, after flowering-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
ramets_late_urbsubs_02_pred$group <- factor(ramets_late_urbsubs_02_pred$group,                    levels(ramets_late_urbsubs_02_pred$group)[c(2,1)])

levels(ramets_late_urbsubs_02_pred$group)

ggpred_Q2.urbsubs_ramets_l <- 
ggplot(ramets_late_urbsubs_02_pred) +
  labs(x = "Urbanization Score",
       y = expression("Ramets (after flowering) (cm)" ^{1/3}), 
       color = "Transect",
       fill = "Transect") +
  ylim(1.25, 2.25) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.14,
                    label = paste0(" Urb. Score: p = ", tidy_anova(ramets_late_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.06,
                    label = paste0(" Transect: p = ", tidy_anova(ramets_late_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.urbsubs_ramets_l

# Mortality-----
## factors (transects) for this object are North, then South. To keep legend consistent, reorder levels first
mortality_urbsubs_02_pred$group <- factor(mortality_urbsubs_02_pred$group,                    levels(mortality_urbsubs_02_pred$group)[c(2,1)])

levels(mortality_urbsubs_02_pred$group)

ggpred_Q2.urbsubs_mortality <- 
ggplot(mortality_urbsubs_02_pred) +
  labs(x = "Urbanization Score",
       y = "Probability of death at\n end of growing season",
       color = "Transect",
       fill = "Transect") +
  ylim(0, 0.25) +
  xlim(4, -2) +
  theme_1() +
  rep_geoms2 +

# adding stats from ANOVA
           ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.97,
                    label = paste0(" Urb. Score: p = ", tidy_anova(mortality_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Urbanization Score") %>%
dplyr::select(p))),
size = 4.5) +
  ggpp::geom_text_npc(aes(npcx = 0.05, npcy = 0.88,
                    label = paste0(" Transect: p = ", tidy_anova(mortality_mods_best_u[[2]]) %>%
dplyr::filter(Predictor == "Subtransect") %>%
dplyr::select(p))),
size = 4.5)

ggpred_Q2.urbsubs_mortality

```

# Combine plots into one figure
## Gradient / City_dist
```{r}
gradient_citydist_plots <- ggarrange(
ggpred_Q1.citydist_ldmc,
ggpred_Q1.citydist_sla,
ggpred_Q1.citydist_height_e,
ggpred_Q1.citydist_height_l,
ggpred_Q1.citydist_rgr,
ggpred_Q1.citydist_ramets_e,
ggpred_Q1.citydist_ramets_l,
ggpred_Q1.citydist_mortality +
            font("x.text"),
          ncol = 4,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D", "E", "F", "G"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot


dev.copy2pdf(file = here::here("./Figures_Tables/Regressions/multi_yr_mods/Growth/Q1_grad_citydist_Growth.pdf"),
             width = 15, height = 7.5)
```


## Gradient / Urbanization Score
```{r}
gradient_urbscore_plots <- ggarrange(
ggpred_Q1.urbscore_ldmc,
ggpred_Q1.urbscore_sla,
ggpred_Q1.urbscore_height_e,
ggpred_Q1.urbscore_height_l,
ggpred_Q1.urbscore_rgr,
ggpred_Q1.urbscore_ramets_e,
ggpred_Q1.urbscore_ramets_l,
ggpred_Q1.urbscore_mortality +
            font("x.text"),
          ncol = 4,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D", "E", "F", "G"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Figures_Tables/Regressions/multi_yr_mods/Growth/Q1_grad_urbscore_Growth.pdf"),
             width = 15, height = 7.5)
```

## Urb Subtransects / City_dist
```{r}
urbsubs_citydist_plots <- ggarrange(
  ggpred_Q2.citydist_ldmc,
  ggpred_Q2.citydist_sla,
  ggpred_Q2.citydist_height_e,
  ggpred_Q2.citydist_height_l,
  ggpred_Q2.citydist_rgr,
  ggpred_Q2.citydist_ramets_e,
  ggpred_Q2.citydist_ramets_l,
  ggpred_Q2.citydist_mortality +
            font("x.text"),
          ncol = 4,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D", "E", "F", "G"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Figures_Tables/Regressions/multi_yr_mods/Growth/Q2_urbsubs_citydist_Growth.pdf"),
             width = 15, height = 8)
```


## Urb Subtransects / Urbanization Score
```{r}
urbsubs_urbscore_plots <- ggarrange(
  ggpred_Q2.urbsubs_ldmc,
  ggpred_Q2.urbsubs_sla,
  ggpred_Q2.urbsubs_height_e,
  ggpred_Q2.urbsubs_height_l,
  ggpred_Q2.urbsubs_rgr,
  ggpred_Q2.urbsubs_ramets_e,
  ggpred_Q2.urbsubs_ramets_l,
  ggpred_Q2.urbsubs_mortality +
            font("x.text"),
          ncol = 4,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D", "E", "F", "G"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Figures_Tables/Regressions/multi_yr_mods/Growth/Q2_urbsubs_urbscore_Growth.pdf"),
             width = 15, height = 8)
```

# Create boxplots
## Heights- Late
```{r}
ggplot(heights %>%
         dplyr::filter(Transect_ID != "Rural"),
       aes(x = Transect_ID,
           y = Total_Height_late)) + 
  geom_boxplot(
       size = 0.5) + 
  # geom_point(position = "jitter") + 
  theme_pubclean()
```

# Find estimated marginal means at terminii
## Urban Subtransects
### City_dist
#### Ramets, after flowering
```{r}
# PERCENT CHANGE, suburban to urban terminus:
Calc_percent_change_urbsubs(ramets_late_urbsubs_01_pred) # -15.5%
```

#### Height, before flowering
```{r}
Calc_percent_change_transects(heights_early_urbsubs_01_pred) # 10.9%
```

#### Height, after flowering

```{r}
Calc_percent_change_transects(heights_late_urbsubs_01_pred) # 4.7%
```

### Urbanization score
#### SLA
```{r}

```