# Set up notebook
## Load libraries & functions
```{r}
source("libraries.R")
source("functions.R")
```

## Import data
```{r}
pop_vars <- read.csv(here::here("./Joined_annual_data/weevil.csv")) %>%
  dplyr::select(-1) %>%
  dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block", "Year", "Transect_ID", "Urb_Rur")), as.character) %>%
    dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block", "Year", "Transect_ID", "Urb_Rur")), as.factor) %>%
  dplyr::select(1:6, 11:20)


source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_1yr_mods.Rmd", quiet=TRUE))

```


# Q1
## Create BLUP vectors for each trait
### Defense
#### City_dist
```{r}
# Create BLUP dfs for each trait
latex_BLUP <- create_BLUP(def.m1) %>%
  dplyr::rename(latex = 2)

herb_e_bin_BLUP <- create_BLUP(def.m2) %>%
  dplyr::rename(herb_e_bin = 2)

herb_e_quant_BLUP <- create_BLUP(def.m3) %>%
  dplyr::rename(herb_e_quant = 2)

herb_l_bin_BLUP <- create_BLUP(def.m4) %>%
  dplyr::rename(herb_l_bin = 2)

herb_l_quant_BLUP <- create_BLUP(def.m5) %>%
  dplyr::rename(herb_l_quant = 2)

weev_bin_BLUP <- create_BLUP(def.m6) %>%
  dplyr::rename(weev_mods_bin = 2)

weev_quant_BLUP <- create_BLUP(def.m7) %>%
  dplyr::rename(weev_mods_quant = 2)


```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
latex_BLUP_u <- create_BLUP(def.m1_u) %>%
  dplyr::rename(latex = 2)

herb_e_bin_BLUP_u <- create_BLUP(def.m2_u) %>%
  dplyr::rename(herb_e_bin = 2)

herb_e_quant_BLUP_u <- create_BLUP(def.m3_u) %>%
  dplyr::rename(herb_e_quant = 2)

herb_l_bin_BLUP_u <- create_BLUP(def.m4_u) %>%
  dplyr::rename(herb_l_bin = 2)

herb_l_quant_BLUP_u <- create_BLUP(def.m5_u) %>%
  dplyr::rename(herb_l_quant = 2)

weev_bin_BLUP_u <- create_BLUP(def.m6_u) %>%
  dplyr::rename(weev_mods_bin = 2)

weev_quant_BLUP_u <- create_BLUP(def.m7_u) %>%
  dplyr::rename(weev_mods_quant = 2)


```

### Growth
#### City_dist
```{r}
# Create BLUP dfs for each trait
ldmc_BLUP <- create_BLUP(grow.m1) %>%
  dplyr::rename(ldmc = 2)

sla_BLUP <- create_BLUP(grow.m2) %>%
  dplyr::rename(sla = 2)

heights_early_BLUP <- create_BLUP(grow.m3) %>%
  dplyr::rename(heights_early = 2)

heights_late_BLUP <- create_BLUP(grow.m4) %>%
  dplyr::rename(heights_late = 2)

rgr_BLUP <- create_BLUP(grow.m5) %>%
  dplyr::rename(rgr = 2)

ramets_early_BLUP <- create_BLUP(grow.m6) %>%
  dplyr::rename(ramets_early = 2)

ramets_late_BLUP <- create_BLUP(grow.m7) %>%
  dplyr::rename(ramets_late = 2)

mortality_BLUP <- create_BLUP(grow.m8) %>%
  dplyr::rename(mortality = 2)
```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
ldmc_BLUP_u <- create_BLUP(grow.m1_u) %>%
  dplyr::rename(ldmc = 2)

sla_BLUP_u <- create_BLUP(grow.m2_u) %>%
  dplyr::rename(sla = 2)

heights_early_BLUP_u <- create_BLUP(grow.m3_u) %>%
  dplyr::rename(heights_early = 2)

heights_late_BLUP_u <- create_BLUP(grow.m4_u) %>%
  dplyr::rename(heights_late = 2)

rgr_BLUP_u <- create_BLUP(grow.m5_u) %>%
  dplyr::rename(rgr = 2)

ramets_early_BLUP_u <- create_BLUP(grow.m6_u) %>%
  dplyr::rename(ramets_early = 2)

ramets_late_BLUP_u <- create_BLUP(grow.m7_u) %>%
  dplyr::rename(ramets_late = 2)

mortality_BLUP_u <- create_BLUP(grow.m8_u) %>%
  dplyr::rename(mortality = 2)
```

### Herbivores
#### City_dist
```{r}
# Create BLUP dfs for each trait
monarch_BLUP <- create_BLUP(herb.m1) %>%
  dplyr::rename(monarch = 2)

asclepiadis_BLUP <- create_BLUP(herb.m2) %>%
  dplyr::rename(asclepiadis = 2)

clivicollis_BLUP <- create_BLUP(herb.m3) %>%
  dplyr::rename(clivicollis = 2)

```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
monarch_BLUP_u <- create_BLUP(herb.m1_u) %>%
  dplyr::rename(monarch = 2)

asclepiadis_BLUP_u <- create_BLUP(herb.m2_u) %>%
  dplyr::rename(asclepiadis = 2)

clivicollis_BLUP_u <- create_BLUP(herb.m3_u) %>%
  dplyr::rename(clivicollis = 2)

```


### Reproductive
#### City_dist
```{r}
# Create BLUP dfs for each trait
flsucc_BLUP <- create_BLUP(repr.m1) %>%
  dplyr::rename(flsucc = 2)

flowers_BLUP <- create_BLUP(repr.m2) %>%
  dplyr::rename(flowers = 2)

flsize_BLUP <- create_BLUP(repr.m3) %>%
  dplyr::rename(flsize = 2)

fltime_BLUP <- create_BLUP(repr.m4) %>%
  dplyr::rename(fltime = 2)

flstart_BLUP <- create_BLUP(repr.m5) %>%
  dplyr::rename(flstart = 2)

pods_BLUP <- create_BLUP(repr.m6) %>%
  dplyr::rename(pods = 2)

firstpods_BLUP <- create_BLUP(repr.m7) %>%
  dplyr::rename(firstpods = 2)

peduncles_BLUP <- create_BLUP(repr.m8) %>%
  dplyr::rename(peduncles = 2)
```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
flsucc_BLUP_u <- create_BLUP(repr.m1_u) %>%
  dplyr::rename(flsucc = 2)

flowers_BLUP_u <- create_BLUP(repr.m2_u) %>%
  dplyr::rename(flowers = 2)

flsize_BLUP_u <- create_BLUP(repr.m3_u) %>%
  dplyr::rename(flsize = 2)

fltime_BLUP_u <- create_BLUP(repr.m4_u) %>%
  dplyr::rename(fltime = 2)

flstart_BLUP_u <- create_BLUP(repr.m5_u) %>%
  dplyr::rename(flstart = 2)

pods_BLUP_u <- create_BLUP(repr.m6_u) %>%
  dplyr::rename(pods = 2)

firstpods_BLUP_u <- create_BLUP(repr.m7_u) %>%
  dplyr::rename(firstpods = 2)

peduncles_BLUP_u <- create_BLUP(repr.m8_u) %>%
  dplyr::rename(peduncles = 2)
```

### Cardenolides
```{r}
# B/c these are general linear models and there are no random effects, I'll add in raw values for each cardenolide peak
cards_BLUPs <- cards %>%
  dplyr::select(2,3,5,7,10,15,17,19) %>%
  dplyr::mutate(Population = as.character(Population))
```

### Merge into single df
#### City_dist
```{r}
all_traits <- purrr::reduce(
  list(
    # defense traits
    latex_BLUP        ,
    herb_e_bin_BLUP   ,
    herb_e_quant_BLUP ,
    herb_l_bin_BLUP   ,
    herb_l_quant_BLUP ,
    weev_bin_BLUP     ,
    weev_quant_BLUP   ,

     # growth traits
    ldmc_BLUP         ,
    sla_BLUP          ,
    heights_early_BLUP,
    heights_late_BLUP ,
    rgr_BLUP          ,
    ramets_early_BLUP ,
    ramets_late_BLUP  ,
    mortality_BLUP    ,
    
    # reproductive traits                  
     flsucc_BLUP,    
     flowers_BLUP,   
     flsize_BLUP,    
     fltime_BLUP,    
     flstart_BLUP,   
     pods_BLUP,   
     firstpods_BLUP,
     peduncles_BLUP, 
    
    # cardenolides
    cards_BLUPs,
    
    # herbivores
    monarch_BLUP,
    asclepiadis_BLUP,
    clivicollis_BLUP
                      ),
              dplyr::left_join,
              by = c('Population',
                     'Transect_ID',
                     'City_dist',
                     'Urb_score')) %>%

# add new col converting transect into urb/rural classes
  dplyr::mutate(Urb_Rur = case_when(
    Transect_ID == "Rural" ~ "Rural",
    TRUE ~ "Urban"
  ))
```

#### Urb_score
```{r}
all_traits_u <- purrr::reduce(
  list(
    # defense traits
    latex_BLUP_u        ,
    herb_e_bin_BLUP_u   ,
    herb_e_quant_BLUP_u ,
    herb_l_bin_BLUP_u   ,
    herb_l_quant_BLUP_u ,
    weev_bin_BLUP_u     ,
    weev_quant_BLUP_u   ,

     # growth traits
    ldmc_BLUP_u         ,
    sla_BLUP_u          ,
    heights_early_BLUP_u,
    heights_late_BLUP_u ,
    rgr_BLUP_u          ,
    ramets_early_BLUP_u ,
    ramets_late_BLUP_u  ,
    mortality_BLUP_u    ,
    
    # reproductive traits                  
     flsucc_BLUP_u,    
     flowers_BLUP_u,   
     flsize_BLUP_u,    
     fltime_BLUP_u,    
     flstart_BLUP_u,   
     pods_BLUP_u,   
     firstpods_BLUP_u,
     peduncles_BLUP_u, 
    
    # cardenolides
    cards_BLUPs,
    
    # herbivores
    monarch_BLUP_u,
    asclepiadis_BLUP_u,
    clivicollis_BLUP_u
                      ),
              dplyr::left_join,
              by = c('Population',
                     'Transect_ID',
                     'City_dist',
                     'Urb_score')) %>%

# add new col converting transect into urb/rural classes
  dplyr::mutate(Urb_Rur = case_when(
    Transect_ID == "Rural" ~ "Rural",
    TRUE ~ "Urban"
  ))
```

## Use mvabund with gaussian family
### City_dist
```{r}
# Use the just the trait data (in columns 5 to 11) and convert it to an mvabund object format used by the mvabund package.
# 
all_traits %<>%
  na.omit()  # removing rows w/NAs

mvab_all <- mvabund(all_traits[,c(2, 6:30)]) 

# look at the spread of our data
par(mar = c(2, 10, 2, 2)) # adjusts the margins
boxplot(all_traits[, c(2, 6:30)],
        horizontal = TRUE,
        las = 2,
        main = "Abundance")

meanvar.plot(mvab_all)

# contrast multivariate phenotype against urban-rural habitat

plot(mvab_all ~ as.factor(all_traits$Urb_Rur),
     cex.axis = 0.8,
     cex = 0.8)
# THIS DOESN'T WORK B/C OF NEGATIVE VALUES

# contrast the multivariate phenotype across urb/rural habitat 
mod1 <- manylm(mvab_all ~ Urb_Rur,
              data = all_traits)

plot(mod1)

# test if multivariate phenotype varied across the habitats by using the anova function

anova(mod1)

# No effect of Urban vs. rural habitat, meaning that the overall phenotype does not differ between the urban/rural classification of population they were sourced from.

# run univariate tests for each trait separately.
anova_blup <- anova(mod1, p.uni = "adjusted") %T>%
  print()
# after adjusting for multiple testing, there are still no effects of habitat on any specific trait.


# use city_dist as habitat descriptor
anova_blup2 <- manylm(mvab_all ~ City_dist,
               data = all_traits) %>%
  anova() %T>%
  print()
# Still no effect of urbanization on herbivore abundance.
```

### Urb_score
```{r}

all_traits_u %<>%
  na.omit()  # removing rows w/NAs

# Use the just the trait data (in columns 5 to 11) and convert it to an mvabund object format used by the mvabund package.
mvab_all_u <- mvabund(all_traits_u[, c(2, 6:30)]) 

# look at the spread of our data
par(mar = c(2, 10, 2, 2)) # adjusts the margins
boxplot(all_traits_u[, c(2, 6:30)],
        horizontal = TRUE,
        las = 2,
        main = "Abundance")


meanvar.plot(mvab_all_u)

# contrast multivariate phenotype against urban-rural habitat

plot(mvab_all_u ~ as.factor(all_traits_u$Urb_Rur),
     cex.axis = 0.8,
     cex = 0.8)
# THIS DOESN'T WORK B/C OF NEGATIVE VALUES

# contrast the multivariate phenotype across urb/rural habitat 
mod1_u <- manylm(mvab_all_u ~ Urb_Rur,
              data = all_traits_u)

plot(mod1_u)

# test if multivariate phenotype varied across the habitats by using the anova function

anova(mod1_u)

# No effect of Urban vs. rural habitat, meaning that the overall phenotype does not differ between the urban/rural classification of population they were sourced from.

# run univariate tests for each trait separately.
anova_blup_u <- anova(mod1_u, p.uni = "adjusted") %T>%
  print()
# after adjusting for multiple testing, there are still no effects of habitat on any specific trait.


# use urbscore as habitat descriptor
anova_blup2_u <- manylm(mvab_all_u ~ Urb_score,
               data = all_traits_u) %>%
  anova() %T>%
  print()
# Still no effect of urbanization on herbivore abundance.
```


### Export
#### City_dist models
```{r}
tab1 <- anova_blup_table(anova_blup)  %>%
  dplyr::mutate("Urbanization" = ifelse(row_number() == 2,
                           "Urban/Rural (Distance)",
                           "Intercept")) %>%
    dplyr::filter(Urbanization != "Intercept")

tab2 <- anova_blup_table(anova_blup2) %>%
    dplyr::mutate("Urbanization" = ifelse(row_number() == 2,
                           "Distance to City Center",
                           "Intercept")) %>%
    dplyr::filter(Urbanization != "Intercept")


city_tables <- rbind(tab1, tab2) %>%
  flextable() %>%
  hline(i = 2 ) %>%
  autofit() 

```

#### Urbanization score models
```{r}

tab1u <- anova_blup_table(anova_blup_u) %>%
  dplyr::mutate("Urbanization" = ifelse(row_number() == 2,
                           "Urban/Rural (Urb. Score)",
                           "Intercept")) %>%
    dplyr::filter(Urbanization != "Intercept")

tab2u <- anova_blup_table(anova_blup2_u) %>%
    dplyr::mutate("Urbanization" = ifelse(row_number() == 2,
                           "Urbanization Score",
                           "Intercept")) %>%
    dplyr::filter(Urbanization != "Intercept")


urb_sc_tables <- rbind(tab1u, tab2u) %>%
  flextable() %>%
  hline(i = 2 ) %>%
  autofit() 

```

### Export all anovas in one table
```{r}
word_export <- read_docx()
  
  body_add_par(word_export, value = "Urbanization = Distance to City Center", style = "heading 1")
  body_add_flextable(word_export, city_tables)
  
  body_add_par(word_export, value = "")
  body_add_par(word_export, value = "")
  
    body_add_par(word_export, value = "Urbanization = Urbanization Score", style = "heading 1")
  body_add_flextable(word_export, urb_sc_tables)

  print(word_export, here::here("./Figures_Tables/mvabund/mvabund_anovas_1yr_Q1.docx"))
```

# Q2
## Create BLUP vectors for each trait
### Defense
#### City_dist
```{r}
# Create BLUP dfs for each trait
latex_BLUP <- create_BLUP(def.tr.m1) %>%
  dplyr::rename(latex = 2)

herb_e_bin_BLUP <- create_BLUP(def.tr.m2) %>%
  dplyr::rename(herb_e_bin = 2)

herb_e_quant_BLUP <- create_BLUP(def.tr.m3) %>%
  dplyr::rename(herb_e_quant = 2)

herb_l_bin_BLUP <- create_BLUP(def.tr.m4) %>%
  dplyr::rename(herb_l_bin = 2)

herb_l_quant_BLUP <- create_BLUP(def.tr.m5) %>%
  dplyr::rename(herb_l_quant = 2)

weev_bin_BLUP <- create_BLUP(def.tr.m6) %>%
  dplyr::rename(weev_mods_bin = 2)

weev_quant_BLUP <- create_BLUP(def.tr.m7) %>%
  dplyr::rename(weev_mods_quant = 2)


```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
latex_BLUP_u <- create_BLUP(def.tr.m1_u) %>%
  dplyr::rename(latex = 2)

herb_e_bin_BLUP_u <- create_BLUP(def.tr.m2_u) %>%
  dplyr::rename(herb_e_bin = 2)

herb_e_quant_BLUP_u <- create_BLUP(def.tr.m3_u) %>%
  dplyr::rename(herb_e_quant = 2)

herb_l_bin_BLUP_u <- create_BLUP(def.tr.m4_u) %>%
  dplyr::rename(herb_l_bin = 2)

herb_l_quant_BLUP_u <- create_BLUP(def.tr.m5_u) %>%
  dplyr::rename(herb_l_quant = 2)

weev_bin_BLUP_u <- create_BLUP(def.tr.m6_u) %>%
  dplyr::rename(weev_mods_bin = 2)

weev_quant_BLUP_u <- create_BLUP(def.tr.m7_u) %>%
  dplyr::rename(weev_mods_quant = 2)


```

### Growth
#### City_dist
```{r}
# Create BLUP dfs for each trait
ldmc_BLUP <- create_BLUP(grow.tr.m1) %>%
  dplyr::rename(ldmc = 2)

sla_BLUP <- create_BLUP(grow.tr.m2) %>%
  dplyr::rename(sla = 2)

heights_early_BLUP <- create_BLUP(grow.tr.m3) %>%
  dplyr::rename(heights_early = 2)

heights_late_BLUP <- create_BLUP(grow.tr.m4) %>%
  dplyr::rename(heights_late = 2)

rgr_BLUP <- create_BLUP(grow.tr.m5) %>%
  dplyr::rename(rgr = 2)

ramets_early_BLUP <- create_BLUP(grow.tr.m6) %>%
  dplyr::rename(ramets_early = 2)

ramets_late_BLUP <- create_BLUP(grow.tr.m7) %>%
  dplyr::rename(ramets_late = 2)

mortality_BLUP <- create_BLUP(grow.tr.m8) %>%
  dplyr::rename(mortality = 2)
```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
ldmc_BLUP_u <- create_BLUP(grow.tr.m1_u) %>%
  dplyr::rename(ldmc = 2)

sla_BLUP_u <- create_BLUP(grow.tr.m2_u) %>%
  dplyr::rename(sla = 2)

heights_early_BLUP_u <- create_BLUP(grow.tr.m3_u) %>%
  dplyr::rename(heights_early = 2)

heights_late_BLUP_u <- create_BLUP(grow.tr.m4_u) %>%
  dplyr::rename(heights_late = 2)

rgr_BLUP_u <- create_BLUP(grow.tr.m5_u) %>%
  dplyr::rename(rgr = 2)

ramets_early_BLUP_u <- create_BLUP(grow.tr.m6_u) %>%
  dplyr::rename(ramets_early = 2)

ramets_late_BLUP_u <- create_BLUP(grow.tr.m7_u) %>%
  dplyr::rename(ramets_late = 2)

mortality_BLUP_u <- create_BLUP(grow.tr.m8_u) %>%
  dplyr::rename(mortality = 2)
```

### Herbivores
#### City_dist
```{r}
# Create BLUP dfs for each trait
monarch_BLUP <- create_BLUP(herb.tr.m1) %>%
  dplyr::rename(monarch = 2)

asclepiadis_BLUP <- create_BLUP(herb.tr.m2) %>%
  dplyr::rename(asclepiadis = 2)

clivicollis_BLUP <- create_BLUP(herb.tr.m3) %>%
  dplyr::rename(clivicollis = 2)

```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
monarch_BLUP_u <- create_BLUP(herb.tr.m1_u) %>%
  dplyr::rename(monarch = 2)

asclepiadis_BLUP_u <- create_BLUP(herb.tr.m2_u) %>%
  dplyr::rename(asclepiadis = 2)

clivicollis_BLUP_u <- create_BLUP(herb.tr.m3_u) %>%
  dplyr::rename(clivicollis = 2)

```


### Reproductive
#### City_dist
```{r}
# Create BLUP dfs for each trait
flsucc_BLUP <- create_BLUP(repr.tr.m1) %>%
  dplyr::rename(flsucc = 2)

flowers_BLUP <- create_BLUP(repr.tr.m2) %>%
  dplyr::rename(flowers = 2)

flsize_BLUP <- create_BLUP(repr.tr.m3) %>%
  dplyr::rename(flsize = 2)

fltime_BLUP <- create_BLUP(repr.tr.m4) %>%
  dplyr::rename(fltime = 2)

flstart_BLUP <- create_BLUP(repr.tr.m5) %>%
  dplyr::rename(flstart = 2)

pods_BLUP <- create_BLUP(repr.tr.m6) %>%
  dplyr::rename(pods = 2)

firstpods_BLUP <- create_BLUP(repr.tr.m7) %>%
  dplyr::rename(firstpods = 2)

peduncles_BLUP <- create_BLUP(repr.tr.m8) %>%
  dplyr::rename(peduncles = 2)
```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
flsucc_BLUP_u <- create_BLUP(repr.tr.m1_u) %>%
  dplyr::rename(flsucc = 2)

flowers_BLUP_u <- create_BLUP(repr.tr.m2_u) %>%
  dplyr::rename(flowers = 2)

flsize_BLUP_u <- create_BLUP(repr.tr.m3_u) %>%
  dplyr::rename(flsize = 2)

fltime_BLUP_u <- create_BLUP(repr.tr.m4_u) %>%
  dplyr::rename(fltime = 2)

flstart_BLUP_u <- create_BLUP(repr.tr.m5_u) %>%
  dplyr::rename(flstart = 2)

pods_BLUP_u <- create_BLUP(repr.tr.m6_u) %>%
  dplyr::rename(pods = 2)

firstpods_BLUP_u <- create_BLUP(repr.tr.m7_u) %>%
  dplyr::rename(firstpods = 2)

peduncles_BLUP_u <- create_BLUP(repr.tr.m8_u) %>%
  dplyr::rename(peduncles = 2)
```

### Cardenolides
Not including these because such small sample size for Q2
### Merge into single df
#### City_dist
```{r}
all_traits <- purrr::reduce(
  list(
    # defense traits
    latex_BLUP        ,
    herb_e_bin_BLUP   ,
    herb_e_quant_BLUP ,
    herb_l_bin_BLUP   ,
    herb_l_quant_BLUP ,
    weev_bin_BLUP     ,
    weev_quant_BLUP   ,

     # growth traits
    ldmc_BLUP         ,
    sla_BLUP          ,
    heights_early_BLUP,
    heights_late_BLUP ,
    rgr_BLUP          ,
    ramets_early_BLUP ,
    ramets_late_BLUP  ,
    mortality_BLUP    ,
    
    # reproductive traits                  
     flsucc_BLUP,    
     flowers_BLUP,   
     flsize_BLUP,    
     fltime_BLUP,    
     flstart_BLUP,   
     pods_BLUP,    
     firstpods_BLUP,
     peduncles_BLUP, 
    
    # herbivores
    monarch_BLUP,
    asclepiadis_BLUP,
    clivicollis_BLUP
                      ),
              dplyr::left_join,
              by = c('Population',
                     'Transect_ID',
                     'City_dist',
                     'Urb_score')) %>%

# add new col converting transect into urb/rural classes
  dplyr::mutate(Urb_Rur = case_when(
    Transect_ID == "Rural" ~ "Rural",
    TRUE ~ "Urban"
  ))
```

#### Urb_score
```{r}
all_traits_u <- purrr::reduce(
  list(
    # defense traits
    latex_BLUP_u        ,
    herb_e_bin_BLUP_u   ,
    herb_e_quant_BLUP_u ,
    herb_l_bin_BLUP_u   ,
    herb_l_quant_BLUP_u ,
    weev_bin_BLUP_u     ,
    weev_quant_BLUP_u   ,

     # growth traits
    ldmc_BLUP_u         ,
    sla_BLUP_u          ,
    heights_early_BLUP_u,
    heights_late_BLUP_u ,
    rgr_BLUP_u          ,
    ramets_early_BLUP_u ,
    ramets_late_BLUP_u  ,
    mortality_BLUP_u    ,
    
    # reproductive traits                  
     flsucc_BLUP_u,    
     flowers_BLUP_u,   
     flsize_BLUP_u,    
     fltime_BLUP_u,    
     flstart_BLUP_u,   
     pods_BLUP_u,   
     firstpods_BLUP_u,
     peduncles_BLUP_u, 
    

    # herbivores
    monarch_BLUP_u,
    asclepiadis_BLUP_u,
    clivicollis_BLUP_u
                      ),
              dplyr::left_join,
              by = c('Population',
                     'Transect_ID',
                     'City_dist',
                     'Urb_score')) %>%

# add new col converting transect into urb/rural classes
  dplyr::mutate(Urb_Rur = case_when(
    Transect_ID == "Rural" ~ "Rural",
    TRUE ~ "Urban"
  ))
```

## Use mvabund with gaussian family
### City_dist
```{r}
# Use the just the trait data (in columns 5 to 11) and convert it to an mvabund object format used by the mvabund package.

all_traits %<>%
  dplyr::filter(Transect_ID != "Rural") %<>% # remove rural pops
  na.omit()  # removing rows w/NAs

mvab_all <- mvabund(all_traits[,c(2, 6:29)]) 

# look at the spread of our data
par(mar = c(2, 10, 2, 2)) # adjusts the margins
boxplot(all_traits[, c(2, 6:29)],
        horizontal = TRUE,
        las = 2,
        main = "Abundance")

# It looks like some traits are much more variable than others. It’s probably a good idea to check our mean-variance relationship then! We can do this using the meanvar.plot function:
meanvar.plot(mvab_all)

# the species with high means (on the x axis) also have high variances (y axis).
# We can deal with this relationship by choosing a family of GLMs with an appropriate mean-variance assumption. The default family used by mvabund when fitting multivariate GLMs is negative binomial which assumes a quadratic mean-variance relationship and a log-linear relationship between the response variables and any continuous variables. In [the site's] example, we only have categorical variables so that one’s not too important. If you are unsure of these relationships, don’t worry, we can check our model fit later. [I have quantitative variables too]

# There is a ‘quick and dirty’ built-in plotting function in the mvabund package that allows us to contrast transformed abundances to the predictor variables of our choice. To contrast abundances against urban-rural habitat, we would use:

plot(mvab_all ~ as.factor(all_traits$Urb_Rur),
     cex.axis = 0.8,
     cex = 0.8)
# THIS DOESN'T WORK B/C OF NEGATIVE VALUES

mod1 <- manylm(mvab_all ~ City_dist*Transect_ID,
              data = all_traits)

# Before we examine the output, we need to check our model assumptions. We can use the plot function to generate a plot of residuals.

plot(mod1)
# We can test the multivariate hypothesis of whether species composition varied across the habitats by using the anova function. This gives an analysis of deviance table where we use likelihood ratio tests and resampled p values to look for a significant effect of Habitat on the community data.

anova(mod1)

anova_blup <- anova(mod1, p.uni = "adjusted") %T>%
  print()
```


### Urb_score
```{r}

all_traits_u %<>%
  dplyr::filter(Transect_ID != "Rural") %<>% # remove rural pops
  na.omit()  # removing rows w/NAs

# Use the just the trait data (in columns 5 to 11) and convert it to an mvabund object format used by the mvabund package.
mvab_all_u <- mvabund(all_traits_u[, c(2, 6:29)]) 

# look at the spread of our data
par(mar = c(2, 10, 2, 2)) # adjusts the margins
boxplot(all_traits_u[, c(2, 6:29)],
        horizontal = TRUE,
        las = 2,
        main = "Abundance")


meanvar.plot(mvab_all_u)


plot(mvab_all_u ~ as.factor(all_traits_u$Urb_Rur),
     cex.axis = 0.8,
     cex = 0.8)
# THIS DOESN'T WORK B/C OF NEGATIVE VALUES




mod1_u <- manylm(mvab_all_u ~ Urb_score*Transect_ID,
              data = all_traits_u)

# Before we examine the output, we need to check our model assumptions. We can use the plot function to generate a plot of residuals.

plot(mod1_u)
# We can test the multivariate hypothesis of whether species composition varied across the habitats by using the anova function. This gives an analysis of deviance table where we use likelihood ratio tests and resampled p values to look for a significant effect of Habitat on the community data.

anova(mod1_u)

anova_blup_u <- anova(mod1_u, p.uni = "adjusted") %T>%
  print()
```

### Export
#### City_dist models
```{r}
tab2 <- anova_blup_table(anova_blup) %>%
  dplyr::filter(Urbanization != "(Intercept)") %>%
    dplyr::mutate(Urbanization = case_when(
    str_detect(Urbanization, ":")~
      "D x S",
    str_detect(Urbanization, "City_dist")~
      "Distance to City Center",
    str_detect(Urbanization, "Transect_ID")~
      "Subtransect"))

city_table <- tab2 %>%
  flextable() %>%
  autofit() 

```

#### Urbanization score models
```{r}

tab2u <- anova_blup_table(anova_blup_u) %>%
  dplyr::filter(Urbanization != "(Intercept)") %>%
    dplyr::mutate(Urbanization = case_when(
    str_detect(Urbanization, ":")~
      "U x S",
    str_detect(Urbanization, "Urb_score")~
      "Urbanization Score",
    str_detect(Urbanization, "Transect_ID")~
      "Subtransect"))

urb_sc_table <- tab2u %>%
  flextable() %>%
  autofit() 

```

### Export all anovas in one table
```{r}
word_export <- read_docx()
  
  body_add_par(word_export, value = "Urbanization = Distance to City Center", style = "heading 1")
  body_add_flextable(word_export, city_table)
  
  body_add_par(word_export, value = "")
  body_add_par(word_export, value = "")
  
    body_add_par(word_export, value = "Urbanization = Urbanization Score", style = "heading 1")
  body_add_flextable(word_export, urb_sc_table)

  print(word_export, here::here("./Figures_Tables/mvabund/mvabund_anovas_1yr_Q2.docx"))
```

