# Set up notebook
## Load libraries & functions
```{r}
source("libraries.R")
source("functions.R")
```

## Import data
```{r}
pop_vars <- read.csv(here::here("./data/Joined_annual_data/weevil.csv")) %>%
  dplyr::select(-1) %>%
  dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block", "Year", "Transect_ID", "Urb_Rur")), as.character) %>%
    dplyr::mutate_at(vars(c("Population", "Family", "Replicate", "Block", "Year", "Transect_ID", "Urb_Rur")), as.factor) %>%
  dplyr::select(1:6, 11:20)


source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_Growth.Rmd", quiet=TRUE))

source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_defense.Rmd", quiet=TRUE))

source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_Reproduc.Rmd", quiet=TRUE))

source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_herbivores.Rmd", quiet=TRUE))
```


# Q1
## Create BLUP vectors for each trait
### Defense
#### City_dist
```{r}
# Create BLUP dfs for each trait
latex_BLUP <- create_BLUP(latex_mods[[1]]) %>%
  dplyr::rename(latex = 2)

herb_e_bin_BLUP <- create_BLUP(herb_early_mods_binomial[[1]]) %>%
  dplyr::rename(herb_e_bin = 2)

herb_e_quant_BLUP <- create_BLUP(herb_early_mods_quant[[1]]) %>%
  dplyr::rename(herb_e_quant = 2)

herb_l_bin_BLUP <- create_BLUP(herb_late_mods_binomial[[1]]) %>%
  dplyr::rename(herb_l_bin = 2)

herb_l_quant_BLUP <- create_BLUP(herb_late_mods_quant[[1]]) %>%
  dplyr::rename(herb_l_quant = 2)

weev_bin_BLUP <- create_BLUP(weev_mods_binomial[[1]]) %>%
  dplyr::rename(weev_mods_bin = 2)

weev_quant_BLUP <- create_BLUP(weev_mods_quant[[1]]) %>%
  dplyr::rename(weev_mods_quant = 2)


```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
latex_BLUP_u <- create_BLUP(latex_mods[[2]]) %>%
  dplyr::rename(latex = 2)

herb_e_bin_BLUP_u <- create_BLUP(herb_early_mods_binomial[[2]]) %>%
  dplyr::rename(herb_e_bin = 2)

herb_e_quant_BLUP_u <- create_BLUP(herb_early_mods_quant[[2]]) %>%
  dplyr::rename(herb_e_quant = 2)

herb_l_bin_BLUP_u <- create_BLUP(herb_late_mods_binomial[[2]]) %>%
  dplyr::rename(herb_l_bin = 2)

herb_l_quant_BLUP_u <- create_BLUP(herb_late_mods_quant[[2]]) %>%
  dplyr::rename(herb_l_quant = 2)

weev_bin_BLUP_u <- create_BLUP(weev_mods_binomial[[2]]) %>%
  dplyr::rename(weev_mods_bin = 2)

weev_quant_BLUP_u <- create_BLUP(weev_mods_quant[[2]]) %>%
  dplyr::rename(weev_mods_quant = 2)


```


### Growth
#### City_dist
```{r}
# Create BLUP dfs for each trait
ldmc_BLUP <- create_BLUP(ldmc_mods[[1]]) %>%
  dplyr::rename(ldmc = 2)

sla_BLUP <- create_BLUP(sla_mods[[1]]) %>%
  dplyr::rename(sla = 2)

heights_early_BLUP <- create_BLUP(heights_early_mods[[1]]) %>%
  dplyr::rename(heights_early = 2)

heights_late_BLUP <- create_BLUP(heights_late_mods[[1]]) %>%
  dplyr::rename(heights_late = 2)

rgr_BLUP <- create_BLUP(rgr_mods[[1]]) %>%
  dplyr::rename(rgr = 2)

ramets_early_BLUP <- create_BLUP(ramets_early_mods[[1]]) %>%
  dplyr::rename(ramets_early = 2)

ramets_late_BLUP <- create_BLUP(ramets_late_mods[[1]]) %>%
  dplyr::rename(ramets_late = 2)

mortality_BLUP <- create_BLUP(mortality_mods[[1]]) %>%
  dplyr::rename(mortality = 2)
```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
ldmc_BLUP_u <- create_BLUP(ldmc_mods[[2]]) %>%
  dplyr::rename(ldmc = 2)

sla_BLUP_u <- create_BLUP(sla_mods[[2]]) %>%
  dplyr::rename(sla = 2)

heights_early_BLUP_u <- create_BLUP(heights_early_mods[[2]]) %>%
  dplyr::rename(heights_early = 2)

heights_late_BLUP_u <- create_BLUP(heights_late_mods[[2]]) %>%
  dplyr::rename(heights_late = 2)

rgr_BLUP_u <- create_BLUP(rgr_mods[[2]]) %>%
  dplyr::rename(rgr = 2)

ramets_early_BLUP_u <- create_BLUP(ramets_early_mods[[2]]) %>%
  dplyr::rename(ramets_early = 2)

ramets_late_BLUP_u <- create_BLUP(ramets_late_mods[[2]]) %>%
  dplyr::rename(ramets_late = 2)

mortality_BLUP_u <- create_BLUP(mortality_mods[[2]]) %>%
  dplyr::rename(mortality = 2)
```

### Herbivores
#### City_dist
```{r}
# Create BLUP dfs for each trait
monarch_BLUP <- create_BLUP(monarch_mods[[1]]) %>%
  dplyr::rename(monarch = 2)

asclepiadis_BLUP <- create_BLUP(asclepiadis_mods[[1]]) %>%
  dplyr::rename(asclepiadis = 2)

clivicollis_BLUP <- create_BLUP(clivicollis_mods[[1]]) %>%
  dplyr::rename(clivicollis = 2)


```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
monarch_BLUP_u <- create_BLUP(monarch_mods[[2]]) %>%
  dplyr::rename(monarch = 2)

asclepiadis_BLUP_u <- create_BLUP(asclepiadis_mods[[2]]) %>%
  dplyr::rename(asclepiadis = 2)

clivicollis_BLUP_u <- create_BLUP(clivicollis_mods[[2]]) %>%
  dplyr::rename(clivicollis = 2)

```


### Reproductive
#### City_dist
```{r}
# Create BLUP dfs for each trait
flsucc_BLUP <- create_BLUP(flsucc_mods[[1]]) %>%
  dplyr::rename(flsucc = 2)

flowers_BLUP <- create_BLUP(flowers_mods[[1]]) %>%
  dplyr::rename(flowers = 2)

flsize_BLUP <- create_BLUP(flsize_mods[[1]]) %>%
  dplyr::rename(flsize = 2)

fltime_BLUP <- create_BLUP(fltime_mods[[1]]) %>%
  dplyr::rename(fltime = 2)

flstart_BLUP <- create_BLUP(flstart_mods[[1]]) %>%
  dplyr::rename(flstart = 2)

pods_BLUP <- create_BLUP(pods_mods[[1]]) %>%
  dplyr::rename(pods = 2)

firstpods_BLUP <- create_BLUP(first_pods_mods[[1]]) %>%
  dplyr::rename(firstpods = 2)

peduncles_BLUP <- create_BLUP(peduncles_mods[[1]]) %>%
  dplyr::rename(peduncles = 2)

poll_BLUP <- create_BLUP(poll_mods[[1]]) %>%
  dplyr::rename(poll = 2)
```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
flsucc_BLUP_u <- create_BLUP(flsucc_mods[[2]]) %>%
  dplyr::rename(flsucc = 2)

flowers_BLUP_u <- create_BLUP(flowers_mods[[2]]) %>%
  dplyr::rename(flowers = 2)

flsize_BLUP_u <- create_BLUP(flsize_mods[[2]]) %>%
  dplyr::rename(flsize = 2)

fltime_BLUP_u <- create_BLUP(fltime_mods[[2]]) %>%
  dplyr::rename(fltime = 2)

flstart_BLUP_u <- create_BLUP(flstart_mods[[2]]) %>%
  dplyr::rename(flstart = 2)

pods_BLUP_u <- create_BLUP(pods_mods[[2]]) %>%
  dplyr::rename(pods = 2)

firstpods_BLUP_u <- create_BLUP(first_pods_mods[[2]]) %>%
  dplyr::rename(firstpods = 2)

peduncles_BLUP_u <- create_BLUP(peduncles_mods[[2]]) %>%
  dplyr::rename(peduncles = 2)

poll_BLUP_u <- create_BLUP(poll_mods[[2]]) %>%
  dplyr::rename(poll = 2)
```

### Cardenolides
```{r}
# B/c these are general linear models and there are no random effects, I'll add in raw values for each cardenolide peak
cards_BLUPs <- cards %>%
  dplyr::select(2,3,5,7,10,15,17,19) %>%
  dplyr::mutate(Population = as.character(Population))
```

### Merge into single df
#### City_dist
```{r}
all_traits <- purrr::reduce(
  list(
    # defense traits
    latex_BLUP        ,
    herb_e_bin_BLUP   ,
    herb_e_quant_BLUP ,
    herb_l_bin_BLUP   ,
    herb_l_quant_BLUP ,
    weev_bin_BLUP     ,
    weev_quant_BLUP   ,

     # growth traits
    ldmc_BLUP         ,
    sla_BLUP          ,
    heights_early_BLUP,
    heights_late_BLUP ,
    rgr_BLUP          ,
    ramets_early_BLUP ,
    ramets_late_BLUP  ,
    mortality_BLUP    ,
    
    # reproductive traits                  
     flsucc_BLUP,    
     flowers_BLUP,   
     flsize_BLUP,    
     fltime_BLUP,    
     flstart_BLUP,   
     pods_BLUP,      
     firstpods_BLUP,      
     peduncles_BLUP, 
     poll_BLUP,
    
    # cardenolides
    cards_BLUPs,
    
    # herbivores
    monarch_BLUP,
    asclepiadis_BLUP,
    clivicollis_BLUP
                      ),
              dplyr::left_join,
              by = c('Population',
                     'Transect_ID',
                     'City_dist',
                     'Urb_score')) %>%

# add new col converting transect into urb/rural classes
  dplyr::mutate(Urb_Rur = case_when(
    Transect_ID == "Rural" ~ "Rural",
    TRUE ~ "Urban"
  ))
```

#### Urb_score
```{r}
all_traits_u <- purrr::reduce(
  list(
    # defense traits
    latex_BLUP_u        ,
    herb_e_bin_BLUP_u   ,
    herb_e_quant_BLUP_u ,
    herb_l_bin_BLUP_u   ,
    herb_l_quant_BLUP_u ,
    weev_bin_BLUP_u     ,
    weev_quant_BLUP_u   ,

     # growth traits
    ldmc_BLUP_u         ,
    sla_BLUP_u          ,
    heights_early_BLUP_u,
    heights_late_BLUP_u ,
    rgr_BLUP_u          ,
    ramets_early_BLUP_u ,
    ramets_late_BLUP_u  ,
    mortality_BLUP_u    ,
    
    # reproductive traits                  
     flsucc_BLUP_u,    
     flowers_BLUP_u,   
     flsize_BLUP_u,    
     fltime_BLUP_u,    
     flstart_BLUP_u,   
     pods_BLUP_u,      
     firstpods_BLUP,      
     peduncles_BLUP_u, 
     poll_BLUP_u,
    
    # cardenolides
    cards_BLUPs,
    
    # herbivores
    monarch_BLUP_u,
    asclepiadis_BLUP_u,
    clivicollis_BLUP_u
                      ),
              dplyr::left_join,
              by = c('Population',
                     'Transect_ID',
                     'City_dist',
                     'Urb_score')) %>%

# add new col converting transect into urb/rural classes
  dplyr::mutate(Urb_Rur = case_when(
    Transect_ID == "Rural" ~ "Rural",
    TRUE ~ "Urban"
  ))
```

## Use mvabund with gaussian family
### City_dist
```{r}
# Use the just the trait data (in columns 5 to 11) and convert it to an mvabund object format used by the mvabund package.
# 
all_traits %<>%
  na.omit()  # removing rows w/NAs

mvab_all <- mvabund(all_traits[,c(2, 6:35)]) 

# look at the spread of our data
boxplot(all_traits[, c(2, 6:35)],
        horizontal = TRUE,
        las = 2,
        main = "Abundance")

# Check our mean-variance relationship
meanvar.plot(mvab_all)

plot(mvab_all ~ as.factor(all_traits$Urb_Rur),
     cex.axis = 0.8,
     cex = 0.8)
# THIS DOESN'T WORK B/C OF NEGATIVE VALUES

# Let’s now contrast the species composition across urb/rural habitat type to see if the models support our observations.

mod1 <- manylm(mvab_all ~ Urb_Rur,
              data = all_traits)

# Check our model assumptions
plot(mod1)

# We can test the multivariate hypothesis of whether species composition varied across the habitats by using the anova function. This gives an analysis of deviance table where we use likelihood ratio tests and resampled p values to look for a significant effect of Habitat on the community data.

anova(mod1)

# We can see from this table that there is NOT an effect of Urban vs. rural habitat, meaning that the overall phenotype does not differ between the urban/rural classification of population they were sourced from.
# 
# To examine this further, and see which traits are more likely to diverge re: habitat type, we can run univariate tests for each species separately.
# 
# This is done by using the p.uni="adjusted" argument in the anova function. The “adjusted” part of the argument refers to the resampling method used to compute the p values, taking into account the correlation between the response variables. This correlation is often found in ecological systems where different species will interact with each other, competing with or facilitating each others’ resource use.

anova_blup <- anova(mod1, p.uni = "adjusted") %T>%
  print()

# after adjusting for multiple testing, there are still no effects of habitat on any specific trait.


# use city_dist as habitat descriptor
anova_blup2 <- manylm(mvab_all ~ City_dist,
               data = all_traits) %>%
  anova() %T>%
  print()

# Still no effect of urbanization on herbivore abundance.
```


### Urb_score
```{r}

all_traits_u %<>%
  na.omit()  # removing rows w/NAs

# Use the just the trait data (in columns 5 to 11) and convert it to an mvabund object format used by the mvabund package.
mvab_all_u <- mvabund(all_traits_u[, c(2, 6:35)]) 

# look at the spread of our data
boxplot(all_traits_u[, c(2, 6:35)],
        horizontal = TRUE,
        las = 2,
        main = "Abundance")

meanvar.plot(mvab_all_u)

plot(mvab_all_u ~ as.factor(all_traits_u$Urb_Rur),
     cex.axis = 0.8,
     cex = 0.8)
# THIS DOESN'T WORK B/C OF NEGATIVE VALUES


mod1_u <- manylm(mvab_all_u ~ Urb_Rur,
               data = all_traits_u)

# Check our model assumptions
plot(mod1_u)

# anova
anova(mod1_u)

# We can see from this table that there is NOT an effect of Urban vs. rural habitat, meaning that the overall phenotype does not differ between the urban/rural classification of population they were sourced from.
# 
# To examine this further, and see which traits are more likely to diverge re: habitat type, we can run univariate tests for each species separately.
# 
# This is done by using the p.uni="adjusted" argument in the anova function. The “adjusted” part of the argument refers to the resampling method used to compute the p values, taking into account the correlation between the response variables. This correlation is often found in ecological systems where different species will interact with each other, competing with or facilitating each others’ resource use.

anova_blup_u <- anova(mod1_u,
                      p.uni = "adjusted") %T>%
  print()

# after adjusting for multiple testing, there are still no effects of habitat on any specific trait.


# use urb_score as habitat descriptor
anova_blup2_u <- manylm(mvab_all_u ~ Urb_score,
               data = all_traits_u) %>%
  anova() %T>%
  print()

# Still no effect of urbanization on traits.
```


### Export
#### City_dist models
```{r}
tab1 <- anova_blup_table(anova_blup) %>%
  dplyr::mutate("Urbanization" = ifelse(row_number() == 2,
                           "Urban/Rural (Distance)",
                           "Intercept")) %>%
    dplyr::filter(Urbanization != "Intercept")

tab2 <- anova_blup_table(anova_blup2) %>%
    dplyr::mutate("Urbanization" = ifelse(row_number() == 2,
                           "Distance to City Center",
                           "Intercept")) %>%
    dplyr::filter(Urbanization != "Intercept")


city_tables <- rbind(tab1, tab2) %>%
  flextable() %>%
  hline(i = 2 ) %>%
  autofit() 

```

#### Urbanization score models
```{r}

tab1u <- anova_blup_table(anova_blup_u) %>%
  dplyr::mutate("Urbanization" = ifelse(row_number() == 2,
                           "Urban/Rural (Urb. Score)",
                           "Intercept")) %>%
    dplyr::filter(Urbanization != "Intercept")

tab2u <- anova_blup_table(anova_blup2_u) %>%
    dplyr::mutate("Urbanization" = ifelse(row_number() == 2,
                           "Urbanization Score",
                           "Intercept")) %>%
    dplyr::filter(Urbanization != "Intercept")


urb_sc_tables <- rbind(tab1u, tab2u) %>%
  flextable() %>%
  hline(i = 2 ) %>%
  autofit() 

```

### Export all anovas in one table
```{r}
word_export <- read_docx()
  
  body_add_par(word_export, value = "Urbanization = Distance to City Center", style = "heading 1")
  body_add_flextable(word_export, city_tables)
  
  body_add_par(word_export, value = "")
  body_add_par(word_export, value = "")
  
    body_add_par(word_export, value = "Urbanization = Urbanization Score", style = "heading 1")
  body_add_flextable(word_export, urb_sc_tables)

  print(word_export, here::here("./Figures_Tables/mvabund/mvabund_anovas_allyears_Q1.docx"))
```


# Q2
## Create BLUP vectors for each trait
### Defense
#### City_dist
```{r}
# Create BLUP dfs for each trait
latex_BLUP <- create_BLUP(latex_mods_best_c[[2]]) %>%
  dplyr::rename(latex = 2)

herb_e_bin_BLUP <- create_BLUP(herb_e_bin_mods_best_c[[2]]) %>%
  dplyr::rename(herb_e_bin = 2)

herb_e_quant_BLUP <- create_BLUP(herb_e_quant_mods_best_c[[2]]) %>%
  dplyr::rename(herb_e_quant = 2)

herb_l_bin_BLUP <- create_BLUP(herb_l_bin_mods_best_c[[2]]) %>%
  dplyr::rename(herb_l_bin = 2)

herb_l_quant_BLUP <- create_BLUP(herb_l_quant_mods_best_c[[2]]) %>%
  dplyr::rename(herb_l_quant = 2)

weev_bin_BLUP <- create_BLUP(weev_bin_mods_best_c[[2]]) %>%
  dplyr::rename(weev_mods_best_c_bin = 2)

weev_quant_BLUP <- create_BLUP(weev_quant_mods_best_c[[2]]) %>%
  dplyr::rename(weev_quant_mods_best_c = 2)


```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
latex_BLUP_u <- create_BLUP(latex_mods_best_u[[2]]) %>%
  dplyr::rename(latex = 2)

herb_e_bin_BLUP_u <- create_BLUP(herb_e_bin_mods_best_u[[2]]) %>%
  dplyr::rename(herb_e_bin = 2)

herb_e_quant_BLUP_u <- create_BLUP(herb_e_quant_mods_best_u[[2]]) %>%
  dplyr::rename(herb_e_quant = 2)

herb_l_bin_BLUP_u <- create_BLUP(herb_l_bin_mods_best_u[[2]]) %>%
  dplyr::rename(herb_l_bin = 2)

herb_l_quant_BLUP_u <- create_BLUP(herb_l_quant_mods_best_u[[2]]) %>%
  dplyr::rename(herb_l_quant = 2)

weev_bin_BLUP_u <- create_BLUP(weev_bin_mods_best_u[[2]]) %>%
  dplyr::rename(weev_mods_best_u_bin = 2)

weev_quant_BLUP_u <- create_BLUP(weev_quant_mods_best_u[[2]]) %>%
  dplyr::rename(weev_quant_mods_best_u = 2)


```


### Growth
#### City_dist
```{r}
# Create BLUP dfs for each trait
ldmc_BLUP <- create_BLUP(ldmc_mods_best_c[[2]]) %>%
  dplyr::rename(ldmc = 2)

sla_BLUP <- create_BLUP(sla_mods_best_c[[2]]) %>%
  dplyr::rename(sla = 2)

heights_early_BLUP <- create_BLUP(heights_early_mods_best_c[[2]]) %>%
  dplyr::rename(heights_early = 2)

heights_late_BLUP <- create_BLUP(heights_late_mods_best_c[[2]]) %>%
  dplyr::rename(heights_late = 2)

rgr_BLUP <- create_BLUP(rgr_mods_best_c[[2]]) %>%
  dplyr::rename(rgr = 2)

ramets_early_BLUP <- create_BLUP(ramets_early_mods_best_c[[2]]) %>%
  dplyr::rename(ramets_early = 2)

ramets_late_BLUP <- create_BLUP(ramets_late_mods_best_c[[2]]) %>%
  dplyr::rename(ramets_late = 2)

mortality_BLUP <- create_BLUP(mortality_mods_best_c[[2]]) %>%
  dplyr::rename(mortality = 2)
```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
ldmc_BLUP_u <- create_BLUP(ldmc_mods_best_u[[2]]) %>%
  dplyr::rename(ldmc = 2)

sla_BLUP_u <- create_BLUP(sla_mods_best_u[[2]]) %>%
  dplyr::rename(sla = 2)

heights_early_BLUP_u <- create_BLUP(heights_early_mods_best_u[[2]]) %>%
  dplyr::rename(heights_early = 2)

heights_late_BLUP_u <- create_BLUP(heights_late_mods_best_u[[2]]) %>%
  dplyr::rename(heights_late = 2)

rgr_BLUP_u <- create_BLUP(rgr_mods_best_u[[2]]) %>%
  dplyr::rename(rgr = 2)

ramets_early_BLUP_u <- create_BLUP(ramets_early_mods_best_u[[2]]) %>%
  dplyr::rename(ramets_early = 2)

ramets_late_BLUP_u <- create_BLUP(ramets_late_mods_best_u[[2]]) %>%
  dplyr::rename(ramets_late = 2)

mortality_BLUP_u <- create_BLUP(mortality_mods_best_u[[2]]) %>%
  dplyr::rename(mortality = 2)
```

### Herbivores
#### City_dist
```{r}
# Create BLUP dfs for each trait
monarch_BLUP <- create_BLUP(monarch_mods_best_c[[2]]) %>%
  dplyr::rename(monarch = 2)

asclepiadis_BLUP <- create_BLUP(asclepiadis_mods_best_c[[2]]) %>%
  dplyr::rename(asclepiadis = 2)

clivicollis_BLUP <- create_BLUP(clivicollis_mods_best_c[[2]]) %>%
  dplyr::rename(clivicollis = 2)


```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
monarch_BLUP_u <- create_BLUP(monarch_mods_best_u[[2]]) %>%
  dplyr::rename(monarch = 2)

asclepiadis_BLUP_u <- create_BLUP(asclepiadis_mods_best_u[[2]]) %>%
  dplyr::rename(asclepiadis = 2)

clivicollis_BLUP_u <- create_BLUP(clivicollis_mods_best_u[[2]]) %>%
  dplyr::rename(clivicollis = 2)

```


### Reproductive
#### City_dist
```{r}
# Create BLUP dfs for each trait
flsucc_BLUP <- create_BLUP(flsucc_mods_best_c[[2]]) %>%
  dplyr::rename(flsucc = 2)

flowers_BLUP <- create_BLUP(flowers_mods_best_c[[2]]) %>%
  dplyr::rename(flowers = 2)

flsize_BLUP <- create_BLUP(flsize_mods_best_c[[2]]) %>%
  dplyr::rename(flsize = 2)

fltime_BLUP <- create_BLUP(fltime_mods_best_c[[2]]) %>%
  dplyr::rename(fltime = 2)

flstart_BLUP <- create_BLUP(flstart_mods_best_c[[2]]) %>%
  dplyr::rename(flstart = 2)

pods_BLUP <- create_BLUP(pods_mods_best_c[[2]]) %>%
  dplyr::rename(pods = 2)

peduncles_BLUP <- create_BLUP(peduncles_mods_best_c[[2]]) %>%
  dplyr::rename(peduncles = 2)

poll_BLUP <- create_BLUP(poll_mods_best_c[[2]]) %>%
  dplyr::rename(poll = 2)
```

#### Urb_score
```{r}
# Create BLUP dfs for each trait
flsucc_BLUP_u <- create_BLUP(flsucc_mods_best_u[[2]]) %>%
  dplyr::rename(flsucc = 2)

flowers_BLUP_u <- create_BLUP(flowers_mods_best_u[[2]]) %>%
  dplyr::rename(flowers = 2)

flsize_BLUP_u <- create_BLUP(flsize_mods_best_u[[2]]) %>%
  dplyr::rename(flsize = 2)

fltime_BLUP_u <- create_BLUP(fltime_mods_best_u[[2]]) %>%
  dplyr::rename(fltime = 2)

flstart_BLUP_u <- create_BLUP(flstart_mods_best_u[[2]]) %>%
  dplyr::rename(flstart = 2)

pods_BLUP_u <- create_BLUP(pods_mods_best_u[[2]]) %>%
  dplyr::rename(pods = 2)

peduncles_BLUP_u <- create_BLUP(peduncles_mods_best_u[[2]]) %>%
  dplyr::rename(peduncles = 2)

poll_BLUP_u <- create_BLUP(poll_mods_best_u[[2]]) %>%
  dplyr::rename(poll = 2)
```

### Cardenolides
Not including these because such small sample size for Q2
### Merge into single df
#### City_dist
```{r}
all_traits <- purrr::reduce(
  list(
    # defense traits
    latex_BLUP        ,
    herb_e_bin_BLUP   ,
    herb_e_quant_BLUP ,
    herb_l_bin_BLUP   ,
    herb_l_quant_BLUP ,
    weev_bin_BLUP     ,
    weev_quant_BLUP   ,

     # growth traits
    ldmc_BLUP         ,
    sla_BLUP          ,
    heights_early_BLUP,
    heights_late_BLUP ,
    rgr_BLUP          ,
    ramets_early_BLUP ,
    ramets_late_BLUP  ,
    mortality_BLUP    ,
    
    # reproductive traits                  
     flsucc_BLUP,    
     flowers_BLUP,   
     flsize_BLUP,    
     fltime_BLUP,    
     flstart_BLUP,   
     pods_BLUP,      
     peduncles_BLUP, 
     poll_BLUP,
    
    # herbivores
    monarch_BLUP,
    asclepiadis_BLUP,
    clivicollis_BLUP
                      ),
              dplyr::left_join,
              by = c('Population',
                     'Transect_ID',
                     'City_dist',
                     'Urb_score')) %>%

# add new col converting transect into urb/rural classes
  dplyr::mutate(Urb_Rur = case_when(
    Transect_ID == "Rural" ~ "Rural",
    TRUE ~ "Urban"
  ))
```

#### Urb_score
```{r}
all_traits_u <- purrr::reduce(
  list(
    # defense traits
    latex_BLUP_u        ,
    herb_e_bin_BLUP_u   ,
    herb_e_quant_BLUP_u ,
    herb_l_bin_BLUP_u   ,
    herb_l_quant_BLUP_u ,
    weev_bin_BLUP_u     ,
    weev_quant_BLUP_u   ,

     # growth traits
    ldmc_BLUP_u         ,
    sla_BLUP_u          ,
    heights_early_BLUP_u,
    heights_late_BLUP_u ,
    rgr_BLUP_u          ,
    ramets_early_BLUP_u ,
    ramets_late_BLUP_u  ,
    mortality_BLUP_u    ,
    
    # reproductive traits                  
     flsucc_BLUP_u,    
     flowers_BLUP_u,   
     flsize_BLUP_u,    
     fltime_BLUP_u,    
     flstart_BLUP_u,   
     pods_BLUP_u,      
     peduncles_BLUP_u, 
     poll_BLUP_u,
    

    # herbivores
    monarch_BLUP_u,
    asclepiadis_BLUP_u,
    clivicollis_BLUP_u
                      ),
              dplyr::left_join,
              by = c('Population',
                     'Transect_ID',
                     'City_dist',
                     'Urb_score')) %>%

# add new col converting transect into urb/rural classes
  dplyr::mutate(Urb_Rur = case_when(
    Transect_ID == "Rural" ~ "Rural",
    TRUE ~ "Urban"
  ))
```

## Use mvabund with gaussian family
### City_dist
```{r}
# Use the just the trait data (in columns 5 to 11) and convert it to an mvabund object format used by the mvabund package.

all_traits %<>%
  dplyr::filter(Transect_ID != "Rural") %<>% # remove rural pops
  na.omit()  # removing rows w/NAs

mvab_all <- mvabund(all_traits[,c(2, 6:30)]) 

# look at the spread of our data
boxplot(all_traits[, c(2, 6:30)],
        horizontal = TRUE,
        las = 2,
        main = "Abundance")

meanvar.plot(mvab_all)

plot(mvab_all ~ as.factor(all_traits$Urb_Rur),
     cex.axis = 0.8,
     cex = 0.8)
# THIS DOESN'T WORK B/C OF NEGATIVE VALUES

mod1 <- manylm(mvab_all ~ City_dist*Transect_ID,
              data = all_traits)


plot(mod1)

anova(mod1)

anova_blup <- anova(mod1, p.uni = "adjusted") %T>%
  print()
```


### Urb_score
```{r}

all_traits_u %<>%
  dplyr::filter(Transect_ID != "Rural") %<>% # remove rural pops
  na.omit()  # removing rows w/NAs

# Use the just the trait data (in columns 5 to 11) and convert it to an mvabund object format used by the mvabund package.
mvab_all_u <- mvabund(all_traits_u[, c(2, 6:30)]) 

# look at the spread of our data
boxplot(all_traits_u[, c(2, 6:30)],
        horizontal = TRUE,
        las = 2,
        main = "Abundance")


meanvar.plot(mvab_all_u)


plot(mvab_all_u ~ as.factor(all_traits_u$Urb_Rur),
     cex.axis = 0.8,
     cex = 0.8)
# THIS DOESN'T WORK B/C OF NEGATIVE VALUES


mod1_u <- manylm(mvab_all_u ~ Urb_score*Transect_ID,
              data = all_traits_u)


plot(mod1_u)

anova(mod1_u)

anova_blup_u <- anova(mod1_u, p.uni = "adjusted") %T>%
  print()
```

### Export
#### City_dist models
```{r}
tab2 <- anova_blup_table(anova_blup) %>%
  dplyr::filter(Urbanization != "(Intercept)") %>%
    dplyr::mutate(Urbanization = case_when(
    str_detect(Urbanization, ":")~
      "D x S",
    str_detect(Urbanization, "City_dist")~
      "Distance to City Center",
    str_detect(Urbanization, "Transect_ID")~
      "Subtransect"))

city_table <- tab2 %>%
  flextable() %>%
  autofit() 

```

#### Urbanization score models
```{r}

tab2u <- anova_blup_table(anova_blup_u) %>%
  dplyr::filter(Urbanization != "(Intercept)") %>%
    dplyr::mutate(Urbanization = case_when(
    str_detect(Urbanization, ":")~
      "U x S",
    str_detect(Urbanization, "Urb_score")~
      "Urbanization Score",
    str_detect(Urbanization, "Transect_ID")~
      "Subtransect"))

urb_sc_table <- tab2u %>%
  flextable() %>%
  autofit() 

```

### Export all anovas in one table
```{r}
word_export <- read_docx()
  
  body_add_par(word_export, value = "Urbanization = Distance to City Center", style = "heading 1")
  body_add_flextable(word_export, city_table)
  
  body_add_par(word_export, value = "")
  body_add_par(word_export, value = "")
  
    body_add_par(word_export, value = "Urbanization = Urbanization Score", style = "heading 1")
  body_add_flextable(word_export, urb_sc_table)

  print(word_export, here::here("./Figures_Tables/mvabund/mvabund_anovas_allyears_Q2.docx"))
```

