# Set up notebook
## Load libraries & functions
```{r}
source("libraries.R")
source("functions.R")
```

## Import representative figures
NOTE: specific chunks of code from the commented-out Rmds should be run manually. Otherwise, this takes a very long time since each Figures_x.Rmd file has to run the same Model_diagnostics_1yr_mods.Rmd listed below.

1. Run the trait-specific section of the "Create ggpredict objects" chunk
2. Run the trait-specific section of the "Create regression plots" chunk 
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_1yr_mods.Rmd", quiet=TRUE))

# source(knitr::purl("scripts/Create_regression_figs/1yr_mods/Figures_growth.Rmd", quiet=TRUE))
# 
# source(knitr::purl("scripts/Create_regression_figs/1yr_mods/Figures_defense.Rmd", quiet=TRUE))
# 
# source(knitr::purl("scripts/Create_regression_figs/1yr_mods/Figures_Reproductive.Rmd", quiet=TRUE))
# 
# source(knitr::purl("scripts/Create_regression_figs/1yr_mods/Figures_herbivores_2021.Rmd", quiet=TRUE))
```

# Combine plots into one figure
## Gradient / City_dist
### Add points (family means)
```{r}
# Defense
points_Q1.citydist_weev_bin <- ggpred_Q1.citydist_weev_bin +
  geom_point(data = weevil %>%
               dplyr::filter(Year == 2021) %>%
               dplyr::group_by(Population, Family) %>%
               dplyr::summarise(Scar_binary  = mean(Scar_binary,
                                                na.rm = T),
                                City_dist = first(City_dist)),
             aes(x = City_dist,
                 y = Scar_binary),
    color = "#66a182") +
  ylim(0, NA)

# Reproduction
points_Q1.citydist_firstpods <- ggpred_Q1.citydist_firstpods +
  geom_point(data = flowering %>%
               dplyr::filter(Year == 2022) %>%
               dplyr::group_by(Population, Family) %>%
               dplyr::summarise(foll_sum = mean(first_foll_minus200,
                                                na.rm = T),
                                City_dist = first(City_dist)),
             aes(x = City_dist,
                 y = foll_sum),
    color = "#66a182") +
  ylim(0, NA)

# Herbivores
points_Q1.citydist_asclepiadis <- ggpred_Q1.citydist_asclepiadis +
  geom_point(data = herbivores %>%
               dplyr::filter(Year == 2021) %>%
               dplyr::group_by(Population, Family) %>%
               dplyr::summarise(Liriomyza_asclepiadis = mean(Liriomyza_asclepiadis,
                                                na.rm = T),
                                City_dist = first(City_dist)),
             aes(x = City_dist,
                 y = Liriomyza_asclepiadis),
    color = "#66a182") +
  ylim(-1, NA)

# Growth
points_Q1.citydist_height_e <- ggpred_Q1.citydist_height_e +
  geom_point(data = heights %>%
               dplyr::filter(Year == 2021) %>%
               dplyr::group_by(Population, Family) %>%
               dplyr::summarise(Total_Height_early = mean(Total_Height_early,
                                                na.rm = T),
                                City_dist = first(City_dist)) %>%
               dplyr::mutate(height_cubert = Total_Height_early^(1/3)),
             aes(x = City_dist,
                 y = height_cubert),
    color = "#66a182") +
  ylim(0, NA)

```

### Arrange, export
```{r}
ggarrange(
  addborder(points_Q1.citydist_weev_bin, "defense"),
  addborder(points_Q1.citydist_firstpods, "reproduction"),
  addborder(points_Q1.citydist_asclepiadis, "herbivores"),
  addborder(points_Q1.citydist_height_e, "growth") +
            font("x.text"),
          ncol = 2,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Figures_Tables/Regressions/1yr_mods/Q1_grad_citydist_representative_panels.pdf"),
             width = 10, height = 8)
```


## Urb Subtransects / City_dist
### Add points (family means)
```{r}
# Defense
points_Q2.citydist_weev_bin <- ggpred_Q2.citydist_weev_bin +
  geom_point(data = weevil %>%
               dplyr::filter(Year == 2021) %>%
               dplyr::filter(Transect_ID != "Rural") %>%
               dplyr::group_by(Population, Family) %>%
               dplyr::summarise(Scar_binary = mean(Scar_binary,
                                                na.rm = T),
                                City_dist = first(City_dist),
                                Transect_ID = first(Transect_ID)),
             aes(x = City_dist,
                 y = Scar_binary,
                 color = Transect_ID)) +
  scale_y_continuous(limits = c(0, 1.2),
                     breaks = c(0, 0.25, 0.5, 0.75, 1)) +
    scale_colour_brewer(labels = c("Corridor",
                                 "Non-Corridor"),
                      palette = "Set2")

# Reproduction
points_Q2.citydist_firstpods <- ggpred_Q2.citydist_firstpods +
  geom_point(data = flowering %>%
               dplyr::filter(Year == 2022) %>%
               dplyr::filter(Transect_ID != "Rural") %>%
               dplyr::group_by(Population, Family) %>%
               dplyr::summarise(foll_sum = mean(first_foll_minus200,
                                                na.rm = T),
                                City_dist = first(City_dist),
                                Transect_ID = first(Transect_ID)),
             aes(x = City_dist,
                 y = foll_sum,
                 color = Transect_ID)) +
  ylim(0, 40) +
    scale_colour_brewer(labels = c("Corridor",
                                 "Non-Corridor"),
                      palette = "Set2")

# Herbivores
points_Q2.citydist_asclepiadis <- ggpred_Q2.citydist_asclepiadis +
  geom_point(data = herbivores %>%
               dplyr::filter(Year == 2021) %>%
               dplyr::filter(Transect_ID != "Rural") %>%
               dplyr::group_by(Population, Family) %>%
               dplyr::summarise(Liriomyza_asclepiadis = mean(Liriomyza_asclepiadis,
                                                na.rm = T),
                                City_dist = first(City_dist),
                                Transect_ID = first(Transect_ID)),
             aes(x = City_dist,
                 y = Liriomyza_asclepiadis,
                 color = Transect_ID)) +
  ylim(0, 7) +
    scale_colour_brewer(labels = c("Corridor",
                                 "Non-Corridor"),
                      palette = "Set2")

# Growth
points_Q2.citydist_height_e <- ggpred_Q2.citydist_height_e +
  geom_point(data = heights %>%
               dplyr::filter(Year == 2021) %>%
               dplyr::filter(Transect_ID != "Rural") %>%
               dplyr::group_by(Population, Family) %>%
               dplyr::summarise(Total_Height_early = mean(Total_Height_early,
                                                na.rm = T),
                                City_dist = first(City_dist),
                                Transect_ID = first(Transect_ID)) %>%
             dplyr::mutate(height_cubert = Total_Height_early^(1/3)),
             aes(x = City_dist,
                 y = height_cubert,
                 color = Transect_ID)) +
  ylim(0, 7) +
    scale_colour_brewer(labels = c("Corridor",
                                 "Non-Corridor"),
                      palette = "Set2")

```


### Arrange, export
```{r}
ggarrange(
  addborder(points_Q2.citydist_weev_bin, "defense"),
  addborder(points_Q2.citydist_firstpods, "reproduction"),
  addborder(points_Q2.citydist_asclepiadis, "herbivores"),
  addborder(points_Q2.citydist_height_e, "growth") +
            font("x.text"),
          ncol = 2,
          nrow = 2,
          align = "hv",
          labels = list("A", "B", "C", "D"),
          font.label = (size =16),
          common.legend = T,
          legend = "top") %T>%
  plot

dev.copy2pdf(file = here::here("./Figures_Tables/Regressions/1yr_mods/Q2_urbsubs_citydist_representative_panels.pdf"),
             width = 10, height = 8)
```