# Load libraries & functions
```{r}
source("libraries.R")
source("functions.R")
```

# Import data
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_1yr_mods.Rmd", quiet=TRUE))

```

# Create tables with ANOVA results from all one-year models (lmers)
## Q1
### City_dist
#### Create 1-yr ANOVA table
```{r}
# perform tidy_anova on all list items (i.e., models)
all_1yr_mods %>% 
  lapply(., tidy_anova) %>%

# merge all items
  reduce(full_join, all = T) %>%

# make flextable
  dplyr::rename(Variable = 1) %>%
  dplyr::select(-Sites) %>%
  dplyr::mutate(Variable = case_when(
    
    # Defense
    str_detect(Variable, "Latex")~
      "Latex exudation",
    str_detect(Variable, "Herbivory_mean_early_binary") ~
      "Herbivory before flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_early)") ~
                 "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Herbivory_mean_late_binary")~
      "Herbivory after flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_late)")~
      "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Scar_binary")~
      "Weevil damage (binary)",
    str_detect(Variable, "Scar_length_cm")~
      "Weevil damage (quantitative)",
    
    # Reproduction
    str_detect(Variable, "Flowered")~
      "Flowering success",
    str_detect(Variable, "mean_flower_c")~
      "Flowers per Inflorescence",
    str_detect(Variable, "Overall")~
      "Flower size",
    str_detect(Variable, "flowering_time")~
      "Flowering duration",
    str_detect(Variable, "Julian_oldest_inflor")~
      "Date of first flower",
    str_detect(Variable, "Pods")~
      "Follicles",
    str_detect(Variable, "Julian_first")~
      "Date of first follicle",
    str_detect(Variable, "Peduncles")~
      "Inflorescences",
    
    # Herbivores
    str_detect(Variable, "Monarch")~
      "Danaus plexippus abundance",
    str_detect(Variable, "asclep")~
      "Liriomyza asclepiadis abundance",
    str_detect(Variable, "clivi")~
      "Labidomera clivicollis abundance",
    
    # Growth
    str_detect(Variable, "LDMC")~
      "LDMC",
    str_detect(Variable, "SLA")~
      "SLA",
    str_detect(Variable, "Total_Height_early")~
      "Height before flowering",
    str_detect(Variable, "Total_Height_late")~
      "Height after flowering",
    str_detect(Variable, "rel_gr")~
      "Relative growth rate",
    str_detect(Variable, "Ramets_early")~
      "Ramets before flowering",
    str_detect(Variable, "Ramets_late")~
      "Ramets after flowering",
    str_detect(Variable, "Dead")~
      "Mortality"
    
    
    )) %>%
  flextable() %>%
  theme_box() %>%
  merge_v(j = ~Variable) %>% 
  align(j = 3:4, align = "center", part = "all") %>%
  hline(j = ~Variable, border = NULL, part = "body") %>%
  flextable::compose(i = 1, j = 3, part = "header",
                     value = as_paragraph("χ", as_sup("2"))) %>%
  bold(i = ~ p <= 0.05, j = 4) %>%
  padding(padding = 3) %>%
  autofit() %T>%
  
# Export
  flextable::save_as_docx(.,
                          path = here::here("./Figures_Tables/ANOVA_1yr/ANOVA_1yr_Citydist.docx"))
```

### Urb_score
#### Create 1-yr ANOVA table
```{r}
all_1yr_mods.u %>% 
  lapply(., tidy_anova) %>%

  reduce(full_join, all = T) %>%

  dplyr::rename(Variable = 1) %>%
  dplyr::select(-Sites) %>%
  dplyr::mutate(Variable = case_when(
    
    # Defense
    str_detect(Variable, "Latex")~
      "Latex exudation",
    str_detect(Variable, "Herbivory_mean_early_binary") ~
      "Herbivory before flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_early)") ~
                 "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Herbivory_mean_late_binary")~
      "Herbivory after flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_late)")~
      "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Scar_binary")~
      "Weevil damage (binary)",
    str_detect(Variable, "Scar_length_cm")~
      "Weevil damage (quantitative)",
    
    # Reproduction
    str_detect(Variable, "Flowered")~
      "Flowering success",
    str_detect(Variable, "mean_flower_c")~
      "Flowers per Inflorescence",
    str_detect(Variable, "Overall")~
      "Flower size",
    str_detect(Variable, "flowering_time")~
      "Flowering duration",
    str_detect(Variable, "Julian_oldest_inflor")~
      "Date of first flower",
    str_detect(Variable, "Pods")~
      "Follicles",
    str_detect(Variable, "Julian_first")~
      "Date of first follicle",
    str_detect(Variable, "Peduncles")~
      "Inflorescences",
    
    # Herbivores
    str_detect(Variable, "Monarch")~
      "Danaus plexippus abundance",
    str_detect(Variable, "asclep")~
      "Liriomyza asclepiadis abundance",
    str_detect(Variable, "clivi")~
      "Labidomera clivicollis abundance",
    
    # Growth
    str_detect(Variable, "LDMC")~
      "LDMC",
    str_detect(Variable, "SLA")~
      "SLA",
    str_detect(Variable, "Total_Height_early")~
      "Height before flowering",
    str_detect(Variable, "Total_Height_late")~
      "Height after flowering",
    str_detect(Variable, "rel_gr")~
      "Relative growth rate",
    str_detect(Variable, "Ramets_early")~
      "Ramets before flowering",
    str_detect(Variable, "Ramets_late")~
      "Ramets after flowering",
    str_detect(Variable, "Dead")~
      "Mortality"
    
    
    )) %>%
  flextable() %>%
  theme_box() %>%
  merge_v(j = ~Variable) %>% 
  align(j = 3:4, align = "center", part = "all") %>%
  hline(j = ~Variable, border = NULL, part = "body") %>%
  flextable::compose(i = 1, j = 3, part = "header",
                     value = as_paragraph("χ", as_sup("2"))) %>%
  bold(i = ~ p <= 0.05, j = 4) %>%
  padding(padding = 3) %>%
  autofit() %T>%
  
  flextable::save_as_docx(.,
                          path = here::here("./Figures_Tables/ANOVA_1yr/ANOVA_1yr_Urbscore.docx"))
```

## Q2
### City_dist
#### Create 1-yr ANOVA table
```{r}
# STEP 3: perform tidy_anova on all list items (i.e., models)
all_1yr_mods_tr %>% 
  lapply(., tidy_anova) %>%

# STEP 4: merge all items
  reduce(full_join, all = T) %>%

# STEP 5: make flextable
  dplyr::rename(Variable = 1) %>%
  dplyr::select(-Sites) %>% 
  dplyr::mutate(Variable = case_when(
    
    # Defense
    str_detect(Variable, "Latex")~
      "Latex exudation",
    str_detect(Variable, "Herbivory_mean_early_binary") ~
      "Herbivory before flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_early)") ~
                 "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Herbivory_mean_late_binary")~
      "Herbivory after flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_late)")~
      "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Scar_binary")~
      "Weevil damage (binary)",
    str_detect(Variable, "Scar_length_cm")~
      "Weevil damage (quantitative)",
    
    # Reproduction
    str_detect(Variable, "Flowered")~
      "Flowering success",
    str_detect(Variable, "mean_flower_c")~
      "Flowers per Inflorescence",
    str_detect(Variable, "Overall")~
      "Flower size",
    str_detect(Variable, "flowering_time")~
      "Flowering duration",
    str_detect(Variable, "Julian_oldest_inflor")~
      "Date of first flower",
    str_detect(Variable, "Pods")~
      "Follicles",
    str_detect(Variable, "Julian_first")~
      "Date of first follicle",
    str_detect(Variable, "Peduncles")~
      "Inflorescences",
    
    # Herbivores
    str_detect(Variable, "Monarch")~
      "Danaus plexippus abundance",
    str_detect(Variable, "asclep")~
      "Liriomyza asclepiadis abundance",
    str_detect(Variable, "clivi")~
      "Labidomera clivicollis abundance",
    
    # Growth
    str_detect(Variable, "LDMC")~
      "LDMC",
    str_detect(Variable, "SLA")~
      "SLA",
    str_detect(Variable, "Total_Height_early")~
      "Height before flowering",
    str_detect(Variable, "Total_Height_late")~
      "Height after flowering",
    str_detect(Variable, "rel_gr")~
      "Relative growth rate",
    str_detect(Variable, "Ramets_early")~
      "Ramets before flowering",
    str_detect(Variable, "Ramets_late")~
      "Ramets after flowering",
    str_detect(Variable, "Dead")~
      "Mortality"
    
    
    )) %>%
  flextable() %>%
  theme_box() %>%
  merge_v(j = ~Variable) %>% 
  align(j = 3:4, align = "center", part = "all") %>%
  hline(j = ~Variable, border = NULL, part = "body") %>%
  flextable::compose(i = 1, j = 3, part = "header",
                     value = as_paragraph("χ", as_sup("2"))) %>%
  bold(i = ~ p <= 0.05, j = 4) %>%
  padding(padding = 3) %>%
  autofit() %T>%
  
# STEP 6: Export
  flextable::save_as_docx(.,
                          path = here::here("./Figures_Tables/ANOVA_1yr/ANOVA_1yr_Citydist_transects.docx"))
```

### Urb_score
#### Create 1-yr ANOVA table
```{r}
# STEP 3: perform tidy_anova on all list items (i.e., models)
all_1yr_mods.u_tr %>% 
  lapply(., tidy_anova) %>%

# STEP 4: merge all items
  reduce(full_join, all = T) %>%

# STEP 5: make flextable
  dplyr::rename(Variable = 1) %>%
  dplyr::select(-Sites) %>%
  dplyr::mutate(Variable = case_when(
    
    # Defense
    str_detect(Variable, "Latex")~
      "Latex exudation",
    str_detect(Variable, "Herbivory_mean_early_binary") ~
      "Herbivory before flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_early)") ~
                 "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Herbivory_mean_late_binary")~
      "Herbivory after flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_late)")~
      "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Scar_binary")~
      "Weevil damage (binary)",
    str_detect(Variable, "Scar_length_cm")~
      "Weevil damage (quantitative)",
    
    # Reproduction
    str_detect(Variable, "Flowered")~
      "Flowering success",
    str_detect(Variable, "mean_flower_c")~
      "Flowers per Inflorescence",
    str_detect(Variable, "Overall")~
      "Flower size",
    str_detect(Variable, "flowering_time")~
      "Flowering duration",
    str_detect(Variable, "Julian_oldest_inflor")~
      "Date of first flower",
    str_detect(Variable, "Pods")~
      "Follicles",
    str_detect(Variable, "Julian_first")~
      "Date of first follicle",
    str_detect(Variable, "Peduncles")~
      "Inflorescences",
    
    # Herbivores
    str_detect(Variable, "Monarch")~
      "Danaus plexippus abundance",
    str_detect(Variable, "asclep")~
      "Liriomyza asclepiadis abundance",
    str_detect(Variable, "clivi")~
      "Labidomera clivicollis abundance",
    
    # Growth
    str_detect(Variable, "LDMC")~
      "LDMC",
    str_detect(Variable, "SLA")~
      "SLA",
    str_detect(Variable, "Total_Height_early")~
      "Height before flowering",
    str_detect(Variable, "Total_Height_late")~
      "Height after flowering",
    str_detect(Variable, "rel_gr")~
      "Relative growth rate",
    str_detect(Variable, "Ramets_early")~
      "Ramets before flowering",
    str_detect(Variable, "Ramets_late")~
      "Ramets after flowering",
    str_detect(Variable, "Dead")~
      "Mortality"
    
    
    )) %>%
  flextable() %>%
  theme_box() %>%
  merge_v(j = ~Variable) %>% 
  align(j = 3:4, align = "center", part = "all") %>%
  hline(j = ~Variable, border = NULL, part = "body") %>%
  flextable::compose(i = 1, j = 3, part = "header",
                     value = as_paragraph("χ", as_sup("2"))) %>%
  bold(i = ~ p <= 0.05, j = 4) %>%
  padding(padding = 3) %>%
  autofit() %T>%
  
# STEP 6: Export
  flextable::save_as_docx(.,
                          path = here::here("./Figures_Tables/ANOVA_1yr/ANOVA_1yr_Urbscore_transects.docx"))
```


# Create tables with ANOVA results from cardenolide models (lms)
## Q1, City_dist & Urb_score
### Create 1-yr ANOVA table (only 1 year of data anyway)
Not doing this for Q2 since sample size so small
```{r}

# anova on all list items (i.e., models)
flatten(all_card_models) %>% 
  lapply(., tidy_anova_cards) %>%

# merge all items
  reduce(full_join, all = T) %>%

# make flextable
  flextable() %>%
  theme_box() %>%
  merge_v(j = ~Variable) %>% 
  align(j = 3:6, align = "center", part = "all") %>%
  hline(j = ~Variable, border = NULL, part = "body") %>%
  flextable::compose(i = 1, j = 6, part = "header",
                         value = as_paragraph(as_i("p"))) %>%
  bold(i = ~ p <= 0.05, j = 6) %>%
  padding(padding = 3) %>%
  autofit() %T>%
  
# STEP 6: Export
  flextable::save_as_docx(.,
                          path = here::here("./Figures_Tables/ANOVA_1yr/ANOVA_1yr_cardenolides.docx"))
```
