# Set up notebook
## Load libraries and functions
```{r}
source("libraries.R")
source("functions.R")
```

## Import final models
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_Defense.Rmd", quiet=TRUE))
```

# Ranova
The point: to determine if there is much genetic diversity present within populations for natural selection to act on.
- ranova can't handle GLMMTMB functions so I'll use lmer instead
- NOT doing this for cardenolides because samples were pooled by population
## Set seed for random processes (bootstrapping)
```{r}
set.seed(45)
```

## Gradient
### Gaussian models
```{r}
############ MEASURED ONLY IN 2020 #############
################################################

# Latex-----
# fit original model
latex_ranova_mod1 <- lmer(Latex_weight_mg^(1/3) ~
                            Block +
                            (1|Population/Family),
                          data = latex,
                          REML = T)

# check diagnostics and transform if necessary
performance::check_model(latex_ranova_mod1)

# export
ranova_2step(latex_ranova_mod1,
             "Latex",
             "./Figures_Tables/ranova_PVE/Defense/latex.docx")


############ MEASURED IN MULTIPLE YEARS ########
################################################
# Herbivory (before flowering) (quantitative)-------
herbiv_e_quant_ranova_mod1 <- lmer(log(Herbivory_mean_early) ~
                                Block +
                               (1|Population/Family),
                              data = herbivory %>%
                        dplyr::filter(
                          Herbivory_mean_early_binary == 1 &
                            Year == 2020),
                              REML = T)

# check diagnostics and transform if necessary
performance::check_model(herbiv_e_quant_ranova_mod1)

# export
ranova_2step(herbiv_e_quant_ranova_mod1,
             "Herbivory before flowering, quantitative: 2020",
             "./Figures_Tables/ranova_PVE/Defense/herbivory_early_quant_2020.docx")


herbiv_e_quant_ranova_mod2 <- lmer(log(Herbivory_mean_early) ~
                               Block +
                               (1|Population/Family),
                              data = herbivory %>%
                        dplyr::filter(
                          Herbivory_mean_early_binary == 1 &
                            Year == 2021),
                              REML = T)

# check diagnostics and transform if necessary
performance::check_model(herbiv_e_quant_ranova_mod2)

# export
ranova_2step(herbiv_e_quant_ranova_mod2,
             "Herbivory before flowering, quantitative: 2021",
             "./Figures_Tables/ranova_PVE/Defense/herbivory_early_quant_2021.docx")


# Herbivory (after flowering) (quantitative)-------
herbiv_l_quant_ranova_mod1 <- lmer(log(Herbivory_mean_late) ~
                                Block +
                               (1|Population/Family),
                              data = herbivory %>%
                        dplyr::filter(
                          Herbivory_mean_late_binary == 1 &
                            Year == 2020),
                              REML = T)

# check diagnostics and transform if necessary
performance::check_model(herbiv_l_quant_ranova_mod1)

# export
ranova_2step(herbiv_l_quant_ranova_mod1,
             "Herbivory after flowering, quantitative: 2020",
             "./Figures_Tables/ranova_PVE/Defense/herbivory_late_quant_2020.docx")


herbiv_l_quant_ranova_mod2 <- lmer(log(Herbivory_mean_late) ~
                                Block +
                               (1|Population/Family),
                              data = herbivory %>%
                        dplyr::filter(
                          Herbivory_mean_late_binary == 1 &
                            Year == 2021),
                              REML = T)

# check diagnostics and transform if necessary
performance::check_model(herbiv_l_quant_ranova_mod2)

# export
ranova_2step(herbiv_l_quant_ranova_mod2,
             "Herbivory after flowering, quantitative: 2021",
             "./Figures_Tables/ranova_PVE/Defense/herbivory_late_quant_2021.docx")




# Weevil scar length (quantitative)-----
weev_quant_ranova_mod1 <- lmer(log(Scar_length_cm) ~
                                    Block +
                                   (1|Population/Family), 
                              data = weevil %>%
                                dplyr::filter(Scar_length_cm > 0 &
                                                Year == 2020),
                              REML = T)


# check diagnostics and transform if necessary
performance::check_model(weev_quant_ranova_mod1)

# export
ranova_2step(weev_quant_ranova_mod1,
             "Weevil damage, quantitative: 2020",
             "./Figures_Tables/ranova_PVE/Defense/weevil_quant_2020.docx")


weev_quant_ranova_mod2 <- lmer(log(Scar_length_cm) ~
                                    Block +
                                   (1|Population/Family), 
                              data = weevil %>%
                                dplyr::filter(Scar_length_cm > 0 &
                                                Year == 2021),
                              REML = T)


# check diagnostics and transform if necessary
performance::check_model(weev_quant_ranova_mod2)

# export
ranova_2step(weev_quant_ranova_mod2,
             "Weevil damage, quantitative: 2021",
             "./Figures_Tables/ranova_PVE/Defense/weevil_quant_2021.docx")


```

### non-Gaussian models
```{r}
# Herbivory (before flowering) (Binary)-------
# 2020-----
herb_e_bin_ranova1 <- glmer(Herbivory_mean_early_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivory %>%
                               dplyr::filter(Year == 2020),
                            na.action = na.exclude,
                             family = binomial)

# performance::check_model(herb_e_bin_ranova1)

pb_ranova_2step(herb_e_bin_ranova1,
          "Herbivory before flowering, binary: 2020",
          "./Figures_Tables/ranova_PVE/Defense/herb_e_bin_2020.docx")



# 2021-----
herb_e_bin_ranova2 <- glmer(Herbivory_mean_early_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivory %>%
                               dplyr::filter(Year == 2021),
                 na.action = na.exclude,
                             family = binomial)

# performance::check_model(herb_e_bin_ranova2)

pb_ranova_2step(herb_e_bin_ranova2,
          "Herbivory before flowering, binary: 2021",
          "./Figures_Tables/ranova_PVE/Defense/herb_e_bin_2021.docx")


# Herbivory (after flowering) (Binary)-------
# 2020-----
herb_l_bin_ranova1 <- glmer(Herbivory_mean_late_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivory %>%
                               dplyr::filter(Year == 2020),
                            na.action = na.exclude,
                            nAGQ = 0,# won't converge w/o this
                             family = binomial)

# performance::check_model(herb_l_bin_ranova1)

pb_ranova_2step(herb_l_bin_ranova1,
          "Herbivory after flowering, binary: 2020",
          "./Figures_Tables/ranova_PVE/Defense/herb_l_bin_2020.docx")



# 2021-----
herb_l_bin_ranova2 <- glmer(Herbivory_mean_late_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivory %>%
                               dplyr::filter(Year == 2021),
                            nAGQ = 0,# won't converge w/o this
                            na.action = na.exclude,
                             family = binomial)

# performance::check_model(herb_l_bin_ranova2)

pb_ranova_2step(herb_l_bin_ranova2,
          "Herbivory after flowering, binary: 2021",
          "./Figures_Tables/ranova_PVE/Defense/herb_l_bin_2021.docx")



# Weevil scar length (binary)-----
# 2020-----
weev_bin_ranova1 <- glmer(Scar_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = weevil %>%
                               dplyr::filter(Year == 2020),
                            na.action = na.exclude,
                          family = binomial)

# performance::check_model(weev_bin_ranova1)

pb_ranova_2step(weev_bin_ranova1,
          "Weevil Damage, binary: 2020",
          "./Figures_Tables/ranova_PVE/Defense/weevil_bin_2020.docx")


# 2021-----
weev_bin_ranova2 <- glmer(Scar_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = weevil %>%
                               dplyr::filter(Year == 2021),
                          na.action = na.exclude,
                             family = binomial)

# performance::check_model(weev_bin_ranova2)

pb_ranova_2step(weev_bin_ranova2,
          "Weevil Damage, binary: 2021",
          "./Figures_Tables/ranova_PVE/Defense/weevil_bin_2021.docx")
```

## Urban Subtransects
### Gaussian models
```{r}
############ MEASURED ONLY IN 2020 #############
################################################

# Latex-----
latex_ranova_mod1 <- lmer(Latex_weight_mg^(1/3) ~
                            (1|Population/Family) +
                            Block,
                             data = latex %>%
                          dplyr::filter(Transect_ID != "Rural"),
                           REML = T)

# check diagnostics and transform if necessary
performance::check_model(latex_ranova_mod1)

ranova_transect(latex_ranova_mod1,
                "Latex",
                "./Figures_Tables/ranova_PVE/Defense/latex_transects.docx")


############ MEASURED IN MULTIPLE YEARS ########
################################################
# Herbivory (before flowering)- (quantitative)-------

# 2020-----
herb_e_quant_ranova_mod1 <- lmer(log(Herbivory_mean_early) ~
                                   (1|Population/Family) +
                                   Block,
                             data = herbivory %>%
                      dplyr::filter(
                        Herbivory_mean_early_binary == 1 &
                          Transect_ID != "Rural" &
                          Year == 2020),
                           REML = T)

# check diagnostics and transform if necessary
performance::check_model(herb_e_quant_ranova_mod1)

ranova_transect(herb_e_quant_ranova_mod1,
                "Herbivory before flowering, quantitative: 2020",
                "./Figures_Tables/ranova_PVE/Defense/herb_e_quant_transects_2020.docx")

# 2021-----
herb_e_quant_ranova_mod2 <- lmer(log(Herbivory_mean_early) ~
                                   (1|Population/Family) +
                                   Block,
                             data = herbivory %>%
                      dplyr::filter(
                        Herbivory_mean_early_binary == 1 &
                          Transect_ID != "Rural" &
                          Year == 2021),
                           REML = T)

# check diagnostics and transform if necessary
performance::check_model(herb_e_quant_ranova_mod2)

ranova_transect(herb_e_quant_ranova_mod2,
                "Herbivory before flowering, quantitative: 2021",
                "./Figures_Tables/ranova_PVE/Defense/herb_e_quant_transects_2021.docx")


# Herbivory (after flowering) (quantitative)-------
# 2020-----
herb_l_quant_ranova_mod1 <- lmer(log(Herbivory_mean_late) ~
                                   (1|Population/Family) +
                                   Block,
                             data = herbivory %>%
                      dplyr::filter(
                        Herbivory_mean_late_binary == 1 &
                          Transect_ID != "Rural" &
                          Year == 2020),
                           REML = T)

# check diagnostics and transform if necessary
performance::check_model(herb_l_quant_ranova_mod1)

ranova_transect(herb_l_quant_ranova_mod1,
                "Herbivory after flowering, quantitative: 2020",
                "./Figures_Tables/ranova_PVE/Defense/herb_l_quant_transects_2020.docx")

# 2021-----
herb_l_quant_ranova_mod2 <- lmer(log(Herbivory_mean_late) ~
                                   (1|Population/Family) +
                                   Block,
                             data = herbivory %>%
                      dplyr::filter(
                        Herbivory_mean_late_binary == 1 &
                          Transect_ID != "Rural" &
                          Year == 2021),
                           REML = T)

# check diagnostics and transform if necessary
performance::check_model(herb_l_quant_ranova_mod2)

ranova_transect(herb_l_quant_ranova_mod2,
                "Herbivory after flowering, quantitative: 2021",
                "./Figures_Tables/ranova_PVE/Defense/herb_l_quant_transects_2021.docx")



# Weevil scar length (quantitative)-----
# 2020-----
weev_quant_ranova_mod1 <- lmer(log(Scar_length_cm) ~
                                   (1|Population/Family) +
                                   Block,
                             data = weevil %>%
                      dplyr::filter(
                        Scar_length_cm > 0 &
                          Transect_ID != "Rural" &
                          Year == 2020),
                           REML = T)

# check diagnostics and transform if necessary
performance::check_model(weev_quant_ranova_mod1)

ranova_transect(weev_quant_ranova_mod1,
                "Weevil damage, quantitative: 2020",
                "./Figures_Tables/ranova_PVE/Defense/weevil_quant_transects_2020.docx")

# 2021-----
weev_quant_ranova_mod2 <- lmer(log(Scar_length_cm) ~
                                   (1|Population/Family) +
                                   Block,
                             data = weevil %>%
                      dplyr::filter(
                        Scar_length_cm > 0 &
                          Transect_ID != "Rural" &
                          Year == 2021),
                           REML = T)

# check diagnostics and transform if necessary
performance::check_model(weev_quant_ranova_mod2)

ranova_transect(weev_quant_ranova_mod2,
                "Weevil damage, quantitative: 2021",
                "./Figures_Tables/ranova_PVE/Defense/weevil_quant_transects_2021.docx")


```

### non-Gaussian models
```{r}
# Herbivory (before flowering) (binary)-------
# 2020-----
herb_e_bin_ranova1_pb <- glmer(Herbivory_mean_early_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivory %>%
                               dplyr::filter(Transect_ID != "Rural" & 
                                                Year == 2020),
                            na.action = na.exclude,
                             family = binomial)

# performance::check_model(herb_e_bin_ranova1_pb)

pb_ranova_transects(herb_e_bin_ranova1_pb,
          "Herbivory before flowering, binary: 2020",
          "./Figures_Tables/ranova_PVE/Defense/herb_e_bin_2020_transects.docx")


# 2021-----
herb_e_bin_ranova2_pb <- glmer(Herbivory_mean_early_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivory %>%
                               dplyr::filter(Transect_ID != "Rural" & 
                                                Year == 2021),
                            na.action = na.exclude,
                             family = binomial  ,control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5))
                       )

# performance::check_model(herb_e_bin_ranova2_pb)

pb_ranova_transects(herb_e_bin_ranova2_pb,
          "Herbivory before flowering, binary: 2021",
          "./Figures_Tables/ranova_PVE/Defense/herb_e_bin_2021_transects.docx")

# Herbivory (after flowering) (binary)-------
# 2020-----
herb_l_bin_ranova1_pb <- glmer(Herbivory_mean_late_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivory %>%
                               dplyr::filter(Transect_ID != "Rural" & 
                                                Year == 2020),
                            na.action = na.exclude,
                             family = binomial ,control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))

# performance::check_model(herb_l_bin_ranova1_pb)

pb_ranova_transects(herb_l_bin_ranova1_pb,
          "Herbivory after flowering, binary: 2020",
          "./Figures_Tables/ranova_PVE/Defense/herb_l_bin_2020_transects.docx")


# 2021-----
herb_l_bin_ranova2_pb <- glmer(Herbivory_mean_late_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivory %>%
                               dplyr::filter(Transect_ID != "Rural" & 
                                                Year == 2021),
                            na.action = na.exclude,
                            nAGQ = 0, # won't converge w/o this
                       family = binomial)

# performance::check_model(herb_l_bin_ranova2_pb)

pb_ranova_transects(herb_l_bin_ranova2_pb,
          "Herbivory after flowering, binary: 2021",
          "./Figures_Tables/ranova_PVE/Defense/herb_l_bin_2021_transects.docx")

# Weevil scar length (binary)-----
# 2020-----
weev_bin_ranova1_pb <- glmer(Scar_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = weevil %>%
                               dplyr::filter(Transect_ID != "Rural" & 
                                                Year == 2020),
                            na.action = na.exclude,
                             family = binomial,
                            nAGQ = 0
                      )

# performance::check_model(weev_bin_ranova1_pb)

pb_ranova_transects(weev_bin_ranova1_pb,
          "Weevil damage, binary: 2020",
          "./Figures_Tables/ranova_PVE/Defense/weevil_bin_2020_transects.docx")


# 2021-----
weev_bin_ranova2_pb <- glmer(Scar_binary ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = weevil %>%
                               dplyr::filter(Transect_ID != "Rural" & 
                                                Year == 2021),
                            na.action = na.exclude,
                             family = binomial)

# performance::check_model(herb_l_bin_ranova2_pb)

pb_ranova_transects(weev_bin_ranova2_pb,
          "Weevil damage, binary: 2021",
          "./Figures_Tables/ranova_PVE/Defense/weevil_bin_2021_transects.docx")

```

## Recalculate PVE for non-Gaussian models
As far as we know, there isn't a solid way to calculate percent variance explained for variables with a non-Gaussian distribution.
The way that we handled this was to refit our non-Gaussian models (generalized linear mixed models) to general linear mixed models, then extract PVE for the last year of data collection.
These new PVEs will be estimates. This is *not* a perfect solution but it will help us approximate PVE for these variables.
### Q1
```{r}
# main models
herb_e_bin_lmer <- lmer(Herbivory_mean_early_binary ~
                               (1|Block) +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivory %>%
                               dplyr::filter(Year == 2021),
                            na.action = na.exclude)

herb_l_bin_lmer <- lmer(Herbivory_mean_late_binary ~
                               (1|Block) +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivory %>%
                               dplyr::filter(Year == 2021),
                            na.action = na.exclude)

weev_bin_lmer <- lmer(Scar_binary ~
                               (1|Block) +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = weevil %>%
                               dplyr::filter(Year == 2021),
                          na.action = na.exclude)

# get PVE from models
pve_hbfb <- PVE_lm(herb_e_bin_lmer) 
pve_hafb <- PVE_lm(herb_l_bin_lmer)
pve_weevb <- PVE_lm(weev_bin_lmer)

pve_hbfb_city <- PVE_lm(update(herb_e_bin_lmer, .~. + City_dist))
pve_hafb_city <- PVE_lm(update(herb_l_bin_lmer, .~. + City_dist))
pve_weevb_city <- PVE_lm(update(weev_bin_lmer, .~. + City_dist))

pve_hbfb_urbsc <- PVE_lm(update(herb_e_bin_lmer, .~. + Urb_score))
pve_hafb_urbsc <- PVE_lm(update(herb_l_bin_lmer, .~. + Urb_score))
pve_weevb_urbsc <- PVE_lm(update(weev_bin_lmer, .~. + Urb_score))


# make tables
recalc_tab1 <- pve_table_recalc(pve_hbfb, pve_hafb, pve_weevb,
                 "Herbivory before flowering (binary)",
                              "Herbivory after flowering (binary)",
                              "Weevil damage (binary)")

recalc_tab2 <- pve_table_recalc(pve_hbfb_city, pve_hafb_city, pve_weevb_city,
                 "Herbivory before flowering (binary)",
                              "Herbivory after flowering (binary)",
                              "Weevil damage (binary)")

recalc_tab3 <- pve_table_recalc(pve_hbfb_urbsc, pve_hafb_urbsc, pve_weevb_urbsc,
                 "Herbivory before flowering (binary)",
                              "Herbivory after flowering (binary)",
                              "Weevil damage (binary)")

# Export to word
export_recalc(recalc_tab1,
              recalc_tab2,
              recalc_tab3,
              "./Figures_Tables/ranova_PVE/Defense/PVE_nonGaussmods/PVE_nonGaussmods_defense_Q1.docx")

```

### Q2
```{r}
# main models
herb_e_bin_lmer2 <- update(herb_e_bin_lmer,
                             data = herbivory %>%
                               dplyr::filter(Year == 2021 &
                                            Transect_ID != "Rural"))

herb_l_bin_lmer2 <- update(herb_l_bin_lmer,
                             data = herbivory %>%
                               dplyr::filter(Year == 2021 &
                                            Transect_ID != "Rural"))

weev_bin_lmer2 <- update(weev_bin_lmer,
                             data = weevil %>%
                               dplyr::filter(Year == 2021 &
                                            Transect_ID != "Rural"))
# get PVE from models
pve_hbfb2 <- PVE_lm(herb_e_bin_lmer2) 
pve_hafb2 <- PVE_lm(herb_l_bin_lmer2)
pve_weevb2 <- PVE_lm(weev_bin_lmer2)

pve_hbfb_city2 <- PVE_lm(update(herb_e_bin_lmer2, .~. + City_dist*Transect_ID))
pve_hafb_city2 <- PVE_lm(update(herb_l_bin_lmer2, .~. + City_dist*Transect_ID))
pve_weevb_city2 <- PVE_lm(update(weev_bin_lmer2, .~. + City_dist*Transect_ID))

pve_hbfb_urbsc2 <- PVE_lm(update(herb_e_bin_lmer2, .~. + Urb_score*Transect_ID))
pve_hafb_urbsc2 <- PVE_lm(update(herb_l_bin_lmer2, .~. + Urb_score*Transect_ID))
pve_weevb_urbsc2 <- PVE_lm(update(weev_bin_lmer2, .~. + Urb_score*Transect_ID))


# make tables
recalc_tab1_Q2 <- pve_table_recalc(pve_hbfb2, pve_hafb2, pve_weevb2,
                 "Herbivory before flowering (binary)",
                              "Herbivory after flowering (binary)",
                              "Weevil damage (binary)")

recalc_tab2_Q2 <- pve_table_recalc(pve_hbfb_city2, pve_hafb_city2, pve_weevb_city2,
                 "Herbivory before flowering (binary)",
                              "Herbivory after flowering (binary)",
                              "Weevil damage (binary)")

recalc_tab3_Q2 <- pve_table_recalc(pve_hbfb_urbsc2, pve_hafb_urbsc2, pve_weevb_urbsc2,
                 "Herbivory before flowering (binary)",
                              "Herbivory after flowering (binary)",
                              "Weevil damage (binary)")

# Export to word
export_recalc(recalc_tab1_Q2,
              recalc_tab2_Q2,
              recalc_tab3_Q2,
              "./Figures_Tables/ranova_PVE/Defense/PVE_nonGaussmods/PVE_nonGaussmods_defense_Q2.docx")
```
