# Set up notebook
## Load libraries & functions
```{r}
source("libraries.R")
source("functions.R")
```

## Import data
```{r}
herbivores <- read.csv(here::here("./data/Joined_annual_data/herbivores.csv")) %>%
  dplyr::select(., -1) %>%
  dplyr::mutate_at(vars(c("Population",
                          "Family",
                          "Replicate",
                          "Block",
                          "Transect_ID",
                          "Sample",
                          "Patch_ID",
                          "Urb_Rur",
                          "Year",
                          "Surveyor",
                          "Date")),
                   as.character) %>%
    dplyr::mutate_at(vars(c("Population",
                            "Family",
                            "Replicate",
                            "Block",
                            "Transect_ID",
                            "Sample",
                            "Patch_ID",
                            "Urb_Rur",
                            "Year",
                            "Surveyor",
                          "Date")),
                     as.factor) %>%
  dplyr::mutate(Fam_uniq = paste0(Population, "_", Family))

# Take mean of two sampling events
herbivores %<>%
  dplyr::group_by(Population, Row, Column, Block, Family, Replicate, Year) %>%
  dplyr::summarise(Monarch_Quantity_Observed = mean(Monarch_Quantity_Observed, na.rm = T),
                   Liriomyza_asclepiadis = mean(Liriomyza_asclepiadis, na.rm = T),
                   Labidomera_clivicollis = mean(Labidomera_clivicollis, na.rm = T),
                   Transect_ID = first(Transect_ID),
                   City_dist = first(City_dist),
                   Urb_Rur = first(Urb_Rur),
                   Urb_score = first(Urb_score),
                   Fam_uniq = first(Fam_uniq))
```

## Import final models
```{r}
source(knitr::purl("scripts/Model_diagnostics/Model_diagnostics_herbivores.Rmd", quiet=TRUE))

all_models <- list(
monarch_mods          , 
asclepiadis_mods           , 
clivicollis_mods)

names(all_models) <- c(
"monarch_mods"          ,
"asclepiadis_mods"           ,
"clivicollis_mods"         )
```

# Ranova
## Set seed
```{r}
set.seed(45)
```

## Gradient / City_dist
### non-Gaussian models
#### Monarchs
```{r}
# 2020-----
monarch_ranova1 <- glmer.nb(Monarch_Quantity_Observed ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivores %>%
                              dplyr::filter(Year == 2020),
                            na.action = na.exclude)

# performance::check_model(monarch_ranova1)

pb_ranova_2step(monarch_ranova1,
          "Monarch butterfly: 2020",
          "./Figures_Tables/ranova_PVE/Defense/Monarch_2020.docx")

# 2021-----
monarch_ranova2 <- glmer.nb(Monarch_Quantity_Observed ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivores %>%
                              dplyr::filter(Year == 2021),
                            na.action = na.exclude)

# performance::check_model(monarch_ranova2)

pb_ranova_2step(monarch_ranova2,
          "Monarch butterfly: 2021",
          "./Figures_Tables/ranova_PVE/Defense/Monarch_2021.docx")
```

#### L. asclepiadis
```{r}
# 2020-----
asclepiadis_ranova1 <- glmer.nb(Liriomyza_asclepiadis ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivores %>%
                              dplyr::filter(Year == 2020),
                            na.action = na.exclude)

# performance::check_model(asclepiadis_ranova1)

pb_ranova_2step(asclepiadis_ranova1,
          "Liriomyza asclepiadis: 2020",
          "./Figures_Tables/ranova_PVE/Defense/asclepiadis_2020.docx")


# 2021-----
asclepiadis_ranova2 <- glmer.nb(Liriomyza_asclepiadis ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivores %>%
                              dplyr::filter(Year == 2021),
                            na.action = na.exclude)

# performance::check_model(asclepiadis_ranova2)

pb_ranova_2step(asclepiadis_ranova2,
          "Liriomyza asclepiadis: 2021",
          "./Figures_Tables/ranova_PVE/Defense/asclepiadis_2021.docx")
```

#### L. clivicollis
```{r}
# 2020-----
clivicoll_ranova1 <- glmer.nb(Labidomera_clivicollis ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivores %>%
                dplyr::filter(Labidomera_clivicollis < 10 &
                                Year == 2020),
                            na.action = na.exclude)

# performance::check_model(clivicoll_ranova1)

pb_ranova_2step(clivicoll_ranova1,
          "Labidomera clivicollis: 2020",
          "./Figures_Tables/ranova_PVE/Defense/clivicollis_2020.docx")


# 2021-----
clivicoll_ranova2 <- glmer.nb(Labidomera_clivicollis ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivores %>%
                dplyr::filter(Labidomera_clivicollis < 10 & Year == 2021),
                            na.action = na.exclude,
                control=glmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))

# performance::check_model(clivicoll_ranova2)

pb_ranova_2step(clivicoll_ranova2,
          "Labidomera clivicollis: 2021",
          "./Figures_Tables/ranova_PVE/Defense/clivicollis_2021.docx")

```

## Urban Subtransects / City_dist
### non-Gaussian models
#### Monarchs
```{r}
# 2020-----
monarchs_ranova1_pb <- glmer.nb(Monarch_Quantity_Observed ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                               data = herbivores %>%
                dplyr::filter(Transect_ID != "Rural" &
                                Year == 2020),
                            na.action = na.exclude) 

# performance::check_model(monarchs_ranova1_pb)

pb_ranova_transects(monarchs_ranova1_pb,
          "Monarch butterfly: 2020",
          "./Figures_Tables/ranova_PVE/Defense/monarch_2020_transects.docx")


# 2021-----
monarchs_ranova2_pb <- glmer.nb(Monarch_Quantity_Observed ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                               data = herbivores %>%
                dplyr::filter(Transect_ID != "Rural" &
                                Year == 2021),
                            na.action = na.exclude)

# performance::check_model(monarchs_ranova2_pb)

pb_ranova_transects(monarchs_ranova2_pb,
          "Monarch butterfly: 2021",
          "./Figures_Tables/ranova_PVE/Defense/monarch_2021_transects.docx")

```

#### L. asclepiadis
```{r}
# 2020-----
asclepiadis_ranova1_pb <- glmer.nb(Liriomyza_asclepiadis ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                               data = herbivores %>%
                dplyr::filter(Transect_ID != "Rural" &
                                Year == 2020),
                            na.action = na.exclude) 

# performance::check_model(asclepiadis_ranova1_pb)

pb_ranova_transects(asclepiadis_ranova1_pb,
          "Liriomyza asclepiadis: 2020",
          "./Figures_Tables/ranova_PVE/Defense/asclepiadis_2020_transects.docx")


# 2021-----
asclepiadis_ranova2_pb <- glmer.nb(Liriomyza_asclepiadis ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                               data = herbivores %>%
                dplyr::filter(Transect_ID != "Rural" &
                                Year == 2021),
                            na.action = na.exclude)

# performance::check_model(asclepiadis_ranova2_pb)

pb_ranova_transects(asclepiadis_ranova2_pb,
          "Liriomyza asclepiadis: 2021",
          "./Figures_Tables/ranova_PVE/Defense/asclepiadis_2021_transects.docx")

```

#### L. clivicollis
```{r}
# 2020-----
clivicollis_ranova1_pb <- glmer.nb(Labidomera_clivicollis ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                               data = herbivores %>%
                dplyr::filter(Transect_ID != "Rural" &
                                Year == 2020 &
                                Labidomera_clivicollis < 9),
                            na.action = na.exclude)

# performance::check_model(clivicollis_ranova1_pb)

pb_ranova_transects(clivicollis_ranova1_pb,
          "Labidomera clivicollis: 2020",
          "./Figures_Tables/ranova_PVE/Defense/clivicollis_2020_transects.docx")


# 2021-----
clivicollis_ranova2_pb <- glmer.nb(Labidomera_clivicollis ~
                               Block +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                               data = herbivores %>%
                dplyr::filter(Transect_ID != "Rural" &
                                Year == 2021 &
                                Labidomera_clivicollis < 9),
                nAGQ = 0, # won't run without this
                            na.action = na.exclude)

# performance::check_model(clivicollis_ranova2_pb)

pb_ranova_transects(clivicollis_ranova2_pb,
          "Labidomera clivicollis: 2021",
          "./Figures_Tables/ranova_PVE/Defense/clivicollis_2021_transects.docx")

```

## Recalculate PVE for non-Gaussian models
As far as we know, there isn't a solid way to calculate percent variance explained for variables with a non-Gaussian distribution.
The way that we handled this was to refit our non-Gaussian models (generalized linear mixed models) to general linear mixed models, then extract PVE for the last year of data collection.
These new PVEs will be estimates. This is *not* a perfect solution but it will help us approximate PVE for these variables.
### Q1
```{r}
# main models
monarch_lmer <- lmer(Monarch_Quantity_Observed ~
                               (1|Block) +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivores %>%
                               dplyr::filter(Year == 2021),
                            na.action = na.exclude)

lasclep_lmer <- lmer(Liriomyza_asclepiadis ~
                               (1|Block) +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivores %>%
                               dplyr::filter(Year == 2021),
                            na.action = na.exclude)

lclivicoll_lmer <- lmer(Labidomera_clivicollis ~
                               (1|Block) +
                               (1|Population) +
                               (1|Population:Fam_uniq),
                             data = herbivores %>%
                               dplyr::filter(Year == 2021),
                          na.action = na.exclude)

# get PVE from models
pve_mon <- PVE_lm(monarch_lmer) 
pve_lasclep <- PVE_lm(lasclep_lmer)
pve_lclivi <- PVE_lm(lclivicoll_lmer)

pve_mon_city <- PVE_lm(update(monarch_lmer, .~. + City_dist))
pve_lasclep_city <- PVE_lm(update(lasclep_lmer, .~. + City_dist))
pve_lclivi_city <- PVE_lm(update(lclivicoll_lmer, .~. + City_dist))

pve_mon_urbsc <- PVE_lm(update(monarch_lmer, .~. + Urb_score))
pve_lasclep_urbsc <- PVE_lm(update(lasclep_lmer, .~. + Urb_score))
pve_lclivi_urbsc <- PVE_lm(update(lclivicoll_lmer, .~. + Urb_score))


# make tables
recalc_tab1 <- pve_table_recalc(pve_mon, pve_lasclep, pve_lclivi,
                 "Danaus plexippus",
                 "Liriomyza asclepiadis",
                 "Labidomera clivicollis")

recalc_tab2 <- pve_table_recalc(pve_mon_city, pve_lasclep_city, pve_lclivi_city,
                 "Danaus plexippus",
                 "Liriomyza asclepiadis",
                 "Labidomera clivicollis")

recalc_tab3 <- pve_table_recalc(pve_mon_urbsc, pve_lasclep_urbsc, pve_lclivi_urbsc,
                 "Danaus plexippus",
                 "Liriomyza asclepiadis",
                 "Labidomera clivicollis")

# Export to word
export_recalc(recalc_tab1,
              recalc_tab2,
              recalc_tab3,
              "./Figures_Tables/ranova_PVE/Defense/PVE_nonGaussmods/PVE_nonGaussmods_herbivores_Q1.docx")

```

### Q2
```{r}
# main models
monarch_lmer2 <- update(monarch_lmer,
                             data = herbivores %>%
                               dplyr::filter(Year == 2021 &
                                            Transect_ID != "Rural"))

lasclep_lmer2 <- update(lasclep_lmer,
                             data = herbivores %>%
                               dplyr::filter(Year == 2021 &
                                            Transect_ID != "Rural"))

lclivicoll_lmer2 <- update(lclivicoll_lmer,
                             data = herbivores %>%
                               dplyr::filter(Year == 2021 &
                                            Transect_ID != "Rural"),
                           control=lmerControl(optimizer="bobyqa",
                            optCtrl=list(maxfun=2e5)))

# get PVE from models
pve_mon2 <- PVE_lm(monarch_lmer2) 
pve_lasclep2 <- PVE_lm(lasclep_lmer2)
pve_lclivi2 <- PVE_lm(lclivicoll_lmer2)

pve_mon_city2 <- PVE_lm(update(monarch_lmer2, .~. + City_dist*Transect_ID))
pve_lasclep_city2 <- PVE_lm(update(lasclep_lmer2, .~. + City_dist*Transect_ID))
pve_lclivi_city2 <- PVE_lm(update(lclivicoll_lmer2, .~. + City_dist*Transect_ID))

pve_mon_urbsc2 <- PVE_lm(update(monarch_lmer2, .~. + Urb_score*Transect_ID))
pve_lasclep_urbsc2 <- PVE_lm(update(lasclep_lmer2, .~. + Urb_score*Transect_ID))
pve_lclivi_urbsc2 <- PVE_lm(update(lclivicoll_lmer2, .~. + Urb_score*Transect_ID))


# make tables
recalc_tab1 <- pve_table_recalc(pve_mon2, pve_lasclep2, pve_lclivi2,
                 "Danaus plexippus",
                 "Liriomyza asclepiadis",
                 "Labidomera clivicollis")

recalc_tab2 <- pve_table_recalc(pve_mon_city2, pve_lasclep_city2, pve_lclivi_city2,
                 "Danaus plexippus",
                 "Liriomyza asclepiadis",
                 "Labidomera clivicollis")

recalc_tab3 <- pve_table_recalc(pve_mon_urbsc2, pve_lasclep_urbsc2, pve_lclivi_urbsc2,
                 "Danaus plexippus",
                 "Liriomyza asclepiadis",
                 "Labidomera clivicollis")

# Export to word
export_recalc(recalc_tab1,
              recalc_tab2,
              recalc_tab3,
              "./Figures_Tables/ranova_PVE/Defense/PVE_nonGaussmods/PVE_nonGaussmods_herbivores_Q2.docx")

```
