# Load libraries
```{r}
source("libraries.R")
```

# Import data
## Reproductive traits
```{r}
source(knitr::purl("Reproductive_trait_analyses/Model_diagnostics_Reproduc.Rmd", quiet=TRUE))

# Best Models (first is Q1, second is Q2)
## City_dist
best_repro_mods <- list(
flsucc_mods_best_c    ,   # flowering success
flowers_mods_best_c    ,   # total flowers
flsize_mods_best_c      , # mean flower size
fltime_mods_best_c    ,   # flowering time
flstart_mods_best_c    ,   # flowering start
pods_mods_best_c      , # pods (follicles)
peduncles_mods_best_c        # peduncles (inflors)
)

```

## Defense traits
```{r}
source(knitr::purl("Defense_trait_analyses/Model_diagnostics_Defense.Rmd", quiet=TRUE))

# Best Models (first is Q1, second is Q2)
## City_dist
best_defense_mods <- list(
latex_mods_best_c, # latex
herb_e_bin_mods_best_c, # herbivory early (0/1)
herb_e_quant_mods_best_c, # herbivory early (quantitative)
herb_l_bin_mods_best_c, # herbivory late (0/1)
herb_l_quant_mods_best_c, # herbivory late (quantiative)
weev_bin_mods_best_c, # weevil damage (0/1)
weev_quant_mods_best_c # weevil damage (quantitative)
)
```

## Growth traits
```{r}
source(knitr::purl("Growth_trait_analyses/Model_diagnostics_Growth.Rmd", quiet=TRUE))
# I don't know why but this Rmd usually doesn't fully run with this line of code, so instead, just open the Rmd and run it all manually

# Best Models (first is Q1, second is Q2)
## City_dist
best_growth_mods <- list(
ldmc_mods_best_c,
sla_mods_best_c,
heights_early_mods_best_c,
heights_late_mods_best_c,
rgr_mods_best_c,
ramets_early_mods_best_c,
ramets_late_mods_best_c,
mortality_mods_best_c
)

```

## Cardenolides (part of defense, technically)
```{r}
# ONLY FOR Q1
source(knitr::purl("Defense_trait_analyses/Analysis_cardenolides.Rmd", quiet=TRUE))

# Best Models' p-values
## City_dist
card1 <- city_dist_list[["X6.6_main"]][[2]][["Pr(>F)"]][1] %>% as.character()

card2 <- city_dist_list[["X15_main"]][[2]][["Pr(>F)"]][1] %>% as.character()

card3 <- city_dist_list[["X17.6_main"]][[2]][["Pr(>F)"]][1] %>% as.character()

card4 <- city_dist_list[["total"]][[2]][["Pr(>F)"]][1] %>% as.character()

card_df <- data_frame(
  variable = c("cardenolide_6.6", "cardenolide_15", "cardenolide_17.6", "cardenolide_Total"),
  p = c(card1, card2, card3, card4))

```

# Extract p values where predictor = city_dist, then put into df
```{r}
# merge lists
all_best_mods <- do.call(c, list(best_growth_mods,
                                 best_defense_mods,
                                 best_repro_mods))


# Question 1-----
extract_p_Q1 <- function(best_mod_list){
 response_var <- tidy_anova(best_mod_list[[1]]) %>%
    dplyr::filter(Predictor == "Distance to City Center") %>%
    dplyr::select(Response) %>%
  as.character()
    
  pval <- tidy_anova(best_mod_list[[1]]) %>%
    dplyr::filter(Predictor == "Distance to City Center") %>%
    dplyr::select(p) %>%
  as.character()
  
  output_vector <- as.vector(c(response_var, pval))
  
  return(output_vector)
  
}

all_pvalues_Q1 <- sapply(all_best_mods,
                         extract_p_Q1) %>%
  t() %>%
  as.data.frame() %>%
  dplyr::rename("variable" = 1,
                "p" = 2) %>%
  # add in cardenolide p values
  full_join(card_df, by = c("variable", "p")) %>%
  # order df by p-value
  dplyr::arrange(-desc(p)) %>%
# remove asterisk from a p-value
  dplyr::mutate(p = str_replace(
    p,
    "\\*",
    "")) %>%
  dplyr::mutate(p = as.numeric(p))


# Question 2-----
extract_p_Q2 <- function(best_mod_list){
 response_var <- tidy_anova(best_mod_list[[2]]) %>%
    dplyr::filter(Predictor != "Distance to City Center" &
                  Predictor != "Year" &
                  Predictor != "Block") %>%
    dplyr::select(Response) %>%
  as.character()
    
  pval <- tidy_anova(best_mod_list[[2]]) %>%
    dplyr::filter(Predictor != "Distance to City Center" &
                  Predictor != "Year" &
                  Predictor != "Block") %>%
    dplyr::select(p) %>%
  as.character()
  
  output_vector <- as.vector(c(response_var, pval))
  
  return(output_vector)
  
}

all_pvalues_Q2 <- sapply(all_best_mods,
                         extract_p_Q2) %>%
  t() %>%
  as.data.frame() %>%
  dplyr::rename("variable" = 1,
                "p" = 2) %>%
  # order df by p-value
  dplyr::arrange(-desc(p))

# 3 models had interactions btwn subtransect & dist or year, so I'll manually add those p-values

# this p-value is for dist x subtr interaxn though dist and subtr are also marg sig (0.065 and 0.064, respectively)
# tidy_anova(all_best_mods[[10]][[2]])
all_pvalues_Q2[20,1] = "Herbivory_mean_early_binary"
all_pvalues_Q2[20,2] = "0.068"


# this p-value is for dist x subtr interaxn
# tidy_anova(all_best_mods[[11]][[2]])
all_pvalues_Q2[22,1] = "log(Herbivory_mean_early)"
all_pvalues_Q2[22,2] = "0.145"

# this p-value is for dist x subtr interaxn
# tidy_anova(all_best_mods[[18]][[2]])
all_pvalues_Q2[21,1] = "Overall_mean"
all_pvalues_Q2[21,2] = "0.141"

# order df by p-value again
all_pvalues_Q2 %<>% 
  dplyr::arrange(-desc(p)) %>%
# remove asterisk from a p-value
  dplyr::mutate(p = str_replace(
    p,
    "\\*",
    "")) %>%
  dplyr::mutate(p = as.numeric(p))
```
  
# Control the false discovery rate with Benjamini–Hochberg procedure
The methods Holm, Hochberg, Hommel, and Bonferroni control the family-wise error rate.  These methods attempt to limit the probability of even one false discovery (a type I error, incorrectly rejecting the null hypothesis when there is no real effect), and so are all relatively strong (conservative).

The methods BH (Benjamini–Hochberg, which is the same as FDR in R) and BY control the false discovery rate.  These methods attempt to control the expected proportion of false discoveries.

(From this site: https://rcompanion.org/rcompanion/f_01.html)

## Q1
```{r}
all_pvalues_Q1 %<>%

# Perform p-value adjustment and add to df-----

# Adjustment procedures that give strong control of the family-wise error rate are the Bonferroni, Holm, Hochberg, and Hommel procedures.

# Adjustments that control for the false discovery rate, which is the expected proportion of false discoveries among the rejected hypotheses, are the Benjamini and Hochberg, and Benjamini, Hochberg, and Yekutieli procedures.
  dplyr::mutate(
    Bonferroni = p.adjust(
      p,
      method = "bonferroni"), # usually too conservative
    BH = p.adjust(
      p,
      method = "BH"), # Benjamini-Hochberg procedure- what I want (tests for FDR)
    Holm = p.adjust(
      p,
      method = "holm"),
    Hochberg = p.adjust(
      p,
      method = "hochberg"),
    Hommel = p.adjust(
      p,
      method = "hommel"),
    BY = p.adjust(
      p,
<<<<<<< HEAD
      method = "BY")  # stands for Benjamini, Hochberg, and Yekutieli procedure- what I want (tests for FDR)
=======
      method = "BY")  # stands for Benjamini, Hochber, and Yekutieli procedure- what I want (tests for FDR)
>>>>>>> efb1855698431e1692f306a79d57be2ffdd9fede
    )

# All the tests suggest I can't reject any null hypothesis!
```


## Q2
```{r}
all_pvalues_Q2 %<>%
# Perform p-value adjustment and add to df-----

# Adjustment procedures that give strong control of the family-wise error rate are the Bonferroni, Holm, Hochberg, and Hommel procedures.

# Adjustments that control for the false discovery rate, which is the expected proportion of false discoveries among the rejected hypotheses, are the Benjamini and Hochberg, and Benjamini, Hochberg, and Yekutieli procedures.
  dplyr::mutate(
    Bonferroni = p.adjust(
      p,
      method = "bonferroni"), # usually too conservative
    BH = p.adjust(
      p,
      method = "BH"), # Benjamini-Hochberg procedure- what I want (tests for FDR)
    Holm = p.adjust(
      p,
      method = "holm"),
    Hochberg = p.adjust(
      p,
      method = "hochberg"),
    Hommel = p.adjust(
      p,
      method = "hommel"),
    BY = p.adjust(
      p,
<<<<<<< HEAD
      method = "BY")  # stands for Benjamini, Hochberg, and Yekutieli procedure- what I want (tests for FDR)
=======
      method = "BY")  # stands for Benjamini, Hochber, and Yekutieli procedure- what I want (tests for FDR)
>>>>>>> efb1855698431e1692f306a79d57be2ffdd9fede
    )

# All the tests suggest I can't reject any null hypothesis!
```
