# Load libraries
```{r}
source("libraries.R")
```

# Import data
## Reproductive traits
```{r}
source(knitr::purl("Reproductive_trait_analyses/Model_diagnostics_Reproduc.Rmd", quiet=TRUE))

```

## Defense traits (including cardenolides)
```{r}
source(knitr::purl("Defense_trait_analyses/Model_diagnostics_Defense.Rmd", quiet=TRUE))

```

## Growth traits
```{r}
source(knitr::purl("Growth_trait_analyses/Model_diagnostics_Growth.Rmd", quiet=TRUE))
# I don't know why but this Rmd usually doesn't fully run with this line of code, so instead, just open the Rmd and run it all manually
```

# Make function that makes multi-year model --> one-year model
```{r}
# Q1
make_1yrmod <- function(orig_mod, last_year, mod_allyrs_df){
  return(
    update(orig_mod,
                    .~. - Year,
                    data = mod_allyrs_df %>%
                      dplyr::filter(Year == last_year))
  )
}

# Q2
make_1yrmod_transects <- function(orig_mod, last_year, mod_allyrs_df){
  return(
    update(orig_mod,
                    .~. - Year,
                    data = mod_allyrs_df %>%
                      dplyr::filter(Year == last_year &
                                      Transect_ID != "Rural"))
  )
}
```


# Create tables with ANOVA results from all one-year models (lmers)
## Q1
### City_dist
#### Make lists of models
##### Defense
```{r}
latex_mods_best_c[[1]]

def.m1 <- make_1yrmod(herb_e_bin_mods_best_c[[1]], "2021", herbivory)

def.m2 <- update(herb_e_quant_mods_best_c[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

def.m3 <- make_1yrmod(herb_l_bin_mods_best_c[[1]], "2021", herbivory)

def.m4 <- update(herb_l_quant_mods_best_c[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

def.m5 <- make_1yrmod(weev_bin_mods_best_c[[1]], "2021", weevil)

def.m6 <- update(weev_quant_mods_best_c[[1]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Year == "2021" &
                                   Scar_length_cm > 0))
```

##### Reproduction
```{r}
repr.m1 <- make_1yrmod(flsucc_mods_best_c[[1]], "2022", reproduc)

repr.m2 <- make_1yrmod(flowers_mods_best_c[[1]], "2022", flowering)

repr.m3 <- make_1yrmod(flsize_mods_best_c[[1]], "2022", flowering)

repr.m4 <- make_1yrmod(fltime_mods_best_c[[1]], "2022", flowering)

repr.m5 <- make_1yrmod(flstart_mods_best_c[[1]], "2022", flowering)

repr.m6 <- make_1yrmod(pods_mods_best_c[[1]], "2022", flowering)

repr.m7 <- make_1yrmod(first_pods_mods_best_c[[1]], "2022", flowering)

repr.m8 <- make_1yrmod(peduncles_mods_best_c[[1]], "2022", flowering)
```

##### Herbivores
```{r}
herb.m1 <- make_1yrmod(monarch_mods_best_c[[1]], "2021", herbivores)

herb.m2 <- make_1yrmod(asclepiadis_mods_best_c[[1]], "2021", herbivores)

herb.m3 <- make_1yrmod(clivicollis_mods_best_c[[1]], "2021", herbivores)
```

##### Growth
```{r}
grow.m1 <- ldmc_mods_best_c[[1]]

grow.m2 <- sla_mods_best_c[[1]]

grow.m3 <- make_1yrmod(heights_early_mods_best_c[[1]], "2021", heights)

grow.m4 <- make_1yrmod(heights_late_mods_best_c[[1]], "2021", heights)

grow.m5 <- make_1yrmod(rgr_mods_best_c[[1]], "2021", heights)

grow.m6 <- make_1yrmod(ramets_early_mods_best_c[[1]], "2021", heights)

grow.m7 <- make_1yrmod(ramets_late_mods_best_c[[1]], "2021", heights)

grow.m8 <- make_1yrmod(mortality_mods_best_c[[1]], "2022", survival)
```

##### All
```{r}
all_1yr_mods <- list(
  
  # defense
  latex_mods_best_c[[1]],
  def.m1,
  def.m2,
  def.m3,
  def.m4,
  def.m5,
  def.m6,
  
  # reproduction
  repr.m1,
  repr.m2,
  repr.m3,
  repr.m4,
  repr.m5,
  repr.m6,
  repr.m7,
  repr.m8,
  
  # Herbivores
  herb.m1,
  herb.m2,
  herb.m3,
  
  # growth
  grow.m1,
  grow.m2,
  grow.m3,
  grow.m4,
  grow.m5,
  grow.m6,
  grow.m7,
  grow.m8
  )
```

#### Create 1-yr ANOVA table
```{r}
# STEP 3: perform tidy_anova on all list items (i.e., models)
all_1yr_mods %>% 
  lapply(., tidy_anova) %>%

# STEP 4: merge all items
  reduce(full_join, all = T) %>%

# STEP 5: make flextable
  dplyr::rename(Variable = 1) %>%
  dplyr::select(-Sites) %>%
  dplyr::mutate(Variable = case_when(
    
    # Defense
    str_detect(Variable, "Latex")~
      "Latex exudation",
    str_detect(Variable, "Herbivory_mean_early_binary") ~
      "Herbivory before flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_early)") ~
                 "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Herbivory_mean_late_binary")~
      "Herbivory after flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_late)")~
      "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Scar_binary")~
      "Weevil damage (binary)",
    str_detect(Variable, "Scar_length_cm")~
      "Weevil damage (quantitative)",
    
    # Reproduction
    str_detect(Variable, "Flowered")~
      "Flowering success",
    str_detect(Variable, "mean_flower_c")~
      "Flowers per Inflorescence",
    str_detect(Variable, "Overall")~
      "Flower size",
    str_detect(Variable, "flowering_time")~
      "Flowering duration",
    str_detect(Variable, "Julian_oldest_inflor")~
      "Date of first flower",
    str_detect(Variable, "Pods")~
      "Follicles",
    str_detect(Variable, "Julian_first")~
      "Date of first follicle",
    str_detect(Variable, "Peduncles")~
      "Inflorescences",
    
    # Herbivores
    str_detect(Variable, "Monarch")~
      "Danaus plexippus abundance",
    str_detect(Variable, "asclep")~
      "Liriomyza asclepiadis abundance",
    str_detect(Variable, "clivi")~
      "Labidomera clivicollis abundance",
    
    # Growth
    str_detect(Variable, "LDMC")~
      "LDMC",
    str_detect(Variable, "SLA")~
      "SLA",
    str_detect(Variable, "Total_Height_early")~
      "Height before flowering",
    str_detect(Variable, "Total_Height_late")~
      "Height after flowering",
    str_detect(Variable, "rel_gr")~
      "Relative growth rate",
    str_detect(Variable, "Ramets_early")~
      "Ramets before flowering",
    str_detect(Variable, "Ramets_late")~
      "Ramets after flowering",
    str_detect(Variable, "Dead")~
      "Mortality"
    
    
    )) %>%
  flextable() %>%
  theme_box() %>%
  merge_v(j = ~Variable) %>% 
  align(j = 3:4, align = "center", part = "all") %>%
  hline(j = ~Variable, border = NULL, part = "body") %>%
  flextable::compose(i = 1, j = 3, part = "header",
                     value = as_paragraph("χ", as_sup("2"))) %>%
  bold(i = ~ p <= 0.05, j = 4) %>%
  padding(padding = 3) %>%
  autofit() %T>%
  
# STEP 6: Export
  flextable::save_as_docx(.,
                          path = here::here("./Figures_Tables/ANOVA_1yr/ANOVA_1yr_Citydist.docx"))
```

### Urb_score
#### Make lists of models
##### Defense
```{r}
latex_mods_best_u[[1]]

def.m1_u <- make_1yrmod(herb_e_bin_mods_best_u[[1]], "2021", herbivory)

def.m2_u <- update(herb_e_quant_mods_best_u[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

def.m3_u <- make_1yrmod(herb_l_bin_mods_best_u[[1]], "2021", herbivory)

def.m4_u <- update(herb_l_quant_mods_best_u[[1]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

def.m5_u <- make_1yrmod(weev_bin_mods_best_u[[1]], "2021", weevil)

def.m6_u <- update(weev_quant_mods_best_u[[1]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Year == "2021" &
                                   Scar_length_cm > 0))
```

##### Reproduction
```{r}
repr.m1_u <- make_1yrmod(flsucc_mods_best_u[[1]], "2022", reproduc)

repr.m2_u <- make_1yrmod(flowers_mods_best_u[[1]], "2022", flowering)

repr.m3_u <- make_1yrmod(flsize_mods_best_u[[1]], "2022", flowering)

repr.m4_u <- make_1yrmod(fltime_mods_best_u[[1]], "2022", flowering)

repr.m5_u <- make_1yrmod(flstart_mods_best_u[[1]], "2022", flowering)

repr.m6_u <- make_1yrmod(pods_mods_best_u[[1]], "2022", flowering)

repr.m7_u <- make_1yrmod(first_pods_mods_best_u[[1]], "2022", flowering)

repr.m8_u <- make_1yrmod(peduncles_mods_best_u[[1]], "2022", flowering)
```

##### Herbivores
```{r}
herb.m1_u <- make_1yrmod(monarch_mods_best_u[[1]], "2021", herbivores)

herb.m2_u <- make_1yrmod(asclepiadis_mods_best_u[[1]], "2021", herbivores)

herb.m3_u <- make_1yrmod(clivicollis_mods_best_u[[1]], "2021", herbivores)
```

##### Growth
```{r}
grow.m1_u <- ldmc_mods_best_u[[1]]

grow.m2_u <- sla_mods_best_u[[1]]

grow.m3_u <- make_1yrmod(heights_early_mods_best_u[[1]], "2021", heights)

grow.m4_u <- make_1yrmod(heights_late_mods_best_u[[1]], "2021", heights)

grow.m5_u <- make_1yrmod(rgr_mods_best_u[[1]], "2021", heights)

grow.m6_u <- make_1yrmod(ramets_early_mods_best_u[[1]], "2021", heights)

grow.m7_u <- make_1yrmod(ramets_late_mods_best_u[[1]], "2021", heights)

grow.m8_u <- make_1yrmod(mortality_mods_best_u[[1]], "2022", survival)
```

##### All
```{r}
all_1yr_mods.u <- list(
  
  # defense
  latex_mods_best_u[[1]],
  def.m1_u,
  def.m2_u,
  def.m3_u,
  def.m4_u,
  def.m5_u,
  def.m6_u,
  
  # reproduction
  repr.m1_u,
  repr.m2_u,
  repr.m3_u,
  repr.m4_u,
  repr.m5_u,
  repr.m6_u,
  repr.m7_u,
  repr.m8_u,
  
  # Herbivores
  herb.m1_u,
  herb.m2_u,
  herb.m3_u,
  
  # growth
  grow.m1_u,
  grow.m2_u,
  grow.m3_u,
  grow.m4_u,
  grow.m5_u,
  grow.m6_u,
  grow.m7_u,
  grow.m8_u
  )
```

#### Create 1-yr ANOVA table
```{r}
# STEP 3: perform tidy_anova on all list items (i.e., models)
all_1yr_mods.u %>% 
  lapply(., tidy_anova) %>%

# STEP 4: merge all items
  reduce(full_join, all = T) %>%

# STEP 5: make flextable
  dplyr::rename(Variable = 1) %>%
  dplyr::select(-Sites) %>%
  dplyr::mutate(Variable = case_when(
    
    # Defense
    str_detect(Variable, "Latex")~
      "Latex exudation",
    str_detect(Variable, "Herbivory_mean_early_binary") ~
      "Herbivory before flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_early)") ~
                 "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Herbivory_mean_late_binary")~
      "Herbivory after flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_late)")~
      "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Scar_binary")~
      "Weevil damage (binary)",
    str_detect(Variable, "Scar_length_cm")~
      "Weevil damage (quantitative)",
    
    # Reproduction
    str_detect(Variable, "Flowered")~
      "Flowering success",
    str_detect(Variable, "mean_flower_c")~
      "Flowers per Inflorescence",
    str_detect(Variable, "Overall")~
      "Flower size",
    str_detect(Variable, "flowering_time")~
      "Flowering duration",
    str_detect(Variable, "Julian_oldest_inflor")~
      "Date of first flower",
    str_detect(Variable, "Pods")~
      "Follicles",
    str_detect(Variable, "Julian_first")~
      "Date of first follicle",
    str_detect(Variable, "Peduncles")~
      "Inflorescences",
    
    # Herbivores
    str_detect(Variable, "Monarch")~
      "Danaus plexippus abundance",
    str_detect(Variable, "asclep")~
      "Liriomyza asclepiadis abundance",
    str_detect(Variable, "clivi")~
      "Labidomera clivicollis abundance",
    
    # Growth
    str_detect(Variable, "LDMC")~
      "LDMC",
    str_detect(Variable, "SLA")~
      "SLA",
    str_detect(Variable, "Total_Height_early")~
      "Height before flowering",
    str_detect(Variable, "Total_Height_late")~
      "Height after flowering",
    str_detect(Variable, "rel_gr")~
      "Relative growth rate",
    str_detect(Variable, "Ramets_early")~
      "Ramets before flowering",
    str_detect(Variable, "Ramets_late")~
      "Ramets after flowering",
    str_detect(Variable, "Dead")~
      "Mortality"
    
    
    )) %>%
  flextable() %>%
  theme_box() %>%
  merge_v(j = ~Variable) %>% 
  align(j = 3:4, align = "center", part = "all") %>%
  hline(j = ~Variable, border = NULL, part = "body") %>%
  flextable::compose(i = 1, j = 3, part = "header",
                     value = as_paragraph("χ", as_sup("2"))) %>%
  bold(i = ~ p <= 0.05, j = 4) %>%
  padding(padding = 3) %>%
  autofit() %T>%
  
# STEP 6: Export
  flextable::save_as_docx(.,
                          path = here::here("./Figures_Tables/ANOVA_1yr/ANOVA_1yr_Urbscore.docx"))
```

## Q2
### City_dist
#### Make lists of models
##### Defense
```{r}
latex_mods_best_c[[2]]

def.tr.m1 <- make_1yrmod_transects(herb_e_bin_mods_best_c[[2]], "2021", herbivory)

def.tr.m2 <- update(herb_e_quant_mods_best_c[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

def.tr.m3 <- make_1yrmod_transects(herb_l_bin_mods_best_c[[2]], "2021", herbivory)

def.tr.m4 <- update(herb_l_quant_mods_best_c[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

def.tr.m5 <- make_1yrmod_transects(weev_bin_mods_best_c[[2]], "2021", weevil)

def.tr.m6 <- update(weev_quant_mods_best_c[[2]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Scar_length_cm > 0))
```

##### Reproduction
```{r}
repr.tr.m1 <- make_1yrmod_transects(flsucc_mods_best_c[[2]], "2022", reproduc)

repr.tr.m2 <- make_1yrmod_transects(flowers_mods_best_c[[2]], "2022", flowering)

repr.tr.m3 <- make_1yrmod_transects(flsize_mods_best_c[[2]], "2022", flowering)

repr.tr.m4 <- make_1yrmod_transects(fltime_mods_best_c[[2]], "2022", flowering)

repr.tr.m5 <- make_1yrmod_transects(flstart_mods_best_c[[2]], "2022", flowering)

repr.tr.m6 <- make_1yrmod_transects(pods_mods_best_c[[2]], "2022", flowering)

repr.tr.m7 <- make_1yrmod_transects(first_pods_mods_best_c[[2]], "2022", flowering)

repr.tr.m8 <- make_1yrmod_transects(peduncles_mods_best_c[[2]], "2022", flowering)
```

##### Herbivores
```{r}
herb.tr.m1 <- make_1yrmod_transects(monarch_mods_best_c[[2]], "2021", herbivores)

herb.tr.m2 <- make_1yrmod_transects(asclepiadis_mods_best_c[[2]], "2021", herbivores)

herb.tr.m3 <- make_1yrmod_transects(clivicollis_mods_best_c[[2]], "2021", herbivores)
```

##### Growth
```{r}
grow.tr.m1 <- ldmc_mods_best_c[[2]]

grow.tr.m2 <- sla_mods_best_c[[2]]

grow.tr.m3 <- make_1yrmod_transects(heights_early_mods_best_c[[2]], "2021", heights)

grow.tr.m4 <- make_1yrmod_transects(heights_late_mods_best_c[[2]], "2021", heights)

grow.tr.m5 <- make_1yrmod_transects(rgr_mods_best_c[[2]], "2021", heights)

grow.tr.m6 <- make_1yrmod_transects(ramets_early_mods_best_c[[2]], "2021", heights)

grow.tr.m7 <- make_1yrmod_transects(ramets_late_mods_best_c[[2]], "2021", heights)

grow.tr.m8 <- make_1yrmod_transects(mortality_mods_best_c[[2]], "2022", survival)
```

##### All
```{r}
all_1yr_mods_tr <- list(
  
  # defense
  latex_mods_best_c[[2]],
  def.tr.m1,
  def.tr.m2,
  def.tr.m3,
  def.tr.m4,
  def.tr.m5,
  def.tr.m6,
  
  # reproduction
  repr.tr.m1,
  repr.tr.m2,
  repr.tr.m3,
  repr.tr.m4,
  repr.tr.m5,
  repr.tr.m6,
  repr.tr.m7,
  repr.tr.m8,
  
  # Herbivores
  herb.tr.m1,
  herb.tr.m2,
  herb.tr.m3,
  
  # growth
  grow.tr.m1,
  grow.tr.m2,
  grow.tr.m3,
  grow.tr.m4,
  grow.tr.m5,
  grow.tr.m6,
  grow.tr.m7,
  grow.tr.m8
  )
```

#### Create 1-yr ANOVA table
```{r}
# STEP 3: perform tidy_anova on all list items (i.e., models)
all_1yr_mods_tr %>% 
  lapply(., tidy_anova) %>%

# STEP 4: merge all items
  reduce(full_join, all = T) %>%

# STEP 5: make flextable
  dplyr::rename(Variable = 1) %>%
  dplyr::select(-Sites) %>% 
  dplyr::mutate(Variable = case_when(
    
    # Defense
    str_detect(Variable, "Latex")~
      "Latex exudation",
    str_detect(Variable, "Herbivory_mean_early_binary") ~
      "Herbivory before flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_early)") ~
                 "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Herbivory_mean_late_binary")~
      "Herbivory after flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_late)")~
      "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Scar_binary")~
      "Weevil damage (binary)",
    str_detect(Variable, "Scar_length_cm")~
      "Weevil damage (quantitative)",
    
    # Reproduction
    str_detect(Variable, "Flowered")~
      "Flowering success",
    str_detect(Variable, "mean_flower_c")~
      "Flowers per Inflorescence",
    str_detect(Variable, "Overall")~
      "Flower size",
    str_detect(Variable, "flowering_time")~
      "Flowering duration",
    str_detect(Variable, "Julian_oldest_inflor")~
      "Date of first flower",
    str_detect(Variable, "Pods")~
      "Follicles",
    str_detect(Variable, "Julian_first")~
      "Date of first follicle",
    str_detect(Variable, "Peduncles")~
      "Inflorescences",
    
    # Herbivores
    str_detect(Variable, "Monarch")~
      "Danaus plexippus abundance",
    str_detect(Variable, "asclep")~
      "Liriomyza asclepiadis abundance",
    str_detect(Variable, "clivi")~
      "Labidomera clivicollis abundance",
    
    # Growth
    str_detect(Variable, "LDMC")~
      "LDMC",
    str_detect(Variable, "SLA")~
      "SLA",
    str_detect(Variable, "Total_Height_early")~
      "Height before flowering",
    str_detect(Variable, "Total_Height_late")~
      "Height after flowering",
    str_detect(Variable, "rel_gr")~
      "Relative growth rate",
    str_detect(Variable, "Ramets_early")~
      "Ramets before flowering",
    str_detect(Variable, "Ramets_late")~
      "Ramets after flowering",
    str_detect(Variable, "Dead")~
      "Mortality"
    
    
    )) %>%
  flextable() %>%
  theme_box() %>%
  merge_v(j = ~Variable) %>% 
  align(j = 3:4, align = "center", part = "all") %>%
  hline(j = ~Variable, border = NULL, part = "body") %>%
  flextable::compose(i = 1, j = 3, part = "header",
                     value = as_paragraph("χ", as_sup("2"))) %>%
  bold(i = ~ p <= 0.05, j = 4) %>%
  padding(padding = 3) %>%
  autofit() %T>%
  
# STEP 6: Export
  flextable::save_as_docx(.,
                          path = here::here("./Figures_Tables/ANOVA_1yr/ANOVA_1yr_Citydist_transects.docx"))
```

### Urb_score
#### Make lists of models
##### Defense
```{r}
latex_mods_best_u[[2]]

def.tr.m1_u <- make_1yrmod_transects(herb_e_bin_mods_best_u[[2]], "2021", herbivory)

def.tr.m2_u <- update(herb_e_quant_mods_best_u[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_early_binary == 1))

def.tr.m3_u <- make_1yrmod_transects(herb_l_bin_mods_best_u[[2]], "2021", herbivory)

def.tr.m4_u <- update(herb_l_quant_mods_best_u[[2]],
                 .~. - Year,
                 data = herbivory %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Herbivory_mean_late_binary == 1))

def.tr.m5_u <- make_1yrmod_transects(weev_bin_mods_best_u[[2]], "2021", weevil)

def.tr.m6_u <- update(weev_quant_mods_best_u[[2]],
                 .~. - Year,
                 data = weevil %>%
                   dplyr::filter(Transect_ID != "Rural" &
                                   Year == "2021" &
                                   Scar_length_cm > 0))
```

##### Reproduction
```{r}
repr.tr.m1_u <- make_1yrmod_transects(flsucc_mods_best_u[[2]], "2022", reproduc)

repr.tr.m2_u <- make_1yrmod_transects(flowers_mods_best_u[[2]], "2022", flowering)

repr.tr.m3_u <- make_1yrmod_transects(flsize_mods_best_u[[2]], "2022", flowering)

repr.tr.m4_u <- make_1yrmod_transects(fltime_mods_best_u[[2]], "2022", flowering)

repr.tr.m5_u <- make_1yrmod_transects(flstart_mods_best_u[[2]], "2022", flowering)

repr.tr.m6_u <- make_1yrmod_transects(pods_mods_best_u[[2]], "2022", flowering)

repr.tr.m7_u <- make_1yrmod_transects(first_pods_mods_best_u[[2]], "2022", flowering)

repr.tr.m8_u <- make_1yrmod_transects(peduncles_mods_best_u[[2]], "2022", flowering)
```

##### Herbivores
```{r}
herb.tr.m1_u <- make_1yrmod_transects(monarch_mods_best_u[[2]], "2021", herbivores)

herb.tr.m2_u <- make_1yrmod_transects(asclepiadis_mods_best_u[[2]], "2021", herbivores)

herb.tr.m3_u <- make_1yrmod_transects(clivicollis_mods_best_u[[2]], "2021", herbivores)
```

##### Growth
```{r}
grow.tr.m1_u <- ldmc_mods_best_u[[2]]

grow.tr.m2_u <- sla_mods_best_u[[2]]

grow.tr.m3_u <- make_1yrmod_transects(heights_early_mods_best_u[[2]], "2021", heights)

grow.tr.m4_u <- make_1yrmod_transects(heights_late_mods_best_u[[2]], "2021", heights)

grow.tr.m5_u <- make_1yrmod_transects(rgr_mods_best_u[[2]], "2021", heights)

grow.tr.m6_u <- make_1yrmod_transects(ramets_early_mods_best_u[[2]], "2021", heights)

grow.tr.m7_u <- make_1yrmod_transects(ramets_late_mods_best_u[[2]], "2021", heights)

grow.tr.m8_u <- make_1yrmod_transects(mortality_mods_best_u[[2]], "2022", survival)
```

##### All
```{r}
all_1yr_mods.u_tr <- list(
  
  # defense
  latex_mods_best_u[[2]],
  def.tr.m1_u,
  def.tr.m2_u,
  def.tr.m3_u,
  def.tr.m4_u,
  def.tr.m5_u,
  def.tr.m6_u,
  
  # reproduction
  repr.tr.m1_u,
  repr.tr.m2_u,
  repr.tr.m3_u,
  repr.tr.m4_u,
  repr.tr.m5_u,
  repr.tr.m6_u,
  repr.tr.m7_u,
  repr.tr.m8_u,
  
  # Herbivores
  herb.tr.m1_u,
  herb.tr.m2_u,
  herb.tr.m3_u,
  
  # growth
  grow.tr.m1_u,
  grow.tr.m2_u,
  grow.tr.m3_u,
  grow.tr.m4_u,
  grow.tr.m5_u,
  grow.tr.m6_u,
  grow.tr.m7_u,
  grow.tr.m8_u
  )
```

#### Create 1-yr ANOVA table
```{r}
# STEP 3: perform tidy_anova on all list items (i.e., models)
all_1yr_mods.u_tr %>% 
  lapply(., tidy_anova) %>%

# STEP 4: merge all items
  reduce(full_join, all = T) %>%

# STEP 5: make flextable
  dplyr::rename(Variable = 1) %>%
  dplyr::select(-Sites) %>%
  dplyr::mutate(Variable = case_when(
    
    # Defense
    str_detect(Variable, "Latex")~
      "Latex exudation",
    str_detect(Variable, "Herbivory_mean_early_binary") ~
      "Herbivory before flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_early)") ~
                 "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Herbivory_mean_late_binary")~
      "Herbivory after flowering (binary)",
    str_detect(Variable, "(Herbivory_mean_late)")~
      "Herbivory before flowering (quantitative)",
    str_detect(Variable, "Scar_binary")~
      "Weevil damage (binary)",
    str_detect(Variable, "Scar_length_cm")~
      "Weevil damage (quantitative)",
    
    # Reproduction
    str_detect(Variable, "Flowered")~
      "Flowering success",
    str_detect(Variable, "mean_flower_c")~
      "Flowers per Inflorescence",
    str_detect(Variable, "Overall")~
      "Flower size",
    str_detect(Variable, "flowering_time")~
      "Flowering duration",
    str_detect(Variable, "Julian_oldest_inflor")~
      "Date of first flower",
    str_detect(Variable, "Pods")~
      "Follicles",
    str_detect(Variable, "Julian_first")~
      "Date of first follicle",
    str_detect(Variable, "Peduncles")~
      "Inflorescences",
    
    # Herbivores
    str_detect(Variable, "Monarch")~
      "Danaus plexippus abundance",
    str_detect(Variable, "asclep")~
      "Liriomyza asclepiadis abundance",
    str_detect(Variable, "clivi")~
      "Labidomera clivicollis abundance",
    
    # Growth
    str_detect(Variable, "LDMC")~
      "LDMC",
    str_detect(Variable, "SLA")~
      "SLA",
    str_detect(Variable, "Total_Height_early")~
      "Height before flowering",
    str_detect(Variable, "Total_Height_late")~
      "Height after flowering",
    str_detect(Variable, "rel_gr")~
      "Relative growth rate",
    str_detect(Variable, "Ramets_early")~
      "Ramets before flowering",
    str_detect(Variable, "Ramets_late")~
      "Ramets after flowering",
    str_detect(Variable, "Dead")~
      "Mortality"
    
    
    )) %>%
  flextable() %>%
  theme_box() %>%
  merge_v(j = ~Variable) %>% 
  align(j = 3:4, align = "center", part = "all") %>%
  hline(j = ~Variable, border = NULL, part = "body") %>%
  flextable::compose(i = 1, j = 3, part = "header",
                     value = as_paragraph("χ", as_sup("2"))) %>%
  bold(i = ~ p <= 0.05, j = 4) %>%
  padding(padding = 3) %>%
  autofit() %T>%
  
# STEP 6: Export
  flextable::save_as_docx(.,
                          path = here::here("./Figures_Tables/ANOVA_1yr/ANOVA_1yr_Urbscore_transects.docx"))
```


# Create tables with ANOVA results from cardenolide models (lms)
## Q1, City_dist & Urb_score
### Create 1-yr ANOVA table (only 1 year of data anyway)
Not doing this for Q2 since sample size so small
```{r}

# anova on all list items (i.e., models)
flatten(all_card_models) %>% 
  lapply(., tidy_anova_cards) %>%

# merge all items
  reduce(full_join, all = T) %>%

# make flextable
  flextable() %>%
  theme_box() %>%
  merge_v(j = ~Variable) %>% 
  align(j = 3:6, align = "center", part = "all") %>%
  hline(j = ~Variable, border = NULL, part = "body") %>%
  flextable::compose(i = 1, j = 6, part = "header",
                         value = as_paragraph(as_i("p"))) %>%
  bold(i = ~ p <= 0.05, j = 6) %>%
  padding(padding = 3) %>%
  autofit() %T>%
  
# STEP 6: Export
  flextable::save_as_docx(.,
                          path = here::here("./Figures_Tables/ANOVA_1yr/ANOVA_1yr_cardenolides.docx"))
```
